### 2017-11-07 paper/figures/ferrario_illustrated.tex
frest start

\begin{tikzpicture}

  \draw[dashed, thick, color=orange] (1.2,2.0) edge[->] (9.2,2);
  \node[orange, right, text width=3.2cm] at (7.2, 1.7) {Particle trajectory};

  %\draw[thick] (1.2,2.5) edge (9,2.5);
  %\draw[thick] (1.2,1.5) edge (9,1.5);
  %\node[above] at (1.0, 1.45) {Beam pipe};

  \draw[thick,color=red, fill=red, fill opacity=0.1, rounded corners=2mm] (5.0,1.2)
      rectangle (5.4,2.8);
  \draw[thick, dashed] (5.0,1.0) edge (5.0,3.4) node[below] {$3.0$m};
  \draw[thick,color=red, fill=red, fill opacity=0.1, rounded corners=2mm] (5.4,1.2)
      rectangle (5.8,2.8);
  \draw[thick,color=red, fill=red, fill opacity=0.1, rounded corners=2mm] (5.8,1.2)
      rectangle (6.2,2.8);
  \draw[thick,color=red, fill=red, fill opacity=0.1, rounded corners=2mm] (6.2,1.2)
      rectangle (6.6,2.8);
  \node[right, red, text width=2.8cm] at (7.0, 3.5) {Traveling Wave Structure};
  \draw[dashed, thick, color=red, bend right] (7.0,3.5) edge[->] (6.4,2.55);

  \draw[thick, cyan] plot [smooth, tension=0.5] coordinates {
      (1.2,0.5)
      (2.5,1.8)
      (5.0,0.4)
      (8.8,1.2)};
  \draw[thick, dashed] (5.0,0.6) edge (5.0,0.2);
  \draw[thick] (5.0,0.4) circle (2pt);
  \node[very thick, right] at (6.5, 0.4) {rms$_x$};
  \node[below] at (5.0, 0.3) {rms$_{x\text{, peak}}$};

  \draw[thick, blue] plot [smooth, tension=0.5] coordinates {
      (1.2,2.1)
      (2.5,2.8)
      (3.5,1.9)
      (5.0,3.3)
      (7.9,2.2)
      (8.8,2.6)};
  \draw[thick] (5.0,3.3) circle (2pt);
  \node[right] at (5.7, 3.2) {$\varepsilon_x$};
  \node[above] at (5.0, 3.4) {$\varepsilon_{x\text{, peak}}$};

\end{tikzpicture}

### 2017-11-07 paper/paper.tex
frest start

\documentclass[final]{siamltex}

\usepackage{todonotes}

\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{cite}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{url}
\usepackage{footmisc}
\usepackage{multicol}
\usepackage{color}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows,snakes,backgrounds}
\usetikzlibrary{mindmap,trees}
\usetikzlibrary{decorations.pathreplacing}
\usetikzlibrary{plotmarks}

\usepackage{listings}
\newcounter{lstmain}
\setcounter{lstmain}{1}

\lstnewenvironment{code}[1][]
{ \vspace{0.3cm}\footnotesize{\textsc{Code Listing \thelstmain: #1}}
  \hspace{0.1cm} \hrulefill
  \lstset{language=C++, basicstyle=\ttfamily\scriptsize,
    keywordstyle=\color{blue}\bfseries,commentstyle=\color{mygreen},
    stringstyle=\color{red}
  }
}
{
  \hrule \vspace{0.3cm}
  \addtocounter{lstmain}{1}
}

\lstnewenvironment{codeln}[1][]
{\textbf{Code Listing} \hspace{1cm} \hrulefill \lstset{language=C++, basicstyle=\ttfamily\scriptsize, numbers=left, numberstyle=\tiny, stepnumber=1, numbersep=5pt, keywordstyle=\color{blue}\bfseries,commentstyle=\color{mygreen}, stringstyle=\color{red}}}
{\hrule\smallskip}

\lstnewenvironment{smallcode}[1][]
{\lstset{language=C++, basicstyle=\ttfamily\scriptsize, keywordstyle=\color{myblue}\bfseries,commentstyle=\color{mygreen}, stringstyle=\color{red}}}
{\smallskip}

\xdefinecolor{mygreen}{RGB}{0,220,0}
\xdefinecolor{myblue}{RGB}{26,150,255}

\begin{document}

\title{A Parallel General Purpose Multi-Objective Optimization Framework,
  with Application To Beam Dynamics}

\author{Y. Ineichen\footnotemark[2]\ \footnotemark[3]\ \footnotemark[4]
  \and A. Adelmann\footnotemark[2]\ \footnotemark[6]
  \and A. Kolano\footnotemark[2]\ \footnotemark[5]
  \and C. Bekas\footnotemark[3]
  \and A. Curioni\footnotemark[3]
  \and P. Arbenz\footnotemark[4]
}

\maketitle

\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\footnotetext[2]{PSI, Villigen, Switzerland}
\footnotetext[3]{IBM Research -- Zurich, Switzerland}
\footnotetext[4]{Department of Computer Science, ETH Zurich, Switzerland}
\footnotetext[5]{University of Huddersfield, West Yorkshire, United Kingdom}
\footnotetext[6]{Corresponding author: \url{andreas.adelmann@psi.ch}}
\renewcommand{\thefootnote}{\arabic{footnote}}

\begin{abstract}
Particle accelerators are invaluable tools for research in the basic and
  applied sciences, in fields such as materials science, chemistry,
  the biosciences, particle physics, nuclear physics and medicine.
The design, commissioning, and operation of accelerator facilities is a
  non-trivial task, due to the large number of control parameters and the
  complex interplay of several conflicting design goals.

We propose to tackle this problem by means of multi-objective optimization
  algorithms which also facilitate a parallel deployment.
In order to compute solutions in a meaningful time frame we require a fast
  and scalable software framework.

In this paper, we present the implementation of such a general-purpose
  framework for simulation-based multi-objective optimization methods that
  allows the automatic investigation of optimal sets of machine parameters.
The implementation is based on a master/slave paradigm, employing several
  masters that govern a set of slaves executing simulations and performing
  optimization tasks.

Using evolutionary algorithms and \textsc{OPAL}~simulations as optimizer and
  forward solver in our framework, we present validation experiments and first
  results of multi-objective optimization problems in the domain of beam
  dynamics.
\end{abstract}

\begin{keywords}
multi-objective optimization, beam dynamics, high performance computing
\end{keywords}

\section{INTRODUCTION} \label{sec:introduction}

Particle accelerators play a significant role in many aspects of science and
  technology.
Fields, such as material science, chemistry, the biosciences, particle
  physics, nuclear physics and medicine depend on reliable and effective
  particle accelerators, both as research but as well as practical tools.
Achieving the required performance in the design, commissioning, and operation
  of accelerator facilities is a complex and versatile problem.
Today, tuning machine parameters, e.g., bunch charge, emission time and
  various parameters of beamline elements, is most commonly done manually by
  running simulation codes to scan the parameter space.
This approach is tedious, time consuming and can be error prone.
In order to be able to reliably identify optimal configurations of
  accelerators we propose to solve large multi-objective design optimization
  problems to automate the investigation for an optimal set of tuning
  parameters.
Observe that multiple and conflicting optimality criteria call for a
  multi-objective approach.

\begin{figure}[h!]
\begin{center}\normalsize
  \begin{tikzpicture}[text=black]%[scale=0.95, transform shape]
    \input{figures/opt-framework_code.tex}
  \end{tikzpicture}
\caption{Multi-objective framework: the pilot (master) solves the
optimization problem specified in the input file by coordinating optimizer
algorithms and workers running forward solves.}
\label{fig:framenetwork}
\end{center}
\end{figure}

We developed a modular multi-objective software framework (see
  Fig.~\ref{fig:framenetwork}) where the core functionality is decoupled from
  the ``forward solver'' and the optimizer.
To that end, we use a master/slave mechanism where a master process governs a
  set of slave processes given some computational tasks to complete.
This separation allows to easily interchange optimizer algorithms, forward
  solvers and optimization problems.
A ``pilot'' coordinates all efforts between the optimization algorithm and the
  forward solver.
This forms a robust and general framework for massively parallel
  multi-objective optimization.
Currently the framework offers one concrete optimization algorithm, an
  evolutionary algorithm employing a \textsc{NSGAII} selector \cite{pisa}.
Normally, simulation based approaches are plagued by the trade-of between
  level of detail and time to solution.
We address this problem by using forward solvers with different time and
  resolution complexity.

The framework discussed here, incorporates the following three contributions:
%
\begin{enumerate}
  \item Implementation of a scalable optimization algorithm capable of
        approximating Pareto fronts in high dimensional spaces,
  \item design and implementation of a modular framework that is simple to use
        and deploy on large scale computation resources, and
  \item demonstrating the usefulness of the proposed framework on a real world
        application in the domain of particle accelerators.
\end{enumerate}

Here, we will focus on a real world application arising from PSI's
  \textsc{SwissFEL}~\cite{pedr:10} activities, which have an immediate and a
  long-range impact, by optimizing important parameters of PSI's \textsc{250
  MeV injector} test facility (and later for the full PSI \textsc{SwissFEL}).

The next section introduces the notation of multi-objective optimization
  theory and describes the first implemented optimizer.
In Section~\ref{sec:framework} we discuss the implementation of the framework.
We introduce the employed forward-solver in Section~\ref{sec:forward-solver}.
A validation and a proof of concept application of a beam dynamics problem is
  discussed in Section~\ref{sec:experiments}.

\section{MULTI-OBJECTIVE OPTIMIZATION} \label{sec:optimization}

Optimization problems deal with finding one or more feasible solutions
  corresponding to extreme values of objectives.
If more than one objective is present in the optimization problem we call this
  a multi-objective optimization problem (MOOP).
A MOOP is defined as
%
\begin{align}
  \text{ min} \quad & \quad f_m({\bf x}), ~& m &= 1, \dots, M, \label{eq:moop:obj}\\
  \text{s.t.} \quad & \quad g_j({\bf x}) \geq 0, & j &= 0, \dots, J,
  \label{eq:moop:constr}\\
  \quad & \quad  x_i^L \leq {\bf x}=x_i \leq x_i^U,& i &=0, \dots, n
  \label{eq:moop:dvar} \text{,}
\end{align}
%
where $\bf f$ denotes the objectives (\ref{eq:moop:obj}),
  $\bf g$ the constraints (\ref{eq:moop:constr}),
  and $\bf x$ the design variables (\ref{eq:moop:dvar}).

Often, we encounter conflicting objectives complicating the concept of
  optimality.
To illustrate this, let us consider the problem of buying a car.
Naturally, we try to bargain the lowest price for the best performance,
  e.g.\ maximal horsepower or minimal fuel consumption.
This can be formulated as MOOP (\ref{eq:car-moop}).
%
\begin{equation}
  \begin{array}{cl}
  \min          & \quad \left[ \text{price}, -\text{performance} \right]^T \\
    \text{s.t.} & \quad \text{low}_\text{pr} \leq \text{price} \leq \text{high}_\text{pr}\\
                & \quad \text{low}_\text{pe} \leq \text{performance} \leq \text{high}_\text{pe}
  \end{array}
  \label{eq:car-moop}
\end{equation}

\begin{figure}
  \begin{center}
    \begin{tikzpicture}[scale=1.3, transform shape]
      \input{figures/car-trade-off}
    \end{tikzpicture}
  \end{center}
  \caption{Two competing objectives can not be optimal at the same time.
    Red dots represent Pareto optimal points, while the green square $x_4$ is
    dominated (exhibits a worse price per performance ratio than e.g. $x_2^*$)
    by all points on the blue curve (Pareto front).
  }
  \label{fig:tradeoff}
\end{figure}

In general, it is not possible to get the maximal performance for the lowest
  price and a trade-off decision between performance and price has to be
  reached (see Figure~\ref{fig:tradeoff}).
Since not every choice is equally profitable for the buyer (for example, car
  $x_4$ costs as much as $x_2^*$ but offers less performance), we pick
  trade-offs (red points) that are essentially ``equally optimal'' in both
  conflicting objectives, meaning, we cannot improve one point without hurting
  at least one other solution.
This is known as \textit{Pareto optimality}.
The set of Pareto optimal points (blue curve) forms the Pareto front or
  surface.
All points on this surface are considered to be Pareto optimal.

Once the shape of the Pareto front has been determined the buyer can
  \textit{specify preference}, balancing the features by observing the
  effect on the optimality criteria, converging to the preferred solution.
This is called \textit{a posteriori} preference specification since we select
  a solution after all possible trade-offs have been presented to us.
An alternative is to specify preference \textit{a priori}, e.g., by
  weighting (specifying preference before solving the problem) and combining
  all objectives into one and applying a single-objective method to solve the
  problem (yielding only one solution).
In many situations preference is not known \textit{a priori} and an
  \textit{a posteriori} preference specification helps conveying a deeper
  understanding of the solution space.
The Pareto front can be explored and the impact of a trade-off decision then
  becomes visible.

Sampling Pareto fronts is far from trivial.
A number of approaches have been proposed,
  e.g.\ evolutionary algorithms~\cite{deb:09},
  simulated annealing~\cite{kigv:83},
  swarm methods~\cite{keeb:95},
  and many more~\cite{domc:96,cati:02,kara:05,hoss:09}.
In the next section we briefly introduce the theory of evolutionary algorithms
  used in the present work.

\subsection{Evolutionary Algorithms}

Evolutionary algorithms are loosely based on nature's evolutionary
  principles to guide a population of individuals towards an improved solution
  by honoring the ``survival of the fittest'' principle.
This ``simulated'' evolutionary process preserves entropy (or diversity in
  biological terms) by applying genetic operators, such as mutation and
  crossover, to remix the fittest individuals in a population.
Maintaining diversity is a crucial feature for the success of all evolutionary
  algorithms.

In general, a generic evolutionary algorithm consists of the following
  components:
%
\begin{itemize}
  \item \textit{Genes}: traits defining an individual,
  \item \textit{Fitness}: a mapping from genes to a fitness value for each
    individual,
  \item \textit{Selector}: selecting the $k$ fittest individuals of a
    population based on some sort of ordering,
  \item \textit{Variator}: recombination (mutations and crossover) operators
    for offspring generation.
\end{itemize}

\begin{figure}
    \centering
    \begin{tikzpicture}[scale=0.8, transform shape, text=black]
      \input{figures/ga_explained_big.tex}
    \end{tikzpicture}
  \caption{Schematic view of interplay between selector and variator. The
  selector ranks all individuals in the population according to fitness and
  subsequently the variator uses the fittest individuals to produces new
  offspring. Finally, the new children are reintroduced in the population.}
  \label{fig:varsel}
\end{figure}

Applied to multi-objective optimization problems, genes correspond to
  design variables.
The fitness of an individual is loosely related to the value of the objective
  functions for the corresponding genes.
Figure~\ref{fig:varsel} schematically depicts the connection of the
  components introduced above.
The process starts with an initially random population of individuals, each
  individual with a unique set of genes and corresponding fitness,
  representing one location in the search space.
In a next step the population is processed by the selector
  determining the $k$ fittest individuals according to their fitness values.
While the $k$ fittest individuals are passed to the variator, the
  remaining $n-k$ individuals are eliminated from the population.
The \textsc{Variator} mates and recombines the $k$ fittest individuals to
  generate new offspring.
After evaluating the fitness of all the freshly born individuals a
  \textit{generation} cycle has completed and the process can start anew.

Since there already exist plenty of implementations of evolutionary algorithms,
  we decided to incorporate the PISA library \cite{pisa} into our
  framework.
One of the advantages of PISA is that it separates variator from selector,
  rendering the library expandable and configurable.
Implementing a variator was enough to use PISA in our framework and
  retain access to all available PISA selectors.
As shown in Figure~\ref{fig:varsel}, the selector is in charge of ordering a
  set of $d$-dimensional vectors and selecting the $k$ fittest individuals
  currently in the population.
The performance of a selector depends on the number of objectives and the
  surface of the search space.
So far, we used an NSGA-II selector \cite{dpam:02} exhibiting satisfactory
  convergence performance.

The task of the variator is to generate offspring and ensure diversity in the
  population.
The variator can start generating offspring once the fitness of every
  individual of the population has been evaluated.
This explicit synchronization point defines an obvious bottleneck for parallel
  implementations of evolutionary algorithms.
In the worst case some MPI processes are taking a long time to compute the
  fitness of the last individual in the pool of individuals to evaluate.
During this time all other resources are idle and wait for the result of
  this one individual in order to continue to generate and evaluate offspring.
To counteract this effect we call the selector already when two individuals
  have finished evaluating their fitness, lifting the boundaries between
  generations and evaluating the performance of individuals.
New offspring will be generated and MPI processes can immediately return to
  work on the next fitness evaluation.
By calling the selector more frequently (already after two offspring
  individuals have been evaluated) results in better populations since bad
  solutions are rejected earlier.
On the other hand, calling the selector more often is computationally more
  expensive.

Our variator implementation uses the master/slave architecture, presented in
  the next section, to run as many function evaluations as possible in parallel.
Additionally, various crossover and mutation policies are available for tuning
  the algorithm to the optimization problem.

\section{THE FRAMEWORK} \label{sec:framework}

Simulation based multi-objective optimization problems are omnipresent in
  research and the industry.
The simulation and optimization problems arising in such problems are in
  general very big and computationally demanding.
This motivated us to design a massively parallel general purpose framework.
The key traits of such a design can be summarized as:
%
\begin{itemize}
  \item support any multi-objective optimization method,
  \item support any function evaluator: simulation code or measurements,
  \item offer a general description/specification of objectives, constraints
        and design variables,
  \item run efficiently in parallel on current large-scale high-end clusters
        and supercomputers.
\end{itemize}
%

\subsection{Related Work}

Several similar frameworks, e.g.~\cite{fide:09,lems:09,lbjt:07,dnld:06}, have
  been proposed.
Commonly these frameworks are tightly coupled to an optimization algorithm,
  e.g.\ only providing evolutionary algorithms as optimizers.
Users can merely specify optimization problems, but cannot change the
  optimization algorithm.
Our framework follows a more general approach, providing a user-friendly way
  to introduce new or choose from existing built-in multi-objective
  optimization algorithms.
Tailoring the optimization algorithm to the optimization problem at hand is
  an important feature due to the many different characteristics of
  optimization problems that should be handled by such a general framework.
As an example, we show how \textsc{Pisa} \cite{pisa}, an existing evolutionary
  algorithm library, was integrated with ease.
Similarly, other multi-objective algorithms could be incorporated and
  used to solve optimization problems.

The framework presented in \cite{lems:09} resembles our implementation the
  most, aside from their tight coupling with an evolutionary algorithm
  optimization strategy.
The authors propose a plug-in based framework employing an island
  parallelization model, where multiple populations are evaluated concurrently
  and independently up to a point where some number of individuals of the
  population are exchanged.
This is especially useful to prevent the search algorithm to get stuck in
  a local minimum.
A set of default plug-ins for genetic operators, selectors and other
  components of the algorithms are provided by their framework.
User-based plug-ins can be incorporated into the framework by implementing a
  simple set of functions.

%Unfortunately, the island parallelization approach is not well suited for
  %running search algorithms in the massively parallel environment.
%The decision how many processors are assigned to an island is non-trivial.
%\todo{PA: what are roles?}
%Parallel performance is sensitive to placement and assignment of roles to
  %processors of such frameworks and therefore should be considered carefully.
%Especially the master thread on an island (used to exchange individuals
  %between the islands and aggregate solutions) can be overwhelmed with
  %messages from slaves evaluating individuals.
%This creates hotspots on the network and as a result the network performance
  %suffers.

Additionally, as with simulation based multi-objective optimization, we can
  exploit the fact that both the optimizer and simulation part of the process
  use a certain amount of resources.
The ratio of work between optimizer and simulation costs can be reflected in
  the ratio of number of processors assigned to each task.
This not only provides users with  great flexibility in using any simulation
  or optimizer, but renders influencing the role assignment easy as well.

\subsection{Components}

The basic assumption in simulation-based optimization is that we need to
  call an expensive simulation software component present in the
  constraints or objectives.
We divide the framework in three exchangeable components, as shown in
  Figure~\ref{fig:opt-framework-layout}, to encapsulate the major behavioral
  patterns of the framework.
%
\begin{figure}
  \centering
  \begin{tikzpicture}[text=black]
    \input{figures/opt-framework-layout.tex}
  \end{tikzpicture}

  \caption{Schematic view of messages passed within the network between the
    three roles.
  The dashed cyan path describes a request (job $j_1$) sent from $O_i$ to the
  \textsc{Pilot} being handled by $W_j$. Subsequently the result $r_k$ is
  returned to the requesting \textsc{Optimizer} ($O_i$).}
  \label{fig:opt-framework-layout}
\end{figure}

%
The \textsc{Pilot} component acts as a bridge between the optimizer and
  forward solvers, providing the necessary functionality to handle passing
  requests and results between the \textsc{Optimizer} and the
  \textsc{Simulation} modules.

We implemented the framework in \texttt{C++}, utilizing features like template
  parameters to specify the composition of the framework (shown in Listing 1).

\noindent\begin{minipage}{\textwidth}
\begin{code}[Assembling the optimizer from components]
typedef OpalInputFileParser Input_t;
typedef PisaVariator        Opt_t;
typedef OpalSimulation      Sim_t;

typedef Pilot< Input_t, Opt_t, Sim_t > Pilot_t;
\end{code}
\end{minipage}

The framework provides ``default'' implementations that can be controlled via
  command line options.
Due to its modular design, all components can be completely customized.

Every available MPI process will take up one of the three available roles (see
  Figure~\ref{fig:framenetwork}):  one process acts as \textsc{Pilot}, the
  remaining processes are divided amongst \textsc{Worker} and
  \textsc{Optimizer} roles.
Both, the \textsc{Worker} and the \textsc{Optimizer} can consist of multiple
  MPI processes to exploit parallelism.
As shown in Figure~\ref{fig:opt-framework-layout} the \textsc{Pilot} is used
  to coordinate all ``information requests'' between the \textsc{Optimizer}
  and the \textsc{Worker}.
An information request is a job that consists of a set of design variables
  (e.g.~the genes of an individual) and a type of information it requests
  (e.g.~function evaluation or derivative).
The \textsc{Pilot} keeps checking for idle \textsc{Worker} and assigns jobs
  in the queue to any free \textsc{Worker}.
Once the \textsc{Worker} has computed and evaluated the request its results
  are returned to the \textsc{Optimizer} that originally requested the
  information.

After a process gets appointed a role it starts a polling loop asynchronously
  checking for appropriate incoming requests.
To that end a \textsc{Poller} interface helper class has been introduced.
The \textsc{Poller} interface consists of an infinite loop that checks
  periodically for new MPI messages.
Upon reception a new message is immediately forwarded to the appropriate
  handler, the \texttt{onMessage()} method.
The method is called with the \texttt{MPI\_Status} of the received message and
  a \texttt{size\_t} value specifying different values depending on the value
  of the \texttt{MPI\_Tag}.
The \textsc{Poller} interface allows the implementation of special methods
  (denoted \textit{hooks}) determining the behavior of the polling process,
  e.g.\ for actions that need to be taken after a message has been handled.
Every \textsc{Poller} terminates the loop upon receiving a special MPI tag.

\subsection{Implementing an Optimizer}

All \textsc{Optimizer} implementations have to respect the API shown in
Listing 2.

\noindent\begin{minipage}{\textwidth}
\begin{code}[Optimizer API]
virtual void initialize() = 0;

// Poller hooks
virtual void setupPoll() = 0;
virtual void prePoll() = 0;
virtual void postPoll() = 0;
virtual void onStop() = 0;
virtual bool onMessage(MPI_Status status,
                       size_t length) = 0;
\end{code}
\end{minipage}

All processors running an \textsc{Optimizer} component call the
  \texttt{initialize} entry point after role assignment in the
  \textsc{Pilot}.
The implementation of \texttt{initialize} must set up and start the poller and
  the optimization code.
Since an optimizer derives from the \texttt{Poller} interface, predefined
  hooks can be used to determine the polling procedure.
Hooks can be implemented as empty methods, but the \texttt{onMessage}
  implementation should reflect the optimization part of the protocol for
  handling events from the \textsc{Pilot}.
A special set of communicator groups serves as communication channels to the
  \textsc{Pilot} and its job queue and if existing to processes supporting the
  \textsc{Optimizer} component.

\subsection{Implementing a Forward Solver}

In most cases \textsc{Simulation} implementations are simple wrappers to run
  an existing ``external'' simulation code using a set of design variables as
  input.
As for the \textsc{Optimizer} component there exists a base class, labeled
  \texttt{Simulation} as common basis for all \textsc{Simulation}
  implementations.
In addition, this component also inherits from the \texttt{Worker} class,
  already implementing the polling protocol for default worker types.
As shown in the API in Listing 3 the \texttt{Worker} class expects an
  implementation to provide implementations for those three methods.

\begin{code}[Simulation API]
virtual void run() = 0;
virtual void collectResults() = 0;
virtual reqVarContainer_t getResults() = 0;
\end{code}

First, upon receiving a new job, the \texttt{Worker} will call the
  \texttt{run} method on the \textsc{Simulation} implementation.
This expects the \textsc{Simulation} implementation to run the simulation in a
  \textit{blocking} fashion, meaning the method call blocks and does not return
  until the simulation has terminated.
Subsequently, the \texttt{Worker} calls \texttt{collectResults}, where the
  \textsc{Simulation} prepares the result data, e.g., parsing output files,
  and stores the requested information in a \texttt{reqVarContainer\_t} data
  structure.
Finally, the results obtained with \texttt{getResults} are sent to the
  \textsc{Pilot}.
As before, the serialized data is exchanged using MPI point-to-point
  communication using a specific set of communicators.

\subsection{Specifying the Optimization Problem}

We aimed at an easy and expressive way for users to specify multi-objective
  optimization problems.
Following the principle of keeping metadata (optimization and simulation
  input data) together, we decided to embed the optimization problem
  specification in the simulation input file by prefixing it with special
  characters, e.g., as annotations prefixed with a special character.
In some cases it might not be possible to annotate the simulation input file.
By providing an extra input file parser, optimization problems can be read
  from stand-alone files.

To allow arbitrary constraints and objective expressions, such as
%
\vspace{0.2cm}
{\footnotesize \begin{verbatim}
  name: OBJECTIVE,
        EXPR="5 * average(42.0, "measurement.dat") + ENERGY";
\end{verbatim}}
\vspace{0.2cm}
%
\noindent
  we implemented an expression parser using Boost
  Spirit\footnote{\url{http://boost-spirit.com/}}.
In addition to the parser, we need an evaluator able to evaluate an expression,
  given a parse tree and variable assignments to an actual value.
Expressions arising in multi-objective optimization problems usually evaluate
  to booleans or floating point values.
The parse tree, also denoted abstract syntax tree (AST), is constructed
  recursively while an expression is parsed.
Upon evaluation, all unknown variables are replaced with values, either
  obtained from simulation results or provided by other subtrees in the AST.
In this stage, the AST can be evaluated bottom-up and the desired result is
  returned after processing the root of the tree.

To improve the expressive power of objectives and constraints we introduced a
  simple mechanism to define and call custom functions in expressions.
Using simple functors, e.g., as the one shown in Listing 4 to compute an
  average over a set of data points, enriches expressions with custom
  functions.
Custom function implementations overload the \texttt{()} parenthesis operator.
The function arguments specified in the corresponding expression are stored in
  a \texttt{std::vector} of Boost
  variants\footnote{\url{www.boost.org/doc/html/variant.html}} that can be
  booleans, strings or floating point values.

\begin{code}[Simple Average Functor]
struct avg {

    double operator()(
      client::function::arguments_t args) const {

        double limit = boost::get<double>(args[0]);
        std::string filename =
          boost::get<std::string>(args[1]);

        double sum = 0.0;
        for(int i = 0; i < limit; i++)
            sum += getDataFromFile(filename, i);

        return sum / limit;
    }
};
\end{code}

All custom functions are registered with expression objects.
This is necessary to ensure that expressions know how they can resolve
  function calls in their AST.
As shown in Listing 5 this is done by creating a collection of Boost
  functions\footnote{\url{www.boost.org/libs/function/}} corresponding to the
  available custom functions in expressions and passing this to the
  \textsc{Pilot}.

\noindent\begin{minipage}{\textwidth}
\begin{code}[Creating function pointer for registering functor]
functionDictionary_t funcs;
client::function::type ff;
ff = average();
funcs.insert(std::pair<std::string, client::function::type>
        ("my_average_name", ff));
\end{code}
\end{minipage}

A set of default operators, corresponding to a mapping to \texttt{C} math
  functions, is included in the dictionary by default.
This enables an out of source description of optimization problem containing
  only simple math primitives.

\subsection{Parallelization} \label{sec:parallelization}

The parallelization is defined by a mapping of the roles introduced above to
  available cores.
Command-line options allow the user to steer the number of processors used in
  worker and optimizer groups.
Here, we mainly use the command-line options to steer the number of processors
  running a forward solver.

The parallelization will be explained and benchmarked in detail in a
  forthcoming publication.
One major disadvantage of the master/slave implementation model is the fast
  saturation of the network links surrounding the master node.
In \cite{bctg:09} authors observe an exponential increase in hot-spot latency
  with increasing number of workers that are attached to one master process.
Clearly, the limiting factor is the number of outgoing links of a node in the
  network topology and already for a few workers the links surrounding a
  master process are subject to congestions.
This effect is amplified further by large message sizes.

To that end we implemented a solution propagation based on rumor networks (see
  e.g.\ \cite{bgps:06,ayss:09}) using only one-sided communication.
This limits the number of messages sent over the already heavily used links
  surrounding the master node and at the same time helps to prevent the use of
  global communication.
Using information about the interconnection network topology and the
  application communication graph the task of assigning roles helps to further
  improve the parallel performance.

\section{FORWARD SOLVER} \label{sec:forward-solver}

The framework contains a wrapper implementing the API mentioned in
  Listing 3 for using \textsc{OPAL} \cite{opal} as the forward solver.
\textsc{OPAL} provides different trackers for cyclotrons and linear
  accelerators with satisfactory parallel performance \cite{akir:09}.
Recently we introduced a reduced envelope model \cite{iabc:12} into
  \textsc{OPAL} reducing time to solution by several orders of magnitude.

With access to the \textsc{OPAL} forward solver the framework is able to
  tackle a multitude of optimization problems arising in the domain of
  particle accelerators.
By abiding to the API from Listing 3 it becomes trivial to add new forward
  solvers to the framework (see Appendix A).
If the objectives and constraints are simple arithmetical expressions, the
  \texttt{FunctionEvaluator} simulator can be used.
Using functors and the default expression primitives already powerful
  multi-objective optimization problems can be specified, i.e.\ the benchmark
  problem presented in \cite{hbwh:05}:
%
\begin{align} \label{eqn:bench}
  \text{ min} \quad & \quad \left[ 1 - \exp \left( -1 \left(
    \left(x_1 - \frac{1}{\sqrt{3}} \right)^2 +
    \left(x_2 - \frac{1}{\sqrt{3}} \right)^2 +
    \left(x_3 - \frac{1}{\sqrt{3}} \right)^2 \right)\right), \right. \\
                    & \quad \left. 1 - \exp \left( -1 \left(
    \left(x_1 + \frac{1}{\sqrt{3}} \right)^2 +
    \left(x_2 + \frac{1}{\sqrt{3}} \right)^2 +
    \left(x_3 + \frac{1}{\sqrt{3}} \right)^2 \right)\right) \right]^T \nonumber \\
    \text{s.t.} \quad & \quad -1 \le x_i \le 1, \quad i=1,2,3 \nonumber
  \text{.}
\end{align}
%
Using the default expression primitives this can be stated in an input file
  as:

\vspace{0.2cm}
{\footnotesize \begin{verbatim}
  d1: DVAR, VARIABLE="x1", LOWERBOUND="-1.0", UPPERBOUND="1.0";
  d2: DVAR, VARIABLE="x2", LOWERBOUND="-1.0", UPPERBOUND="1.0";
  d3: DVAR, VARIABLE="x3", LOWERBOUND="-1.0", UPPERBOUND="1.0";

  obj1: OBJECTIVE,
    EXPR="1- exp(-1 * (sq(x1 - 1/sqrt(3)) + sq(x2 - 1/sqrt(3)) + sq(x3 - 1/sqrt(3))))";
  obj2: OBJECTIVE,
    EXPR="1- exp(-1 * (sq(x1 + 1/sqrt(3)) + sq(x2 + 1/sqrt(3)) + sq(x3 + 1/sqrt(3))))";

  objs:    OBJECTIVES = (obj1, obj2);
  dvars:   DVARS = (d1, d2, d3);
  constrs: CONSTRAINTS = ();
  opt: OPTIMIZE, OBJECTIVES=objs, DVARS=dvars, CONSTRAINTS=constrs;
\end{verbatim}}
\vspace{0.2cm}

\input{theor-experiment}

\section{CONCLUSIONS} \label{sec:conclusions}

We presented a general-purpose framework for solving multi-objective
  optimization problems.
Its modular design simplifies the application to simulation-based optimization
  problems for a wide range of problems and allows to exchange the
  optimization algorithm.
In a recent work, we successfully implemented and integrated another
  optimization algorithm, originally presented in~\cite{pesc:11}, into our
  framework.
The flexibility of being able to adapt both ends of the optimization
  process, the forward solver and the optimization algorithm simultaneously
  not only leads to broad applicability but it facilitates the ability to
  tailor the optimization strategy to the optimization problem as well.

In this paper we applied the framework to reproduce the important and well
  known Ferrario matching condition for the \textsc{250 MeV injector}, a part of PSI's
  \textsc{SwissFEL} project.
The beam size and emittance optimization was successful and emittance damping
  is observed in the accelerating cavity.
Also, the influence of the number of slices employed by the envelope tracker
  with respect to convergence was investigated.
We found that the optimal slice number is around 400 for the problem addressed
  here, producing the best trade-off between computational cost and accuracy
  of the solution of the simulation.
Similarly, the gun and beam line time step was investigated confirming the
  convergence of the results.
This first study shows that the framework is ready to tackle problems arising
  in the domain of beam dynamics.

Interestingly, the computation of a good approximation of the Pareto front is
  already feasible on a small cluster using only a modest number of MPI
  procsses.
For 1000 generations consisting of 2048 feasible and 8354 infeasible function
  evaluations (simulations) the optimizer needed $845$ minutes on the
  \textsc{Felsim} cluster on $16$ processes.
When we double the number of processes to $32$ (\textsc{Felsim} allows a
  maximum of $64$ processes per job) the runtime improves to $302$ minutes (2048
  accepted and 5426 infeasible individuals).
Notice that the runtime can vary due to the random nature of the process.
Nevertheless we see a reasonable speeduo when using more cores to solve the
  optimization problem and the parallel performance will be further evaluated
  in a forthcoming publication.
%The number of individuals is the only limiting factor.

In contrast to approaches that are tightly coupled to the optimization
  algorithm, the range of possible applications is much wider.
Even in cases where the mathematical model of the forward solver is not known
  exactly, fixed or on the real time measurements can be used to guide the
  search for the Pareto optimal solutions.
Finally, combining the presented multi-objective optimization framework with
  a physicist long standing experience in the field provides a solid basis
  for better understanding and improving the decision making process in the
  design and operation of particle accelerators.

\section{ACKNOWLEDGMENT}

The authors thank the \textsc{SwissFEL} team for contributing to the
  formulation of optimization problems.

\appendix

\section{Forward Solver Implementation}

A simple implementation, e.g.\ using a Python forward solver, is given below
  in Listing 6.
We assume the Python script executes a simulation and dumps results in the
  \textsc{SDDS} file format~\cite{borl:00}.
Utility classed are used to parse the result data and fill the appropriate
  structures returned to the optimizer algorithm.

\begin{code}[Simple Simulation Wrapper]
#include <map>
#include <string>
#include <vector>

#include "Util/Types.h"
#include "Util/CmdArguments.h"
#include "Simulation/Simulation.h"

#include "boost/smart_ptr.hpp"

class SimpleSimulation : public Simulation {

public:

    SimpleSimulation(Expressions::Named_t objectives,
                     Expressions::Named_t constraints,
                     Param_t params, std::string name, MPI_Comm comm,
                     CmdArguments_t args);

    ~SimpleSimulation();

    /// Calls simulation through Python wrapper and returns when simulation
    /// has either failed or finished.
    void run() {
        // user implements wrappers
        prepare_input_file();
        run_python_simulation();
    }

    /// Parse SDDS stat file and build up requested variable dictionary.
    void collectResults(){

        Expressions::Named_t::iterator it;
        for(it = objectives_.begin(); it != objectives_.end(); it++) {

            Expressions::Expr_t *objective = it->second;

            // find out which variables we need in order to evaluate the
            // objective
            variableDictionary_t variable_dictionary;
            std::set<std::string> req_vars = objective->getReqVars();

            if(req_vars.size() != 0) {

                boost::scoped_ptr<SDDSReader> sddsr(new SDDSReader(fn));

                try {
                    sddsr->parseFile();
                } catch(OptPilotException &e) {
                    std::cout << "Exception while parsing SDDS file: "
                        << e.what() << std::endl;
                    break;
                }

                // get all the required variable values from the stat file
                foreach(std::string req_var, req_vars) {
                    if(variable_dictionary.count(req_var) == 0) {

                        try {
                            double value = 0.0;
                            sddsr->getValue(1 /*atTime*/, req_var, value);
                            variable_dictionary.insert(
                                std::pair<std::string, double>(req_var, value));
                        } catch(OptPilotException &e) {
                            std::cout << "Exception while getting value "
                                      << "from SDDS file: " << e.what()
                                      << std::endl;
                        }
                    }
                }
            }

            // and evaluate the expression using the built dictionary of
            // variable values
            Expressions::Result_t result =
                objective->evaluate(variable_dictionary);

            std::vector<double> values;
            values.push_back(boost::get<0>(result));
            bool is_valid = boost::get<1>(result);

            reqVarInfo_t tmps = {EVALUATE, values, is_valid};
            requestedVars_.insert(
                std::pair<std::string, reqVarInfo_t>(it->first, tmps));

        }
    }

    /// returns container containing all requested variables with results
    reqVarContainer_t getResults() { return requestedVars_; }

private:

    /// holds solutions returned to the optimizer
    reqVarContainer_t requestedVars_;

    Expressions::Named_t objectives_;
    Expressions::Named_t constraints_;

    MPI_Comm comm_;
};

#endif
\end{code}

\bibliographystyle{abbrv}
\bibliography{../../bibliography/phd}

\end{document}

### 2017-11-07 paper/theor-experiment.tex
frest start

\section{EXPERIMENTS} \label{sec:experiments}

In this section we present numerical results of the validation benchmark and
  discuss a proof of concept application in the domain of particle
  accelerators.

\subsection{Optimizer Validation}

\begin{figure}
    \centering
    \begin{tikzpicture}[text=black]
      \input{figures/hypervolume.tex}
    \end{tikzpicture}
  \caption{The hypervolume for a two-objective optimization problem
  corresponds to the shaded area formed by the dashed rectangles spanned by
  all points on the Pareto front and an arbitrary selected origin $p_o$.}
  \label{fig:hypervolume}
\end{figure}

To ensure that the optimizer works correctly we solved the benchmark
  problem (\ref{eqn:bench}).
To that end, we use a metric for comparing the quality of a Pareto
  front.
Given a point in the Pareto set, we compute the $m$ dimensional volume (for
  $m$ objectives) of the dominated space, relative a chosen origin.
We visualize this for $2$ objectives in Figure~\ref{fig:hypervolume}.
For further information and details of the implementation see~\cite{whbb:12}.
Figure~\ref{fig:pisa_bench} and the corresponding hypervolume values in
  Table~\ref{tbl:bench_rms_error}.
The reference Pareto front is clearly very well approximated.
It took a total of 1100 function evaluations to perform this computation.
The hypervolume of the reference solution ($0.6575$) for our benchmark was
  computed by sampling the solution provided in~\cite{hbwh:05}.

\begin{figure}
  \centering
    \includegraphics[width=0.7\linewidth]{figures/valid_front}
  \caption{Variator benchmark after $1100$ function evaluations using binary
           crossover and independent gene mutations (each gene mutates with
           probability $p=\frac{1}{2}$) on a population of $100$
           individuals.}
  \label{fig:pisa_bench}
\end{figure}

\begin{table}[h!]
\begin{center}
  \caption{Convergence of benchmark problem with errors relative to
    hypervolume of sampled reference solution.}
  \label{tbl:bench_rms_error}
  \begin{tabular}{lcc}
    \hline\noalign{\smallskip}
    tot.\ function  & hyper volume & relative error\\
    evaluations    & & \\
    \noalign{\smallskip}\hline\noalign{\smallskip}
    100  &  0.859753 & $3.076 \times 10^{-1}$ \\
    \noalign{\smallskip}\hline\noalign{\smallskip}
    200  &  0.784943 & $1.938 \times 10^{-1}$ \\
    500  &  0.685183 & $4.210 \times 10^{-2}$ \\
    900  &  0.661898 & $6.689 \times 10^{-3}$ \\
    1100 &  0.657615 & $1.749 \times 10^{-4}$ \\
    \noalign{\smallskip}\hline
  \end{tabular}
\end{center}
\end{table}

From Table~\ref{tbl:bench_rms_error} we deduce that we achieved satisfactory
  convergence to the sampled reference Pareto front after 1000 (plus the
  additional 100 evaluations for the initial population) function evaluations.

\subsection{Ferrario Matching Point}

As a verification and proof of concept we reproduce the Ferrario
  matching point discovered by Ferrario \textit{et~al.}~\cite{fcpr:00},
  by formulating the problem as a  multi-objective optimization problem.
Using the low-dimensional and fast nature of their new simulation code
  Homdyn~\cite{homdyn}, an extensive beam dynamics study was conducted.

One of the results of the study presented in \cite{fcpr:00} was the discovery
  of a novel working point.
The authors noticed that the second emittance minimum can profit from the
  additional emittance compensation in the accelerating traveling wave
  structure ensuring that the second emittance minimum occurs at a higher
  energy.
This property is attained if the beam emittance has a maximum and the root
  mean square (rms) beam size has a minimum at the entrance of the first
  accelerating traveling wave structure.
This behavior is illustrated in Figure~\ref{fig:fer_match}.

\begin{figure}
  \centering
  \input{figures/ferrario_illustrated}
  \caption{Illustration of the Ferrario matching criteria: beam emittance
  attains a maximum and rms beamsize a minimum at the entrance to the first
  accelerating traveling wave structure.}
  \label{fig:fer_match}
\end{figure}

By artificially reproducing this working point as the solution of a
  multi-objective optimization problem given in equations
  (\ref{eq:swissfel:p1}) to (\ref{eq:swissfel:lastdvar}),
  we demonstrate the automation of discovering optimal beam dynamics behaviors
  given a set of desired objectives.

\begin{align}
  \text{min}  \quad & \left[ \Delta \text{rms}_{x,\text{peak}} = \vert 3.0 -
  \text{rms}_{x,\text{peak}} \vert, \right. \label{eq:swissfel:p1}\\
                    & \Delta \varepsilon_{x,\text{peak}}  = \vert 3.0 -
                    \varepsilon_{x,\text{peak}} \vert, \label{eq:swissfel:p2}\\
                    & \left. \vert \text{rms}_{x, \text{peak\_pos}} -
                    \varepsilon_{x,\text{peak\_pos}} \vert
                    \label{eq:swissfel:p3} \right]^T\\
  \text{subject to} \quad & q = 200 \left[\text{pC}\right] \label{eq:swissfel:firstconstr}\\
              \quad & \text{Volt}_{\text{RF}} = 100 \left[\text{MV/m}\right] \label{eq:swissfel:lastconstr}\\
              \quad & \sigma_{L} \leq \sigma_x = \sigma_y \leq \sigma_{U} \label{eq:swissfel:firstdvar}\\
              \quad & \text{KS}_{L} \leq \text{KS}_{\text{RF}} \leq \text{KS}_{U} \label{eq:swissfel:seconddvar}\\
              \quad & \text{LAG}_{L} \leq \text{LAG}_{\text{RF}} \leq \text{LAG}_{U} \\
              \quad & \Delta z_{L\text{KS}} \leq \Delta z_{\text{KS}} \leq \Delta z_{U\text{KS}} \label{eq:swissfel:lastdvar}
\end{align}

The first two objectives minimize the distance from the position of the current
  minimum peak to the expected peak location at $3.0$\,m for transverse bunch
  size (beam waist) and emittance (see Figure~\ref{fig:fer_match}).
The third objective (\ref{eq:swissfel:p3}) adds a condition preferring
  solutions that have their emittance and rms peak locations at the same
  $z$-coordinate.
Equations (\ref{eq:swissfel:firstconstr}) and (\ref{eq:swissfel:lastconstr})
  define constraints for initial conditions for the simulation: charge,
  gun voltage and laser spot size.
Design variables given in (\ref{eq:swissfel:firstdvar}) to
  (\ref{eq:swissfel:lastdvar}) correspond to field strengths of the
  first focusing magnet, its displacement, and the phase of the gun.

In order to compute the peaks, we employed an additional Python script.
This script was called in the \textsc{OPAL}~input file, after the simulation
  finished using the \texttt{SYSTEM} functionality.
Once the peaks (in a given range) were located, the two objectives
  (\ref{eq:swissfel:p1}) and (\ref{eq:swissfel:p2}) were computed and their
  values written into corresponding files.
The custom \texttt{fromFile} functor allows us to access the values stored in
  the peak finder Python script result files

\vspace{0.2cm}
{\footnotesize \begin{verbatim}
    rmsx:  OBJECTIVE, EXPR="fromFile("rms_x-err.dat", "var")";
    emitx: OBJECTIVE, EXPR="fromFile("emit_x-err.dat", "var")";
    match: OBJECTIVE, EXPR="fabs(fromFile("emit_x-peak.dat", "var") -
                                 fromFile("rms_x-peak.dat", "var"))";
\end{verbatim}}
\vspace{0.2cm}

\noindent
The design variables and the assembly of the multi-objective optimization problem
  can be included in the \textsc{OPAL}~input file as shown below:

\vspace{0.2cm}
{\footnotesize \begin{verbatim}
    d1:  DVAR, VARIABLE="SIGX", LOWERBOUND="0.00025", UPPERBOUND="0.00029";
    d2:  DVAR, VARIABLE="FIND1_MSOL10_i", LOWERBOUND="110", UPPERBOUND="120";
    d3:  DVAR, VARIABLE="D_LAG_RGUN", LOWERBOUND="-0.1", UPPERBOUND="0.1";
    d4:  DVAR, VARIABLE="D_SOLPOS", LOWERBOUND="-0.05", UPPERBOUND="0.05";

    objs:    OBJECTIVES = (rmsx, emitx);
    dvars:   DVARS = (d1, d2, d3, d4);
    constrs: CONSTRAINTS = ();
    opt:     OPTIMIZE, OBJECTIVES=objs, DVARS=dvars,
             CONSTRAINTS=constrs;
\end{verbatim}}
\vspace{0.2cm}

All numerical experiments in this sections were executed on the
  \textsc{Felsim} cluster at PSI\@.
The \textsc{Felsim} cluster consists of 8 dual quad-core Intel Xeon
  processors at 3.0 GHz and has $2$ GB memory per core with a total of 128
  cores.
The nodes are connected via Infiniband network with a total bandwidth of 16
  GB/s.

The envelope-tracker, mentioned in the previous section, was used to evaluate
  the forward problems.
We performed a beam convergence study in order to tune the simulation input
  parameters to achieve the best trade-off between simulation accuracy and
  time to solution.
These parameters include the number of slices (\texttt{NSLICE}) used in the
  envelope-tracker simulations, simulation timestep (\texttt{DT}) and gun
  timestep (\texttt{DTGUN}).

Before the simulation can be executed a number of initial beam optics
  parameters have to be defined in an input file.
Table~\ref{tbl:et_params} shows the values of these parameters for the
  envelope-tracker.
All simulations were performed up to 12.5~m of the
  \textsc{SwissFEL} 250 MeV injector~\cite{pedr:10} beam line, with
  energies reaching  up to 120 MeV.

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.8\linewidth]{Report/dt_scan}
  \caption{Envelope-tracker with different number of slices and simulation
    time steps.}
  \label{fig:et-dt}
\end{figure}

\begin{table}
  \begin{center}
    \caption{Initial conditions for the envelope tracker.}
    \label{tbl:et_params}
    \begin{tabular}{ll}
      \hline\noalign{\smallskip}
      name & initial value \\
      \noalign{\smallskip}\hline\noalign{\smallskip}
        Gun voltage       & $100$ MV\\
        %Solenoid current & $110.541$ A\\
        %Laser spot size  & $290 \times 10^{-6}$ m in x and y\\
        Bunch charge      & $200$ pC\\
        %DT$_{Gun}$        & $0.06$ ps\\
        DT$_{\text{Beamline}}$  & $1.5$ ps\\
        Number of slices  & $400$ \\
      \noalign{\smallskip}\hline
    \end{tabular}
  \end{center}
\end{table}

The parameter that affects the performance most is the number of slices.
We scanned the range from $100$ to $1000$ slices to determine the minimal
  number of slices required for stable results using various timesteps.
The results (for 100, 400 and 800 slices) of this scan are shown in
  Figure~\ref{fig:et-dt}.
Using this data we settled for $400$ slices -- increasing the slice number
  only minimally improves convergence of the results, therefore using more
  slices is inefficient.

%\begin{figure}
   %\centering
     %\includegraphics[angle=0,width=0.8\linewidth]{Report/sliceNew}
   %\caption{Scan of the envelope-tracker slice number showing its influence
            %on the exit emittance values.}
   %\label{fig:scan_slices}
%\end{figure}

In a next step the influence of different time steps was examined.
To that end a series of optimization runs with 100, 400 and 800 slices and
  varying timestep was performed.
%Figures \ref{fig:pareto_front_1} and \ref{fig:pareto_front_21} show two Pareto
Figure~\ref{fig:pareto_front_21} shows the Pareto fronts for 400 slices
  respectively using different timesteps.
As expected, increasing the number of slices while lowering the timestep
  produces more detailed results.

%\begin{figure}
  %\centering
    %\includegraphics[width=0.9\linewidth]{Report/Run1slices100a}
  %\caption{Pareto Front for the $1000$th generation with $40$ individuals
    %using 100 slices, a simulation timestep of 5 ps and a gun timestep of 0.1
    %ps.}
  %\label{fig:pareto_front_1}
%\end{figure}

\begin{figure}[h!]
  \centering
    \includegraphics[width=0.8\linewidth]{Report/front_plot}
  \caption{Pareto front for the $1000$th generation with $40$ individuals
    using 400 slices (interesting region magnified), a simulation timestep
    of 1.5 ps.
    The individual 3 was selected for further investigations.}
  \label{fig:pareto_front_21}
\end{figure}

\subsection{Optimization Results}

Each of the $40$ points on the Pareto front, shown in
  Figure~\ref{fig:pareto_front_21}, represents an optimal solution, where
  emittance and beamsize values are compromised to achieve the best agreement
  with the Ferrario matching point.
We selected individual $3$ based on a comparison of the emittance and beamsize
  characteristics of all solutions and by retaining the feasibility of the
  beam line optics parameters.
The design variables, emittance and beamsize of the selected solution are
  shown in Table~\ref{tbl:des_vars} and Figure~\ref{fig:rmsemit}.
With the multi-objective optimization framework we attain the same working
  point as reported in~\cite{pedr:10}.

\begin{table}
  \begin{center}
    \caption{The design variables for individual $3$.}
    \label{tbl:des_vars}
    \begin{tabular}{ll}
      \hline\noalign{\smallskip}
      name & value \\
      \noalign{\smallskip}\hline\noalign{\smallskip}
        $\sigma_{x}$          & $0.262$ mm \\
        Solenoid displacement & $28.8467$ mm \\
        Gun voltage lag       & $0.0159067$ MV\\
        Solenoid current      & $111.426$ A \\
      \noalign{\smallskip}\hline
    \end{tabular}
  \end{center}
\end{table}

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.8\linewidth]{Report/iff_plot_emrms}
  \caption{Beamsize and emittance of individual $3$.}
  \label{fig:rmsemit}
\end{figure}

Using the input parameters of the selected solution, we performed a stability
  analysis by varying the slice number and the time step for both the gun and
  the beam line.
Figure~\ref{fig:et-dt} shows that the exit emittance stabilizes for 400
  slices and various time steps.
No difference between $800$ and $400$ slices is visible as their minimum
  maximum extension seems to be in the same range of $0.024$ mm~mrad.

For validation purposes we compared the results of the envelope-tracker using
  the analytical space charge model with the \textsc{OPAL} 3D macro particle
  tracker.
The benchmark was run on the first 12.5 meters of the \textsc{SwissFEL} 250
  MeV injector.
The results for both rms beamsize and emittance are shown in
  Figure~\ref{fig:et-vs-tt}.
A good agreement between the two codes can be observed.
The difference of the larger emittance along the solenoids in case of 3D
  tracker that is not seen by the envelope-tracker is due to the different
  definition of the particle momenta (canonical vs.~mechanical).
Both trackers agree within acceptable limits \cite{chao:99}.

\begin{figure}
  \centering
  \includegraphics[width=0.8\linewidth]{Report/iff_plot_emrms_ettt}
  \caption{Comparison 3D-tracker versus envelope-tracker in case for rms$_{x}$
    and $\varepsilon_{x}$.}
  \label{fig:et-vs-tt}
\end{figure}

%\subsection{IW2: Inverse Problem}

%In order to find cross correlations we try to solve the inverse problem
  %(15) -- (23)
%%
%\begin{align}
  %\text{min}  \quad & \sqrt{\frac{1}{N} \sum \left( \text{rmx}_{x,s} -
                      %\text{m}_{x,s} \right)^2 } \text{,}\\
              %\quad & \sqrt{\frac{1}{N} \sum \left( \text{rmx}_{y,s} -
                      %\text{m}_{y,s} \right)^2 } \text{,}\\
              %\quad & \sqrt{\frac{1}{N} \sum \left( \text{rmx}_{z,s} -
                      %\text{m}_{z,s} \right)^2 } \\
  %\text{s.t.} \quad & -0.95 \leq \text{R52} \leq -0.65 \label{eq:iw2:fistdvar}\\
              %\quad & -0.90 \leq \text{R61} \leq -0.50 \\
              %\quad & 0.0   \leq \text{R62} \leq 0.20 \\
              %\quad & 0.25 \leq \text{CORR}_x \leq 0.65 \\
              %\quad & 0.55 \leq \text{CORR}_y \leq 0.95 \\
              %\quad & 0.10 \leq \text{CORR}_z \leq 0.50 \label{eq:iw2:lastdvar} \text{.}
%\end{align}
%%
%We try to match the beam to measurements from the real machine by minimizing
  %the sum of $N$ squared measurement ($m_{d,s}$ at a given position
  %$s$) errors for rmx beam size in each dimensions.
%The design variables (\ref{eq:iw2:fistdvar}) - (\ref{eq:iw2:lastdvar}) define
  %the correlation matrix used when generating particles, e.g., R51, R52, R61,
  %R62 describe limits of correlations between planes.
%The initial Binomial distribution (with $m = ?$) has the form
%%
%\begin{equation*}
  %\frac{1}{2\pi\sigma_x\sigma_y}exp(-\frac{x^2}{2\sigma_x^2}
  %-\frac{y^2}{2\sigma_y^2})
  %\text{.}
%\end{equation*}
%%

%Since these correlations cannot be measured we get the real values by solving
  %the inverse problem mentioned above.

%Currently we run the simulations on a low resolution space charge grid ($8
  %\times 8 \times 8$) as a proof of concept.
%In a next step a simple Python script would be applied to iteratively rerun
  %the optimizer with increasing space-charge resolution when the limits of the
  %design variables are narrow enough (iteratively diminishing search space).
%\subsection{IW2: Inverse Problem}

%In order to find cross correlations we try to solve the inverse problem
  %(15) -- (23)
%%
%\begin{align}
  %\text{min}  \quad & \sqrt{\frac{1}{N} \sum \left( \text{rmx}_{x,s} -
                      %\text{m}_{x,s} \right)^2 } \text{,}\\
              %\quad & \sqrt{\frac{1}{N} \sum \left( \text{rmx}_{y,s} -
                      %\text{m}_{y,s} \right)^2 } \text{,}\\
              %\quad & \sqrt{\frac{1}{N} \sum \left( \text{rmx}_{z,s} -
                      %\text{m}_{z,s} \right)^2 } \\
  %\text{s.t.} \quad & -0.95 \leq \text{R52} \leq -0.65 \label{eq:iw2:fistdvar}\\
              %\quad & -0.90 \leq \text{R61} \leq -0.50 \\
              %\quad & 0.0   \leq \text{R62} \leq 0.20 \\
              %\quad & 0.25 \leq \text{CORR}_x \leq 0.65 \\
              %\quad & 0.55 \leq \text{CORR}_y \leq 0.95 \\
              %\quad & 0.10 \leq \text{CORR}_z \leq 0.50 \label{eq:iw2:lastdvar} \text{.}
%\end{align}
%%
%We try to match the beam to measurements from the real machine by minimizing
  %the sum of $N$ squared measurement ($m_{d,s}$ at a given position
  %$s$) errors for rmx beam size in each dimensions.
%The design variables (\ref{eq:iw2:fistdvar}) - (\ref{eq:iw2:lastdvar}) define
  %the correlation matrix used when generating particles, e.g., R51, R52, R61,
  %R62 describe limits of correlations between planes.
%The initial Binomial distribution (with $m = ?$) has the form
%%
%\begin{equation*}
  %\frac{1}{2\pi\sigma_x\sigma_y}exp(-\frac{x^2}{2\sigma_x^2}
  %-\frac{y^2}{2\sigma_y^2})
  %\text{.}
%\end{equation*}
%%

%Since these correlations cannot be measured we get the real values by solving
  %the inverse problem mentioned above.

%Currently we run the simulations on a low resolution space charge grid ($8
  %\times 8 \times 8$) as a proof of concept.
%In a next step a simple Python script would be applied to iteratively rerun
  %the optimizer with increasing space-charge resolution when the limits of the
  %design variables are narrow enough (iteratively diminishing search space).

### 2018-01-09 paper/figures/car-trade-off.tex
towards production

\coordinate (y) at (0,3.8);
\coordinate (x) at (3.8,0);
\draw[<->] (y) node[above] {$f_2$} -- (0,0) --  (x) node[right]
{$f_1$};
\node[below=0.05cm] at (1.9, 0.0) {price};
\node[rotate=90, above=0.05cm] at (0.0, 1.9) {performance};

\path
  coordinate (start) at (0.5,0.5)
  coordinate (c1) at +(1.5,3)
  coordinate (c2) at +(2.5,3.1)
  coordinate (top) at (3.3,3.3);

\draw [thick, blue!60!white] (start) .. controls (c1) and (c2) .. (top);

\filldraw [black] (0.5, 0.0) circle (1pt) node[below, black] {\footnotesize{low}};
\filldraw [black] (0.0, 0.5) circle (1pt) node[left, black] {\footnotesize{low}};
\draw[dashed, thick] (start) -- (0.5, 0,0);
\draw[dashed, thick] (start) -- (0.0, 0.5);

\filldraw [black] (3.3, 0.0) circle (1pt) node[below, black] {\footnotesize{high}};
\filldraw [black] (0.0, 3.3) circle (1pt) node[left, black] {\footnotesize{high}};
\draw[dashed, thick] (top) -- (3.3, 0,0);
\draw[dashed, thick] (top) -- (0.0, 3.3);

\filldraw [red!60!white]
(start) circle (2pt) node[above left, black] {$x_0^*$}
(0.96,1.5) circle (2pt) node[above left, black] {$x_1^*$}
(1.68,2.5) circle (2pt) node[above left, black] {$x_2^*$}
(top) circle (2pt) node[above left, black] {$x_3^*$};

\filldraw [green!60!white] (1.62,1.43) rectangle (1.74,1.56) node[right, black] {$x_4$};
\draw[dashed, thick] (1.68,1.5) -- (0.96,1.5);
\draw[dashed, thick] (1.68,1.5) -- (1.68,2.5);

### 2018-03-04 code/setup.sh
small changes to run single simulation case

@@ -2,6 +2,8 @@
 rm -rf results
 rm -rf tmp
 mkdir tmp results
+export TIME=00:30:00
+export QUEUE=knlall
 export TEMPLATES=`pwd`/tmpl/
 export FIELDMAPS=/lcrc/project/AWA-beam-dynamics/FieldFiles/DriveFiles
-
+export OPAL_EXE_PATH=/home/neveu/software/opal-1.9/knl/bin

### 2018-03-04 paper/figures/opt-framework-layout.tex

\node (optimizers) [draw, text centered,
    text width=6.5em, fill=red, fill opacity=0.1, minimum height=12em,
    rounded corners, very thick, draw=red!60, text opacity=1.0]
    {};
\path (0.0, 1.8) node {\textsc{Optimizers}};

\draw [dashed, very thick, draw=red!90!white]
  (-0.4,0.6) circle (14pt) node {$O_1$};
\draw [dashed, very thick, draw=red!90!white]
  (0.2,-0.9) circle (14pt) node {$O_i$};

\path (optimizers.east)+(1.5,0.0) node (pilot) [draw, text centered,
    text width=6.5em, fill=brown, fill opacity=0.1, minimum height=12em,
    rounded corners, very thick, draw=brown, text opacity=1.0]
    {};
\path (2.8, 1.8) node {\textsc{Pilot}};

\path (3.5, 1.35) node [text width=3em]{job};
\path (3.5, 1.05) node [text width=3em]{queue};
\draw [thick, draw=brown!90!white] (3.0,0.5) rectangle (3.4,0.9);
\draw [thick, draw=brown!90!white] (2.6,0.5) rectangle (3.0,0.9);
\draw [thick, draw=brown!90!white] (2.2,0.5) rectangle (2.6,0.9);
\draw [thick, draw=brown!90!white] (1.8,0.5) rectangle (2.2,0.9);
\path (2.0, 0.7) node {$j_2$};
\path (3.2, 0.7) node {$j_1$};
\path (2.4, 0.7) node {$j_3$};
\path (2.8, 0.7) node {$j_4$};

\draw [thick, draw=brown!90!white] (2.2,-1.2) rectangle (2.6,-1.6);
\path (2.4, -1.4) node {$r_1$};

\path (pilot.east)+(1.5,0.0) node (workers) [draw, text centered,
    text width=6.5em, fill=orange, fill opacity=0.1, minimum height=12em,
    rounded corners, very thick, draw=orange, text opacity=1.0]
    {};
\path (5.5, 1.8) node {\textsc{Workers}};

\draw [dashed, very thick, draw=orange!90!white]
  (5.8,0.8) circle (9pt) node {$W_1$};
\draw [dashed, very thick, draw=orange!90!white]
  (5.8,-0.9) circle (9pt) node {$W_j$};

% o2 short path
\path[dotted, thick, ->] (0.5,-0.9) edge [bend right] (2.0, 0.5);

% o2 path
\path[cyan, dashed, thick, ->] (0.5,-1.0) edge [bend right] (3.2, 0.5);
\path[cyan, dashed, thick, ->] (3.2,0.5)  edge [bend right] (5.5, -0.8);
\path[cyan, dashed, thick, ->] (5.5,-0.8) edge [bend left] (2.6, -1.4);
\path[cyan, dashed, thick, ->] (2.2,-1.4) edge [bend left] (0.65, -1.05);

%o1 paths
\path[dotted, thick, ->] (-0.1,1.0) edge [bend left] (2.4, 0.9);
\path[dotted, thick, ->] (-0.1,1.0) edge [bend left] (2.8, 0.9);

### 2018-03-04 code/setup.sh
cleanup

@@ -1,7 +1,4 @@
 # general of opal
-rm -rf results
-rm -rf tmp
-mkdir tmp results
 export TIME=00:30:00
 export QUEUE=knlall
 export TEMPLATES=`pwd`/tmpl/

### 2018-03-04 code/setup.sh
cleanup

@@ -1,7 +1,0 @@
-# general of opal
-rm -rf results
-rm -rf tmp
-mkdir tmp results
-export TEMPLATES=`pwd`/tmpl/
-export FIELDMAPS=/lcrc/project/AWA-beam-dynamics/FieldFiles/DriveFiles
-

### 2018-03-04 paper/figures/opt-framework_code.tex

\node (ML) [draw, text centered,
    text width=12.8em, fill=red!60, fill opacity=0.1, minimum height=2em,
    rounded corners, very thick, draw=red!60, text opacity=1.0]
    {\textsc{Optimizer}};

\path (ML.north)+(-1.38,0.8) node (optimizer) [draw, text centered,
    text width=5em, fill=brown, fill opacity=0.1, minimum height=2em,
    rounded corners, very thick, draw=brown, text opacity=1.0]
    {\textsc{Pilot}};

\path[<->, very thick] (optimizer.east)+(.0,-0.2) edge [bend left] (ML.north);

\path (optimizer)+(-2.5,.8) node (input) [draw, text
    width=2em, fill=olive!60, fill opacity=0.1, minimum height=2em,
    text opacity=1.0] {\tiny{-\\ -\\ input}};
\path (optimizer)+(-2.5,-.4) node (obj) [draw, text
    width=2em, fill=olive!60, fill opacity=0.1, minimum height=2em,
    text opacity=1.0] {\tiny{-\\ -\\ obj}};
\path (optimizer)+(-2.5,-1.6) node (constr) [draw, text
    width=2em, fill=olive!60, fill opacity=0.1, minimum height=2em,
    text opacity=1.0] {\tiny{-\\ -\\ constr}};
\path [<-, very thick] (optimizer.west)+(.0,0.2) edge (input.east);
\path [<-, very thick] (optimizer.west) edge (obj.east);
\path [<-, very thick] (optimizer.west)+(.0,-0.2) edge (constr.east);

\path (optimizer)+(2.0,0.8) node (sims) [draw, text
    width=2em, fill=orange!60, fill opacity=0.1, minimum height=2em,
    text opacity=1.0] {\tiny{-\\ -\\ sims}};

\path (sims.east)+(1.8,0.6) node (opal) [draw, text centered,
    text width=6em, fill=orange, fill opacity=0.1, minimum height=2em,
    rounded corners, very thick, draw=orange, text opacity=1.0]
    {\textsc{Simulation}};

\path[<->, very thick] (optimizer.east) edge [bend right] (sims.south);
\path[<->, very thick] (sims.east) edge [bend left] (opal.west);

\path (ML.south)+(-1.30,-1.8) node (convex) [draw, text centered,
    text width=5em, fill=blue!60, fill opacity=0.1, minimum height=2em,
    rounded corners, thick, draw=blue!60, text opacity=1.0]
    {\footnotesize{Convex Optimization Algorithms}};

\path (ML.south)+(1.30,-1.8) node (heuristic) [draw, text centered, text
    width=5em, fill=blue!60, fill opacity=0.1, minimum height=4em,
    rounded corners, thick, draw=blue!60, text opacity=1.0]
    {\footnotesize{Heuristic Algorithms}};

\path[<->, very thick] (convex.north)+(+0.8,0.0) edge [bend right] (ML.south);
\path[<->, very thick] (heuristic.north)+(-0.8,0.0) edge [bend left] (ML.south);

### 2018-03-06 code/setup.sh
input generation # changes

@@ -1,6 +1,8 @@
 # general of opal
-export TIME=00:30:00
+rm -rf results *.0 *_0
+rm -rf tmp
+mkdir tmp results
 export QUEUE=knlall
 export TEMPLATES=`pwd`/tmpl/
 export FIELDMAPS=/lcrc/project/AWA-beam-dynamics/FieldFiles/DriveFiles
-export OPAL_EXE_PATH=/home/neveu/software/opal-1.9/knl/bin
+export OPAL_EXE_PATH=/lcrc/project/AWA-beam-dynamics/software/opal/opal-1.9/build-knl/src

### 2018-03-15 paper/paper.tex
starting to update paper

@@
 
-\author{Y. Ineichen\footnotemark[2]\ \footnotemark[3]\ \footnotemark[4]
+\author{N. Neveu\footnotemark[7]\ \footnotemark[8]
+  \and Y. Ineichen\footnotemark[2]\ \footnotemark[3]\ \footnotemark[4]
   \and A. Adelmann\footnotemark[2]\ \footnotemark[6]
@@
 \footnotetext[5]{University of Huddersfield, West Yorkshire, United Kingdom}
+\footnotetext[1]{Illinois Institute of Technology, Chicago, USA}
+\footnotetext[8]{Argonne National Laboratory, Lemont, USA}
 \footnotetext[6]{Corresponding author: \url{andreas.adelmann@psi.ch}}
@@
 We introduce the employed forward-solver in Section~\ref{sec:forward-solver}.
-A validation and a proof of concept application of a beam dynamics problem is
+A validation and a proof of concept application in two beam dynamics problems is
   discussed in Section~\ref{sec:experiments}.
@@
 
-The authors thank the \textsc{SwissFEL} team for contributing to the
+The authors thank the \textsc{SwissFEL} and AWA teams for contributing to the
   formulation of optimization problems.
-
+We gratefully acknowledge the computing resources provided on Bebop, a high-performance computing cluster operated by the Laboratory Computing Resource Center at Argonne National Laboratory.
 \appendix

### 2018-03-15 paper/theor-experiment.tex
starting to update paper

@@
 {\footnotesize \begin{verbatim}
-    rmsx:  OBJECTIVE, EXPR="fromFile("rms_x-err.dat", "var")";
-    emitx: OBJECTIVE, EXPR="fromFile("emit_x-err.dat", "var")";
-    match: OBJECTIVE, EXPR="fabs(fromFile("emit_x-peak.dat", "var") -
-                                 fromFile("rms_x-peak.dat", "var"))";
+    rmsx:  OBJECTIVE, EXPR="statVariableAt("rms_x-err.dat", "var")";
+    emitx: OBJECTIVE, EXPR="statVariableAt("emit_x-err.dat", "var")";
+    match: OBJECTIVE, EXPR="fabs(statVariableAt("emit_x-peak.dat", "var") -
+                                 statVariableAt("rms_x-peak.dat", "var"))";
 \end{verbatim}}
@@
 
-\subsection{Optimization Results}
+\subsubsection{Optimization Results}
 
@@
   %design variables are narrow enough (iteratively diminishing search space).
+
+\subsection{AWA}
+Next we apply the optimization framework to an ongoing project in accelerator physics.
+The model is taken from the Argonne Wakefield Accelerator facility, which 
+houses two rf photoinjector beam lines. We consider the high charge beam line
+that consists of an rf photocathode gun, two solenoids, six linear accelerating cavities, 
+and
+
+\subsubsection{AWA Optimization Results}

### 2018-03-15 paper/paper.tex
updating framework fig
changes to intro and layout figure

@@
   \and A. Adelmann\footnotemark[2]\ \footnotemark[6]
-  \and A. Kolano\footnotemark[2]\ \footnotemark[5]
+  \and P. Arbenz\footnotemark[4]
   \and C. Bekas\footnotemark[3]
   \and A. Curioni\footnotemark[3]
-  \and P. Arbenz\footnotemark[4]
+  \and A. Kolano\footnotemark[2]\ \footnotemark[5]
+  \and C. Kraus
 }
@@
 \begin{center}\normalsize
+
+	\pgfdeclarelayer{background}
+	\pgfsetlayers{background,main}
   \begin{tikzpicture}[text=black]%[scale=0.95, transform shape]
@@
 
-Here, we will focus on a real world application arising from PSI's
-  \textsc{SwissFEL}~\cite{pedr:10} activities, which have an immediate and a
-  long-range impact, by optimizing important parameters of PSI's \textsc{250
-  MeV injector} test facility (and later for the full PSI \textsc{SwissFEL}).
+Here, we will focus on a real world applications arising from Paul Scherrer Institut's (PSI)
+  \textsc{SwissFEL}~\cite{pedr:10} activities, and a high charge photoinjector 
+  at the Argonne Wakefield Accelerator (AWA). Both of which have an immediate and a
+  long-range impact, by optimizing important parameters for rf photoinjectors.
 

### 2018-03-15 paper/paper.tex
added sentence on optimizer being in OPAL
starting to add awa parameters

@@
   particle accelerators.
+  The framework is also integrated into \textsc{OPAL} so that users can 
+  define optimization problems within an input file, requiring no 
+  additional knowledge or installation of the API to use it.
+
 By abiding to the API from Listing 3 it becomes trivial to add new forward
@@
 The authors thank the \textsc{SwissFEL} and AWA teams for contributing to the
-  formulation of optimization problems.
-We gratefully acknowledge the computing resources provided on Bebop, a high-performance computing cluster operated by the Laboratory Computing Resource Center at Argonne National Laboratory.
+  formulation of optimization problems. We gratefully acknowledge the computing resources provided on Bebop, a HPC cluster operated by the LCRC at ANL.
 \appendix

### 2018-03-15 paper/theor-experiment.tex
starting to add awa parameters

@@
 
-\subsection{Ferrario Matching Point}
+\subsection{Ferrario Matching Point}\label{ferrario}
 
@@
 
-\subsection{AWA}
-Next we apply the optimization framework to an ongoing project in accelerator physics.
-The model is taken from the Argonne Wakefield Accelerator facility, which 
-houses two rf photoinjector beam lines. We consider the high charge beam line
-that consists of an rf photocathode gun, two solenoids, six linear accelerating cavities, 
-and
+\subsection{AWA Photoinjector Optimization}
+Next we apply the optimization framework to the high charge beam line at the AWA, 
+which consists of an rf photocathode gun, two solenoids, six linear accelerating cavities, 
+followed by four quadrupoles. This beam line has served as the injector for Two Beam 
+Acceleration (TBA) experiments in the past [XX], and will be used in the future for 
+similar experiments. One of the main constraints on prior experimental 
+results was the beam size and emittance as the beam passed through small aperture 
+wakefield structures. In an attempt to maximize charge transmission in future experiments
+we optimize several parameters in the gun and quadrupole leading into the 
+TBA section of the beam line.
+
+Compared to the Ferrario experiment in Section \ref{ferrario}, 
+this problem is larger by a factor of two in both design variables and objectives.
+The problem is also less predictable, meaning there is not a clear idea
+before hand where the pareto front will fall. This work is also meaningful in that
+it will guide future operations at the AWA.
+
+The design variables include both solenoid current, IBF and IM,
+the gun phase, GPHASE, and the laser full width half maximum in 
+the longitudinal direction. The definition of the design variables 
+was included in the OPAL input file:
+\vspace{0.2cm}
+{\footnotesize \begin{verbatim}
+// Gun variables
+dv0: DVAR, VARIABLE="IBF",    LOWERBOUND=350.0, UPPERBOUND=500.0;
+dv1: DVAR, VARIABLE="IM",     LOWERBOUND=170.0, UPPERBOUND=260.0;
+dv2: DVAR, VARIABLE="GPHASE", LOWERBOUND=-30.0, UPPERBOUND=0.0;
+dv3: DVAR, VARIABLE="FWHM",   LOWERBOUND=1.5,   UPPERBOUND=10.0;
+
+// Quad variables
+dv4: DVAR, VARIABLE="KQ1", LOWERBOUND=-8.0, UPPERBOUND=8.0;
+dv5: DVAR, VARIABLE="KQ2", LOWERBOUND=-8.0, UPPERBOUND=8.0;
+dv6: DVAR, VARIABLE="KQ3", LOWERBOUND=-8.0, UPPERBOUND=8.0;
+dv7: DVAR, VARIABLE="KQ4", LOWERBOUND=-8.0, UPPERBOUND=8.0;
+
+	\end{verbatim}}
+\vspace{0.2cm}
+
+ \vspace{0.2cm}
+ {\footnotesize \begin{verbatim}
+rmss1:  OBJECTIVE,EXPR="fabs(statVariableAt('rms_s',16.45))";
+rmsx1:  OBJECTIVE,EXPR="fabs(statVariableAt('rms_x',16.45))";
+emitx1: OBJECTIVE,EXPR="fabs(statVariableAt('emit_x',16.45))";
+
+rmss2:  OBJECTIVE,EXPR="fabs(statVariableAt('rms_s',18.45))";
+rmsx2:  OBJECTIVE,EXPR="fabs(statVariableAt('rms_x',18.45))";
+emitx2: OBJECTIVE,EXPR="fabs(statVariableAt('emit_x',18.45))";
+
+de1:    OBJECTIVE,EXPR="fabs(statVariableAt('dE',16.45))";
+
+	\end{verbatim}}
+\vspace{0.2cm}
+
+All simulations for this experiment were carried out on Bebop a
+high performance computing (HPC)
+cluster provided by the Laboratory Computing Resource Center (LCRC)
+at Argonne National Laboratory (ANL). We used Intel Knights Landing 
+(KNL) processors at 1.3 GHz with 128 GB of memory per node, 
+and 64 cores per node. There are 352 compute nodes available on 
+Bebop, with a total of 22528 cores. 
+This allows for very large optimization jobs, like the AWA case.
+
+OPAL-T was used as the forward solver, and a study on time step and 
+number of particles was done to reduce the time to simulation while 
+maintaining the physics of interest. We choose ten thousand particles 
+in combination with adjusting the time step near sensitive elements (i.e. quadurpoles). 
+The resulting simulations are low fidelity, but closely approximate 
+the mid fidelity simulations for metrics of interest, as shown in Fig. \ref{tstep}.
+\begin{figure}\ref{tstep}
+	\centering
+	%\includegraphics[width=0.8\linewidth]{Report/}
+	\caption{Comparison of different fidelity models.}
+	\label{tstep}
+\end{figure}
+
+As in Section \ref{ferrario}, 
+we also have to define several beam line parameters that 
+are not included in the optimization design variables above.
+These
 

### 2018-03-16 paper/theor-experiment.tex
putting in first figure

@@
 the longitudinal direction. The definition of the design variables 
-was included in the OPAL input file:
+was included in the OPAL input file, 
+As in Section \ref{ferrario}, 
+we also have to define several beam line parameters that 
+are not included in the optimization design variables above.
+These are shown in Table \ref{awatable}.
+
+\begin{align}
+\text{min}  \quad & \text{rms}_{x, s1}, \quad \text{rms}_{x, s2} \label{eq:awa:p1}\\
+& \text{rms}_{s, s1}, \quad \text{rms}_{s, s2} \label{eq:awa:p2}\\
+& \varepsilon_{x,s1}, \quad \varepsilon_{x,s2} \label{eq:awa:p3} \\
+\text{subject to} \quad & q = 200 \left[\text{pC}\right] \label{eq:awa:firstconstr}\\
+\quad & \text{Volt}_{\text{RF}} = 100 \left[\text{MV/m}\right] \label{eq:awa:lastconstr}\\
+\quad & \sigma_{L} \leq \sigma_x = \sigma_y \leq \sigma_{U} \label{eq:awa:firstdvar}\\
+\quad & \text{KS}_{L} \leq \text{KS}_{\text{RF}} \leq \text{KS}_{U} \label{eq:awa:seconddvar}\\
+\quad & \text{LAG}_{L} \leq \text{LAG}_{\text{RF}} \leq \text{LAG}_{U} \\
+\quad & \Delta z_{L\text{KS}} \leq \Delta z_{\text{KS}} \leq \Delta z_{U\text{KS}} \label{eq:awa:lastdvar}
+\end{align}
+
 \vspace{0.2cm}
@@
 number of particles was done to reduce the time to simulation while 
-maintaining the physics of interest. We choose ten thousand particles 
-in combination with adjusting the time step near sensitive elements (i.e. quadurpoles). 
+maintaining the physics of interest. All jobs were run and compared 
+on 8 cores to take advantage of the KNL, by running 8 jobs per node.
+After comparing several options we choose ten thousand particles 
+in combination with adjusting the time step near sensitive elements 
+(i.e. quadurpoles, dipole). 
 The resulting simulations are low fidelity, but closely approximate 
-the mid fidelity simulations for metrics of interest, as shown in Fig. \ref{tstep}.
-\begin{figure}\ref{tstep}
+the mid fidelity simulations for metrics of interest, as shown in 
+Fig. \ref{tstep}.
+
+\begin{table}[h!]
+	\begin{center}
+		\caption{Low and mid fidelity simulation parameters.}
+		\label{fidelity}
+		\begin{tabular}{l ccc}
+			\hline\noalign{\smallskip}
+			 & Number of particles & Time step (seconds) & Time to simulation (minutes)\\
+			\noalign{\smallskip}\hline\noalign{\smallskip}
+			low fidelity  			&  10,000   & $5 \times10^{-11}$  &  2.6 \\
+			mid fidelity 			&  100,000  & $1 \times 10^{-12}$ &  \\
+			adjusted low fidelity  	&  10,000   & $2 \times 10^{-12}$, $1 \times 10^{-11}$ & 1.5 \\
+			\noalign{\smallskip}\hline
+		\end{tabular}
+	\end{center}
+\end{table}
+
+\begin{figure}
 	\centering
-	%\includegraphics[width=0.8\linewidth]{Report/}
+	\includegraphics[width=0.8\linewidth]{Report/timestep_comparison}
 	\caption{Comparison of different fidelity models.}
@@
 
-As in Section \ref{ferrario}, 
-we also have to define several beam line parameters that 
-are not included in the optimization design variables above.
-These
-
 \subsubsection{AWA Optimization Results}

### 2018-03-16 paper/theor-experiment.tex
more changes to awa section of paper

@@
   solutions that have their emittance and rms peak locations at the same
-  $z$-coordinate.
-Equations (\ref{eq:swissfel:firstconstr}) and (\ref{eq:swissfel:lastconstr})
+  $s$-coordinate.
+Equations (\ref{eq:swissfel:firstconstr}) and (\ref{eq:swissfel:firstdvar})
   define constraints for initial conditions for the simulation: charge,
   gun voltage and laser spot size.
-Design variables given in (\ref{eq:swissfel:firstdvar}) to
+Design variables given in (\ref{eq:swissfel:seconddvar}) to
   (\ref{eq:swissfel:lastdvar}) correspond to field strengths of the
@@
 Both trackers agree within acceptable limits \cite{chao:99}.
-
 \begin{figure}
@@
 TBA section of the beam line.
+\begin{figure}
+	\centering
+	\includegraphics[width=0.9\linewidth]{Report/awa-drawing}
+	\caption{High charge beam line layout at the AWA.}
+	\label{awa-pic}
+\end{figure}
 
 Compared to the Ferrario experiment in Section \ref{ferrario}, 
-this problem is larger by a factor of two in both design variables and objectives.
-The problem is also less predictable, meaning there is not a clear idea
-before hand where the pareto front will fall. This work is also meaningful in that
+we increase the number of design variables and objectives by a factor of two.
+The problem is also less predictable, due to the large number of design variables
+and nonlinear effects such as space charge, there is not a definite idea
+before hand where the Pareto front will fall. This work is also meaningful in that
 it will guide future operations at the AWA.
 
-The design variables include both solenoid current, IBF and IM,
-the gun phase, GPHASE, and the laser full width half maximum in 
-the longitudinal direction. The definition of the design variables 
-was included in the OPAL input file, 
-As in Section \ref{ferrario}, 
-we also have to define several beam line parameters that 
-are not included in the optimization design variables above.
-These are shown in Table \ref{awatable}.
+We define the AWA optimization problem using objectives, and parameters given in 
+equations (\ref{eq:awa:p1}) to (\ref{eq:awa:lastdvar}).
 
@@
 & \varepsilon_{x,s1}, \quad \varepsilon_{x,s2} \label{eq:awa:p3} \\
-\text{subject to} \quad & q = 200 \left[\text{pC}\right] \label{eq:awa:firstconstr}\\
-\quad & \text{Volt}_{\text{RF}} = 100 \left[\text{MV/m}\right] \label{eq:awa:lastconstr}\\
+\text{subject to} \quad & q = 40 \left[\text{nC}\right] \label{eq:awa:firstconstr}\\
+\quad & \text{Volt}_{\text{Gun}} = 64\left[\text{MV/m}\right] \label{eq:awa:lastconstr}\\
+\quad & \text{Volt}_{\text{Linac}} = 24-25\left[\text{MV/m}\right] \\
 \quad & \sigma_{L} \leq \sigma_x = \sigma_y \leq \sigma_{U} \label{eq:awa:firstdvar}\\
@@
 \end{align}
+
+The first four objectives minimize the transverse ($rms_x$) and longitudinal ($rms_s$) 
+beam sizes at to locations of interest in the beam line, [$s_1$,$s_2$]. 
+These are the longitudinal positions of 
+the entrance of the kicker and exit of the kicker. The beam size needs to be minimized
+here to prevent scraping and ensure transmission through the wakefield structures 
+following the kicker. The last two objectives (\ref{eq:awa:p3}) minimize the 
+transverse emittance, which favors less divergence in the beam.
 

### 2018-03-16 paper/theor-experiment.tex
fixed table

@@
 
-\begin{table}[h!]
+\begin{table}%[h!]
 \begin{center}
@@
 
-\begin{figure}[h!]
+\begin{figure}%[h!]
   \centering
@@
 Both trackers agree within acceptable limits \cite{chao:99}.
+
 \begin{figure}
   \centering
-  \includegraphics[width=0.8\linewidth]{Report/iff_plot_emrms_ettt}
+  \includegraphics[width=0.9\linewidth]{Report/iff_plot_emrms_ettt}
   \caption{Comparison 3D-tracker versus envelope-tracker in case for rms$_{x}$
@@
   %design variables are narrow enough (iteratively diminishing search space). 
-
+%\vspace{-7em}
 \subsection{AWA Photoinjector Optimization}
@@
 which consists of an rf photocathode gun, two solenoids, six linear accelerating cavities, 
-followed by four quadrupoles. This beam line has served as the injector for Two Beam 
-Acceleration (TBA) experiments in the past [XX], and will be used in the future for 
-similar experiments. One of the main constraints on prior experimental 
-results was the beam size and emittance as the beam passed through small aperture 
-wakefield structures. In an attempt to maximize charge transmission in future experiments
+followed by four quadrupoles and a stripline kicker, as shown in Fig. \ref{awa-pic}. 
+Portions of this beam line served as the injector for Two Beam 
+Acceleration (TBA) experiments in the past [X1], and will be used for 
+similar experiments in the future [X2]. Main constraints on prior experimental 
+results were the beam size and emittance as the beam passed through small aperture 
+wakefield structures located after the quadrupoles. 
+In an attempt to maximize charge transmission in upcoming experiments
 we optimize several parameters in the gun and quadrupole leading into the 
 TBA section of the beam line.
+%\vspace{-1em}
+
 \begin{figure}
@@
 
+\vspace{-1em}
 Compared to the Ferrario experiment in Section \ref{ferrario}, 
 we increase the number of design variables and objectives by a factor of two.
-The problem is also less predictable, due to the large number of design variables
+The problem is also less predictable, due to the increased number of design variables
 and nonlinear effects such as space charge, there is not a definite idea
@@
 
-We define the AWA optimization problem using objectives, and parameters given in 
-equations (\ref{eq:awa:p1}) to (\ref{eq:awa:lastdvar}).
-
 \begin{align}
-\text{min}  \quad & \text{rms}_{x, s1}, \quad \text{rms}_{x, s2} \label{eq:awa:p1}\\
-& \text{rms}_{s, s1}, \quad \text{rms}_{s, s2} \label{eq:awa:p2}\\
-& \varepsilon_{x,s1}, \quad \varepsilon_{x,s2} \label{eq:awa:p3} \\
+\text{min}  \quad & \text{rms}_{x, s_1}, \quad \text{rms}_{x, s_2} \label{eq:awa:p1}\\
+& \text{rms}_{s, s_1}, \quad \text{rms}_{s, s_2} \label{eq:awa:p2}\\
+& \varepsilon_{x,s_1}, \quad \varepsilon_{x,s_2} \label{eq:awa:p3} \\
+& dE \label{eq:awa:p4} \\
 \text{subject to} \quad & q = 40 \left[\text{nC}\right] \label{eq:awa:firstconstr}\\
@@
 \quad & \text{Volt}_{\text{Linac}} = 24-25\left[\text{MV/m}\right] \\
-\quad & \sigma_{L} \leq \sigma_x = \sigma_y \leq \sigma_{U} \label{eq:awa:firstdvar}\\
-\quad & \text{KS}_{L} \leq \text{KS}_{\text{RF}} \leq \text{KS}_{U} \label{eq:awa:seconddvar}\\
-\quad & \text{LAG}_{L} \leq \text{LAG}_{\text{RF}} \leq \text{LAG}_{U} \\
-\quad & \Delta z_{L\text{KS}} \leq \Delta z_{\text{KS}} \leq \Delta z_{U\text{KS}} \label{eq:awa:lastdvar}
+\quad & \sigma_x = \sigma_y = 9 \left[\text{mm}\right] \label{eq:awa:firstdvar}\\
+\quad & \phi_{\text{linac}} =0 \label{eq:awa:lastdvar}
 \end{align}
@@
 The first four objectives minimize the transverse ($rms_x$) and longitudinal ($rms_s$) 
-beam sizes at to locations of interest in the beam line, [$s_1$,$s_2$]. 
-These are the longitudinal positions of 
-the entrance of the kicker and exit of the kicker. The beam size needs to be minimized
+beam sizes at two locations of interest in the beam line ($s_1$,$s_2$). 
+These are the longitudinal positions at the entrance of the kicker and 
+$1[\text{m}]$ after the exit of the kicker. The beam size needs to be minimized
 here to prevent scraping and ensure transmission through the wakefield structures 
-following the kicker. The last two objectives (\ref{eq:awa:p3}) minimize the 
-transverse emittance, which favors less divergence in the beam.
+following the kicker. The next two objectives (\ref{eq:awa:p4}) minimize the 
+transverse emittance, which favors less divergence in the beam and reduces 
+emittance growth during transport. The last objective (\ref{eq:awa:p4}), 
+minimizes energy spread in the bunch at the entrance of the kicker, $s_1$.  
+This helps reduce emittance and beam size growth in the kicker.  
+Equations (\ref{eq:awa:firstconstr}) to
+(\ref{eq:awa:lastdvar}) define the charge, gun voltage, linac voltages, 
+laser radius and linac cavity phases. These are parameters in the simulation 
+that must be defined, but do not vary during the optimization.
+
+%\vspace{-1em}
+As introduced in Section \ref{ferrario}, we define the AWA optimization problem 
+objectives, and design variables in the OPAL input file as shown in
+the following code: %equations (\ref{eq:awa:p1}) to (\ref{eq:awa:lastdvar}).
 
@@
 
-	\end{verbatim}}
-\vspace{0.2cm}
-
- \vspace{0.2cm}
- {\footnotesize \begin{verbatim}
+	// Objectives
 	rmss1:  OBJECTIVE,EXPR="fabs(statVariableAt('rms_s',16.45))";
@@
 	emitx1: OBJECTIVE,EXPR="fabs(statVariableAt('emit_x',16.45))";
-
+	de1:    OBJECTIVE,EXPR="fabs(statVariableAt('dE',16.45))";	
 	rmss2:  OBJECTIVE,EXPR="fabs(statVariableAt('rms_s',18.45))";
@@
 
-de1:    OBJECTIVE,EXPR="fabs(statVariableAt('dE',16.45))";
-
 	\end{verbatim}}
 \vspace{0.2cm}
+
+Design variables include the currents in two gun solenoids (IBF and IM), 
+the gun phase (GPHASE), the laser longitudinal full width half max (FWHM), 
+and four quadrupole strengths (KQ1-KQ2). The objectives include
+beam size, emittance, and energy spread as
+defined in Eqs. (\ref{eq:awa:p1}) to (\ref{eq:awa:p4}). 
+The s location at the entrance of the kicker is $s_1=16.45[\text{m}]$, 
+and the s location of interest after the kicker is $s_1=18.45[\text{m}]$.
 
@@
 at Argonne National Laboratory (ANL). We used Intel Knights Landing 
-(KNL) processors at 1.3 GHz with 128 GB of memory per node, 
+(KNL) processors at 1.3 GHz with 128 GB of memory 
 and 64 cores per node. There are 352 compute nodes available on 
-Bebop, with a total of 22528 cores. 
+Bebop, with a total of 22,528 cores. 
 This allows for very large optimization jobs, like the AWA case.
 
-OPAL-T was used as the forward solver, and a study on time step and 
+OPAL was used as the forward solver, and a study on time step and 
 number of particles was done to reduce the time to simulation while 
 maintaining the physics of interest. All jobs were run and compared 
-on 8 cores to take advantage of the KNL, by running 8 jobs per node.
+on 8 cores each, which allowed 8 jobs per node on the KNL.
+The grid size was $16 \times 16 \times 32$, 
+and parallelized in the x and y directions.
 After comparing several options we choose ten thousand particles 
 in combination with adjusting the time step near sensitive elements 
-(i.e. quadurpoles, dipole). 
+(i.e. quadurpoles, kicker). 
 The resulting simulations are low fidelity, but closely approximate 
@@
 Fig. \ref{tstep}.
-
-\begin{table}[h!]
-	\begin{center}
-		\caption{Low and mid fidelity simulation parameters.}
-		\label{fidelity}
-		\begin{tabular}{l ccc}
-			\hline\noalign{\smallskip}
-			 & Number of particles & Time step (seconds) & Time to simulation (minutes)\\
-			\noalign{\smallskip}\hline\noalign{\smallskip}
-			low fidelity  			&  10,000   & $5 \times10^{-11}$  &  2.6 \\
-			mid fidelity 			&  100,000  & $1 \times 10^{-12}$ &  \\
-			adjusted low fidelity  	&  10,000   & $2 \times 10^{-12}$, $1 \times 10^{-11}$ & 1.5 \\
-			\noalign{\smallskip}\hline
-		\end{tabular}
-	\end{center}
-\end{table}
 
@@
 
+\begin{table}%[h!]
+	\begin{center}
+		\caption{Low and mid fidelity simulation parameters.}
+		\label{fidelity}
+
+		\begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} C c D }
+			\hline\noalign{\smallskip}
+			& Number of particles & dT (seconds) & Time to simulation (minutes)\\
+			\noalign{\smallskip}\hline\noalign{\smallskip}
+			low fidelity  			&  10,000   & $5 \times10^{-11}$  &  2.6 \\
+			adjusted low fidelity  	&  10,000   & $2 \times 10^{-12}$, $1 \times 10^{-11}$ & 1.6 \\
+			mid fidelity 			&  100,000  & $1 \times 10^{-12}$ &  18\\
+			\noalign{\smallskip}\hline
+		\end{tabular*}
+	\end{center}
+\end{table}
+
 \subsubsection{AWA Optimization Results}

### 2018-03-18 paper/theor-experiment.tex
adding awa drawing"

@@
 %\vspace{-7em}
-\subsection{AWA Photoinjector Optimization}
+\subsection{AWA Photoinjector Optimization} \label{awaproblem}
 Next we apply the optimization framework to the high charge beam line at the AWA, 
@@
 and 64 cores per node. There are 352 compute nodes available on 
-Bebop, with a total of 22,528 cores. 
-This allows for very large optimization jobs, like the AWA case.
+Bebop, with a total of 22,528 cores. All jobs were run and compared 
+on 8 cores each, which allowed 8 jobs per node on the KNL.
+This in combination with the amount of nodes available 
+allows for very large optimization jobs, like the AWA case.
 
-OPAL was used as the forward solver, and a study on time step and 
+A study on time step and 
 number of particles was done to reduce the time to simulation while 
-maintaining the physics of interest. All jobs were run and compared 
-on 8 cores each, which allowed 8 jobs per node on the KNL.
+maintaining the physics of interest. 
 The grid size was $16 \times 16 \times 32$, 
@@
 the mid fidelity simulations for metrics of interest, as shown in 
-Fig. \ref{tstep}.
+Fig. \ref{tstep}. For all models, the longitudinal parameters (rms$_s$ and energy) 
+are calculated correctly, but we see discrepancies in the transverse 
+rms$_x$ and $\epsilon_x$ in the low fidelity results. A summary of 
+the parameters used is listed in Table \ref{fidelity}.
 
@@
 		\label{fidelity}
-
 		\begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} C c D }
@@
 \subsubsection{AWA Optimization Results}
+Given the parameters and variable boundaries in Section \ref{awaproblem}, 
+four 50 generation optimization experiments were done with varying GA parameters. 
+Similar to the time step scan, the goal was to determine which set of optimization
+parameters strongly influence the results, and whether there was a time to solution
+difference. (NOTE FOR EDIT: May need to take this out, or compare at 50 generations, none of these runs finished 100 gens)
+
+\vspace{0.2cm}
+{\footnotesize\begin{verbatim}
+OPTIMIZE, INPUT="tmpl/optLinac_40nC.tmpl",
+	OUTPUT="optLinac_40nC",
+	OUTDIR="results",
+	OBJECTIVES = {rmss1, rmsx1, emitx1, de1, rmss2, rmsx2, emitx2},
+	DVARS = {dv0, dv1, dv2, dv3, dv4, dv5, dv6, dv7},
+	CONSTRAINTS = {c1, c2},
+	INITIALPOPULATION=656,
+	MAXGENERATIONS=200,
+	NUM_MASTERS=1,
+	NUM_COWORKERS=8,
+	SIMTMPDIR="tmp",
+	TEMPLATEDIR="tmpl",
+	FIELDMAPDIR="fieldmaps",
+	NUM_IND_GEN=328,
+	GENE_MUTATION_PROBABILITY=0.8,
+	MUTATION_PROBABILITY=0.8,
+	RECOMBINATION_PROBABILITY=0.2;
+QUIT;
+\end{verbatim}}

### 2018-03-19 paper/theor-experiment.tex
updated figure and intro awa text

@@
 \vspace{-1em}
-Compared to the Ferrario experiment in Section \ref{ferrario}, 
-we increase the number of design variables and objectives by a factor of two.
-The problem is also less predictable, due to the increased number of design variables
-and nonlinear effects such as space charge, there is not a definite idea
+We also chose this model to demonstrate the frameworks ability to tackle larger problems.
+The number of design variables is eight, and the number of objectives is seven.
+This problem is also less predictable, due to the high dimensionality 
+and nonlinear effects such as space charge. There is not a definite idea
 before hand where the Pareto front will fall. This work is also meaningful in that
@@
 \quad & \sigma_x = \sigma_y = 9 \left[\text{mm}\right] \label{eq:awa:firstdvar}\\
-\quad & \phi_{\text{linac}} =0 \label{eq:awa:lastdvar}
+\quad & \phi_{\text{linac}} =0^\circ \label{eq:awa:lastdvar}
 \end{align}

### 2018-04-09 makemldb.py
making db's from json files

@@ -1,0 +1,41 @@
+import sys, os
+#sys.path.insert(0, '/lcrc/project/AWA-beam-dynamics/software/pyOPALTools/')
+#sys.path.insert(0, '/lcrc/project/AWA-beam-dynamics/software/pyOPALTools/db/')
+#sys.path.insert(0, '/lcrc/project/AWA-beam-dynamics/software/pyOPALTools/utilities/')
+from db import mldb
+''' 
+We create a Pickle file from a number of OPAL 
+simulations using the format from runOPAL.py
+
+The content of the file is
+
+ y = f (x)  
+
+'''
+
+#baseFN = 'rand_sample'
+#root   = "/lcrc/project/AWA-beam-dynamics/surrogatemodels/random_sample/surrogate_models_rand_sample_bounds2"
+
+baseFN = ['ex-1', 'ex-2', 'ex-3', 'ex-4']
+#root   = "/lcrc/project/AWA-beam-dynamics/surrogatemodels/ga-model/results"
+#root   = "./ex-4/results"
+
+#baseFN = 'paper-pc'
+#root   = "/lcrc/project/AWA-beam-dynamics/surrogatemodels/pc-models/paper-pc-model/data/"
+
+#yNames = ['s','numParticles','rms_x','rms_y','rms_s','emit_x','emit_y','emit_s','energy','dE']
+#dbw    = mldb.mldb()
+
+#Build from stat files
+#dbw.buildFromSDDS(baseFN, root, yNames)
+#dbw.printOverview()
+
+#Build from json files
+#dbw.build(baseFN, root)
+#dbw.printOverview()
+
+#Make bounded db
+for ex in baseFN:
+    pickle = ex+'.pk'
+    mldb.buildBounded(pickle, ex)
+

### 2018-04-09 makemldb.py
making db for first paper run

@@ -1,7 +1,7 @@
 import sys, os
-#sys.path.insert(0, '/lcrc/project/AWA-beam-dynamics/software/pyOPALTools/')
-#sys.path.insert(0, '/lcrc/project/AWA-beam-dynamics/software/pyOPALTools/db/')
-#sys.path.insert(0, '/lcrc/project/AWA-beam-dynamics/software/pyOPALTools/utilities/')
+sys.path.insert(0, '/lcrc/project/AWA-beam-dynamics/software/pyOPALTools/')
+sys.path.insert(0, '/lcrc/project/AWA-beam-dynamics/software/pyOPALTools/db/')
+sys.path.insert(0, '/lcrc/project/AWA-beam-dynamics/software/pyOPALTools/utilities/')
 from db import mldb
 ''' 
 We create a Pickle file from a number of OPAL 
@@ -16,26 +16,25 @@ The content of the file is
 #baseFN = 'rand_sample'
 #root   = "/lcrc/project/AWA-beam-dynamics/surrogatemodels/random_sample/surrogate_models_rand_sample_bounds2"
 
-baseFN = ['ex-1', 'ex-2', 'ex-3', 'ex-4']
-#root   = "/lcrc/project/AWA-beam-dynamics/surrogatemodels/ga-model/results"
+baseFN = 'paper-run-1' #['ex-1', 'ex-2', 'ex-3', 'ex-4']
+root   = "/lcrc/project/AWA-beam-dynamics/Nicole/awa-tba/paper-run-1/results"
 #root   = "./ex-4/results"
 
-#baseFN = 'paper-pc'
-#root   = "/lcrc/project/AWA-beam-dynamics/surrogatemodels/pc-models/paper-pc-model/data/"
-
 #yNames = ['s','numParticles','rms_x','rms_y','rms_s','emit_x','emit_y','emit_s','energy','dE']
-#dbw    = mldb.mldb()
+dbw    = mldb.mldb()
 
 #Build from stat files
 #dbw.buildFromSDDS(baseFN, root, yNames)
 #dbw.printOverview()
 
 #Build from json files
-#dbw.build(baseFN, root)
-#dbw.printOverview()
+dbw.build(baseFN, root)
+dbw.printOverview()
 
 #Make bounded db
-for ex in baseFN:
-    pickle = ex+'.pk'
-    mldb.buildBounded(pickle, ex)
+#for ex in baseFN:
[…]

### 2018-04-09 makemldb.py
fixed bounded db

@@ -15,26 +15,26 @@ The content of the file is
 
 #baseFN = 'rand_sample'
 #root   = "/lcrc/project/AWA-beam-dynamics/surrogatemodels/random_sample/surrogate_models_rand_sample_bounds2"
-
-baseFN = 'paper-run-1' #['ex-1', 'ex-2', 'ex-3', 'ex-4']
-root   = "/lcrc/project/AWA-beam-dynamics/Nicole/awa-tba/paper-run-1/results"
+path    = './databases/'
+baseFN  = ['ex-1', 'ex-2', 'ex-3', 'ex-4']
+#root   = "/lcrc/project/AWA-beam-dynamics/Nicole/awa-tba/paper-run-1/results"
 #root   = "./ex-4/results"
 
 #yNames = ['s','numParticles','rms_x','rms_y','rms_s','emit_x','emit_y','emit_s','energy','dE']
-dbw    = mldb.mldb()
+#dbw    = mldb.mldb()
 
 #Build from stat files
 #dbw.buildFromSDDS(baseFN, root, yNames)
 #dbw.printOverview()
 
 #Build from json files
-dbw.build(baseFN, root)
-dbw.printOverview()
+#dbw.build(baseFN, root)
+#dbw.printOverview()
 
 #Make bounded db
-#for ex in baseFN:
-#    pickle = ex+'.pk'
-#    mldb.buildBounded(pickle, ex)
-pickle = baseFN+'.pk'
-mldb.buildBounded(pickle, baseFN)
+for ex in baseFN:
+    pickle = path+ ex+'.pk'
+    mldb.buildBounded(pickle, ex)
+#pickle = baseFN+'.pk'
+#mldb.buildBounded(pickle, baseFN)
 

### 2018-04-09 parallel_coord_plots.py

@@ -1,135 +1,0 @@
-import numpy as np
-import sys
-import json
-import plotly
-import plotly.plotly as py
-import plotly.graph_objs as go
-import OptPilotJsonReader as optreader
-
-import matplotlib
-matplotlib.use("Agg")
-import matplotlib.pyplot as plt
-import matplotlib.animation as manimation
-
-#def parallelPlot(jsondir, )
-
-ex1   = "/home/nicole/Documents/surrogatemodels/ga-model/results/"
-#ex1    = "./ex-1/results/"
-nobj  = 7#4
-ndvar = 7#8
-cols  = nobj + ndvar + 1 #extra 1 for ID number
-
-# 1. Find all .json files of a directory, e.g. "./"
-optjson = optreader.OptPilotJsonReader(ex1)
-n = optjson.getNumOfGenerations()
-#print(n)
-diff       = 0
-count      = 0
-count2     = 0
-badpoints  = 0
-goodpoints = 0
-
-test     = np.zeros((1,13))
-for gen in range(1,n+1):
-#if True:
-#    gen = n 
-    try:
-        optjson.readGeneration(gen)
-
-        ns = optjson.getIDs()
-        #print(np.size(ns))
-        print('Generation #: ', gen)
-        print('Num of individuals: ', np.size(ns))
-        count = count+1
-        #print('first check:', np.size(ns), cols)
-        data = np.zeros((np.size(ns), cols))
-        #print("individual: ", np.size(indiv)) 
-        ##print('Total num of gens: ', count)
-        dvars = optjson.getDesignVariables()
-        #print ( "Design variables: ", dvars)
-        #print ( "number of design variables", np.size(dvars))
-        objs = optjson.getObjectives()
-        #print ( "Objectives: ", objs)
-        #print ( "number of objectives", np.size(objs))
-
-        for i, simid in enumerate(ns):
-            #Load add data in 1 generation into data array
-            # The data array is N rows X M columns
-            # N = number of simulations in generation
-            # M = number of davars + objs + 1 (for ID number)
-            #print(i)
-            indiv = optjson.getIndividualWithID(simid)
-            if (-10.0 <= indiv[5] <= 0.0) & (-10.0 <= indiv[6] <= 0.0) & (60 <= indiv[0] <= 75) & (15 <= indiv[1] <= 25) & (400 <= indiv[2] <= 550) & (180 <= indiv[3] <= 280) & (0.001 <= indiv[4] <= 0.004):
-                #print('ok') 
[…]

### 2018-04-10 paper/theor-experiment.tex
starting plots for paper

@@
 Given the parameters and variable boundaries in Section \ref{awaproblem}, 
-four 50 generation optimization experiments were done with varying GA parameters. 
-Similar to the time step scan, the goal was to determine which set of optimization
+four optimization experiments were done with varying GA parameters, see Table \ref{extable}.
+From here on, we will reference each experiment as ex-1, ex-2, ex-3 and ex-4. 
+They were each allowed to run for twenty four hours. 
+Similar to the time step scan, the goal of this exercise was to determine which set of optimization
 parameters strongly influence the results, and whether there was a time to solution
-difference. (NOTE FOR EDIT: May need to take this out, or compare at 50 generations, none of these runs finished 100 gens)
+difference.
+
+\begin{table}%[h!]
+	\begin{center}
+		\caption{Input Parameters for initial twenty four hour AWA optimization experiments. 
+			The gene mutation probability was equal to the mutation probability (not shown) in all four experiments.}
+		\label{extable}
+		\begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} C C D }
+			\hline\noalign{\smallskip}
+			& Gene Mutation Probability & Recombination Probibility & Number of completed generations \\
+			\noalign{\smallskip}\hline\noalign{\smallskip}
+			ex-1 &  0.1  & 0.9  &  96 \\
+			ex-2 &  0.3  & 0.7  &  81 \\
+			ex-3 &  0.8  & 0.2  &  53 \\
+			ex-4 &  0.01 & 0.09 &  95 \\
+			\noalign{\smallskip}\hline
+		\end{tabular*}
+	\end{center}
+\end{table}
+
+After collection of all data, the Pareto front of each data set was plotted.
 

### 2018-04-10 expareto.py

@@ -1,0 +1,90 @@
+import sys, os
+import numpy as np
+import pickle as pick
+import matplotlib.pyplot as plt
+from db import mldb
+
+def doscale(vals):
+    smax = np.max(vals)
+    smin = np.min(vals)
+    scaled_vals = (vals - smin)/smax
+    return (scaled_vals)    
+
+def pareto(x, y):
+    #Making holders for my pareto fronts            
+    pareto_y = []
+    pareto_x = [] 
+    pdvars   = [] 
+    w  = np.arange(0,1.001, 0.001)
+    sx = doscale(x)
+    sy = doscale(y)
+    #Finding best point with respect to all weights (w)
+    for i in range(0, len(w)):
+        fobj     = sy * w[i] + sx *(1-w[i])
+        wmins    = np.where(fobj==min(fobj))[0][0]
+        pareto_y = np.append(pareto_y, y[wmins])
+        pareto_x = np.append(pareto_x, x[wmins])
+        pdvars   = np.append(pdvars, dvars[wmins, :])
+    return(pareto_x, pareto_y)#, pdvars)
+
+#def getx(pareto, allx, ally):
+#    return(xvals)
+    
+
+root = './databases/'
+baseFN = ['ex-1-bounded', 'ex-2-bounded','ex-3-bounded','ex-4-bounded']
+style  = ['k--', 'y.-', 'b-.','m.-'] 
+alpha  = [1.0, 0.7, 0.7, 0.7]
+plt.rc('text', usetex=True)
+plt.rc('font', family='serif')
+
+for i, fn in enumerate(baseFN):   
+    nn = root+fn+'.pk' 
+    #Read database and loop through generations:
+    dbr       = mldb.mldb()
+    dbr.load(nn)
+    #dvars = dbr.getXNames()
+    ovals = dbr.getYNames()
+    print(ovals)
+    gens  = dbr.getNumberOfSamples()
+    #Read all data at once:
+    with open(nn, 'rb') as f:
+        dbr = pick.load(f, encoding='latin1')
+
+    allx = dbr[gens+1]['allDvarValues']
+    ally = dbr[gens+1]['allObjValues']
+    print(np.shape(allx), np.shape(ally))
+    emitx1  = np.array(ally[:,0])
+    emitx2  = np.array(ally[:,1])
+    rmss1   = np.array(ally[:,2])
[…]

### 2018-04-10 parallel-from-db.py

@@ -1,0 +1,131 @@
+import numpy as np
+import sys, os
+import plotly
+import plotly.plotly as py
+import plotly.graph_objs as go
+from db import mldb
+import pickle as pick
+
+baseFN = './databases/ex-1-bounded' #paper-run-1-bounded'
+dbr    = mldb.mldb()
+dbr.load(baseFN+'.pk')
+
+dvars = dbr.getXNames()
+ovals = dbr.getYNames()
+gens  = dbr.getNumberOfSamples()
+
+dbr.printOverview()
+
+xvals = [] 
+for gen in range(0,gens):
+    nsims = dbr.getSampleSize(i=gen)
+    print(nsims) #len(dbr[gen]['dvarValues'])
+    for x in range(0,nsims):
+        #print(x)
+        xsim = dbr.getDVarVec(gen,x)
+        ysim = dbr.getObjVec(gen,x)
+        xvals.append(xsim)
+print(np.shape(xvals))
+
+with open(baseFN+'.pk', 'rb') as f:
+    dbr = pick.load(f, encoding='latin1')
+
+allx = dbr[gens+1]['allDvarValues']
+ally = dbr[gens+1]['allObjValues']
+
+print(np.shape(allx), np.shape(ally))
+#        #print('Generation #: ', gen)
+#        #print('Num of individuals: ', np.size(ns))
+#        #print('first check:', np.size(ns), cols)
+#        data = np.zeros((np.size(ns), cols))
+#        #print("individual: ", np.size(indiv)) 
+#        ##print('Total num of gens: ', count)
+#        dvars = optjson.getDesignVariables()
+#        #print ( "Design variables: ", dvars)
+#        #print ( "number of design variables", np.size(dvars))
+#        objs = optjson.getObjectives()
+#        #print ( "Objectives: ", objs)
+#        #print ( "number of objectives", np.size(objs))
+#
+#        print('reader:', np.shape(dvarsall), np.shape(objsall))
+#        for i, simid in enumerate(ns):
+#            #Load add data in 1 generation into data array
+#            # The data array is N rows X M columns
+#            # N = number of simulations in generation
+#            # M = number of davars + objs + 1 (for ID number)
+#            #print(i)
+#            indiv = optjson.getIndividualWithID(simid)
[…]

### 2018-04-10 readmldb.py
read database

@@ -1,0 +1,58 @@
+import sys, os
+import numpy as np
+import pickle as pick
+
+sys.path.insert(0, '/lcrc/project/AWA-beam-dynamics/software/pyOPALTools/')
+sys.path.insert(0, '/lcrc/project/AWA-beam-dynamics/software/pyOPALTools/db/')
+sys.path.insert(0, '/lcrc/project/AWA-beam-dynamics/software/pyOPALTools/utilities/')
+from db import mldb
+
+baseFN = './databases/paper-run-1-bounded'#'rand_sample'
+
+#Read database and loop through generations:
+dbr       = mldb.mldb()
+dbr.load(baseFN+'.pk')
+dvars = dbr.getXNames()
+ovals = dbr.getYNames()
+gens  = dbr.getNumberOfSamples()
+
+dbr.printOverview()
+
+xvals = []
+yvals = [] 
+for gen in range(0,gens):
+    nsims = dbr.getSampleSize(i=gen)
+    #print(nsims) #len(dbr[gen]['dvarValues'])
+    for x in range(0,nsims):
+        #print(x)
+        xsim = dbr.getDVarVec(gen,x)
+        ysim = dbr.getObjVec(gen,x)
+        xvals.append(xsim)
+print(dvars, np.shape(xvals))
+xvals = np.array(xvals)
+for j in range(0, len(dvars)):
+        print('Now printing bounds of good points:')
+        print("max of "+ dvars[j] + '= '+ str(np.max(xvals[:,j])))
+        print("min of "+ dvars[j] + '= '+ str(np.min(xvals[:,j])))
+        print('\n')
+
+#Read all data at once:
+with open(baseFN+'.pk', 'rb') as f:
+    dbr = pick.load(f, encoding='latin1')
+
+allx = dbr[gens+1]['allDvarValues']
+ally = dbr[gens+1]['allObjValues']
+
+print(np.shape(allx), np.shape(ally))
+
+
+#z       = np.zeros([dbr.getSampleSize()])
+#numpart = np.zeros([dbr.getSampleSize()])
+#
+#for i in range(dbr.getSampleSize()):
+#    z[i]       = dbr.getObjVec(0,i)[0]
+#    numpart[i] = dbr.getObjVec(0,i)[1]
+#    if numpart[i] != 1e4:
+#        print(numpart[i])
+#    if z[i] < 3.15:
+#        print(z[i]) 

### 2018-04-11 expareto.py
cleaning up pareto plots

@@ -3,33 +3,8 @@ import numpy as np
 import pickle as pick
 import matplotlib.pyplot as plt
 from db import mldb
-
-def doscale(vals):
-    smax = np.max(vals)
-    smin = np.min(vals)
-    scaled_vals = (vals - smin)/smax
-    return (scaled_vals)    
-
-def pareto(x, y):
-    #Making holders for my pareto fronts            
-    pareto_y = []
-    pareto_x = [] 
-    pdvars   = [] 
-    w  = np.arange(0,1.001, 0.001)
-    sx = doscale(x)
-    sy = doscale(y)
-    #Finding best point with respect to all weights (w)
-    for i in range(0, len(w)):
-        fobj     = sy * w[i] + sx *(1-w[i])
-        wmins    = np.where(fobj==min(fobj))[0][0]
-        pareto_y = np.append(pareto_y, y[wmins])
-        pareto_x = np.append(pareto_x, x[wmins])
-        pdvars   = np.append(pdvars, dvars[wmins, :])
-    return(pareto_x, pareto_y)#, pdvars)
-
-#def getx(pareto, allx, ally):
-#    return(xvals)
-    
+from visualize import scaleData
+from visualize import pareto 
 
 root = './databases/'
 baseFN = ['ex-1-bounded', 'ex-2-bounded','ex-3-bounded','ex-4-bounded']
@@ -61,13 +36,13 @@ for i, fn in enumerate(baseFN):
 
     #emittance vs rmss
     dvars = np.array(allx)
-    (prmss1, pemitx1) = pareto(rmss1, emitx1)
-    (prmss2, pemitx2) = pareto(rmss2, emitx2)
+    (prmss1, pemitx1, pdvars) = pareto(rmss1, emitx1, allx)
+    (prmss2, pemitx2, pdvars) = pareto(rmss2, emitx2, allx)
     
     print(np.shape(prmss1)) #, np.shape(pdvars1))
     ex = fn.split('-')[1]
     #Plotting
-    plot =1 
+    plot =0 
     if plot == 0:
         plt.plot(prmss1*10**3, pemitx1*10**6, style[i], alpha=alpha[i], label='ex-'+ex)
     else:

### 2018-04-11 parallel-from-db.py

@@ -5,35 +5,68 @@ import plotly.plotly as py
 import plotly.graph_objs as go
 from db import mldb
 import pickle as pick
+from visualize import scaleData
+from visualize import pareto
+import matplotlib.pyplot as plt
+import pandas as pd
 
-baseFN = './databases/ex-1-bounded' #paper-run-1-bounded'
-dbr    = mldb.mldb()
-dbr.load(baseFN+'.pk')
+plt.rc('text', usetex=True)
+plt.rc('font', family='serif') 
 
-dvars = dbr.getXNames()
-ovals = dbr.getYNames()
-gens  = dbr.getNumberOfSamples()
+root = './databases/'
+baseFN = ['ex-1-bounded', 'ex-2-bounded','ex-3-bounded','ex-4-bounded']
 
-dbr.printOverview()
+for i, fn in enumerate(baseFN):
+    nn  = root+fn+'.pk'
+    dbr = mldb.mldb()
+    dbr.load(nn)
+    dvars = dbr.getXNames()
+    ovals = dbr.getYNames()
+    gens  = dbr.getNumberOfSamples()
+    #dbr.printOverview()
 
-xvals = [] 
-for gen in range(0,gens):
-    nsims = dbr.getSampleSize(i=gen)
-    print(nsims) #len(dbr[gen]['dvarValues'])
-    for x in range(0,nsims):
-        #print(x)
-        xsim = dbr.getDVarVec(gen,x)
-        ysim = dbr.getObjVec(gen,x)
-        xvals.append(xsim)
-print(np.shape(xvals))
+    with open(nn, 'rb') as f: 
+        dbr = pick.load(f, encoding='latin1')   
 
-with open(baseFN+'.pk', 'rb') as f:
-    dbr = pick.load(f, encoding='latin1')
+    allx  = dbr[gens+1]['allDvarValues'] 
+    ally  = dbr[gens+1]['allObjValues'] 
+    dvars = np.array(allx)
+    emitx1  = np.array(ally[:,0])
+    emitx2  = np.array(ally[:,1])
+    rmss1   = np.array(ally[:,2])
+    rmss2   = np.array(ally[:,3])
 
-allx = dbr[gens+1]['allDvarValues']
-ally = dbr[gens+1]['allObjValues']
+    (px, py, pd) = pareto(rmss1, emitx1, dvars)
+    #(prmss2, pemitx2, pdvars) = pareto(rmss2, emitx2, dvars)
 
[…]

### 2018-04-11 parallel-from-db.py
parallel plots for pareto front

@@ -20,9 +20,9 @@ for i, fn in enumerate(baseFN):
     nn  = root+fn+'.pk'
     dbr = mldb.mldb()
     dbr.load(nn)
-    dvars = dbr.getXNames()
-    ovals = dbr.getYNames()
-    gens  = dbr.getNumberOfSamples()
+    dvars  = dbr.getXNames()
+    onames = dbr.getYNames()
+    gens   = dbr.getNumberOfSamples()
     #dbr.printOverview()
 
     with open(nn, 'rb') as f: 
@@ -30,26 +30,63 @@ for i, fn in enumerate(baseFN):
 
     allx  = dbr[gens+1]['allDvarValues'] 
     ally  = dbr[gens+1]['allObjValues'] 
-    dvars = np.array(allx)
     emitx1  = np.array(ally[:,0])
     emitx2  = np.array(ally[:,1])
     rmss1   = np.array(ally[:,2])
     rmss2   = np.array(ally[:,3])
 
-    (px, py, pd) = pareto(rmss1, emitx1, dvars)
+    (px, py, pd) = pareto(rmss1, emitx1, allx)
     #(prmss2, pemitx2, pdvars) = pareto(rmss2, emitx2, dvars)
 
     print(np.shape(px), np.shape(py), np.shape(pd))
-#    xvals = []
-#    for y in prmss1: 
-#        p = np.where(prmss1==y)[0][0]
-#        xvals = np.append(xvals, dvars[p, :])
-#
-#    print(np.shape(xvals))
+    pardata = [go.Parcoords(
+                line = dict(color = 'blue'),
+                dimensions = list([
+                    dict(#range = [1.5,10],
+                         label = dvars[0], values = pd[:,0]),
+                    
+                    dict(#range = [-30,0],
+                         label = dvars[1], values = pd[:,1]),
+                    
+                    dict(#range = [200,500],
+                         #tickvals = [1.5,3,4.5],
+                         label = dvars[2], values = pd[:,2]),
 
-#    xvals = [] 
+                    dict(#range = [170,260],
+                         #tickvals = [1,2,4,5],
+                         label = dvars[3], values = pd[:,3]),
+                         #ticktext = ['text 1', 'text 2', 'text 3', 'text 4']),
+
+                    dict(#range = [1.5,10],
+                         label = dvars[4], values = pd[:,4]),
+                    
+                    dict(#range = [-30,0],
+                         label = dvars[5], values = pd[:,5]),
+                    
+                    dict(#range = [200,500],
[…]

### 2018-04-11 paper/theor-experiment.tex
paper changes

@@
 \subsubsection{AWA Optimization Results}
-Given the parameters and variable boundaries in Section \ref{awaproblem}, 
-four optimization experiments were done with varying GA parameters, see Table \ref{extable}.
-From here on, we will reference each experiment as ex-1, ex-2, ex-3 and ex-4. 
-They were each allowed to run for twenty four hours. 
-Similar to the time step scan, the goal of this exercise was to determine which set of optimization
-parameters strongly influence the results, and whether there was a time to solution
-difference.
-
+While the optimization problem and goals are well defined (Section \ref{awaproblem}), 
+it is not clear what the best input parameters for the NSGA-II are.
+These parameters include gene mutation probability, mutation probability, 
+recombination probability, number of individuals (initial and independent), and number of generations. 
+Given the beam line and design variables given in Section \ref{awaproblem}, 
+four optimization experiments were done with varying NSGA-II parameters, see Table \ref{extable}. 
 \begin{table}%[h!]
@@
 		\caption{Input Parameters for initial twenty four hour AWA optimization experiments. 
-			The gene mutation probability was equal to the mutation probability (not shown) in all four experiments.}
+			The gene mutation probability was equal to the mutation probability (not shown) in all four experiments. The number of individuals}
 		\label{extable}
@@
 \end{table} 
+From here on, we will reference each experiment as ex-1, ex-2, ex-3, and ex-4. 
+The initial number of individuals was fixed at 656, 
+and the number of independent individuals per generation was fixed at 328. 
+These numbers we in part based on the architecture of the KNL's. 
+Since each simulation takes 8 cores, and there are 64 cores per KNL node, 
+we wanted a large population size that would fit evenly on these resources. 
+We also reduced the number of objectives to the four most important for quicker evaluation of these tests.
+These objectives include: 
+$\epsilon_{x, s_1}\text{, } \epsilon_{x, s_2}\text{, } \text{rms}_{s, s_1}\text{, and }  \text{rms}_{s, s_2}$
+The optimization in the OPAL input file was defined as follows:
+\vspace{0.2cm}
+{\footnotesize \begin{verbatim}
+	dv0: DVAR, VARIABLE="IBF",    LOWERBOUND=200.0, UPPERBOUND=500.0;
+	dv1: DVAR, VARIABLE="IM",     LOWERBOUND=170.0, UPPERBOUND=260.0;
+	dv2: DVAR, VARIABLE="GPHASE", LOWERBOUND=-30.0, UPPERBOUND=0.0;
+	dv3: DVAR, VARIABLE="FWHM",   LOWERBOUND=1.5,   UPPERBOUND=10.0;
+
+	// Quad values
+	dv4: DVAR, VARIABLE="KQ1", LOWERBOUND=-8.0, UPPERBOUND=8.0;
+	dv5: DVAR, VARIABLE="KQ2", LOWERBOUND=-8.0, UPPERBOUND=8.0;
+	dv6: DVAR, VARIABLE="KQ3", LOWERBOUND=-8.0, UPPERBOUND=8.0;
+	dv7: DVAR, VARIABLE="KQ4", LOWERBOUND=-8.0, UPPERBOUND=8.0;
+
+	rmss1:  OBJECTIVE,EXPR="fabs(statVariableAt('rms_s',16.5))";
+	emitx1: OBJECTIVE,EXPR="fabs(statVariableAt('emit_x',16.5))";
+
+	rmss2:  OBJECTIVE,EXPR="fabs(statVariableAt('rms_s',18.5))";
+	emitx2: OBJECTIVE,EXPR="fabs(statVariableAt('emit_x',18.5))";
+	\end{verbatim}}
+\vspace{0.2cm}
+
+They were each allowed to run for twenty four hours. 
+Similar to the time step scan, the goal of this exercise was to determine which set of optimization
+parameters strongly influence the results, and whether there was a time to solution
+difference.
 

### 2018-04-11 parallel-from-db.py

@@ -52,22 +52,22 @@ for i, fn in enumerate(baseFN):
                          #tickvals = [1.5,3,4.5],
                          label = dvars[2], values = pd[:,2]),
 
-                    dict(#range = [170,260],
+                    dict(#range = [-8,8],
                          #tickvals = [1,2,4,5],
                          label = dvars[3], values = pd[:,3]),
                          #ticktext = ['text 1', 'text 2', 'text 3', 'text 4']),
 
-                    dict(#range = [1.5,10],
+                    dict(range = [-8,8],
                          label = dvars[4], values = pd[:,4]),
                     
-                    dict(#range = [-30,0],
+                    dict(range = [-8,8],
                          label = dvars[5], values = pd[:,5]),
                     
-                    dict(#range = [200,500],
+                    dict(range = [-8,8],
                          #tickvals = [1.5,3,4.5],
                          label = dvars[6], values = pd[:,6]),
 
-                    dict(#range = [170,260],
+                    dict(range = [-8,8],
                          #tickvals = [1,2,4,5],
                          label = dvars[7], values = pd[:,7]),
                          #ticktext = ['text 1', 'text 2', 'text 3', 'text 4']),

### 2018-04-11 paper/theor-experiment.tex
adding results

--- 2018-04-10 paper/theor-experiment.tex
@@
 \begin{align}
-\text{min}  \quad & \text{rms}_{x, s_1}, \quad \text{rms}_{x, s_2} \label{eq:awa:p1}\\
-& \text{rms}_{s, s_1}, \quad \text{rms}_{s, s_2} \label{eq:awa:p2}\\
-& \varepsilon_{x,s_1}, \quad \varepsilon_{x,s_2} \label{eq:awa:p3} \\
+\text{min}  \quad & \text{rms}_{x}\left(s = s_1\right), \quad \text{rms}_{x}\left(s = s_2\right) \label{eq:awa:p1}\\
+& \text{rms}_{s}\left(s = s_1\right), \quad \text{rms}_{s}\left(s = s_2\right), \label{eq:awa:p2}\\
+& \varepsilon_{x}\left(s = s_1\right), \quad \varepsilon_{x}\left(s = s_2\right), \label{eq:awa:p3} \\
 & dE \label{eq:awa:p4} \\
@@
 \subsubsection{AWA Optimization Results}
-Given the parameters and variable boundaries in Section \ref{awaproblem}, 
-four optimization experiments were done with varying GA parameters, see Table \ref{extable}.
-From here on, we will reference each experiment as ex-1, ex-2, ex-3 and ex-4. 
-They were each allowed to run for twenty four hours. 
-Similar to the time step scan, the goal of this exercise was to determine which set of optimization
-parameters strongly influence the results, and whether there was a time to solution
-difference.
-
+While the optimization problem and goals are well defined (Section \ref{awaproblem}), 
+it is not clear what the best input parameters for the NSGA-II are.
+These parameters include gene mutation probability, mutation probability, 
+recombination probability, number of individuals (initial and and for later generations), and number of generations to complete. 
+Given the beam line and design variables given in Section \ref{awaproblem}, 
+four optimization experiments were done with varying NSGA-II parameters. 
+Similar to the time step scan, 
+the goal of this exercise was to determine which set of optimization
+parameters strongly influence the results, 
+and whether there was a time to solution difference.
+From here on, we will reference each experiment as ex-1, ex-2, ex-3, and ex-4
+as shown in Table \ref{extable}. 
 \begin{table}%[h!]
@@
 
-After collection of all data, the Pareto front of each data set was plotted.
+The initial number of individuals was fixed at 656, 
+and the minimum number individuals in later generations was fixed at 328. 
+These numbers we in part based on the architecture of the KNL's. 
+Since each simulation takes 8 cores, and there are 64 cores per KNL node, 
+we wanted a large population size that would fit evenly on these resources. 
+Each experiment was allowed to run for twenty four hours, with 
+a max generation limit of 100. 
+We also reduced the six objectives to the four most important for quicker evaluation of these tests \nrnote{Q for Andreas, is it true less obj is faster}.
+The objectives include: 
+$\varepsilon_{x}\left(s = s_1\right)\text{, } \varepsilon_{x}\left(s = s_2\right)\text{, } \text{rms}_{s}\left(s = s_1\right)\text{, and }  \text{rms}_{s}\left(s = s_2\right)$. 
+The OPAL input file for ex-3 is given as an example:
 
 \vspace{0.2cm}
-{\footnotesize\begin{verbatim}
+{\footnotesize \begin{verbatim}
+	TITLE, STRING="ANL Optimisation";
+
+	// Gun variables
+	dv0: DVAR, VARIABLE="IBF",    LOWERBOUND=200.0, UPPERBOUND=500.0;
+	dv1: DVAR, VARIABLE="IM",     LOWERBOUND=170.0, UPPERBOUND=260.0;
+	dv2: DVAR, VARIABLE="GPHASE", LOWERBOUND=-30.0, UPPERBOUND=0.0;
+	dv3: DVAR, VARIABLE="FWHM",   LOWERBOUND=1.5,   UPPERBOUND=10.0;
+
+	// Quad variables
+	dv4: DVAR, VARIABLE="KQ1", LOWERBOUND=-8.0, UPPERBOUND=8.0;
+	dv5: DVAR, VARIABLE="KQ2", LOWERBOUND=-8.0, UPPERBOUND=8.0;
+	dv6: DVAR, VARIABLE="KQ3", LOWERBOUND=-8.0, UPPERBOUND=8.0;
+	dv7: DVAR, VARIABLE="KQ4", LOWERBOUND=-8.0, UPPERBOUND=8.0;
+
+	// Objectives
+	rmss1:  OBJECTIVE,EXPR="fabs(statVariableAt('rms_s',16.5))";
+	emitx1: OBJECTIVE,EXPR="fabs(statVariableAt('emit_x',16.5))";	
+	rmss2:  OBJECTIVE,EXPR="fabs(statVariableAt('rms_s',18.5))";
+	emitx2: OBJECTIVE,EXPR="fabs(statVariableAt('emit_x',18.5))";
+
 	OPTIMIZE, INPUT="tmpl/optLinac_40nC.tmpl",
@@
 	\end{verbatim}}
+\vspace{0.2cm}
+
+After collection of the data for all four experiments, several metrics
+were compared, including number of generations completed in twenty four hours,
+location of Pareto fronts at $s_1$ and $s_2$, and the design variables at the Pareto front. From Table \ref{extable}, we clearly see ex-3 is significantly 
+slower, as it evaluated about 30 to 40 fewer generations than the other experiments.
+Perhaps this trade off would be acceptable if the Pareto front was significantly 
+improved, but from Fig. \ref{expareto1}, we can see this is not the case.
+The Pareto fronts at $s_1$, are nearly identical. We could expect
+they would continue to converge given more time. 
+When looking at the Pareto front for $s_2$, we see ex-4 has a slight 
+edge over the others.  
+\begin{figure}
+	\centering
+	\begin{subfigure}{0.49\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{Report/ex-pareto1}
+		\caption{Pareto fronts at $s_1$.}
+		\label{exparetos1}
+	\end{subfigure}
+	\begin{subfigure}{0.49\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{Report/ex-pareto2}
+	\caption{Pareto fronts at $s_2$.}
+	\label{exparetos2}
+	\end{subfigure}
+	\caption{Comparison of Pareto fronts for initial experiments.}
+	\label{expareto}
+\end{figure}

### 2018-05-20 paper/paper.tex
fixed table
adding pareto plots
adding DOE in acknowledgments

@@
 \usetikzlibrary{plotmarks}
+\usepackage{subcaption}
 
@@
 
+\usepackage{array}
+\newcolumntype{C}{ >{\centering\arraybackslash} m{2.5cm} }
+\newcolumntype{D}{ >{\centering\arraybackslash} m{3cm} }
+
+\newcommand{\nrnote}[1]{\textsf{{\color{violet}{ NN note:}   #1 }}}
 \begin{document}
@@
   \and A. Kolano\footnotemark[2]\ \footnotemark[5]
-  \and C. Kraus
+  \and C. Metzger-Kraus 
 }
@@
 The authors thank the \textsc{SwissFEL} and AWA teams for contributing to the
-  formulation of optimization problems. We gratefully acknowledge the computing resources provided on Bebop, a HPC cluster operated by the LCRC at ANL.
+  formulation of optimization problems. 
+  We gratefully acknowledge the computing resources provided on Bebop,
+  a high performance computing cluster operated by the 
+  Labratory Computing Resource Center at Argonne National Laboratory.
+  This work was partly supported by the 
+  U.S. Department of Energy, Office of Science, under 
+  contract number DE-AC02-06CH11357 and grant number DE-SC0015479. 
 \appendix

### 2018-05-20 paper/theor-experiment.tex
small changes
adding DOE in acknowledgments

@@
 \subsection{AWA Photoinjector Optimization} \label{awaproblem}
-Next we apply the optimization framework to the high charge beam line at the AWA, 
-which consists of an rf photocathode gun, two solenoids, six linear accelerating cavities, 
-followed by four quadrupoles and a stripline kicker, as shown in Fig. \ref{awa-pic}. 
-Portions of this beam line served as the injector for Two Beam 
+Next we apply the optimization framework to the high charge beam line at the AWA. 
+As shown in Fig.  \ref{awa-pic}, this beam line consists of an rf photocathode gun, 
+two solenoids, six linear accelerating cavities, 
+followed by four quadrupoles and a stripline kicker. 
+This beam line has served as the injector for Two Beam 
 Acceleration (TBA) experiments in the past [X1], and will be used for 
@@
 
-\vspace{-1em}
+%\vspace{-1em}
 We also chose this model to demonstrate the frameworks ability to tackle larger problems.
@@
 Perhaps this trade off would be acceptable if the Pareto front was significantly 
-improved, but from Fig. \ref{expareto1}, we can see this is not the case.
+improved, but from Fig. \ref{expareto}, we can see this is not the case.
 The Pareto fronts at $s_1$, are nearly identical. We could expect
@@
 		\caption{Pareto fronts at $s_1$.}
-		\label{exparetos1}
+		\label{expareto1}
 	\end{subfigure}
@@
 	\caption{Pareto fronts at $s_2$.}
-	\label{exparetos2}
+	\label{expareto2}
 	\end{subfigure}
-	\caption{Comparison of Pareto fronts for initial experiments.}
+	\caption{Comparison of Pareto fronts for initial optimization experiments.}
 	\label{expareto}
 \end{figure}
+
+Next compare the design variables at each point on the 
+Pareto front.
+\begin{figure}
+	\centering
+	\begin{subfigure}{1\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{Report/ex-pareto1}
+		\caption{Pareto fronts at $s_1$.}
+		\label{bounds1}
+	\end{subfigure}
+	\begin{subfigure}{1\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{Report/ex-pareto2}
+		\caption{Pareto fronts at $s_2$.}
+		\label{bounds2}
+	\end{subfigure}
+	\caption{Comparison of design variables for each Pareto front.}
+	\label{bounds}
+\end{figure}

### 2018-05-20 paper/paper.tex
editing awa section 5.3

@@
 We introduce the employed forward-solver in Section~\ref{sec:forward-solver}.
-A validation and a proof of concept application in two beam dynamics problems is
-  discussed in Section~\ref{sec:experiments}.
+A validation and a proof of concept application in the two beam dynamics problems 
+mentioned above is discussed in Section~\ref{sec:experiments}.
 
@@
   We gratefully acknowledge the computing resources provided on Bebop,
-  a high performance computing cluster operated by the 
-  Labratory Computing Resource Center at Argonne National Laboratory.
+  a HPC cluster operated by the LCRC at ANL.
   This work was partly supported by the 
@@
 \bibliographystyle{abbrv}
-\bibliography{../../bibliography/phd}
+\bibliography{paper}
 

### 2018-05-20 paper/theor-experiment.tex
editing awa section 5.3

@@
 followed by four quadrupoles and a stripline kicker. 
-This beam line has served as the injector for Two Beam 
-Acceleration (TBA) experiments in the past [X1], and will be used for 
-similar experiments in the future [X2]. Main constraints on prior experimental 
-results were the beam size and emittance as the beam passed through small aperture 
+The charge of interest is 40 nC, and based on Two Beam 
+Acceleration (TBA) \cite{gai_power_jing_2012} experiments performed in the past 
+at AWA. Similar experiments will take place in the future and motivate this work. 
+Prior experimental results were limited by beam size and emittance as the beam passed through small aperture 
 wakefield structures located after the quadrupoles. 
 In an attempt to maximize charge transmission in upcoming experiments
-we optimize several parameters in the gun and quadrupole leading into the 
+we optimize several parameters in the gun and quadrupoles leading into the 
 TBA section of the beam line.
@@
 %\vspace{-1em}
-We also chose this model to demonstrate the frameworks ability to tackle larger problems.
+In addition to the physics challenges, we chose this model to demonstrate the frameworks ability to tackle large problems.
 The number of design variables is eight, and the number of objectives is seven.
-This problem is also less predictable, due to the high dimensionality 
-and nonlinear effects such as space charge. There is not a definite idea
-before hand where the Pareto front will fall. This work is also meaningful in that
+This problem encompasses high dimensionality 
+and nonlinear effects such as space charge. There is no existing information
+that accurately predicts where the Pareto front will fall. This work is also meaningful in that
 it will guide future operations at the AWA.
@@
 
-The first four objectives minimize the transverse ($rms_x$) and longitudinal ($rms_s$) 
-beam sizes at two locations of interest in the beam line ($s_1$,$s_2$). 
-These are the longitudinal positions at the entrance of the kicker and 
-$1[\text{m}]$ after the exit of the kicker. The beam size needs to be minimized
-here to prevent scraping and ensure transmission through the wakefield structures 
-following the kicker. The next two objectives (\ref{eq:awa:p4}) minimize the 
+The first four objectives, Eqs. (\ref{eq:awa:p1}) and (\ref{eq:awa:p2}),
+minimize the transverse ($rms_x$) and longitudinal ($rms_s$) 
+beam sizes at two locations of interest in the beam line ($s_1$,$s_2$);
+the longitudinal positions at the entrance of the kicker and 
+$1$ meter after the exit of the kicker. 
+Minimizing the beam size at these locations is essential to 
+to preventing scraping and ensuring transmission through the wakefield structures 
+following the kicker. The next two objectives (\ref{eq:awa:p3}) minimize the 
 transverse emittance, which favors less divergence in the beam and reduces 
 emittance growth during transport. The last objective (\ref{eq:awa:p4}), 
-minimizes energy spread in the bunch at the entrance of the kicker, $s_1$.  
+minimizes energy spread in the bunch at the entrance of the kicker at $s_1$.  
 This helps reduce emittance and beam size growth in the kicker.  
@@
 (\ref{eq:awa:lastdvar}) define the charge, gun voltage, linac voltages, 
-laser radius and linac cavity phases. These are parameters in the simulation 
+laser radius and linac cavity phases (in that order). These are parameters in the simulation 
 that must be defined, but do not vary during the optimization.
@@
 defined in Eqs. (\ref{eq:awa:p1}) to (\ref{eq:awa:p4}). 
-The s location at the entrance of the kicker is $s_1=16.45[\text{m}]$, 
-and the s location of interest after the kicker is $s_1=18.45[\text{m}]$.
+The location at the entrance of the kicker is $s_1=16.45$~meters, 
+and the location of interest after the kicker is $s_1=18.45$~meters.
 
@@
 Bebop, with a total of 22,528 cores. All jobs were run and compared 
-on 8 cores each, which allowed 8 jobs per node on the KNL.
+on 8 cores each, which allowed 8 jobs per node on the KNLs.
 This in combination with the amount of nodes available 
@@
 After comparing several options we choose ten thousand particles 
-in combination with adjusting the time step near sensitive elements 
+in combination with adjusting the time step (dT) near sensitive elements 
 (i.e. quadurpoles, kicker). 
@@
 are calculated correctly, but we see discrepancies in the transverse 
-rms$_x$ and $\epsilon_x$ in the low fidelity results. A summary of 
-the parameters used is listed in Table \ref{fidelity}.
+rms$_x$ and $\epsilon_x$ in the low fidelity results. 
+Average run time each simulation with the adjusted time steps was 1.6~minutes.
+In comparison the mid fidelity simulations ran for 18~minutes.
+%A summary of the parameters used is listed in Table \ref{fidelity}.
 
@@
 	\includegraphics[width=0.8\linewidth]{Report/timestep_comparison}
-	\caption{Comparison of different fidelity models.}
+	\caption{Comparison of different fidelity models (dT stands for time step).}
 	\label{tstep}
@@
 
+\iffalse
 \begin{table}%[h!]
@@
 \end{table}
+\fi
 
 \subsubsection{AWA Optimization Results}
-While the optimization problem and goals are well defined (Section \ref{awaproblem}), 
-it is not clear what the best input parameters for the NSGA-II are.
+While the optimization problem and goals were well defined (Section \ref{awaproblem}), 
+it was not clear what the best input parameters for the NSGA-II should be.
 These parameters include gene mutation probability, mutation probability, 
@@
 		\caption{Input Parameters for initial twenty four hour AWA optimization experiments. 
-			The gene mutation probability was equal to the mutation probability (not shown) in all four experiments. The number of individuals}
+			The gene mutation probability was equal to the mutation probability (not shown) in all four experiments. 
+			The max number of individuals per generation was~80.}
 		\label{extable}
@@
 a max generation limit of 100. 
-We also reduced the six objectives to the four most important for quicker evaluation of these tests \nrnote{Q for Andreas, is it true less obj is faster}.
+We also reduced the six objectives to the four most important for quicker evaluation of these tests 
+%\nrnote{Q for Andreas, is it true less obj is faster}.
 The objectives include: 

### 2018-05-22 paper-run-ex4/setup.sh
adding paper-run-ex4

@@ -1,0 +1,7 @@
+# general of opal
+rm -rf results *.0 *_0
+rm -rf tmp
+mkdir tmp results
+export QUEUE=knlall
+export TEMPLATES=`pwd`/tmpl/
+export TIME=01:00:00

### 2018-05-22 paper/theor-experiment.tex

@@
 Average run time each simulation with the adjusted time steps was 1.6~minutes.
-In comparison the mid fidelity simulations ran for 18~minutes.
+In comparison the mid fidelity simulations ran for 18~minutes each.
 %A summary of the parameters used is listed in Table \ref{fidelity}.
@@
 These parameters include gene mutation probability, mutation probability, 
-recombination probability, number of individuals (initial and and for later generations), and number of generations to complete. 
+recombination probability, number of individuals (initial and and for later generations), 
+and number of generations to complete. 
 Given the beam line and design variables given in Section \ref{awaproblem}, 
@@
 
-The initial number of individuals was fixed at 656, 
-and the minimum number individuals in later generations was fixed at 328. 
-These numbers we in part based on the architecture of the KNL's. 
-Since each simulation takes 8 cores, and there are 64 cores per KNL node, 
-we wanted a large population size that would fit evenly on these resources. 
+The maximum number of individuals per generation was fixed at 80, 
 Each experiment was allowed to run for twenty four hours, with 
-a max generation limit of 100. 
-We also reduced the six objectives to the four most important for quicker evaluation of these tests 
-%\nrnote{Q for Andreas, is it true less obj is faster}.
-The objectives include: 
-$\varepsilon_{x}\left(s = s_1\right)\text{, } \varepsilon_{x}\left(s = s_2\right)\text{, } \text{rms}_{s}\left(s = s_1\right)\text{, and }  \text{rms}_{s}\left(s = s_2\right)$. 
-The OPAL input file for ex-3 is given as an example:
+a maximum generation limit of 100. 
+We reduced the seven objectives to the four needed to construct 
+the Pareto fronts that would be the final goal of this study.
+The objectives include: $\varepsilon_{x}\left(s = s_1\right)\text{, } \varepsilon_{x}\left(s = s_2\right)\text{, } \text{rms}_{s}\left(s = s_1\right)\text{, and }  \text{rms}_{s}\left(s = s_2\right)$.
+The optimization parameters specific to OPAL input for ex-3 is given as an example.
+Note the design variables defined in Section \ref{awaproblem}
+precede the optimization parameters in the OPAL input file.
 
@@
 {\footnotesize \begin{verbatim}
-	TITLE, STRING="ANL Optimisation";
-
-	// Gun variables
-	dv0: DVAR, VARIABLE="IBF",    LOWERBOUND=200.0, UPPERBOUND=500.0;
-	dv1: DVAR, VARIABLE="IM",     LOWERBOUND=170.0, UPPERBOUND=260.0;
-	dv2: DVAR, VARIABLE="GPHASE", LOWERBOUND=-30.0, UPPERBOUND=0.0;
-	dv3: DVAR, VARIABLE="FWHM",   LOWERBOUND=1.5,   UPPERBOUND=10.0;
-
-	// Quad variables
-	dv4: DVAR, VARIABLE="KQ1", LOWERBOUND=-8.0, UPPERBOUND=8.0;
-	dv5: DVAR, VARIABLE="KQ2", LOWERBOUND=-8.0, UPPERBOUND=8.0;
-	dv6: DVAR, VARIABLE="KQ3", LOWERBOUND=-8.0, UPPERBOUND=8.0;
-	dv7: DVAR, VARIABLE="KQ4", LOWERBOUND=-8.0, UPPERBOUND=8.0;
-
-	// Objectives
-	rmss1:  OBJECTIVE,EXPR="fabs(statVariableAt('rms_s',16.5))";
-	emitx1: OBJECTIVE,EXPR="fabs(statVariableAt('emit_x',16.5))";	
-	rmss2:  OBJECTIVE,EXPR="fabs(statVariableAt('rms_s',18.5))";
-	emitx2: OBJECTIVE,EXPR="fabs(statVariableAt('emit_x',18.5))";
-
 	OPTIMIZE, INPUT="tmpl/optLinac_40nC.tmpl",
@@
 were compared, including number of generations completed in twenty four hours,
-location of Pareto fronts at $s_1$ and $s_2$, and the design variables at the Pareto front. From Table \ref{extable}, we clearly see ex-3 is significantly 
+Pareto fronts at $s_1$ and $s_2$, and the design variables at the Pareto front. 
+From Table \ref{extable}, we clearly see ex-3 is significantly 
 slower, as it evaluated about 30 to 40 fewer generations than the other experiments.
@@
 edge over the others.  
+\begin{figure}
+	\centering
+	\includegraphics[width=0.75\textwidth]{Report/ex-pareto1}%
+	\llap{\raisebox{1.8cm}{%  move next graphics to top right corner
+			\includegraphics[height=5.5cm]{Report/ex-pareto2}%
+	}}
+	\caption{My overlay figure.}
+\end{figure}
+
 \begin{figure}
@@
 \end{figure}
+
+The initial number of individuals was fixed at 656, 
+and the minimum number individuals in later generations was fixed at 328. 
+These numbers we in part based on the architecture of the KNL's. 
+Since each simulation takes 8 cores, and there are 64 cores per KNL node, 
+we wanted a large population size that would fit evenly on these resources.

### 2018-05-23 paper/theor-experiment.tex
using pyopaltools

@@
 edge over the others. 
-\begin{figure}
+\begin{figure}[h]
 	\centering
-	\includegraphics[width=0.75\textwidth]{Report/ex-pareto1}%
-	\llap{\raisebox{1.8cm}{%  move next graphics to top right corner
-			\includegraphics[height=5.5cm]{Report/ex-pareto2}%
-	}}
-	\caption{My overlay figure.}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\begin{subfigure}{0.49\textwidth}
+	\begin{subfigure}{0.8\textwidth}
 		\centering
@@
 	\end{subfigure}
-	\begin{subfigure}{0.49\textwidth}
+	\begin{subfigure}{0.8\textwidth}
 		\centering
@@
 \end{figure}
-
-Next compare the design variables at each point on the 
-Pareto front.
+\iffalse 
 \begin{figure}
 	\centering
-	\begin{subfigure}{1\textwidth}
+	\includegraphics[width=0.75\textwidth]{Report/ex-pareto1}%
+	\llap{\raisebox{1.8cm}{%  move next graphics to top right corner
+			\includegraphics[height=5.5cm]{Report/ex-pareto2}%
+	}}
+	\caption{Comparison of Pareto fronts for initial optimization experiments.}
+\end{figure}  
+\begin{figure}
+	\centering
+	\begin{subfigure}{0.49\textwidth}
 		\centering
@@
 		\caption{Pareto fronts at $s_1$.}
-		\label{bounds1}
+		%\label{expareto1}
 	\end{subfigure}
-	\begin{subfigure}{1\textwidth}
+	\begin{subfigure}{0.49\textwidth}
 	\centering
@@
 	\caption{Pareto fronts at $s_2$.}
-		\label{bounds2}
+	%\label{expareto2}
 	\end{subfigure}
-	\caption{Comparison of design variables for each Pareto front.}
-	\label{bounds}
+	\caption{Comparison of Pareto fronts for initial optimization experiments.}
+	%\label{expareto}
 \end{figure}
+\fi
 
+Next we compared the design variables at each point on several of the Pareto fronts. 
+We eliminate ex-3 from this exercise due to it's significantly slower execution time.
+There is no
+
+Since there was no clear advantage in the design variables, we choose
+the best Pareto front in Fig. \ref{expareto2}, ex-4, for an extended optimization run. 
 The initial number of individuals was fixed at 656, 
 and the minimum number individuals in later generations was fixed at 328. 
-These numbers we in part based on the architecture of the KNL's. 
-Since each simulation takes 8 cores, and there are 64 cores per KNL node, 
+These numbers were in part based on the architecture of the KNL's. 
+Each simulation takes 8 cores, and there are 64 cores per KNL node, 
 we wanted a large population size that would fit evenly on these resources. 
+We allowed the simulation to run for 200 generations.5

### 2018-05-23 parallel-from-db.py

@@ -1,92 +1,186 @@
 import numpy as np
-import sys, os
-import plotly
-import plotly.plotly as py
-import plotly.graph_objs as go
 from db import mldb
-import pickle as pick
-from visualize import scaleData
-from visualize import pareto
 import matplotlib.pyplot as plt
-import pandas as pd
 
+#Functions from pyOPALTools
+#https://gitlab.psi.ch/OPAL/pyOPALTools
+from opal.analysis.pareto_fronts import *
 plt.rc('text', usetex=True)
 plt.rc('font', family='serif') 
 
 root = './databases/'
-baseFN = ['ex-1-bounded', 'ex-2-bounded','ex-3-bounded','ex-4-bounded']
+baseFN = ['ex-1-bounded', 'ex-2-bounded', 'ex-4-bounded'] #'ex-3-bounded',
+#baseFN = ['paper-run-ex4']
+#dbpath = root+baseFN[0]+'.pk'
 
-for i, fn in enumerate(baseFN):
-    nn  = root+fn+'.pk'
-    dbr = mldb.mldb()
-    dbr.load(nn)
-    dvars  = dbr.getXNames()
-    onames = dbr.getYNames()
-    gens   = dbr.getNumberOfSamples()
-    #dbr.printOverview()
+#Read db and save data to file
+#data = get_all_data_db(dbpath)
+#np.save('data.npy', data)
 
-    with open(nn, 'rb') as f: 
-        dbr = pick.load(f, encoding='latin1')   
+# Load db dict from file
+#data = np.load('dict_paper-run-ex4.npy').item()
+#(pfdata1, ind1) = pareto_pts(data['RMSS1'], data['EMITX1'])
+#(pfdata2, ind2) = pareto_pts(data['RMSS2'], data['EMITX2'])
 
-    allx  = dbr[gens+1]['allDvarValues'] 
-    ally  = dbr[gens+1]['allObjValues'] 
-    emitx1  = np.array(ally[:,0])
-    emitx2  = np.array(ally[:,1])
-    rmss1   = np.array(ally[:,2])
-    rmss2   = np.array(ally[:,3])
+for fn in baseFN:
+    dbpath = root+fn+'.pk'
+    #data = get_all_data_db(dbpath)
+    #np.save(fn+'.npy', data)
+    data = np.load(fn+'.npy').item()
 
-    (px, py, pd) = pareto(rmss1, emitx1, allx)
[…]

### 2018-07-08 pareto_stat_plots/pareto_plots.py
updating plots for tba

@@ -25,23 +25,46 @@ plt.rc('axes', labelsize=18)
 #baseFN = ['./noquads/corrected/']
 #baseFN = ['./extquads', './noquads']
 #baseFN = ['to_q7-9']
-z1=True; z2=False; z3=False; z4=False
+z1=True; z2=False; z3=False; z4=False; z5=False;
 gun     = True
-lphase  = True
-quads   = False
+lphase  = False 
+quads   = True 
 doublet = False
-triplet = False
-baseFN  = ['../phases']
-savefile = 'xy_pareto_front_linac_phases_after_quads'
-plottitle = 'Pareto Front After Quads \n $\sigma_{x,y}$ vs. $\sigma_z$'
-#xtitle = "Energy Spread [MeV]"
-xtitle = 'Bunch Length: $\sigma_z$ [mm]'
-ytitle =  'Beam Size: $\sigma_{x,y}$ [mm]'
+triplet = False 
+baseFN  = ['../phases/quads-relaxed']
+
+x=True
+y=True
+if x==True:
+    savefile = 'x_vs_px_pareto_front_quads_before_kicker'
+    plottitle = 'Pareto Front After Quads \n $\sigma_{x}$ vs. $\sigma_{px}$'
+    #xtitle = "Energy Spread [MeV]"
+    #xtitle = 'Bunch Length: $\sigma_z$ [mm]'
+    xtitle =  'Momentum: $\sigma_{px}$ [$\gamma$ ]'
+    ytitle =  'Beam Size: $\sigma_{x}$ [mm]'
+
+if y==True:
+    savefile = 'y_vs_py_pareto_front_quads_before_pets'
+    plottitle = 'Pareto Front After Quads \n $\sigma_{y}$ vs. $\sigma_{py}$'
+    #xtitle = "Energy Spread [MeV]"
+    #xtitle = 'Bunch Length: $\sigma_z$ [mm]'
+    xtitle =  'Momentum: $\sigma_{py}$ [$\gamma$ ]'
+    ytitle =  'Beam Size: $\sigma_{y}$ [mm]'
+
+if y==True and x==True:
+    savefile = 'xy_vs_py_pareto_front_quads_before_pets'
+    plottitle = 'Pareto Front After Quads \n $\sigma_{x,y}$ vs. $\sigma_{px}$'
+    #xtitle = "Energy Spread [MeV]"
+    #xtitle = 'Bunch Length: $\sigma_z$ [mm]'
[…]

### 2018-07-09 paper/theor-experiment.tex
updating paper

--- 2018-05-22 paper/theor-experiment.tex
@@
 Next we apply the optimization framework to the high charge beam line at the AWA. 
+The purpose of the Argonne Wakefield Accelerator (AWA) optimization is to produce beams of electrons meeting 
+design specifications including number of particles (charge), energy, and particle distribution (characterized by transverse beam sizes and energy spread).
 As shown in Fig.  \ref{awa-pic}, this beam line consists of an rf photocathode gun, 
@@
 followed by four quadrupoles and a stripline kicker. 
-The charge of interest is 40 nC, and based on Two Beam 
+The charge of interest, 40 nC, is needed for Two Beam 
 Acceleration (TBA) \cite{gai_power_jing_2012} experiments performed in the past 
 at AWA. Similar experiments will take place in the future and motivate this work. 
-Prior experimental results were limited by beam size and emittance as the beam passed through small aperture 
+Prior experimental results were limited by beam size as the beam passed through small aperture 
 wakefield structures located after the quadrupoles. 
@@
 \begin{figure}
-	\centering
-	\includegraphics[width=0.9\linewidth]{Report/awa-drawing}
+	\begin{tikzpicture}[every node/.style={anchor=south west,inner sep=0pt},x=1mm, y=1mm,]   
+	\node (fig1) at (0,0)
+	{\includegraphics[width=0.9\textwidth]{Report/awa-drawing}};
+	\node[fill=white, inner sep=2pt] (txt2) at (35,15) {Interferometer};
+	\node[fill=white, inner sep=2pt, rotate=26] (txt2) at (18,19.5) {Slit};	
+	\node[fill=white, inner sep=2pt, rotate=20] (txt2) at (13,27) {Window};
+	\end{tikzpicture}
 	\caption{High charge beam line layout at the AWA.}
@@
 \end{figure}
-
 %\vspace{-1em}
-In addition to the physics challenges, we chose this model to demonstrate the frameworks ability to tackle large problems.
-The number of design variables is eight, and the number of objectives is seven.
+In addition to the physics challenges, we chose this model to demonstrate the ability of the framework to tackle large problems.
+Six design variables and objectives were used, 
+along with three constraints.
+The objectives include transverse and longitudinal beam size, 
+transverse momentum and longitudinal energy spread. 
+The design variables include the two gun solenoids and 
+the first four quadrupoles. The objectives are calculated at 
+$s_1=19.4$~[m], at the entrance of the fifth quadrupole in Fig.~\ref{awa-pic}.  
 This problem encompasses high dimensionality 
@@
 \begin{align}
-\text{min}  \quad & \text{rms}_{x}\left(s = s_1\right), \quad \text{rms}_{x}\left(s = s_2\right) \label{eq:awa:p1}\\
-& \text{rms}_{s}\left(s = s_1\right), \quad \text{rms}_{s}\left(s = s_2\right), \label{eq:awa:p2}\\
-& \varepsilon_{x}\left(s = s_1\right), \quad \varepsilon_{x}\left(s = s_2\right), \label{eq:awa:p3} \\
-& dE \label{eq:awa:p4} \\
-\text{subject to} \quad & q = 40 \left[\text{nC}\right] \label{eq:awa:firstconstr}\\
+\text{min}  \quad & \text{rms}_{x}\left(s = s_1\right), \quad \text{rms}_{y}\left(s = s_1\right) \label{eq:awa:p1}\\
+& \text{rms}_{px}\left(s = s_1\right), \quad \text{rms}_{py}\left(s = s_1\right), \label{eq:awa:p2}\\
+& \text{rms}_{s}\left(s = s_1\right), \quad dE \label{eq:awa:p4} \\
+\text{subject to} \quad & rms_x(s=s_0) < 0.1 \, [m]\label{eq:awa:c1}\\
+\quad & rms_y(s=s_0) < 0.1\, [m]\label{eq:awa:c2}\\
+\quad & |rms_y(s=s_0) - rms_x(s=s_0) | < 0.005 \, [m]\label{eq:awa:c3}\\
+\quad & q = 40 \left[\text{nC}\right] \label{eq:awa:firstconstr}\\
 \quad & \text{Volt}_{\text{Gun}} = 64\left[\text{MV/m}\right] \label{eq:awa:lastconstr}\\
 \quad & \text{Volt}_{\text{Linac}} = 24-25\left[\text{MV/m}\right] \\
-\quad & \sigma_x = \sigma_y = 9 \left[\text{mm}\right] \label{eq:awa:firstdvar}\\
-\quad & \phi_{\text{linac}} =0^\circ \label{eq:awa:lastdvar}
+\quad & R_x = R_y = 9 \left[\text{mm}\right] \label{eq:awa:firstdvar}\\
+\quad & \phi_{\text{gun}} =-20^\circ \label{eq:awa:gphidvar}\\
+\quad & \phi_{\text{linac}} =-20^\circ \label{eq:awa:lastdvar}
 \end{align}
 
-The first four objectives, Eqs. (\ref{eq:awa:p1}) and (\ref{eq:awa:p2}),
-minimize the transverse ($rms_x$) and longitudinal ($rms_s$) 
-beam sizes at two locations of interest in the beam line ($s_1$,$s_2$);
-the longitudinal positions at the entrance of the kicker and 
-$1$ meter after the exit of the kicker. 
-Minimizing the beam size at these locations is essential to 
-to preventing scraping and ensuring transmission through the wakefield structures 
-following the kicker. The next two objectives (\ref{eq:awa:p3}) minimize the 
-transverse emittance, which favors less divergence in the beam and reduces 
-emittance growth during transport. The last objective (\ref{eq:awa:p4}), 
-minimizes energy spread in the bunch at the entrance of the kicker at $s_1$.  
-This helps reduce emittance and beam size growth in the kicker.  
+The first four objectives, Eqs. (\ref{eq:awa:p1}) to (\ref{eq:awa:p2}),
+minimize the transverse ($rms_{x,y}$) beam size and transverse momentum ($rms_{px,py}$)
+at the location of interest in the beam line ($s_1$).
+Where $s_1$ is the longitudinal entrance of the fifth quadrupole. 
+Minimizing the beam size at this location is essential to 
+to preventing loss of particles by scraping.
+Preventing scraping ensures better transmission through the wakefield structures downstream. 
+Less divergence in the beam (lower transverse momentum) 
+reduces growth of transverse beam size during transport in bending elements, 
+which also helps with transmission downstream. 
+The next two objectives (\ref{eq:awa:p2}) minimize the 
+longitudinal beam size ($rms_s$), and energy spread (dE) at $s_1$.
+This helps reduce longitudinal beam size growth in bending elements.
+
+Three constraints were also defined to help guide the algorithm;
+Eqs.~\ref{eq:awa:c1} to \ref{eq:awa:c3}.
+The bounding values may seem large, but this is done to avoid over constraing the 
+problem in early generations. If the constraints are set tighter, 
+runs do not reach the second generation, because enough satisfactory 
+points are not produced to fill a complete generation. 
+Leaving the value large allows for enough simulations to finish
+in order to reach the next generation, and subsequent improved points in later generations.
+The difference constraint, Eq.~\ref{eq:awa:c3}, is used to favor nearly round beams.
+This prevents one dimension from becoming disproportionately large compared to the other.
+In this case, there is some room in the beam pipe to allow the y dimension to grow, but round beams 
+are preferred for easier data analysis.
+
 Equations (\ref{eq:awa:firstconstr}) to
 (\ref{eq:awa:lastdvar}) define the charge, gun voltage, linac voltages, 
-laser radius and linac cavity phases (in that order). These are parameters in the simulation 
+laser radius, gun phase, and linac cavity phases (in that order). 
+These are parameters in the simulation 
 that must be defined, but do not vary during the optimization.
-
 %\vspace{-1em}
-As introduced in Section \ref{ferrario}, we define the AWA optimization problem 
-objectives, and design variables in the OPAL input file as shown in
+As introduced in Section \ref{ferrario}, we define the AWA optimization 
+design variables, objectives, and constraints in the OPAL input file as shown in
 the following code: %equations (\ref{eq:awa:p1}) to (\ref{eq:awa:lastdvar}).
@@
 {\footnotesize \begin{verbatim}
+
 	// Gun variables 
-	dv0: DVAR, VARIABLE="IBF",    LOWERBOUND=350.0, UPPERBOUND=500.0;
-	dv1: DVAR, VARIABLE="IM",     LOWERBOUND=170.0, UPPERBOUND=260.0;
-	dv2: DVAR, VARIABLE="GPHASE", LOWERBOUND=-30.0, UPPERBOUND=0.0;
-	dv3: DVAR, VARIABLE="FWHM",   LOWERBOUND=1.5,   UPPERBOUND=10.0;
+	dv0: DVAR, VARIABLE="IBF",    LOWERBOUND=300.0, UPPERBOUND=500.0;
+	dv1: DVAR, VARIABLE="IM",     LOWERBOUND=180.0, UPPERBOUND=280.0;
 
@@
 
-	// Objectives
-	rmss1:  OBJECTIVE,EXPR="fabs(statVariableAt('rms_s',16.45))";
-	rmsx1:  OBJECTIVE,EXPR="fabs(statVariableAt('rms_x',16.45))";
-	emitx1: OBJECTIVE,EXPR="fabs(statVariableAt('emit_x',16.45))";
-	de1:    OBJECTIVE,EXPR="fabs(statVariableAt('dE',16.45))";	
-	rmss2:  OBJECTIVE,EXPR="fabs(statVariableAt('rms_s',18.45))";
-	rmsx2:  OBJECTIVE,EXPR="fabs(statVariableAt('rms_x',18.45))";
-	emitx2: OBJECTIVE,EXPR="fabs(statVariableAt('emit_x',18.45))";
+	//Objectives
+	de3: OBJECTIVE,EXPR="fabs(statVariableAt('dE',19.4))";
+	rmss3: OBJECTIVE,EXPR="fabs(statVariableAt('rms_s',19.4))";
+	rmsx3: OBJECTIVE,EXPR="fabs(statVariableAt('rms_x',19.4))";
+	rmsy3: OBJECTIVE,EXPR="fabs(statVariableAt('rms_y',19.4))";
+	rmspx3: OBJECTIVE,EXPR="fabs(statVariableAt('rms_px',19.4))";
+	rmspy3: OBJECTIVE,EXPR="fabs(statVariableAt('rms_py',19.4))";
+
+	//Kicker apeture
+	c1: CONSTRAINT, EXPR="fabs(statVariableAt('rms_x',16.5))<0.1";
+	c2: CONSTRAINT, EXPR="fabs(statVariableAt('rms_y',16.5))<0.1";
+	c3: CONSTRAINT, EXPR="fabs(statVariableAt('rms_y',16.5)-statVariableAt('rms_x',16.5))<0.005";
+
+	OPTIMIZE, INPUT="tmpl/optLinac-40nC.tmpl",
+	OUTPUT="optLinac-40nC",
+	OUTDIR="results",
+	OBJECTIVES = {rmss3, rmsx3, rmsy3, rmspx3, rmspy3, de3},
+	DVARS = {dv0, dv1, dv4, dv5, dv6, dv7},
+	CONSTRAINTS = {c1, c2, c3},
+	INITIALPOPULATION=656,
+	MAXGENERATIONS=200,
+	NUM_MASTERS=1,
+	NUM_COWORKERS=8,
+	SIMTMPDIR="tmp",
+	TEMPLATEDIR="tmpl",
+	FIELDMAPDIR="fieldmaps",
+	NUM_IND_GEN=328,
+	GENE_MUTATION_PROBABILITY=0.01,
+	MUTATION_PROBABILITY=0.01,
+	RECOMBINATION_PROBABILITY=0.09;
+	QUIT;
 
@@
 Design variables include the currents in two gun solenoids (IBF and IM), 
-the gun phase (GPHASE), the laser longitudinal full width half max (FWHM), 
 and four quadrupole strengths (KQ1-KQ2). The objectives include
-beam size, emittance, and energy spread as
+beam size (transverse and longitudinal), transverse momentum, and energy spread as
 defined in Eqs. (\ref{eq:awa:p1}) to (\ref{eq:awa:p4}). 
-The location at the entrance of the kicker is $s_1=16.45$~meters, 
-and the location of interest after the kicker is $s_1=18.45$~meters.
+The location at the entrance of the kicker is $s_0=16.45$~meters, 
+and the location of interest for objectives is $s_1=19.4$~meters.
 
@@
 on 8 cores each, which allowed 8 jobs per node on the KNLs.
-This in combination with the amount of nodes available 
+This in combination with the number of nodes available 
 allows for very large optimization jobs, like the AWA case.
+Typical runs for this paper used 41 nodes, which corresponds to 2624 KNL cores 
+and a generation size of 328 individuals.
 
@@
 maintaining the physics of interest. 
-The grid size was $16 \times 16 \times 32$, 
+The grid size $16 \times 16 \times 32$ was chosen, 
 and parallelized in the x and y directions.
@@
 are calculated correctly, but we see discrepancies in the transverse 
-rms$_x$ and $\epsilon_x$ in the low fidelity results. 
-Average run time each simulation with the adjusted time steps was 1.6~minutes.
-In comparison the mid fidelity simulations ran for 18~minutes each.
+rms$_x$ and $\epsilon_x$ in the low fidelity results. The
+average run time of each simulation with the adjusted time steps was 1.6~minutes.
+In comparison the mid fidelity simulations ran for 18~minutes.
 %A summary of the parameters used is listed in Table \ref{fidelity}.
@@
 These parameters include gene mutation probability, mutation probability, 
-recombination probability, number of individuals (initial and and for later generations), 
+recombination probability, number of individuals (initial \lsnote{you have an extra `and' here} and for later generations), 
 and number of generations to complete. 
@@
 The objectives include: $\varepsilon_{x}\left(s = s_1\right)\text{, } \varepsilon_{x}\left(s = s_2\right)\text{, } \text{rms}_{s}\left(s = s_1\right)\text{, and }  \text{rms}_{s}\left(s = s_2\right)$.
-The optimization parameters specific to OPAL input for ex-3 is given as an example.
+\lsnote{You could define $\varepsilon_{x1}$ to be $\varepsilon_{x} (s=s1)$ and similarly in the table and then use going forward to simplify notation}
+The optimization parameters specific to OPAL input for ex-3 \lsnote{are} given as an example.
 Note the design variables defined in Section \ref{awaproblem}
@@
 and the minimum number individuals in later generations was fixed at 328. 
-These numbers we in part based on the architecture of the KNL's. 
+These numbers \lsnote{were} in part based on the architecture of the KNL's. 
 Since each simulation takes 8 cores, and there are 64 cores per KNL node, 

### 2018-07-10 paper/theor-experiment.tex
more edits to awa paper section

@@
 
+\subsubsection{Preliminary Tests} \label{awa:subsection:test}
+\nrnote{What else could we name this subsection?}
 A study on time step and 
@@
 
-\subsubsection{AWA Optimization Results}
 While the optimization problem and goals were well defined (Section \ref{awaproblem}), 
@@
 These parameters include gene mutation probability, mutation probability, 
-recombination probability, number of individuals (initial \lsnote{you have an extra `and' here} and for later generations), 
+recombination probability, number of individuals, 
 and number of generations to complete. 
 Given the beam line and design variables given in Section \ref{awaproblem},
+\nrnote{Changed variables for final run, the variables in 5.3 no longer match these small runs. Need to rework this section} 
 four optimization experiments were done with varying NSGA-II parameters. 
@@
 \lsnote{You could define $\varepsilon_{x1}$ to be $\varepsilon_{x} (s=s1)$ and similarly in the table and then use going forward to simplify notation}
-The optimization parameters specific to OPAL input for ex-3 \lsnote{are} given as an example.
+The optimization parameters specific to OPAL input for ex-3 are given as an example.
 Note the design variables defined in Section \ref{awaproblem}
@@
 
+Next compare the design variables at each point on the 
+Pareto front.
+
 \begin{figure}
@@
 
-Next compare the design variables at each point on the 
-Pareto front.
-\begin{figure}
-	\centering
-	\begin{subfigure}{1\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{Report/ex-pareto1}
-		\caption{Pareto fronts at $s_1$.}
-		\label{bounds1}
-	\end{subfigure}
-	\begin{subfigure}{1\textwidth}
-		\centering
-		\includegraphics[width=\textwidth]{Report/ex-pareto2}
-		\caption{Pareto fronts at $s_2$.}
-		\label{bounds2}
-	\end{subfigure}
-	\caption{Comparison of design variables for each Pareto front.}
-	\label{bounds}
-\end{figure}
-
 The initial number of individuals was fixed at 656, 
 and the minimum number individuals in later generations was fixed at 328. 
-These numbers \lsnote{were} in part based on the architecture of the KNL's. 
+These numbers were in part based on the architecture of the KNL's. 
 Since each simulation takes 8 cores, and there are 64 cores per KNL node, 
 we wanted a large population size that would fit evenly on these resources. 
+This would be the population sizes used for all subsequent runs.
+
+\subsubsection{AWA Optimization Results}
+With the simulation, GA, and node resource parameters set by the work in \ref{awa:subsection:test}, 
+the full optimization problem described in \ref{awaproblem} was run for 200 generations.
+
+\begin{figure}
+	%\includegraphics[width=0.5\textwidth]{}\includegraphics[width=0.5\textwidth]{}
+	\label{beamsizes}
+\end{figure}

### 2018-07-10 paper/theor-experiment.tex
adding final data to paper

@@
 it will guide future operations at the AWA.
+\nrnote{Maybe eqs 5.10-5.21 and code example should move after time step scan and hyper parameters}
 
@@
 
-\subsubsection{Preliminary Tests} \label{awa:subsection:test}
-\nrnote{What else could we name this subsection?}
+\subsubsection{Time Step Scan} \label{awa:subsection:test}
 A study on time step and 
@@
 
+\subsubsection{Hyper parameter Scan}
 While the optimization problem and goals were well defined (Section \ref{awaproblem}), 
@@
 they would continue to converge given more time. 
-When looking at the Pareto front for $s_2$, we see ex-4 has a slight 
+Similar arguments can be made for ex-2, which evaluated about 15 less generations
+with no clear benefit in either Pareto front.
+When looking at the Pareto front at $s_2$, only ex-4 has a slight 
 edge over the others.
+With ex-2 and ex-3 eliminated due to evaluation time, 
+the hyper parameters in ex-4 were chosen as the default values for subsequent runs.
+\iffalse  
 \begin{figure}
@@
 \end{figure}  
-
-Next compare the design variables at each point on the 
-Pareto front.
+\fi
 
@@
 
+\subsubsection{AWA Optimization Results}
+With the time steps and hyper parameters set by the work in \ref{awa:subsection:test}, 
+the full optimization problem described in \ref{awaproblem} was run for 200 generations.
 The initial number of individuals was fixed at 656, 
@@
 we wanted a large population size that would fit evenly on these resources.
-This would be the population sizes used for all subsequent runs.
 
-\subsubsection{AWA Optimization Results}
-With the simulation, GA, and node resource parameters set by the work in \ref{awa:subsection:test}, 
-the full optimization problem described in \ref{awaproblem} was run for 200 generations.
+Again, the location of optimization is $s_3=19.4$ [m]. 
+This is the entrance to the fifth quad in the beam line. 
+This location is where the beam should be captured and focused through subsequent elements.
+After collection of the data, Pareto fronts comparing the objectives were plotted, 
+see Figs. X-Z.
+The $\sigma_x$ and $\sigma_{px}$ plots are of most interest, as they are the most heavility 
+impacted by bending elements. With this in mind, several beam parameters corresponding to
+options on Pareto Front in Fig. X were plotted and compared. 
+The best results are shown in Fig. Z. 
+The maximum beam sizes are well below the beam pip aperture limits as shown in Fig. (b).
 

### 2018-07-10 paper/theor-experiment.tex
adding tba beam line

@@
 	{\includegraphics[width=0.9\textwidth]{Report/awa-drawing}};
-	\node[fill=white, inner sep=2pt] (txt2) at (35,15) {Interferometer};
+	\node[fill=white, inner sep=2pt] (txt2) at (10,-10) {$s_1$};
 	\node[fill=white, inner sep=2pt, rotate=26] (txt2) at (18,19.5) {Slit};	
-	\node[fill=white, inner sep=2pt, rotate=20] (txt2) at (13,27) {Window};
 	\end{tikzpicture}
 	\caption{High charge beam line layout at the AWA.}
-	\label{awa-pic}
+	\label{awa-linac}
 \end{figure}
+
+\begin{figure}
+	\begin{tikzpicture}[every node/.style={anchor=south west,inner sep=0pt},x=1mm, y=1mm,]   
+	\node (fig2) at (0,0)
+	{\includegraphics[width=\textwidth]{Report/tba_dogleg}};
+	\node[fill=white, inner sep=2pt] (txt2) at (2,35) {$s_1$};
+	\node[fill=white, inner sep=2pt] (txt2) at (14,35) {$s_2$};
+	\node[fill=white, inner sep=2pt] (txt2) at (35,31) {$s_3$};
+	\node[fill=white, inner sep=2pt] (txt2) at (24,50) {Septum};
+	\draw [blue, ->, line width=1] (30,50) -- (30, 42);	
+	\node[fill=white, inner sep=2pt] (txt2) at (5,50) {Kicker};
+	\draw [blue, ->, line width=1] (10,50) -- (18, 43);
+	\end{tikzpicture}
+	\caption{Continuation of the high charge beam line layout at the AWA. 
+		This is the the two beam acceleration section.}
+	\label{awa-tba}
+\end{figure}
+
 %\vspace{-1em}
@@
 \begin{align}
-\text{min}  \quad & \text{rms}_{x}\left(s = s_1\right), \quad \text{rms}_{y}\left(s = s_1\right) \label{eq:awa:p1}\\
-& \text{rms}_{px}\left(s = s_1\right), \quad \text{rms}_{py}\left(s = s_1\right), \label{eq:awa:p2}\\
-& \text{rms}_{s}\left(s = s_1\right), \quad dE \label{eq:awa:p4} \\
-\text{subject to} \quad & rms_x(s=s_0) < 0.1 \, [m]\label{eq:awa:c1}\\
-\quad & rms_y(s=s_0) < 0.1\, [m]\label{eq:awa:c2}\\
-\quad & |rms_y(s=s_0) - rms_x(s=s_0) | < 0.005 \, [m]\label{eq:awa:c3}\\
+\text{min}  \quad & \text{rms}_{x}\left(s = s_3\right), \quad \text{rms}_{y}\left(s = s_3\right) \label{eq:awa:p1}\\
+& \text{rms}_{px}\left(s = s_3\right), \quad \text{rms}_{py}\left(s = s_3\right), \label{eq:awa:p2}\\
+& \text{rms}_{s}\left(s = s_3\right), \quad dE \label{eq:awa:p4} \\
+\text{subject to} \quad & rms_x(s=s_1) < 0.1 \, [m]\label{eq:awa:c1}\\
+\quad & rms_y(s=s_1) < 0.1\, [m]\label{eq:awa:c2}\\
+\quad & |rms_y(s=s_1) - rms_x(s=s_1) | < 0.005 \, [m]\label{eq:awa:c3}\\
 \quad & q = 40 \left[\text{nC}\right] \label{eq:awa:firstconstr}\\

### 2018-07-10 paper/theor-experiment.tex
small tweaks to tba tikz
fixing linac tikz

@@
 	\node (fig1) at (0,0)
-	{\includegraphics[width=0.9\textwidth]{Report/awa-drawing}};
-	\node[fill=white, inner sep=2pt] (txt2) at (10,-10) {$s_1$};
-	\node[fill=white, inner sep=2pt, rotate=26] (txt2) at (18,19.5) {Slit};	
+	{\includegraphics[width=\textwidth]{Report/awa-drawing}};
+	\node[fill=white, inner sep=2pt] (txt2) at (125,10) {$s_2$};
+	\node[fill=white, inner sep=2pt] (txt2) at (112,8) {$s_1$};
+	\node[fill=white, inner sep=2pt] (txt2) at (115,30) {Kicker};
+	\draw [blue, ->, line width=1] (120,30) -- (120, 23);	
 	\end{tikzpicture}
-	\caption{High charge beam line layout at the AWA.}
+	\caption{Side view of the high charge linac at the AWA. 
+		All hardware in this drawing is currently installed.}
 	\label{awa-linac}
@@
 	\node[fill=white, inner sep=2pt] (txt2) at (14,35) {$s_2$};
-	\node[fill=white, inner sep=2pt] (txt2) at (35,31) {$s_3$};
+	\node[fill=white, inner sep=2pt] (txt2) at (33,31) {$s_3$};
 	\node[fill=white, inner sep=2pt] (txt2) at (24,50) {Septum};
 	\draw [blue, ->, line width=1] (30,50) -- (30, 42);	
-	\node[fill=white, inner sep=2pt] (txt2) at (5,50) {Kicker};
-	\draw [blue, ->, line width=1] (10,50) -- (18, 43);
+	\node[fill=white, inner sep=2pt] (txt2) at (3,50) {Kicker};
+	\draw [blue, ->, line width=1] (9.5,50) -- (9.5, 43);
 	\end{tikzpicture}
-	\caption{Continuation of the high charge beam line layout at the AWA. 
-		This is the the two beam acceleration section.}
+	\caption{Continuation of the high charge beam line layout at the AWA, top view. 
+		This is the proposed two beam acceleration section.}
 	\label{awa-tba}

### 2018-07-10 paper/paper.tex
updating paper
remove some CS stuff which I think is to much for Phys. Rev. AB

@@
 \setcounter{lstmain}{1}
+
+\usepackage{graphicx,xcolor,enumitem}
+\newcommand{\lsnote}[1]{\textsf{{\color{violet}{ LS note:}   #1 }}}
 
@@
 
-By abiding to the API from Listing 3 it becomes trivial to add new forward
-  solvers to the framework (see Appendix A).
+% AA: this is too much for Phys Rev. AB  
+% By abiding to the API from Listing 3 it becomes trivial to add new forward
+% solvers to the framework (see Appendix A).
+
 If the objectives and constraints are simple arithmetical expressions, the
@@
 
-\input{theor-experiment}
+\input{theor-experiment} %periment}
 
@@
   contract number DE-AC02-06CH11357 and grant number DE-SC0015479.
-\appendix
 
-\section{Forward Solver Implementation}
+% AA: this is too much for Phys Rev. AB
 
-A simple implementation, e.g.\ using a Python forward solver, is given below
-  in Listing 6.
-We assume the Python script executes a simulation and dumps results in the
-  \textsc{SDDS} file format~\cite{borl:00}.
-Utility classed are used to parse the result data and fill the appropriate
-  structures returned to the optimizer algorithm.
+% \appendix
 
-\begin{code}[Simple Simulation Wrapper]
-#include <map>
-#include <string>
-#include <vector>
-
-#include "Util/Types.h"
-#include "Util/CmdArguments.h"
-#include "Simulation/Simulation.h"
-
-#include "boost/smart_ptr.hpp"
-
-class SimpleSimulation : public Simulation {
-
-public:
-
-    SimpleSimulation(Expressions::Named_t objectives,
-                     Expressions::Named_t constraints,
-                     Param_t params, std::string name, MPI_Comm comm,
-                     CmdArguments_t args);
-
-    ~SimpleSimulation();
-
-    /// Calls simulation through Python wrapper and returns when simulation
-    /// has either failed or finished.
-    void run() {
-        // user implements wrappers
-        prepare_input_file();
-        run_python_simulation();
-    }
-
-    /// Parse SDDS stat file and build up requested variable dictionary.
-    void collectResults(){
-
-        Expressions::Named_t::iterator it;
-        for(it = objectives_.begin(); it != objectives_.end(); it++) {
-
-            Expressions::Expr_t *objective = it->second;
-
-            // find out which variables we need in order to evaluate the
-            // objective
-            variableDictionary_t variable_dictionary;
-            std::set<std::string> req_vars = objective->getReqVars();
-
-            if(req_vars.size() != 0) {
-
-                boost::scoped_ptr<SDDSReader> sddsr(new SDDSReader(fn));
-
-                try {
-                    sddsr->parseFile();
-                } catch(OptPilotException &e) {
-                    std::cout << "Exception while parsing SDDS file: "
-                        << e.what() << std::endl;
-                    break;
-                }
-
-                // get all the required variable values from the stat file
-                foreach(std::string req_var, req_vars) {
-                    if(variable_dictionary.count(req_var) == 0) {
-
-                        try {
-                            double value = 0.0;
-                            sddsr->getValue(1 /*atTime*/, req_var, value);
-                            variable_dictionary.insert(
-                                std::pair<std::string, double>(req_var, value));
-                        } catch(OptPilotException &e) {
-                            std::cout << "Exception while getting value "
-                                      << "from SDDS file: " << e.what()
-                                      << std::endl;
-                        }
-                    }
-                }
-            }
-
-            // and evaluate the expression using the built dictionary of
-            // variable values
-            Expressions::Result_t result =
-                objective->evaluate(variable_dictionary);
-
-            std::vector<double> values;
-            values.push_back(boost::get<0>(result));
-            bool is_valid = boost::get<1>(result);
-
-            reqVarInfo_t tmps = {EVALUATE, values, is_valid};
-            requestedVars_.insert(
-                std::pair<std::string, reqVarInfo_t>(it->first, tmps));
-
-        }
-    }
-
-    /// returns container containing all requested variables with results
-    reqVarContainer_t getResults() { return requestedVars_; }
-
-private:
-
-    /// holds solutions returned to the optimizer
-    reqVarContainer_t requestedVars_;
-
-    Expressions::Named_t objectives_;
-    Expressions::Named_t constraints_;
-
-    MPI_Comm comm_;
-};
-
-#endif
-\end{code}
+%\section{Forward Solver Implementation}
+%
+%A simple implementation, e.g.\ using a Python forward solver, is given below
+%  in Listing 6.
+%We assume the Python script executes a simulation and dumps results in the
+%  \textsc{SDDS} file format~\cite{borl:00}.
+%Utility classed are used to parse the result data and fill the appropriate
+%  structures returned to the optimizer algorithm.
+%
+%\begin{code}[Simple Simulation Wrapper]
+%#include <map>
+%#include <string>
+%#include <vector>
+%
+%#include "Util/Types.h"
+%#include "Util/CmdArguments.h"
+%#include "Simulation/Simulation.h"
+%
+%#include "boost/smart_ptr.hpp"
+%
+%class SimpleSimulation : public Simulation {
+%
+%public:
+%
+%    SimpleSimulation(Expressions::Named_t objectives,
+%                     Expressions::Named_t constraints,
+%                     Param_t params, std::string name, MPI_Comm comm,
+%                     CmdArguments_t args);
+%
+%    ~SimpleSimulation();
+%
+%    /// Calls simulation through Python wrapper and returns when simulation
+%    /// has either failed or finished.
+%    void run() {
+%        // user implements wrappers
+%        prepare_input_file();
+%        run_python_simulation();
+%    }
+%
+%    /// Parse SDDS stat file and build up requested variable dictionary.
+%    void collectResults(){
+%
+%        Expressions::Named_t::iterator it;
+%        for(it = objectives_.begin(); it != objectives_.end(); it++) {
+%
+%            Expressions::Expr_t *objective = it->second;
+%
+%            // find out which variables we need in order to evaluate the
+%            // objective
+%            variableDictionary_t variable_dictionary;
+%            std::set<std::string> req_vars = objective->getReqVars();
+%
+%            if(req_vars.size() != 0) {
+%
+%                boost::scoped_ptr<SDDSReader> sddsr(new SDDSReader(fn));
+%
+%                try {
+%                    sddsr->parseFile();
+%                } catch(OptPilotException &e) {
+%                    std::cout << "Exception while parsing SDDS file: "
+%                        << e.what() << std::endl;
+%                    break;
+%                }
+%
+%                // get all the required variable values from the stat file
+%                foreach(std::string req_var, req_vars) {
+%                    if(variable_dictionary.count(req_var) == 0) {
+%
+%                        try {
+%                            double value = 0.0;
+%                            sddsr->getValue(1 /*atTime*/, req_var, value);
+%                            variable_dictionary.insert(
+%                                std::pair<std::string, double>(req_var, value));
+%                        } catch(OptPilotException &e) {
+%                            std::cout << "Exception while getting value "
+%                                      << "from SDDS file: " << e.what()
+%                                      << std::endl;
+%                        }
+%                    }
+%                }
+%            }
+%
+%            // and evaluate the expression using the built dictionary of
+%            // variable values
+%            Expressions::Result_t result =
+%                objective->evaluate(variable_dictionary);
+%
+%            std::vector<double> values;
+%            values.push_back(boost::get<0>(result));
+%            bool is_valid = boost::get<1>(result);
+%
+%            reqVarInfo_t tmps = {EVALUATE, values, is_valid};
+%            requestedVars_.insert(
+%                std::pair<std::string, reqVarInfo_t>(it->first, tmps));
+%
+%        }
+%    }
+%
+%    /// returns container containing all requested variables with results
+%    reqVarContainer_t getResults() { return requestedVars_; }
+%
+%private:
+%
+%    /// holds solutions returned to the optimizer
+%    reqVarContainer_t requestedVars_;
+%
+%    Expressions::Named_t objectives_;
+%    Expressions::Named_t constraints_;
+%
+%    MPI_Comm comm_;
+%};
+%
+%#endif
+%\end{code}
 

### 2018-07-10 paper/theor-experiment.tex
rearranging AWA section

@@
 \subsection{AWA Photoinjector Optimization} \label{awaproblem}
-Next we apply the optimization framework to the high charge beam line at the AWA. 
-The purpose of the Argonne Wakefield Accelerator (AWA) optimization is to produce beams of electrons meeting 
-design specifications including number of particles (charge), energy, and particle distribution (characterized by transverse beam sizes and energy spread).
-As shown in Fig.  \ref{awa-pic}, this beam line consists of an rf photocathode gun, 
-two solenoids, six linear accelerating cavities, 
+Next we apply the optimization framework to a high charge beam line
+ at the Argonne Wakefield Accelerator (AWA) facility. 
+The goal of this optimization is to produce beams of electrons that meet 
+design specifications; this includes number of particles (charge), energy, and particle distribution (characterized by beam sizes and energy spread).
+As shown in Fig.~\ref{awa-linac}, the installed portion of the the 
+beam line consists of an rf photocathode gun, 
+two solenoids, and six linear accelerating cavities
 followed by four quadrupoles and a stripline kicker. 
 The charge of interest, 40 nC, is needed for Two Beam 
-Acceleration (TBA) \cite{gai_power_jing_2012} experiments performed in the past 
-at AWA. Similar experiments will take place in the future and motivate this work. 
+Acceleration (TBA) \cite{gai_power_jing_2012,JING201872} 
+experiments performed at AWA, which motivates this work. 
 Prior experimental results were limited by beam size as the beam passed through small aperture 
-wakefield structures located after the quadrupoles. 
+wakefield structures located downstream. 
 In an attempt to maximize charge transmission in upcoming experiments
-we optimize several parameters in the gun and quadrupoles leading into the 
-TBA section of the beam line.
+we optimize magnet strengths in the gun and quadrupoles leading into the 
+TBA section of the beam line, shown in Fig.~\ref{awa-tba}.
+The simulation model includes the linac, kicker, and septum. 
+The optimization location is chosen as the entrance to the fifth quadrupole, $s_3$, on the dog leg.
+Minimizing beam sizes here will enable capture and further focus with quadrupoles five and six before space charge effects dominate the beam. 
+This will also enable cleaner transport through downstream elements.
 %\vspace{-1em}
@@
 	{\includegraphics[width=\textwidth]{Report/awa-drawing}};
+	\node[fill=white, inner sep=2pt] (txt2) at (0,20) {Gun};
+	\node[fill=white, inner sep=2pt] (txt2) at (20,20) {Accelerating Cavities};
+	\node[fill=white, inner sep=2pt] (txt2) at (88,28) {Quadrupoles};
+	\draw [blue, ->, line width=1] (99,28) -- (99, 21);
 	\node[fill=white, inner sep=2pt] (txt2) at (125,10) {$s_2$};
@@
 \end{figure}
-
+%
 %\vspace{-1em}
 In addition to the physics challenges, we chose this model to demonstrate the ability of the framework to tackle large problems.
-Six design variables and objectives were used, 
-along with three constraints.
-The objectives include transverse and longitudinal beam size, 
-transverse momentum and longitudinal energy spread. 
+Six design variables and objectives were used, along with three constraints.
+The objectives include transverse and longitudinal beam sizes, 
+transverse momentum, and longitudinal energy spread. 
 The design variables include the two gun solenoids and 
 the first four quadrupoles. The objectives are calculated at 
-$s_1=19.4$~[m], at the entrance of the fifth quadrupole in Fig.~\ref{awa-pic}.  
+$s_3=19.4$~[m], at the entrance of the fifth quadrupole in Fig.~\ref{awa-tba}.  
 This problem encompasses high dimensionality 
@@
 it will guide future operations at the AWA.
-\nrnote{Maybe eqs 5.10-5.21 and code example should move after time step scan and hyper parameters}
+\nrnote{Moved final run set up and results to after time step scan and hyper parameters}
 
-\begin{align}
-\text{min}  \quad & \text{rms}_{x}\left(s = s_3\right), \quad \text{rms}_{y}\left(s = s_3\right) \label{eq:awa:p1}\\
-& \text{rms}_{px}\left(s = s_3\right), \quad \text{rms}_{py}\left(s = s_3\right), \label{eq:awa:p2}\\
-& \text{rms}_{s}\left(s = s_3\right), \quad dE \label{eq:awa:p4} \\
-\text{subject to} \quad & rms_x(s=s_1) < 0.1 \, [m]\label{eq:awa:c1}\\
-\quad & rms_y(s=s_1) < 0.1\, [m]\label{eq:awa:c2}\\
-\quad & |rms_y(s=s_1) - rms_x(s=s_1) | < 0.005 \, [m]\label{eq:awa:c3}\\
-\quad & q = 40 \left[\text{nC}\right] \label{eq:awa:firstconstr}\\
-\quad & \text{Volt}_{\text{Gun}} = 64\left[\text{MV/m}\right] \label{eq:awa:lastconstr}\\
-\quad & \text{Volt}_{\text{Linac}} = 24-25\left[\text{MV/m}\right] \\
-\quad & R_x = R_y = 9 \left[\text{mm}\right] \label{eq:awa:firstdvar}\\
-\quad & \phi_{\text{gun}} =-20^\circ \label{eq:awa:gphidvar}\\
-\quad & \phi_{\text{linac}} =-20^\circ \label{eq:awa:lastdvar}
-\end{align}
-
-The first four objectives, Eqs. (\ref{eq:awa:p1}) to (\ref{eq:awa:p2}),
-minimize the transverse ($rms_{x,y}$) beam size and transverse momentum ($rms_{px,py}$)
-at the location of interest in the beam line ($s_1$).
-Where $s_1$ is the longitudinal entrance of the fifth quadrupole. 
-Minimizing the beam size at this location is essential to 
-to preventing loss of particles by scraping.
-Preventing scraping ensures better transmission through the wakefield structures downstream. 
-Less divergence in the beam (lower transverse momentum) 
-reduces growth of transverse beam size during transport in bending elements, 
-which also helps with transmission downstream. 
-The next two objectives (\ref{eq:awa:p2}) minimize the 
-longitudinal beam size ($rms_s$), and energy spread (dE) at $s_1$.
-This helps reduce longitudinal beam size growth in bending elements.
-
-Three constraints were also defined to help guide the algorithm;
-Eqs.~\ref{eq:awa:c1} to \ref{eq:awa:c3}.
-The bounding values may seem large, but this is done to avoid over constraing the 
-problem in early generations. If the constraints are set tighter, 
-runs do not reach the second generation, because enough satisfactory 
-points are not produced to fill a complete generation. 
-Leaving the value large allows for enough simulations to finish
-in order to reach the next generation, and subsequent improved points in later generations.
-The difference constraint, Eq.~\ref{eq:awa:c3}, is used to favor nearly round beams.
-This prevents one dimension from becoming disproportionately large compared to the other.
-In this case, there is some room in the beam pipe to allow the y dimension to grow, but round beams 
-are preferred for easier data analysis.
-
-Equations (\ref{eq:awa:firstconstr}) to
-(\ref{eq:awa:lastdvar}) define the charge, gun voltage, linac voltages, 
-laser radius, gun phase, and linac cavity phases (in that order). 
-These are parameters in the simulation 
-that must be defined, but do not vary during the optimization.
-%\vspace{-1em}
-As introduced in Section \ref{ferrario}, we define the AWA optimization 
-design variables, objectives, and constraints in the OPAL input file as shown in
-the following code: %equations (\ref{eq:awa:p1}) to (\ref{eq:awa:lastdvar}).
-
-\vspace{0.2cm}
-{\footnotesize \begin{verbatim}
-
-	// Gun variables 
-	dv0: DVAR, VARIABLE="IBF",    LOWERBOUND=300.0, UPPERBOUND=500.0;
-	dv1: DVAR, VARIABLE="IM",     LOWERBOUND=180.0, UPPERBOUND=280.0;
-
-	// Quad variables 
-	dv4: DVAR, VARIABLE="KQ1", LOWERBOUND=-8.0, UPPERBOUND=8.0;
-	dv5: DVAR, VARIABLE="KQ2", LOWERBOUND=-8.0, UPPERBOUND=8.0;
-	dv6: DVAR, VARIABLE="KQ3", LOWERBOUND=-8.0, UPPERBOUND=8.0;
-	dv7: DVAR, VARIABLE="KQ4", LOWERBOUND=-8.0, UPPERBOUND=8.0;
-
-	//Objectives
-	de3: OBJECTIVE,EXPR="fabs(statVariableAt('dE',19.4))";
-	rmss3: OBJECTIVE,EXPR="fabs(statVariableAt('rms_s',19.4))";
-	rmsx3: OBJECTIVE,EXPR="fabs(statVariableAt('rms_x',19.4))";
-	rmsy3: OBJECTIVE,EXPR="fabs(statVariableAt('rms_y',19.4))";
-	rmspx3: OBJECTIVE,EXPR="fabs(statVariableAt('rms_px',19.4))";
-	rmspy3: OBJECTIVE,EXPR="fabs(statVariableAt('rms_py',19.4))";
-
-	//Kicker apeture
-	c1: CONSTRAINT, EXPR="fabs(statVariableAt('rms_x',16.5))<0.1";
-	c2: CONSTRAINT, EXPR="fabs(statVariableAt('rms_y',16.5))<0.1";
-	c3: CONSTRAINT, EXPR="fabs(statVariableAt('rms_y',16.5)-statVariableAt('rms_x',16.5))<0.005";
-
-	OPTIMIZE, INPUT="tmpl/optLinac-40nC.tmpl",
-	OUTPUT="optLinac-40nC",
-	OUTDIR="results",
-	OBJECTIVES = {rmss3, rmsx3, rmsy3, rmspx3, rmspy3, de3},
-	DVARS = {dv0, dv1, dv4, dv5, dv6, dv7},
-	CONSTRAINTS = {c1, c2, c3},
-	INITIALPOPULATION=656,
-	MAXGENERATIONS=200,
-	NUM_MASTERS=1,
-	NUM_COWORKERS=8,
-	SIMTMPDIR="tmp",
-	TEMPLATEDIR="tmpl",
-	FIELDMAPDIR="fieldmaps",
-	NUM_IND_GEN=328,
-	GENE_MUTATION_PROBABILITY=0.01,
-	MUTATION_PROBABILITY=0.01,
-	RECOMBINATION_PROBABILITY=0.09;
-	QUIT;
-
-	\end{verbatim}}
-\vspace{0.2cm}
-
-Design variables include the currents in two gun solenoids (IBF and IM), 
-and four quadrupole strengths (KQ1-KQ2). The objectives include
-beam size (transverse and longitudinal), transverse momentum, and energy spread as
-defined in Eqs. (\ref{eq:awa:p1}) to (\ref{eq:awa:p4}). 
-The location at the entrance of the kicker is $s_0=16.45$~meters, 
-and the location of interest for objectives is $s_1=19.4$~meters.
-
-All simulations for this experiment were carried out on Bebop a
-high performance computing (HPC)
-cluster provided by the Laboratory Computing Resource Center (LCRC)
-at Argonne National Laboratory (ANL). We used Intel Knights Landing 
-(KNL) processors at 1.3 GHz with 128 GB of memory 
-and 64 cores per node. There are 352 compute nodes available on 
-Bebop, with a total of 22,528 cores. All jobs were run and compared 
-on 8 cores each, which allowed 8 jobs per node on the KNLs.
-This in combination with the number of nodes available 
-allows for very large optimization jobs, like the AWA case.
-Typical runs for this paper used 41 nodes, which corresponds to 2624 KNL cores 
-and a generation size of 328 individuals.
-
+\subsection{Tests}
+Before running a full scale optimization of the problem described in \ref{awaproblem}, 
+several computational settings, and 
 \subsubsection{Time Step Scan} \label{awa:subsection:test}
@@
 
+\subsubsection{AWA Optimization Problem}
+\begin{align}
+\text{min}  \quad & \text{rms}_{x}\left(s = s_3\right), \quad \text{rms}_{y}\left(s = s_3\right) \label{eq:awa:p1}\\
+& \text{rms}_{px}\left(s = s_3\right), \quad \text{rms}_{py}\left(s = s_3\right), \label{eq:awa:p2}\\
+& \text{rms}_{s}\left(s = s_3\right), \quad dE \label{eq:awa:p4} \\
+\text{subject to} \quad & rms_x(s=s_1) < 0.1 \, [m]\label{eq:awa:c1}\\
+\quad & rms_y(s=s_1) < 0.1\, [m]\label{eq:awa:c2}\\
+\quad & |rms_y(s=s_1) - rms_x(s=s_1) | < 0.005 \, [m]\label{eq:awa:c3}\\
+\quad & q = 40 \left[\text{nC}\right] \label{eq:awa:firstconstr}\\
+\quad & \text{Volt}_{\text{Gun}} = 64\left[\text{MV/m}\right] \label{eq:awa:lastconstr}\\
+\quad & \text{Volt}_{\text{Linac}} = 24-25\left[\text{MV/m}\right] \\
+\quad & R_x = R_y = 9 \left[\text{mm}\right] \label{eq:awa:firstdvar}\\
+\quad & \phi_{\text{gun}} =-20^\circ \label{eq:awa:gphidvar}\\
+\quad & \phi_{\text{linac}} =-20^\circ \label{eq:awa:lastdvar}
+\end{align}
+
+The first four objectives, Eqs. (\ref{eq:awa:p1}) to (\ref{eq:awa:p2}),
+minimize the transverse ($rms_{x,y}$) beam size and transverse momentum ($rms_{px,py}$)
+at the location of interest in the beam line ($s_3$).
+%Where $s_3$ is the longitudinal entrance of the fifth quadrupole. 
+Minimizing the beam size at this location is essential to 
+to preventing loss of particles by scraping.
+Preventing scraping ensures better transmission through the wakefield structures downstream. 
+Less divergence in the beam (lower transverse momentum) 
+reduces growth of transverse beam size during transport in bending elements, 
+which also helps with transmission downstream. 
+The next two objectives (\ref{eq:awa:p2}) minimize the 
+longitudinal beam size ($rms_s$), and energy spread (dE) at $s_1$.
+This helps reduce longitudinal beam size growth in bending elements.
+
+Three constraints were also defined to help guide the algorithm;
+Eqs.~\ref{eq:awa:c1} to \ref{eq:awa:c3}.
+The bounding values may seem large, but this is done to avoid over constraing the 
+problem in early generations. If the constraints are set tighter, 
+runs do not reach the second generation, because enough satisfactory 
+points are not produced to fill a complete generation. 
+Leaving the value large allows for enough simulations to finish
+in order to reach the next generation, and subsequent improved points in later generations.
+The difference constraint, Eq.~\ref{eq:awa:c3}, is used to favor nearly round beams.
+This prevents one dimension from becoming disproportionately large compared to the other.
+In this case, there is some room in the beam pipe to allow the y dimension to grow, but round beams 
+are preferred for easier data analysis.
+
+Equations (\ref{eq:awa:firstconstr}) to
+(\ref{eq:awa:lastdvar}) define the charge, gun voltage, linac voltages, 
+laser radius, gun phase, and linac cavity phases (in that order). 
+These are parameters in the simulation 
+that must be defined, but do not vary during the optimization.
+%\vspace{-1em}
+As introduced in Section \ref{ferrario}, we define the AWA optimization 
+design variables, objectives, and constraints in the OPAL input file as shown in
+the following code: %equations (\ref{eq:awa:p1}) to (\ref{eq:awa:lastdvar}).
+
+\vspace{0.2cm}
+{\footnotesize \begin{verbatim}
+
+	// Gun variables 
+	dv0: DVAR, VARIABLE="IBF",    LOWERBOUND=300.0, UPPERBOUND=500.0;
+	dv1: DVAR, VARIABLE="IM",     LOWERBOUND=180.0, UPPERBOUND=280.0;
+
+	// Quad variables 
+	dv4: DVAR, VARIABLE="KQ1", LOWERBOUND=-8.0, UPPERBOUND=8.0;
+	dv5: DVAR, VARIABLE="KQ2", LOWERBOUND=-8.0, UPPERBOUND=8.0;
+	dv6: DVAR, VARIABLE="KQ3", LOWERBOUND=-8.0, UPPERBOUND=8.0;
+	dv7: DVAR, VARIABLE="KQ4", LOWERBOUND=-8.0, UPPERBOUND=8.0;
+
+	//Objectives
+	de3: OBJECTIVE,EXPR="fabs(statVariableAt('dE',19.4))";
+	rmss3: OBJECTIVE,EXPR="fabs(statVariableAt('rms_s',19.4))";
+	rmsx3: OBJECTIVE,EXPR="fabs(statVariableAt('rms_x',19.4))";
+	rmsy3: OBJECTIVE,EXPR="fabs(statVariableAt('rms_y',19.4))";
+	rmspx3: OBJECTIVE,EXPR="fabs(statVariableAt('rms_px',19.4))";
+	rmspy3: OBJECTIVE,EXPR="fabs(statVariableAt('rms_py',19.4))";
+
+	//Kicker apeture
+	c1: CONSTRAINT, EXPR="fabs(statVariableAt('rms_x',16.5))<0.1";
+	c2: CONSTRAINT, EXPR="fabs(statVariableAt('rms_y',16.5))<0.1";
+	c3: CONSTRAINT, EXPR="fabs(statVariableAt('rms_y',16.5)-statVariableAt('rms_x',16.5))<0.005";
+
+	OPTIMIZE, INPUT="tmpl/optLinac-40nC.tmpl",
+	OUTPUT="optLinac-40nC",
+	OUTDIR="results",
+	OBJECTIVES = {rmss3, rmsx3, rmsy3, rmspx3, rmspy3, de3},
+	DVARS = {dv0, dv1, dv4, dv5, dv6, dv7},
+	CONSTRAINTS = {c1, c2, c3},
+	INITIALPOPULATION=656,
+	MAXGENERATIONS=200,
+	NUM_MASTERS=1,
+	NUM_COWORKERS=8,
+	SIMTMPDIR="tmp",
+	TEMPLATEDIR="tmpl",
+	FIELDMAPDIR="fieldmaps",
+	NUM_IND_GEN=328,
+	GENE_MUTATION_PROBABILITY=0.01,
+	MUTATION_PROBABILITY=0.01,
+	RECOMBINATION_PROBABILITY=0.09;
+	QUIT;
+
+	\end{verbatim}}
+\vspace{0.2cm}
+
+Design variables include the currents in two gun solenoids (IBF and IM), 
+and four quadrupole strengths (KQ1-KQ2). The objectives include
+beam size (transverse and longitudinal), transverse momentum, and energy spread as
+defined in Eqs. (\ref{eq:awa:p1}) to (\ref{eq:awa:p4}). 
+The location at the entrance of the kicker is $s_0=16.45$~meters, 
+and the location of interest for objectives is $s_1=19.4$~meters.
+
 \subsubsection{AWA Optimization Results}
+All simulations for this experiment were carried out on Bebop a
+high performance computing (HPC)
+cluster provided by the Laboratory Computing Resource Center (LCRC)
+at Argonne National Laboratory (ANL). We used Intel Knights Landing 
+(KNL) processors at 1.3 GHz with 128 GB of memory 
+and 64 cores per node. There are 352 compute nodes available on 
+Bebop, with a total of 22,528 cores. All jobs were run and compared 
+on 8 cores each, which allowed 8 jobs per node on the KNLs.
+This in combination with the number of nodes available 
+allows for very large optimization jobs, like the AWA case.
+Typical runs for this paper used 41 nodes, which corresponds to 2624 KNL cores 
+and a generation size of 328 individuals.
+
 With the time steps and hyper parameters set by the work in \ref{awa:subsection:test}, 

### 2018-07-10 paper/theor-experiment.tex
more info on time step scan

@@
 
-\subsection{Tests}
+\subsubsection{Time Step Scan} \label{awa:subsection:test}
 Before running a full scale optimization of the problem described in \ref{awaproblem}, 
-several computational settings, and 
-\subsubsection{Time Step Scan} \label{awa:subsection:test}
-A study on time step and 
-number of particles was done to reduce the time to simulation while 
+a study on time step and number of particles in the simulation model 
+was done to reduce the time to simulation while 
 maintaining the physics of interest. 
@@
 and parallelized in the x and y directions.
-After comparing several options we choose ten thousand particles 
+After comparing several options (1,000, 10,000, 20,000, 50,000, 100,000) 
+with a small time step, the number of particles was fixed at ten thousand.
+Next several time steps were explored, see Table~\ref{timestep}.
+The largest steps were too big to resolve the physics needed.
+See low fidelity plot in Fig.~\ref{tstep} for $dT=$\num{5E-11} results.  
+In the drifts and linac tanks, \num{1E-11} was sufficient, 
+but still not acceptable near the quadrupoles.
+
 in combination with adjusting the time step (dT) near sensitive elements 
-(i.e. quadurpoles, kicker). 
+(i.e. quadurpoles, kicker, septum). 
 The resulting simulations are low fidelity, but closely approximate 
 the mid fidelity simulations for metrics of interest, as shown in 
-Fig. \ref{tstep}. For all models, the longitudinal parameters (rms$_s$ and energy) 
+Fig.~\ref{tstep}. For all models, the longitudinal parameters (rms$_s$ and energy) 
 are calculated correctly, but we see discrepancies in the transverse 
-rms$_x$ and $\epsilon_x$ in the low fidelity results. The
+(rms$_x$ and $\epsilon_x$) for low fidelity results. This discrepancy is 
+what led to The
 average run time of each simulation with the adjusted time steps was 1.6~minutes.
 In comparison the mid fidelity simulations ran for 18~minutes.
+Note, a smaller time step, \num{1E-13}, is always used in the gun where the 
+beam is low energy and changing rapidly.
 %A summary of the parameters used is listed in Table \ref{fidelity}.
@@
 \end{figure}
+
+\begin{table}%[h!]
+	\begin{center}
+		\caption{Checkmarks (\cmark) indicate desired physics is resolved. 
+			An (\xmark) indicates the time step is too large.}
+		\label{timestep}
+		\begin{tabular*}{0.6\textwidth}{c c c c }
+			\hline\noalign{\smallskip}
+			Time Step (dT) & Linac & Drift & Quadrupoles \\
+			\noalign{\smallskip}\hline\noalign{\smallskip}
+			$5 \times10^{-10}$  & \xmark & \xmark & \xmark \\
+			$1 \times10^{-10}$  & \xmark & \xmark & \xmark \\
+			$5 \times10^{-11}$  & \xmark & \xmark & \xmark \\
+			$1 \times10^{-11}$  & \cmark & \cmark & \xmark \\
+			$5 \times10^{-12}$  & \cmark & \cmark & \xmark \\
+			$1 \times10^{-12}$  & \cmark & \cmark & \cmark \\
+			\noalign{\smallskip}\hline
+		\end{tabular*}
+	\end{center}
+\end{table}
 

### 2018-07-10 paper/prab.tex
copied paper into prab template

--- 2018-07-10 paper/paper.tex
@@
-\documentclass[final]{siamltex}
+\documentclass[%
+reprint,
+%superscriptaddress,
+%groupedaddress,
+%unsortedaddress,
+%runinaddress,
+%frontmatterverbose, 
+%preprint,
+%showpacs,preprintnumbers,
+%nofootinbib,
+%nobibnotes,
+%bibnotes,
+amsmath,amssymb,
+aps,
+%pra,
+%prb,
+%rmp,
+%prstab,
+%prstper,
+%floatfix,
+]{revtex4-1}
 
+\usepackage{dcolumn}% Align table columns on decimal point
+\usepackage{bm}% bold math
 \usepackage{todonotes}
-
-\usepackage{graphicx}
+\usepackage{siunitx}
+\usepackage{pifont}% http://ctan.org/pkg/pifont
+\newcommand{\cmark}{\ding{51}}%
+\newcommand{\xmark}{\ding{55}}%
 \usepackage{booktabs}
-\usepackage{cite}
+%\usepackage{cite}
 \usepackage{amsmath}
 \usepackage{amsfonts}
-\usepackage{graphicx}
 \usepackage{url}
-\usepackage{footmisc}
-\usepackage{multicol}
+%\usepackage{footmisc}
+%\usepackage{multicol}
 \usepackage{color}
@@
 \usetikzlibrary{plotmarks}
-\usepackage{subcaption}
-
 \usepackage{listings}
@@
 \newcommand{\nrnote}[1]{\textsf{{\color{violet}{ NN note:}   #1 }}}
+
 \begin{document}
@@
   with Application To Beam Dynamics}
+%\thanks{A footnote to the article title}%
 
-\author{N. Neveu\footnotemark[7]\ \footnotemark[8]
-  \and Y. Ineichen\footnotemark[2]\ \footnotemark[3]\ \footnotemark[4]
-  \and A. Adelmann\footnotemark[2]\ \footnotemark[6]
-  \and P. Arbenz\footnotemark[4]
-  \and C. Bekas\footnotemark[3]
-  \and A. Curioni\footnotemark[3]
-  \and A. Kolano\footnotemark[2]\ \footnotemark[5]
-  \and C. Metzger-Kraus 
-}
+\author{N. Neveu}
+\altaffiliation[Also at ]{Argonne National Laboratory, USA}%Lines break automatically or can be forced with \\
 
-\maketitle
+\author{L. Spentzouris}
+\affiliation{Illinois Institute of Technology, Chicago, IL}
 
-\renewcommand{\thefootnote}{\fnsymbol{footnote}}
-\footnotetext[2]{PSI, Villigen, Switzerland}
-\footnotetext[3]{IBM Research -- Zurich, Switzerland}
-\footnotetext[4]{Department of Computer Science, ETH Zurich, Switzerland}
-\footnotetext[5]{University of Huddersfield, West Yorkshire, United Kingdom}
-\footnotetext[1]{Illinois Institute of Technology, Chicago, USA}
-\footnotetext[8]{Argonne National Laboratory, Lemont, USA}
-\footnotetext[6]{Corresponding author: \url{andreas.adelmann@psi.ch}}
-\renewcommand{\thefootnote}{\arabic{footnote}}
+\author{Andreas Adelmann}
+\email{andreas.adelmann@psi.ch}
+\author{A. Kolano}
+\altaffiliation[Also at ]{
+	University of Huddersfield, West Yorkshire, United Kingdom}
+
+\affiliation{
+	PSI, Villigen, Switzerland}%
+
+\author{Y Ineichen}%
+\altaffiliation[Also at ]{Department of Computer Science, ETH Zurich, Switzerland}%Lines break
+
+\author{C. Bekas}
+\author{A. Curioni}
+
+\affiliation{IBM Research, Zurich, Switzerland }%
+
+\author{P. Arbenz}
+\affiliation{%
+	Department of Computer Science, ETH Zurich, Switzerland}%
+
+\author{C. Metzger-Kraus }
+\affiliation{% 
+	place holder \\
+}%
+
+\date{\today}% It is always \today, today,
+%  but any date may be explicitly specified
 
@@
   complex interplay of several conflicting design goals.
-
 We propose to tackle this problem by means of multi-objective optimization
@@
   and scalable software framework.
-
 In this paper, we present the implementation of such a general-purpose
@@
   optimization tasks.
-
 Using evolutionary algorithms and \textsc{OPAL}~simulations as optimizer and
@@
   dynamics.
+
 \end{abstract}
 
-\begin{keywords}
-multi-objective optimization, beam dynamics, high performance computing
-\end{keywords}
+\pacs{Valid PACS appear here}% PACS, the Physics and Astronomy
+% Classification Scheme.
+%\keywords{Suggested keywords}%Use showkeys class option if keyword
+%display desired
+\maketitle
 
@@
 
-\begin{figure}[h!]
-\begin{center}\normalsize
-
+\begin{figure}%[h!]
+%\begin{center}\normalsize
+	\scalebox{0.8}{
 	\pgfdeclarelayer{background}
 	\pgfsetlayers{background,main}
-  \begin{tikzpicture}[text=black]%[scale=0.95, transform shape]
+	\begin{tikzpicture}[text=black]%[scale=0.05]%, transform shape]
 	\input{figures/opt-framework_code.tex}
 	\end{tikzpicture}
+}
+%\end{center}
+%\end{center}
 \caption{Multi-objective framework: the pilot (master) solves the
@@
 	algorithms and workers running forward solves.}
-\label{fig:framenetwork}
-\end{center}
-\end{figure}
+\end{figure}\label{fig:framenetwork}
 
@@
   we implemented an expression parser using Boost
-  Spirit\footnote{\url{http://boost-spirit.com/}}.
+%  Spirit\footnote{\url{http://boost-spirit.com/}}.
 In addition to the parser, we need an evaluator able to evaluate an expression,
@@
   a \texttt{std::vector} of Boost
-  variants\footnote{\url{www.boost.org/doc/html/variant.html}} that can be
+%  variants\footnote{\url{www.boost.org/doc/html/variant.html}} that can be
   booleans, strings or floating point values.
@@
 As shown in Listing 5 this is done by creating a collection of Boost
-  functions\footnote{\url{www.boost.org/libs/function/}} corresponding to the
+%  functions\footnote{\url{www.boost.org/libs/function/}} corresponding to the
   available custom functions in expressions and passing this to the

### 2018-07-11 paper/prab.tex
reformatting for prab

@@
 \begin{figure}%[h!]
-%\begin{center}\normalsize
+%\begin{center}%\normalsize
 	\scalebox{0.8}{
@@
 }
-%\end{center}
 %\end{center}
@@
     \centering
+    \scalebox{1}{
     \begin{tikzpicture}[scale=0.8, transform shape, text=black]
@@
     \end{tikzpicture}
+	}
   \caption{Schematic view of interplay between selector and variator. The
@@
   \centering
+  \scalebox{0.85}{
   \begin{tikzpicture}[text=black]
@@
   \end{tikzpicture}
+}
 
@@
 
-\noindent\begin{minipage}{\textwidth}
-\begin{code}[Assembling the optimizer from components]
+%\noindent\begin{minipage}{0.48\textwidth}
+%\noindent
+\begin{code}[Assembling the optimizer \\ from components]
 typedef OpalInputFileParser Input_t;
@@
 \end{code}
-\end{minipage}
+%\end{minipage}
 
@@
 
-\noindent\begin{minipage}{\textwidth}
+%\noindent\begin{minipage}{0.48\textwidth}
 \begin{code}[Optimizer API]
@@
 
-\noindent\begin{minipage}{\textwidth}
+%\noindent\begin{minipage}{\textwidth}
 \begin{code}[Creating function pointer for registering functor]
@@
 ff = average();
-funcs.insert(std::pair<std::string, client::function::type>
+funcs.insert(std::pair<std::string, 
+		client::function::type> 
        		("my_average_name", ff));
 \end{code}
-\end{minipage}
+%\end{minipage}
 
@@
 %
+\small{
 \begin{align} \label{eqn:bench}
-  \text{ min} \quad & \quad \left[ 1 - \exp \left( -1 \left(
+  \text{ min} & \left[ 1 - \exp \left( -1 \left(
     \left(x_1 - \frac{1}{\sqrt{3}} \right)^2 +
@@
 \end{align}
+}
 %
@@
   obj1: OBJECTIVE,
-    EXPR="1- exp(-1 * (sq(x1 - 1/sqrt(3)) + sq(x2 - 1/sqrt(3)) + sq(x3 - 1/sqrt(3))))";
+    EXPR="1- exp(-1 * (sq(x1 - 1/sqrt(3)) 
+    + sq(x2 - 1/sqrt(3)) 
+    + sq(x3 - 1/sqrt(3))))";
   obj2: OBJECTIVE,
-    EXPR="1- exp(-1 * (sq(x1 + 1/sqrt(3)) + sq(x2 + 1/sqrt(3)) + sq(x3 + 1/sqrt(3))))";
+    EXPR="1- exp(-1 * (sq(x1 + 1/sqrt(3)) 
+    + sq(x2 + 1/sqrt(3)) 
+    + sq(x3 + 1/sqrt(3))))";
 

### 2018-07-11 paper/theor-experiment.tex
reformatting for prab

@@
 %\vspace{-1em}
+
 In addition to the physics challenges, we chose this model to demonstrate the ability of the framework to tackle large problems.
@@
 	\begin{center}
-		\caption{Checkmarks (\cmark) indicate desired physics is resolved. 
-			An (\xmark) indicates the time step is too large.}
+		\caption{Checkmarks (\cmark) indicate desired physics is resolved at that time step. 
+			An (\xmark) indicates the time step is too large, and results are nonphysical.}
 		\label{timestep}
-		\begin{tabular*}{0.6\textwidth}{c c c c }
+		\begin{tabular*}{0.48\textwidth}{c @{\extracolsep{\fill}} C c D }
 			\hline\noalign{\smallskip}
@@
 		\label{fidelity}
-		\begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} C c D }
+		\begin{tabular*}{0.48\textwidth}{l @{\extracolsep{\fill}} C c D }
 			\hline\noalign{\smallskip}
@@
 		\label{extable}
-		\begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} C C D }
+		\begin{tabular*}{0.48\textwidth}{l @{\extracolsep{\fill}} C C D }
 			\hline\noalign{\smallskip}
@@
 	\centering
-	\begin{subfigure}{0.49\textwidth}
+	\begin{minipage}{0.49\textwidth}
 		\centering
 		\includegraphics[width=\textwidth]{Report/ex-pareto1}
-		\caption{Pareto fronts at $s_1$.}
-		\label{expareto1}
-	\end{subfigure}
-	\begin{subfigure}{0.49\textwidth}
+		(a) Pareto fronts for ex-1 through ex-4 at $s_1$.
+		%\caption{(a) Pareto fronts at $s_1$.}
+		%\label{expareto1}
+	\end{minipage}
+	\begin{minipage}{0.49\textwidth}
 		\centering
 		\includegraphics[width=\textwidth]{Report/ex-pareto2}
-		\caption{Pareto fronts at $s_2$.}
-		\label{expareto2}
-	\end{subfigure}
-	\caption{Comparison of Pareto fronts for initial optimization experiments.}
+		(b) Pareto fronts for ex-1 through ex-4 at $s_2$.
+		%\caption{(b) Pareto fronts at $s_2$.}
+		%\label{expareto2}
+	\end{minipage}
+	\caption{Comparison of Pareto fronts for initial optimization experiments, ex-1 through ex-4.}
 	\label{expareto}
@@
 
-\subsubsection{AWA Optimization Problem}
+\subsubsection{TBA Optimization Problem}
 \begin{align}

### 2018-07-11 paper/prab.tex
starting to fix verbatim sections

@@
 \newcommand{\xmark}{\ding{55}}%
+\usepackage{fancyvrb}
 \usepackage{booktabs}
@@
 \vspace{0.2cm}
-{\footnotesize \begin{verbatim}
+\begin{Verbatim}[fontsize=\scriptsize]
   name: OBJECTIVE,
         EXPR="5 * average(42.0, "measurement.dat") + ENERGY";
-\end{verbatim}}
+\end{Verbatim}
 \vspace{0.2cm}
@@
 \vspace{0.2cm}
-{\footnotesize \begin{verbatim}
+\begin{flushleft}
+\noindent
+\begin{Verbatim}[fontsize=\scriptsize]
 d1: DVAR, VARIABLE="x1", LOWERBOUND="-1.0", UPPERBOUND="1.0";
@@
 EXPR="1- exp(-1 * (sq(x1 - 1/sqrt(3)) 
-    + sq(x2 - 1/sqrt(3)) 
-    + sq(x3 - 1/sqrt(3))))";
++ sq(x2 - 1/sqrt(3)) + sq(x3 - 1/sqrt(3))))";
 obj2: OBJECTIVE,
 EXPR="1- exp(-1 * (sq(x1 + 1/sqrt(3)) 
-    + sq(x2 + 1/sqrt(3)) 
-    + sq(x3 + 1/sqrt(3))))";
++ sq(x2 + 1/sqrt(3)) + sq(x3 + 1/sqrt(3))))";
 
@@
 opt: OPTIMIZE, OBJECTIVES=objs, DVARS=dvars, CONSTRAINTS=constrs;
-\end{verbatim}}
+\end{Verbatim}
+\end{flushleft}
+
 \vspace{0.2cm}

### 2018-07-11 paper/theor-experiment.tex
starting to fix verbatim sections

@@
   \caption{Illustration of the Ferrario matching criteria: beam emittance
-  attains a maximum and rms beamsize a minimum at the entrance to the first
+  attains a maximum and rms beam size a minimum at the entrance to the first
   accelerating traveling wave structure.}
@@
   the peak finder Python script result files
-
-\vspace{0.2cm}
-{\footnotesize \begin{verbatim}
+%
+%\vspace{0.2cm}
+\begin{flushleft}
+\noindent
+\begin{Verbatim}[fontsize=\scriptsize]
 rmsx:  OBJECTIVE, EXPR="statVariableAt("rms_x-err.dat", "var")";
@@
 statVariableAt("rms_x-peak.dat", "var"))";
-\end{verbatim}}
+\end{Verbatim}
+\end{flushleft}
 \vspace{0.2cm}
@@
   can be included in the \textsc{OPAL}~input file as shown below:
-
-\vspace{0.2cm}
-{\footnotesize \begin{verbatim}
+%\vspace{0.2cm}
+\begin{flushleft}
+\noindent
+\begin{Verbatim}[fontsize=\scriptsize]
 d1: DVAR, VARIABLE="SIGX", LOWERBOUND="0.00025", UPPERBOUND="0.00029";
@@
 CONSTRAINTS=constrs;
-\end{verbatim}}
+\end{Verbatim}
+\end{flushleft}
 \vspace{0.2cm}
@@
   Figure~\ref{fig:pareto_front_21}, represents an optimal solution, where
-  emittance and beamsize values are compromised to achieve the best agreement
+  emittance and beam size values are compromised to achieve the best agreement
   with the Ferrario matching point.
-We selected individual $3$ based on a comparison of the emittance and beamsize
+We selected individual $3$ based on a comparison of the emittance and beam size
   characteristics of all solutions and by retaining the feasibility of the
   beam line optics parameters.
-The design variables, emittance and beamsize of the selected solution are
+The design variables, emittance and beam size of the selected solution are
   shown in Table~\ref{tbl:des_vars} and Figure~\ref{fig:rmsemit}.
@@
   \includegraphics[width=0.8\linewidth]{Report/iff_plot_emrms}
-  \caption{Beamsize and emittance of individual $3$.}
+  \caption{Beam size and emittance of individual $3$.}
   \label{fig:rmsemit}
@@
   MeV injector.
-The results for both rms beamsize and emittance are shown in
+The results for both rms beam size and emittance are shown in
   Figure~\ref{fig:et-vs-tt}.

### 2018-07-11 paper/theor-experiment.tex
starting to fix verbatim sections

@@
 \begin{flushleft}
-\noindent
 \begin{Verbatim}[fontsize=\scriptsize]
@@
 precede the optimization parameters in the OPAL input file.
-
+%
 \vspace{0.2cm}
-{\footnotesize \begin{verbatim}
+\begin{Verbatim}[fontsize=\scriptsize]
 OPTIMIZE, INPUT="tmpl/optLinac_40nC.tmpl",
@@
 QUIT;
-	\end{verbatim}}
+\end{Verbatim}
 \vspace{0.2cm}
@@
 the following code: %equations (\ref{eq:awa:p1}) to (\ref{eq:awa:lastdvar}). 
-
-\vspace{0.2cm}
-{\footnotesize \begin{verbatim}
+%\vspace{0.2cm}
+\begin{Verbatim}[fontsize=\scriptsize]
 
@@
 c2: CONSTRAINT, EXPR="fabs(statVariableAt('rms_y',16.5))<0.1";
-	c3: CONSTRAINT, EXPR="fabs(statVariableAt('rms_y',16.5)-statVariableAt('rms_x',16.5))<0.005";
+c3: CONSTRAINT, EXPR="fabs(statVariableAt('rms_y',16.5)
+			-statVariableAt('rms_x',16.5))<0.005";
 
@@
 QUIT;
-
-	\end{verbatim}}
+\end{Verbatim}
 \vspace{0.2cm}

### 2018-07-11 paper/theor-experiment.tex
fixing figures of tba beam line

@@
 
-\begin{figure}
+\def \gunheight {25}
+\def \quadheight {35}
+\def \quadleft {127}
+\def \kickerleft {160}
+\def \leftarrow{10}
+\def \bottomofarrows {29}
+\def \topofarrows {34}
+\begin{figure*}
 	\begin{tikzpicture}[every node/.style={anchor=south west,inner sep=0pt},x=1mm, y=1mm,]   
@@
 	{\includegraphics[width=\textwidth]{Report/awa-drawing}};
-	\node[fill=white, inner sep=2pt] (txt2) at (0,20) {Gun};
-	\node[fill=white, inner sep=2pt] (txt2) at (20,20) {Accelerating Cavities};
-	\node[fill=white, inner sep=2pt] (txt2) at (88,28) {Quadrupoles};
-	\draw [blue, ->, line width=1] (99,28) -- (99, 21);
-	\node[fill=white, inner sep=2pt] (txt2) at (125,10) {$s_2$};
-	\node[fill=white, inner sep=2pt] (txt2) at (112,8) {$s_1$};
-	\node[fill=white, inner sep=2pt] (txt2) at (115,30) {Kicker};
-	\draw [blue, ->, line width=1] (120,30) -- (120, 23);	
+	\node[fill=white, inner sep=2pt] (txt2) at (0,\gunheight) {\large Gun};
+	\node[fill=white, inner sep=2pt] (txt2) at (20,\gunheight) {\large Accelerating Cavities};
+	\node[fill=white, inner sep=2pt] (txt2) at (\quadleft,\quadheight) {\large Quadrupoles};
+	\draw [blue, ->, line width=1] (\quadleft+\leftarrow,\topofarrows) -- (\quadleft+\leftarrow, \bottomofarrows);
+	\node[fill=white, inner sep=2pt] (txt2) at (\kickerleft,20) {\large $s_1$};
+	\node[fill=white, inner sep=2pt] (txt2) at (\kickerleft+8,20) {\large $s_2$};
+	\node[fill=white, inner sep=2pt] (txt2) at (\kickerleft,\quadheight) {\large Kicker};
+	\draw [blue, ->, line width=1] (\kickerleft+\leftarrow-3,\topofarrows) -- (\kickerleft+\leftarrow-3, \bottomofarrows);	
+	\draw [black, ->, line width=1] (0,-2) -- (100, -2);
+	\node[fill=white, inner sep=2pt] (txt2) at (50,0) {\large Beam Direction};
 	\end{tikzpicture}
@@
 	\label{awa-linac}
-\end{figure}
+	\vspace{-7em}
+\end{figure*}
 
-\begin{figure}
+\def \septheight {65}
+\def \bottomarrow {57}
+\def \kleft {13}
+\def \sleft {41.5}
+\def \sheight {47}
+\def \beam {32}
+\begin{figure*}
 	\begin{tikzpicture}[every node/.style={anchor=south west,inner sep=0pt},x=1mm, y=1mm,]   
@@
 	{\includegraphics[width=\textwidth]{Report/tba_dogleg}};
-	\node[fill=white, inner sep=2pt] (txt2) at (2,35) {$s_1$};
-	\node[fill=white, inner sep=2pt] (txt2) at (14,35) {$s_2$};
-	\node[fill=white, inner sep=2pt] (txt2) at (33,31) {$s_3$};
-	\node[fill=white, inner sep=2pt] (txt2) at (24,50) {Septum};
-	\draw [blue, ->, line width=1] (30,50) -- (30, 42);	
-	\node[fill=white, inner sep=2pt] (txt2) at (3,50) {Kicker};
-	\draw [blue, ->, line width=1] (9.5,50) -- (9.5, 43);
+	\node[fill=white, inner sep=2pt] (txt2) at (3,\sheight) {\large $s_1$};
+	\node[fill=white, inner sep=2pt] (txt2) at (20,\sheight) {\large $s_2$};
+	\node[fill=white, inner sep=2pt] (txt2) at (46,45) {\large $s_3$};
+	\node[fill=white, inner sep=2pt] (txt2) at (33,\septheight) {\large Septum};
+	\draw [blue, ->, line width=1] (\sleft,\septheight) -- (\sleft, \bottomarrow);	
+	\node[fill=white, inner sep=2pt] (txt2) at (7,\septheight) {\large Kicker};
+	\draw [blue, ->, line width=1] (\kleft,\septheight) -- (\kleft, \bottomarrow);
+	\draw [black, ->, line width=1] (0,\beam) -- (100,\beam);
+	\node[fill=white, inner sep=2pt] (txt2) at (50,\beam+2) {\large Beam Direction};
 	\end{tikzpicture}
+	\vspace{-10em}
 	\caption{Continuation of the high charge beam line layout at the AWA, top view. 
-		This is the proposed two beam acceleration section.}
+		This is the proposed two beam acceleration section. 
+		Only the kicker in this drawing is installed}
 	\label{awa-tba}
-\end{figure}
+\end{figure*}
 %
@@
 %
+
 \vspace{0.2cm}

### 2018-07-11 paper/theor-experiment.tex
edits to timing and hyper parameter sections

@@
 %\vspace{0.2cm}
+
 \begin{flushleft}
@@
 %\vspace{-7em}
+
 \subsection{AWA Photoinjector Optimization} \label{awaproblem}
@@
 experiments performed at AWA, which motivates this work.
-Prior experimental results were limited by beam size as the beam passed through small aperture 
+
+Prior experimental results were limited by beam size when the beam passed through small aperture 
 wakefield structures located downstream. 
@@
 The simulation model includes the linac, kicker, and septum. 
-The optimization location is chosen as the entrance to the fifth quadrupole, $s_3$, on the dog leg.
-Minimizing beam sizes here will enable capture and further focus with quadrupoles five and six before space charge effects dominate the beam. 
+The optimization location is chosen as the longitudinal 
+entrance to the first quadrupole on the dog leg ($s_3$), see Fig.~\ref{awa-tba}.
+Minimizing beam sizes here will enable capture and further focusing before space charge effects dominate the beam. 
 This will also enable cleaner transport through downstream elements.
@@
 \def \sheight {47}
-\def \beam {32}
+\def \beam {35}
 \begin{figure*}
@@
 	\end{tikzpicture}
-	\vspace{-10em}
+	\vspace{-12em}
 	\caption{Continuation of the high charge beam line layout at the AWA, top view. 
@@
 The design variables include the two gun solenoids and 
-the first four quadrupoles. The objectives are calculated at 
-$s_3=19.4$~[m], at the entrance of the fifth quadrupole in Fig.~\ref{awa-tba}.  
+the first four quadrupoles. 
 This problem encompasses high dimensionality 
 and nonlinear effects such as space charge. There is no existing information
-that accurately predicts where the Pareto front will fall. This work is also meaningful in that
+that accurately predicts where the Pareto fronts will fall. This work is also meaningful in that
 it will guide future operations at the AWA.
@@
 \subsubsection{Time Step Scan} \label{awa:subsection:test}
-Before running a full scale optimization of the problem described in \ref{awaproblem}, 
+Before running a full scale optimization of the problem described in Subsection \ref{awaproblem}, 
 a study on time step and number of particles in the simulation model 
@@
 See low fidelity plot in Fig.~\ref{tstep} for $dT=$\num{5E-11} results.
-In the drifts and linac tanks, \num{1E-11} was sufficient, 
-but still not acceptable near the quadrupoles.
-
-in combination with adjusting the time step (dT) near sensitive elements 
-(i.e. quadurpoles, kicker, septum). 
-The resulting simulations are low fidelity, but closely approximate 
-the mid fidelity simulations for metrics of interest, as shown in 
-Fig.~\ref{tstep}. For all models, the longitudinal parameters (rms$_s$ and energy) 
-are calculated correctly, but we see discrepancies in the transverse 
-(rms$_x$ and $\epsilon_x$) for low fidelity results. This discrepancy is 
-what led to The
-average run time of each simulation with the adjusted time steps was 1.6~minutes.
-In comparison the mid fidelity simulations ran for 18~minutes.
-Note, a smaller time step, \num{1E-13}, is always used in the gun where the 
-beam is low energy and changing rapidly.
-%A summary of the parameters used is listed in Table \ref{fidelity}.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.8\linewidth]{Report/timestep_comparison}
-	\caption{Comparison of different fidelity models (dT stands for time step).}
-	\label{tstep}
-\end{figure}
 
@@
 
+In the drifts and linac tanks, $dT=\num{1E-11}$ was sufficient, 
+but not acceptable near the quadrupoles. 
+For all models, the longitudinal parameters (rms$_s$ and energy) 
+are calculated correctly, but we see discrepancies in the transverse 
+(rms$_x$ and $\epsilon_x$) for low fidelity results. This discrepancy is 
+what led to the decision to adjust the time steps w.r.t. beam line elements. 
+In the linac and drift sections $dT=\num{1E-11}$ was used. 
+A time step of $dT=\num{1E-12}$ was used near sensitive elements such as the quadrupoles, kicker, and septum.
+
+The resulting simulations are low fidelity in most places, but closely approximate 
+the mid fidelity simulations for metrics of interest, as shown in 
+Fig.~\ref{tstep}.  Where we consider mid fidelity as a simulation of the 
+beam line using $dT=\num{1E-12}$ everywhere. The
+average run time of each simulation with the adjusted time steps was 1.6~minutes.
+In comparison, the mid fidelity simulation ran for 18~minutes.
+Note, a smaller time step, \num{1E-13}, is always used in the gun where the 
+beam is low energy and changing rapidly.
+%A summary of the parameters used is listed in Table \ref{fidelity}.
+
+\begin{figure}%[h]
+	\centering
+	\includegraphics[width=0.8\linewidth]{Report/timestep_comparison}
+	\caption{Comparison of different fidelity models (dT stands for time step).}
+	\label{tstep}
+\end{figure}
+
 \iffalse
@@
 \subsubsection{Hyper parameter Scan}
-While the optimization problem and goals were well defined (Section \ref{awaproblem}), 
-it was not clear what the best input parameters for the NSGA-II should be.
+While the optimization problem and goals were well defined (Subsection \ref{awaproblem}), 
+it was not clear what the best hyper parameters for the NSGA-II would be.
 These parameters include gene mutation probability, mutation probability, 
@@
 and number of generations to complete. 
-Given the beam line and design variables given in Section \ref{awaproblem},
-\nrnote{Changed variables for final run, the variables in 5.3 no longer match these small runs. Need to rework this section} 
-four optimization experiments were done with varying NSGA-II parameters. 
+Given the beam line in Fig.~\ref{awa-linac},
+four small optimization experiments were done with varying NSGA-II parameters. 
 Similar to the time step scan, 
@@
 a maximum generation limit of 100. 
-We reduced the seven objectives to the four needed to construct 
-the Pareto fronts that would be the final goal of this study.
+We reduced the six objectives to four, 
+and shortened the simulation time by moving the objectives further 
+upstream to $s_1$ and $s_2$.
 The objectives include: $\varepsilon_{x}\left(s = s_1\right)\text{, } \varepsilon_{x}\left(s = s_2\right)\text{, } \text{rms}_{s}\left(s = s_1\right)\text{, and }  \text{rms}_{s}\left(s = s_2\right)$.
 \lsnote{You could define $\varepsilon_{x1}$ to be $\varepsilon_{x} (s=s1)$ and similarly in the table and then use going forward to simplify notation}
-The optimization parameters specific to OPAL input for ex-3 are given as an example.
-Note the design variables defined in Section \ref{awaproblem}
-precede the optimization parameters in the OPAL input file.
+The OPAL input file for ex-3 is given as an example to show how optimization and design variables are defined:
 %
 
-\vspace{0.2cm}
+%\vspace{0.2cm}
 \begin{Verbatim}[fontsize=\scriptsize]
+OPTION, ECHO=FALSE;
+OPTION, INFO=TRUE;
+
+TITLE, STRING="ANL Optimisation";
+
+dv0: DVAR, VARIABLE="IBF",    LOWERBOUND=200.0, UPPERBOUND=500.0;
+dv1: DVAR, VARIABLE="IM",     LOWERBOUND=170.0, UPPERBOUND=260.0;
+dv2: DVAR, VARIABLE="GPHASE", LOWERBOUND=-30.0, UPPERBOUND=0.0;
+dv3: DVAR, VARIABLE="FWHM",   LOWERBOUND=1.5,   UPPERBOUND=10.0;
+
+// Quad values
+dv4: DVAR, VARIABLE="KQ1", LOWERBOUND=-8.0, UPPERBOUND=8.0;
+dv5: DVAR, VARIABLE="KQ2", LOWERBOUND=-8.0, UPPERBOUND=8.0;
+dv6: DVAR, VARIABLE="KQ3", LOWERBOUND=-8.0, UPPERBOUND=8.0;
+dv7: DVAR, VARIABLE="KQ4", LOWERBOUND=-8.0, UPPERBOUND=8.0;
+
+rmss1:  OBJECTIVE,EXPR="fabs(statVariableAt('rms_s',16.5))";
+emitx1: OBJECTIVE,EXPR="fabs(statVariableAt('emit_x',16.5))";
+
+rmss2:  OBJECTIVE,EXPR="fabs(statVariableAt('rms_s',18.5))";
+emitx2: OBJECTIVE,EXPR="fabs(statVariableAt('emit_x',18.5))";
+
+c1: CONSTRAINT, EXPR="fabs(statVariableAt('rms_x',16.5))<1.0e-1";
+c2: CONSTRAINT, EXPR="fabs(statVariableAt('rms_y',16.5))<1.0e-1";
+
 OPTIMIZE, INPUT="tmpl/optLinac_40nC.tmpl",
@@
 OUTDIR="results",
-OBJECTIVES = {rmss1, rmsx1, emitx1, de1, rmss2, rmsx2, emitx2},
+OBJECTIVES = {rmss1, emitx1, rmss2, emitx2},
 DVARS = {dv0, dv1, dv2, dv3, dv4, dv5, dv6, dv7},
 CONSTRAINTS = {c1, c2},
-INITIALPOPULATION=656,
-MAXGENERATIONS=200,
+INITIALPOPULATION=80,
+MAXGENERATIONS=100,
 NUM_MASTERS=1,
@@
 TEMPLATEDIR="tmpl",
-FIELDMAPDIR="fieldmaps",
-NUM_IND_GEN=328,
-GENE_MUTATION_PROBABILITY=0.8,
-MUTATION_PROBABILITY=0.8,
-RECOMBINATION_PROBABILITY=0.2;
-QUIT;
 \end{Verbatim}
-\vspace{0.2cm}
+%\vspace{0.2cm}
 
 After collection of the data for all four experiments, several metrics
-were compared, including number of generations completed in twenty four hours,
-Pareto fronts at $s_1$ and $s_2$, and the design variables at the Pareto front. 
+were compared, including number of generations completed in twenty four hours and
+Pareto fronts at $s_1$ and $s_2$.
 From Table \ref{extable}, we clearly see ex-3 is significantly 
-slower, as it evaluated about 30 to 40 fewer generations than the other experiments.
+slower, as it evaluated only 53 generations compared to the max 
+experiment, ex-1 at 96 generations.
 Perhaps this trade off would be acceptable if the Pareto front was significantly 
 improved, but from Fig. \ref{expareto}, we can see this is not the case.
-The Pareto fronts at $s_1$, are nearly identical. We could expect
-they would continue to converge given more time. 
 Similar arguments can be made for ex-2, which evaluated about 15 less generations
 with no clear benefit in either Pareto front.
+The Pareto fronts at $s_1$, are nearly identical. We could expect
+this trend would continue given more time. 
 When looking at the Pareto front at $s_2$, only ex-4 has a slight 
@@
 With ex-2 and ex-3 eliminated due to evaluation time, 
-the hyper parameters in ex-4 were chosen as the default values for subsequent runs.
+and a slightly better Pareto front at $s_2$ for ex-4, the hyper parameters in ex-4 were chosen as the default values for subsequent runs.
 \iffalse  
@@
 \subsubsection{TBA Optimization Problem}
+With computational and hyper parameters set, 
+the full optimization problem of interest is explored.
+The objectives (beam sizes and energy spread) are calculated at 
+$s_3=19.4$~[m], see Fig.~\ref{awa-tba}.
+
 \begin{align}

### 2018-07-11 paper/theor-experiment.tex
staring to edit last section

@@
 the full optimization problem of interest is explored.
-The objectives (beam sizes and energy spread) are calculated at 
+The objectives (beam sizes and energy spread) are weighted 
+equally and calculated at 
 $s_3=19.4$~[m], see Fig.~\ref{awa-tba}. 
-
+Given the longitudinal location of $s_3$ (unless otherwise noted), 
+we define the objectives and input parameters as:
 \begin{align}
-\text{min}  \quad & \text{rms}_{x}\left(s = s_3\right), \quad \text{rms}_{y}\left(s = s_3\right) \label{eq:awa:p1}\\
-& \text{rms}_{px}\left(s = s_3\right), \quad \text{rms}_{py}\left(s = s_3\right), \label{eq:awa:p2}\\
-& \text{rms}_{s}\left(s = s_3\right), \quad dE \label{eq:awa:p4} \\
-\text{subject to} \quad & rms_x(s=s_1) < 0.1 \, [m]\label{eq:awa:c1}\\
-\quad & rms_y(s=s_1) < 0.1\, [m]\label{eq:awa:c2}\\
-\quad & |rms_y(s=s_1) - rms_x(s=s_1) | < 0.005 \, [m]\label{eq:awa:c3}\\
-\quad & q = 40 \left[\text{nC}\right] \label{eq:awa:firstconstr}\\
+\text{min}  \quad & \text{rms}_{x}, \quad \text{rms}_{y} \label{eq:awa:p1}\\
+& \text{rms}_{px}, \quad \text{rms}_{py}, \label{eq:awa:p2}\\
+& \text{rms}_{s}, \quad dE \label{eq:awa:p4} \\
+\text{constraints} \quad & rms_x < 0.1 \, [m] |_{s=s_1}\label{eq:awa:c1}\\
+\quad & rms_y < 0.1 [m] |_{s=s_1}\, \label{eq:awa:c2}\\
+\quad & |rms_y - rms_x | < 0.005 \, [m] |_{s=s_1}\label{eq:awa:c3}\\
+\text{subject to} \quad & q = 40 \left[\text{nC}\right] \label{eq:awa:firstconstr}\\
 \quad & \text{Volt}_{\text{Gun}} = 64\left[\text{MV/m}\right] \label{eq:awa:lastconstr}\\
@@
 Minimizing the beam size at this location is essential to 
-to preventing loss of particles by scraping.
-Preventing scraping ensures better transmission through the wakefield structures downstream. 
+to preventing loss of particles by scraping; 
+which ensures better transmission through the wakefield structures downstream. 
 Less divergence in the beam (lower transverse momentum) 
-reduces growth of transverse beam size during transport in bending elements, 
-which also helps with transmission downstream. 
-The next two objectives (\ref{eq:awa:p2}) minimize the 
-longitudinal beam size ($rms_s$), and energy spread (dE) at $s_1$.
+reduces growth of transverse beam size after the focal point (min beam size).
+This reduces halo by ensuring the beam is not over focused through a hard waist.
+The momentum is also critical to preventing large growth during transport in bending elements. 
+All of these factors help with transmission downstream.
+
+The next two objectives in Eq. (\ref{eq:awa:p4}) minimize the 
+longitudinal beam size ($rms_s$), and energy spread (dE) at $s_3$.
 This helps reduce longitudinal beam size growth in bending elements.
+A small bunch length ($rms_s$) is also critical.......
 

### 2018-07-12 pareto_stat_plots/pareto_plots.py
plotting scripts

@@ -10,8 +10,8 @@ from opal.datasets.filetype import FileType
 from opal.visualization.plots import *
 from opal.datasets.OptimizerDataset import *
 
-def plot_stuff(title, xname, yname, xyrange=False):
-    plt.title(title, size=25)
+def plot_stuff(xname, yname, xyrange=False):
+    #plt.title(title, size=25)
     plt.xlabel(xname, size=20)
     plt.ylabel(yname, size=20)
     if xyrange:
@@ -25,40 +25,45 @@ plt.rc('axes', labelsize=18)
 #baseFN = ['./noquads/corrected/']
 #baseFN = ['./extquads', './noquads']
 #baseFN = ['to_q7-9']
-z1=True; z2=False; z3=False; z4=False; z5=False;
+z1=False; z2=False; z3=True; z4=False; z5=False;
 gun     = True
 lphase  = False 
 quads   = True 
 doublet = False
 triplet = False 
-baseFN  = ['../phases/quads-relaxed']
+baseFN  = ['../phases/quads1-4_newobj/zrms']
 
 x=True
-y=True
+y=False
+bunch=False
 if x==True:
-    savefile = 'x_vs_px_pareto_front_quads_before_kicker'
-    plottitle = 'Pareto Front After Quads \n $\sigma_{x}$ vs. $\sigma_{px}$'
+    savefile = 'x_vs_px_pareto_front_quads_before_Q5'
+    #plottitle = 'Pareto Front After Kicker and Septum \n $\sigma_{x}$ vs. $\sigma_{px}$'
     #xtitle = "Energy Spread [MeV]"
     #xtitle = 'Bunch Length: $\sigma_z$ [mm]'
     xtitle =  'Momentum: $\sigma_{px}$ [$\gamma$ ]'
     ytitle =  'Beam Size: $\sigma_{x}$ [mm]'
 
 if y==True:
-    savefile = 'y_vs_py_pareto_front_quads_before_pets'
-    plottitle = 'Pareto Front After Quads \n $\sigma_{y}$ vs. $\sigma_{py}$'
+    savefile = 'y_vs_py_pareto_front_quads_before_Q5'
+    #plottitle = 'Pareto Front After Quads \n $\sigma_{y}$ vs. $\sigma_{py}$'
     #xtitle = "Energy Spread [MeV]"
     #xtitle = 'Bunch Length: $\sigma_z$ [mm]'
     xtitle =  'Momentum: $\sigma_{py}$ [$\gamma$ ]'
[…]

### 2018-07-12 pareto_stat_plots/stat_plot.py

@@ -8,10 +8,10 @@ from opal.opal import load_dataset
 ####myfile = 'larger_goodLinac.stat'
 #myfile = 'smaller_goodLinac.stat'
 
-zstop= 24
+zstop= 20
 
 # zero was bad.... files= ['optLinac-40nC_GPHASE=0.stat', 'optLinac-40nC_GPHASE=-10.stat', 'optLinac-40nC_GPHASE=-8.stat', 
-files = ['csr_fields.stat']
+files = ['optLinac-40nC_IBF=330_IM=197_KQ1=-1.2.stat']
 
 for myfile in files:
     try:
@@ -19,48 +19,27 @@ for myfile in files:
         ds = dsets[0]
     except Exception as e:
             print ( e )
-    
+   
+    fig1   = plt.axes()
     pltxy  = plot_profile1D(ds, 's', 'rms_x', xsci=True, label='$\sigma_x$')
     pltxy  = plot_profile1D(ds, 's', 'rms_y', xsci=True, label='$\sigma_y$')
-    
-    #plt.plot([18.5,18.5], [0,0.015], label='Septum')
-    #plt.plot([19.4,19.4], [0,0.015], label='Extra Quads')
-    #plt.plot([20.5,20.5], [0,0.015], label='Dipole')
-    #plt.plot([21.2,21.2], [0,0.015], label='Triplet')
-    #plt.plot([21.8, 21.8], [0,0.015], 'k-')#label='Structure')
-    
+
+    #Dipoles 
     z = np.array([ 18.5,   18.7,   20.5,  20.7])
     y = np.array([0.0041, 0.0041, 0.0083,0.0083 ]) 
 
-    #2 inch pipe
-    plt.plot([10, 16.5],   [0.0083, 0.0083], 'k-', label = '1/6 of 2 inch pipe')
-    plt.plot([16.5, 16.5], [0.0083, 0.006], 'k-')
-    plt.plot([17.6, 18.5], [0.0041, 0.0041], 'k-')
-    plt.plot([18.7, 21.8], [0.0083, 0.0083], 'k-') #label = '1/6 of 2 inch pipe')
-    plt.plot([21.8, 21.8], [0.0083, 0.003], 'k-')
-    plt.plot([18.7, 18.7], [0.0083, 0.0041], 'k-')
-    plt.plot([22.5, 22.5], [0.003, 0.0083], 'k-')
-    plt.plot([22.5, 25], [0.0083, 0.0083], 'k-')
-
-    #1 inch pipe
[…]

### 2018-07-12 paper/theor-experiment.tex
adding result pareto fronts

@@
 The next two objectives in Eq. (\ref{eq:awa:p4}) minimize the 
-longitudinal beam size ($rms_s$), and energy spread (dE) at $s_3$.
+longitudinal beam size ($rms_s$), and energy spread (dE) at location $s_3$.
 This helps reduce longitudinal beam size growth in bending elements.
-A small bunch length ($rms_s$) is also critical.......
+A small bunch length ($rms_s$) is also critical to the goals of 
+TBA experiments. The power generated in the wakefield structures 
+designed for TBA is related to the bunch length \cite{JING201872}.
+\nrnote{need better source for this info} 
+i.e. smaller bunch lengths result in larger wakefields and higher power generation.
 
-Three constraints were also defined to help guide the algorithm;
-Eqs.~\ref{eq:awa:c1} to \ref{eq:awa:c3}.
-The bounding values may seem large, but this is done to avoid over constraing the 
-problem in early generations. If the constraints are set tighter, 
-runs do not reach the second generation, because enough satisfactory 
-points are not produced to fill a complete generation. 
-Leaving the value large allows for enough simulations to finish
-in order to reach the next generation, and subsequent improved points in later generations.
+Eqs.~\ref{eq:awa:c1} to \ref{eq:awa:c3} 
+define three constraints used to guide the algorithm.
+The bounding values may seem large, but this is done to avoid over constraining the 
+problem in early generations. When the constraints were set tighter, 
+optimization runs did not reach the second generation within a 48 hour time limit. 
+In other words, enough satisfactory points were not produced to fill a complete generation in 48 hours. 
+By leaving the value large, a sufficient number of simulations finish
+and subsequent generations are reached in a timely manner. 
+As multiple generations, the objectives continue to improve.
+
 The difference constraint, Eq.~\ref{eq:awa:c3}, is used to favor nearly round beams.
 This prevents one dimension from becoming disproportionately large compared to the other.
-In this case, there is some room in the beam pipe to allow the y dimension to grow, but round beams 
+At the AWA, there is some room in the beam pipe to allow the y dimension to grow, but round beams 
 are preferred for easier data analysis.
@@
 defined in Eqs. (\ref{eq:awa:p1}) to (\ref{eq:awa:p4}). 
-The location at the entrance of the kicker is $s_0=16.45$~meters, 
-and the location of interest for objectives is $s_1=19.4$~meters.
+The location at the entrance of the kicker is $s_1=16.45$~meters, 
+and the location of interest for objectives is $s_3=19.4$~meters.
 
@@
 After collection of the data, Pareto fronts comparing the objectives were plotted, 
-see Figs. X-Z.
-The $\sigma_x$ and $\sigma_{px}$ plots are of most interest, as they are the most heavility 
+see Figs.~\ref{fig:pareto1} and \ref{fig:pareto2}.
+
+\begin{figure}
+	\includegraphics[width=0.5\textwidth]{../pareto_stat_plots/xy_vs_pxy_pareto_front_quads_before_Q5}
+	\caption{Pareto front comparing transverse beam size ($\sigma_{x,y}$) and transverse momentum ($\sigma_{px,py}$).}
+	\label{fig:pareto1}
+\end{figure}
+
+\begin{figure}
+	\includegraphics[width=0.5\textwidth]{../pareto_stat_plots/y_vs_py_pareto_front_quads_before_Q5}
+	\caption{Pareto front comparing longitudinal beam size ($\sigma_z$) and energy spread ($dE$).}
+	\label{fig:pareto2}
+\end{figure}
+
+As expected, the x dimension is impacted by the bending elements, and unable to maintain 
+the small beam sizes seen in the y dimension. 
+The $\sigma_x$ and $\sigma_{px}$ plots are of most interest, as these parameters are the heavily 
 impacted by bending elements. With this in mind, several beam parameters corresponding to
@@
 The maximum beam sizes are well below the beam pip aperture limits as shown in Fig. (b).
-
-\begin{figure}
-	%\includegraphics[width=0.5\textwidth]{}\includegraphics[width=0.5\textwidth]{}
-	\label{beamsizes}
-\end{figure}

### 2018-07-12 pareto_stat_plots/pareto_plots.py
plotting scripts update

@@ -33,9 +33,9 @@ doublet = False
 triplet = False 
 baseFN  = ['../phases/quads1-4_newobj/zrms']
 
-x=True
+x=False
 y=False
-bunch=False
+bunch=True
 if x==True:
     savefile = 'x_vs_px_pareto_front_quads_before_Q5'
     #plottitle = 'Pareto Front After Kicker and Septum \n $\sigma_{x}$ vs. $\sigma_{px}$'
@@ -53,15 +53,15 @@ if y==True:
     ytitle =  'Beam Size: $\sigma_{y}$ [mm]'
 
 if y==True and x==True:
-    savefile = 'xy_vs_py_pareto_front_quads_before_Q5'
+    savefile = 'xy_vs_pxy_pareto_front_quads_before_Q5'
     #plottitle = 'Pareto Front After Quads \n $\sigma_{x,y}$ vs. $\sigma_{px}$'
     #xtitle = "Energy Spread [MeV]"
     #xtitle = 'Bunch Length: $\sigma_z$ [mm]'
-    xtitle =  r'Momentum: $\sigma_{px}$ [$\gamma$ $\beta$]'
+    xtitle =  r'Momentum: $\sigma_{px,py}$ [$\gamma$ $\beta$]'
     ytitle =  'Beam Size: $\sigma_{x,y}$ [mm]'
 
 if bunch==True:
-    savefile = 'xy_vs_py_pareto_front_quads_before_Q5'
+    savefile = 'dE_vs_zrms_pareto_front_quads_before_Q5'
     xtitle = 'Bunch Length: $\sigma_s$ [mm]'
     ytitle = 'Energy Spread: dE [MeV]'
 
@@ -167,7 +167,7 @@ for fn in baseFN:
         if z3==True:
             #Loadig all data in the i-th generation
             de3   = ds.getData('DE3', gen=i)
-            #rmss3 = ds.getData('RMSS3', gen=i)
+            rmss3 = ds.getData('RMSS3', gen=i)
             rmsx3 = ds.getData('RMSX3', gen=i)
             rmsy3 = ds.getData('RMSY3', gen=i)
             rmspx3 = ds.getData('RMSPX3', gen=i)
@@ -177,6 +177,7 @@ for fn in baseFN:
             #that holds data for every generation
             allrmsx3 = np.append(rmsx3, allrmsx3)
             allrmsy3 = np.append(rmsy3, allrmsy3)
[…]

### 2018-07-12 pareto_stat_plots/stat_plot.py

@@ -8,10 +8,10 @@ from opal.opal import load_dataset
 ####myfile = 'larger_goodLinac.stat'
 #myfile = 'smaller_goodLinac.stat'
 
-zstop= 20
+zstop= 20 
 
 # zero was bad.... files= ['optLinac-40nC_GPHASE=0.stat', 'optLinac-40nC_GPHASE=-10.stat', 'optLinac-40nC_GPHASE=-8.stat', 
-files = ['optLinac-40nC_IBF=330_IM=197_KQ1=-1.2.stat']
+files = ['zrms_newobj.stat'] #'optLinac-40nC_KQ3=3.2_IM=250.stat']
 
 for myfile in files:
     try:
@@ -19,27 +19,43 @@ for myfile in files:
         ds = dsets[0]
     except Exception as e:
             print ( e )
-   
-    fig1   = plt.axes()
+    
     pltxy  = plot_profile1D(ds, 's', 'rms_x', xsci=True, label='$\sigma_x$')
     pltxy  = plot_profile1D(ds, 's', 'rms_y', xsci=True, label='$\sigma_y$')
-
-    #Dipoles 
+    
     z = np.array([ 18.5,   18.7,   20.5,  20.7])
     y = np.array([0.0041, 0.0041, 0.0083,0.0083 ]) 
 
-    #Sigma xy plot
-    plt.plot([19.4, 19.4], [0, 0.05], '-g', label='Optimization location')
-    plt.axis([0,zstop,0,0.02])
+#    #2 inch pipe
+#    plt.plot([10, 16.5],   [0.0083, 0.0083], 'k-', label = '1/6 of 2 inch pipe')
+#    plt.plot([16.5, 16.5], [0.0083, 0.006], 'k-')
+#    plt.plot([17.6, 18.5], [0.0041, 0.0041], 'k-')
+#    plt.plot([18.7, 21.8], [0.0083, 0.0083], 'k-') #label = '1/6 of 2 inch pipe')
+#    plt.plot([21.8, 21.8], [0.0083, 0.003], 'k-')
+#    plt.plot([18.7, 18.7], [0.0083, 0.0041], 'k-')
+#    plt.plot([22.5, 22.5], [0.003, 0.0083], 'k-')
+#    plt.plot([22.5, 25], [0.0083, 0.0083], 'k-')
+
+#    #1 inch pipe
+#    plt.plot([17.6, 17.6], [0.006, 0.0041], 'k-')#label = '1/6 of 1 inch pipe')
[…]

### 2018-07-12 paper/prab.tex
starting to fix verbatim sections
fixing figures of tba beam line
edits to timing and hyper parameter sections
first round of figures

@@
 %
-\vspace{0.2cm}
+%{0.2cm}
 \begin{Verbatim}[fontsize=\scriptsize]
@@
 \end{Verbatim}
-\vspace{0.2cm}
+%\vspace{0.2cm}
 %
@@
 %
-\small{
+
+\begin{flushleft}
 \begin{align} \label{eqn:bench}
-  \text{ min} & \left[ 1 - \exp \left( -1 \left(
+\text{min} & \left[ 1 - \exp \left( -1 \left(
 \left(x_1 - \frac{1}{\sqrt{3}} \right)^2 +
@@
 \left(x_3 - \frac{1}{\sqrt{3}} \right)^2 \right)\right), \right. \\
-                    & \quad \left. 1 - \exp \left( -1 \left(
+& \left. 1 - \exp \left( -1 \left(
 \left(x_1 + \frac{1}{\sqrt{3}} \right)^2 +
@@
 \end{align}
-}
+\end{flushleft}
+
 %
@@
   as:
-
-\vspace{0.2cm}
+%
+%\vspace{0.2cm}
+
 \begin{flushleft}
-\noindent
 \begin{Verbatim}[fontsize=\scriptsize]
@@
 \end{flushleft}
-
-\vspace{0.2cm}
+%\vspace{0.2cm}
 
@@
   already feasible on a small cluster using only a modest number of MPI
-  procsses.
+  processes.
 For 1000 generations consisting of 2048 feasible and 8354 infeasible function
@@
 Nevertheless we see a reasonable speeduo when using more cores to solve the
-  optimization problem and the parallel performance will be further evaluated
-  in a forthcoming publication.
+  optimization problem. %and the parallel performance will be further evaluated
+%  in a forthcoming publication.
 %The number of individuals is the only limiting factor.
+
+The framework was then applied to a larger and untested beam dynamics problem at the AWA.
+Optimization of the 3D beam size and energy spread was accomplished.
+A scan of time step and hyper parameters was done to determine computational settings.
+Then a full scale physics optimization was performed.
+The resulting beam tune can and will be used in future TBA experiments at the AWA.
+This problem also took advantage of the frameworks massively parallel capabilities by
+running on 2624 processes on Bebop at LCRC.
 
@@
   a HPC cluster operated by the LCRC at ANL.
+  Thanks to Scott Doran for providing CAD drawings of the AWA beam lines.
   This work was partly supported by the 

### 2018-07-12 paper/theor-experiment.tex
first round of figures

@@
 and a slightly better Pareto front at $s_2$ for ex-4, the hyper parameters in ex-4 were chosen as the default values for subsequent runs.
-\iffalse  
-\begin{figure}
-	\centering
-	\includegraphics[width=0.75\textwidth]{Report/ex-pareto1}%
-	\llap{\raisebox{1.8cm}{%  move next graphics to top right corner
-			\includegraphics[height=5.5cm]{Report/ex-pareto2}%
-	}}
-	\caption{My overlay figure.}
-\end{figure}  
-\fi
 
@@
 		%\label{expareto1}
+		\vspace{2em}
 	\end{minipage}
@@
 \begin{figure}
-	\includegraphics[width=0.5\textwidth]{../pareto_stat_plots/y_vs_py_pareto_front_quads_before_Q5}
-	\caption{Pareto front comparing longitudinal beam size ($\sigma_z$) and energy spread ($dE$).}
+	\centering
+	\includegraphics[width=0.48\textwidth]{../pareto_stat_plots/dE_vs_zrms_pareto_front_quads_before_Q5_zoomout}%
+	\llap{\raisebox{1.9cm}{%  move next graphics to top right corner
+			\includegraphics[height=4.5cm]{../pareto_stat_plots/dE_vs_zrms_pareto_front_quads_before_Q5}%
+	}}
+	\caption{Comparison of energy spread and bunch length ($\sigma_z$). \nrnote{add tikz arrows to point to left side of curve?}}
 	\label{fig:pareto2}
@@
 
-As expected, the x dimension is impacted by the bending elements, and unable to maintain 
-the small beam sizes seen in the y dimension. 
-The $\sigma_x$ and $\sigma_{px}$ plots are of most interest, as these parameters are the heavily 
-impacted by bending elements. With this in mind, several beam parameters corresponding to
-options on Pareto Front in Fig. X were plotted and compared. 
-The best results are shown in Fig. Z. 
-The maximum beam sizes are well below the beam pip aperture limits as shown in Fig. (b).
+As expected, the x dimension is impacted by the bending elements, and unable to reach 
+the small beam sizes seen in the y dimension. This suggest objectives in the x 
+should be weighted higher than y when choosing operating parameters. 
+In the case of bunch length, there are not many options to choose from.
+Ignoring the extreme value on the right, Fig.~\ref{fig:pareto2} shows the 
+range of optimal bunch lengths fall between 1.39 and 1.5 mm.
+
+With these observations in mind, several beam parameters corresponding to
+options on Pareto Front in Fig.~\ref{fig:pareto1} were plotted and compared. 
+A select result is shown in Fig.~\ref{fig:stat}. 
+The maximum beam sizes are well below the beam pipe aperture limits as shown in Fig.~\ref{fig:stat} (b).
+The solution is nearly round, which will increase changes of keeping the beam nearly round
+as it travels to the last triplet in Fig.~\ref{awa-tba}.
+Overall this solution is satisfactory, and meets all requirements at the AWA.
+
+\begin{figure}
+	\includegraphics[width=0.48\textwidth]{../pareto_stat_plots/xyrms-zrms_newobj}\\
+	\includegraphics[width=0.48\textwidth]{../pareto_stat_plots/xy-max-min-zrms_newobj}
+	\caption{Optimized beam sizes along high charge beam line.}
+	\label{fig:stat}
+\end{figure}

### 2018-07-13 pareto_stat_plots/pareto_plots.py
updating plots to have same formatting as previous plots in Ferrario section

@@ -57,13 +57,13 @@ if y==True and x==True:
     #plottitle = 'Pareto Front After Quads \n $\sigma_{x,y}$ vs. $\sigma_{px}$'
     #xtitle = "Energy Spread [MeV]"
     #xtitle = 'Bunch Length: $\sigma_z$ [mm]'
-    xtitle =  r'Momentum: $\sigma_{px,py}$ [$\gamma$ $\beta$]'
-    ytitle =  'Beam Size: $\sigma_{x,y}$ [mm]'
+    xtitle =  r'Momentum: rms$_{px,py}$ ($\gamma$ $\beta$)'
+    ytitle =  'Beam Size: rms$_{x,y}$ (mm)'
 
 if bunch==True:
-    savefile = 'dE_vs_zrms_pareto_front_quads_before_Q5'
-    xtitle = 'Bunch Length: $\sigma_s$ [mm]'
-    ytitle = 'Energy Spread: dE [MeV]'
+    savefile = 'dE_vs_zrms_pareto_front_quads_before_Q5_zoomout'
+    xtitle = 'Bunch Length: rms$_s$ (mm)'
+    ytitle = 'Energy Spread: dE (MeV)'
 
 for fn in baseFN:
     
@@ -266,13 +266,13 @@ for fn in baseFN:
         print('ind', indx)
         mmxrms  = np.asarray(pfdatapx['x'])*10**3
         mmpxrms = np.asarray(pfdatapx['y'])
-        plt.plot(mmpxrms, mmxrms, '-o', label='xrms')
+        plt.plot(mmpxrms, mmxrms, '-o', label='rms$_{x,px}$')
 
     if y==True:
         (pfdatapy, indy) = pareto_pts(allrmsy3, allrmspy3)
         mmyrms = np.asarray(pfdatapy['x'])*10**3
         mmpyrms = np.asarray(pfdatapy['y'])
-        plt.plot(mmpyrms, mmyrms, '-o', label='yrms')
+        plt.plot(mmpyrms, mmyrms, '-o', label='rms$_{y,py}$')
         plt.legend()
 #    if x==True and y==True:
 #        mmyrms = np.asarray(allrmsy1[ind])*10**3
@@ -283,7 +283,7 @@ for fn in baseFN:
     if bunch==True:
         (pfdataz, ind) = pareto_pts(allrmss3, allde3)
         mmzrms = np.asarray(pfdataz['x'])*10**3
[…]

### 2018-07-13 pareto_stat_plots/stat_plot.py

@@ -1,6 +1,9 @@
 from opal.visualization.plots import *
 from opal.opal import load_dataset
 
+plt.rc('text', usetex=True)
+plt.rc('font', family='serif')
+plt.rc('axes', labelsize=18)
 
 #myfile = '3gens_large_xrms_at_triplet.stat'
 #myfile = '3gens_small_xrms_at_triplet.stat'
@@ -20,9 +23,9 @@ for myfile in files:
     except Exception as e:
             print ( e )
     
-    pltxy  = plot_profile1D(ds, 's', 'rms_x', xsci=True, label='$\sigma_x$')
-    pltxy  = plot_profile1D(ds, 's', 'rms_y', xsci=True, label='$\sigma_y$')
-    
+    pltxy  = plot_profile1D(ds, 's', 'rms_x', xsci=True, label='rms$_x$')
+    pltxy  = plot_profile1D(ds, 's', 'rms_y', xsci=True, label='rms$_y$')
+    plt.xlabel('s (m)') 
     z = np.array([ 18.5,   18.7,   20.5,  20.7])
     y = np.array([0.0041, 0.0041, 0.0083,0.0083 ]) 
 
@@ -49,7 +52,7 @@ for myfile in files:
     plt.plot([19.4,19.4],[0,0.015], '-g', label='$s_3$')
     plt.axis([0,zstop,0,0.015])
     plt.legend(loc='lower left')
-    plt.ylabel('Beam sizes: $\sigma_{x,y}$', size=20)
+    plt.ylabel('Beam Sizes: rms$_{x,y}$ (mm)', size=20)
     plt.grid()
     #plt.show()
     savefile = myfile.split('.stat')[0]
@@ -94,9 +97,12 @@ for myfile in files:
     plt.savefig('energy-'+savefile+'.pdf', dpi=1000, bbox_inches='tight')
 
     fig7 = plt.figure(7)
+    ax   = plt.axes()
     pltmax = plot_profile1D(ds, 's', 'max_x', xsci=True, label='max x')
     pltmax = plot_profile1D(ds, 's', 'max_y', xsci=True, label='max y')
+    plt.xlabel('s (m)')
 
+    
     #2 inch pipe
     plt.plot([10, 16.5],   [0.05, 0.05], 'k-', label = 'Beam pipe aperture')
     plt.plot([16.5, 16.5], [0.05, 0.04], 'k-') #Down from kicker to septum
[…]

### 2018-07-13 paper/theor-experiment.tex
awa figure edits

@@
 	\centering
-	\includegraphics[width=0.8\linewidth]{Report/timestep_comparison}
+	\includegraphics[width=\linewidth]{Report/timestep_comparison}
 	\caption{Comparison of different fidelity models (dT stands for time step).}
@@
 	\includegraphics[width=0.5\textwidth]{../pareto_stat_plots/xy_vs_pxy_pareto_front_quads_before_Q5}
-	\caption{Pareto front comparing transverse beam size ($\sigma_{x,y}$) and transverse momentum ($\sigma_{px,py}$).}
+	\caption{Pareto front comparing transverse beam sizes ($\sigma_{x,y}$) and transverse momentum ($\sigma_{px,py}$).}
 	\label{fig:pareto1}
@@
 	}}
-	\caption{Comparison of energy spread and bunch length ($\sigma_z$). \nrnote{add tikz arrows to point to left side of curve?}}
+	\caption{Pareto front comparing energy spread (dE) and bunch length ($\sigma_z$). \nrnote{add tikz arrows to point to left side of curve?}}
 	\label{fig:pareto2}
@@
 	\includegraphics[width=0.48\textwidth]{../pareto_stat_plots/xyrms-zrms_newobj}\\
+	\vspace{2em}
 	\includegraphics[width=0.48\textwidth]{../pareto_stat_plots/xy-max-min-zrms_newobj}

### 2018-07-17 paper/theor-experiment.tex
making small edits from Andreas

@@
 For validation purposes we compared the results of the envelope-tracker using
-  the analytical space charge model with the \textsc{OPAL} 3D macro particle
+  the analytical space charge model with the \textsc{OPAL-T} 3D macro particle
   tracker.
@@
 equally and calculated at 
-$s_3=19.4$~[m], see Fig.~\ref{awa-tba}. 
+$s_3=19.4$~m. See Fig.~\ref{awa-tba} for location of $s_3$ w.r.t. other 
+beam line elements. 
 Given the longitudinal location of $s_3$ (unless otherwise noted), 
@@
 
-With the time steps and hyper parameters set by the work in \ref{awa:subsection:test}, 
+With the time steps and hyper parameters set by the work in Section \ref{awa:subsection:test}, 
 the full optimization problem described in \ref{awaproblem} was run for 200 generations.

### 2018-07-18 paper/prab.tex
making small edits from Andreas
fix Kraus and remove felsim

@@
 
-\author{Andreas Adelmann}
+\author{Y. Ineichen }
+\affiliation{% 
+	place holder 1
+}%
+
+\author{A. Adelmann}
 \email{andreas.adelmann@psi.ch}
@@
 \altaffiliation[Also at ]{
-	University of Huddersfield, West Yorkshire, United Kingdom}
-
+	University of Huddersfield, West Yorkshire, United Kingdom and  CERN, Genf}
+\author{C. Metzger-Kraus}
+\altaffiliation[Also at ]{AiF Projekt GmbH}
 \affiliation{
 	PSI, Villigen, Switzerland}%
-
-\author{Y Ineichen}%
-\altaffiliation[Also at ]{Department of Computer Science, ETH Zurich, Switzerland}%Lines break
 
@@
 	Department of Computer Science, ETH Zurich, Switzerland}%
-
-\author{C. Metzger-Kraus }
-\affiliation{% 
-	place holder \\
-}%
 
@@
   convergence of the results.
-This first study shows that the framework is ready to tackle problems arising
-  in the domain of beam dynamics.
-
-Interestingly, the computation of a good approximation of the Pareto front is
-  already feasible on a small cluster using only a modest number of MPI
-  processes.
-For 1000 generations consisting of 2048 feasible and 8354 infeasible function
-  evaluations (simulations) the optimizer needed $845$ minutes on the
-  \textsc{Felsim} cluster on $16$ processes.
-When we double the number of processes to $32$ (\textsc{Felsim} allows a
-  maximum of $64$ processes per job) the runtime improves to $302$ minutes (2048
-  accepted and 5426 infeasible individuals).
-Notice that the runtime can vary due to the random nature of the process.
-Nevertheless we see a reasonable speeduo when using more cores to solve the
-  optimization problem. %and the parallel performance will be further evaluated
+
+%This first study shows that the framework is ready to tackle problems arising
+%  in the domain of beam dynamics.
+%
+%Interestingly, the computation of a good approximation of the Pareto front is
+%  already feasible on a small cluster using only a modest number of MPI
+%  processes.
+%  
+%For 1000 generations consisting of 2048 feasible and 8354 infeasible function
+%  evaluations (simulations) the optimizer needed $845$ minutes on the
+%  \textsc{Felsim} cluster on $16$ processes.
+%
+%When we double the number of processes to $32$ (\textsc{Felsim} allows a
+%  maximum of $64$ processes per job) the runtime improves to $302$ minutes (2048
+%  accepted and 5426 infeasible individuals).
+%Notice that the runtime can vary due to the random nature of the process.
+%Nevertheless we see a reasonable speeduo when using more cores to solve the
+%  optimization problem. %and the parallel performance will be further evaluated
 %  in a forthcoming publication.

### 2018-07-19 paper/prab.tex
more changes according to our discussion

@@
 \begin{code}[Assembling the optimizer \\ from components]
-typedef OpalInputFileParser Input_t;
+typedef  \textsc{OPAL-t} InputFileParser Input_t;
 typedef PisaVariator        Opt_t;

### 2018-07-19 paper/theor-experiment.tex
more changes according to our discussion

@@
 
-All numerical experiments in this sections were executed on the
-  \textsc{Felsim} cluster at PSI\@.
-The \textsc{Felsim} cluster consists of 8 dual quad-core Intel Xeon
-  processors at 3.0 GHz and has $2$ GB memory per core with a total of 128
-  cores.
-The nodes are connected via Infiniband network with a total bandwidth of 16
-  GB/s.
+%All numerical experiments in this sections were executed on the
+%  \textsc{Felsim} cluster at PSI\@.
+%The \textsc{Felsim} cluster consists of 8 dual quad-core Intel Xeon
+%  processors at 3.0 GHz and has $2$ GB memory per core with a total of 128
+%  cores.
+%The nodes are connected via Infiniband network with a total bandwidth of 16
+%  GB/s.
 
@@
 For validation purposes we compared the results of the envelope-tracker using
-  the analytical space charge model with the \textsc{OPAL-T} 3D macro particle
+  the analytical space charge model with the \textsc{OPAL-t} 3D macro particle
   tracker.
@@
 \quad & \text{Volt}_{\text{Gun}} = 64\left[\text{MV/m}\right] \label{eq:awa:lastconstr}\\
-\quad & \text{Volt}_{\text{Linac}} = 24-25\left[\text{MV/m}\right] \\
+\quad & \text{Volt}_{\text{Linac}} = 24 \ldots 25\left[\text{MV/m}\right] \\
 \quad & R_x = R_y = 9 \left[\text{mm}\right] \label{eq:awa:firstdvar}\\

### 2018-07-26 paper/theor-experiment.tex
paper edits

@@
 it will guide future operations at the AWA.
-\nrnote{Moved final run set up and results to after time step scan and hyper parameters}
 
@@
 the full optimization problem of interest is explored.
-The objectives (beam sizes and energy spread) are weighted 
-equally and calculated at 
+The objectives (beam sizes and energy spread) are calculated at 
 $s_3=19.4$~m. See Fig.~\ref{awa-tba} for location of $s_3$ w.r.t. other 
@@
 \quad & \text{Volt}_{\text{Gun}} = 64\left[\text{MV/m}\right] \label{eq:awa:lastconstr}\\
-\quad & \text{Volt}_{\text{Linac}} = 24 \ldots 25\left[\text{MV/m}\right] \\
+\quad & \text{Volt}_{\text{Linac}} = 24 \, \text{or} \, 25\left[\text{MV/m}\right] \\
 \quad & R_x = R_y = 9 \left[\text{mm}\right] \label{eq:awa:firstdvar}\\
@@
 the small beam sizes seen in the y dimension. This suggest objectives in the x 
-should be weighted higher than y when choosing operating parameters. 
+dimension will drive design variable choices used in operations. 
+However, it is still necessary to 
+include the y dimension in optimization. Early optimization tests showed the y dimension 
+can easily grow out of control if not included in the objectives.
+Those results are not shown here due to the unfeasible solutions they resulted in
+(i.e. $rms_y$ larger than the beam pipe).
 In the case of bunch length, there are not many options to choose from.

### 2018-07-26 paper/prab.tex
small changes
paper edits

@@
 \title{A Parallel General Purpose Multi-Objective Optimization Framework,
-  with Application To Beam Dynamics}
+  with Application To Electron Beam Dynamics}
 %\thanks{A footnote to the article title}%
@@
 
-The framework was then applied to a larger and untested beam dynamics problem at the AWA.
+The framework was then applied to a larger beam dynamics problem at the AWA.
 Optimization of the 3D beam size and energy spread was accomplished.

### 2018-08-01 paper/prab.tex
add affiliation of Yves
taking out Ferrario and changing Figure to Fig.

@@
   price and a trade-off decision between performance and price has to be
-  reached (see Figure~\ref{fig:tradeoff}).
+  reached (see Fig.~\ref{fig:tradeoff}).
 Since not every choice is equally profitable for the buyer (for example, car
@@
   functions for the corresponding genes.
-Figure~\ref{fig:varsel} schematically depicts the connection of the
+Fig.~\ref{fig:varsel} schematically depicts the connection of the
   components introduced above.
@@
   retain access to all available PISA selectors.
-As shown in Figure~\ref{fig:varsel}, the selector is in charge of ordering a
+As shown in Fig.~\ref{fig:varsel}, the selector is in charge of ordering a
   set of $d$-dimensional vectors and selecting the $k$ fittest individuals
@@
 We divide the framework in three exchangeable components, as shown in
-  Figure~\ref{fig:opt-framework-layout}, to encapsulate the major behavioral
+  Fig.~\ref{fig:opt-framework-layout}, to encapsulate the major behavioral
   patterns of the framework.
@@
 Every available MPI process will take up one of the three available roles (see
-  Figure~\ref{fig:framenetwork}):  one process acts as \textsc{Pilot}, the
+  Fig.~\ref{fig:framenetwork}):  one process acts as \textsc{Pilot}, the
   remaining processes are divided amongst \textsc{Worker} and
@@
   MPI processes to exploit parallelism.
-As shown in Figure~\ref{fig:opt-framework-layout} the \textsc{Pilot} is used
+As shown in Fig.~\ref{fig:opt-framework-layout} the \textsc{Pilot} is used
   to coordinate all ``information requests'' between the \textsc{Optimizer}
@@
 
-In this paper we applied the framework to reproduce the important and well
-  known Ferrario matching condition for the \textsc{250 MeV injector}, a part of PSI's
-  \textsc{SwissFEL} project.
-The beam size and emittance optimization was successful and emittance damping
-  is observed in the accelerating cavity.
-Also, the influence of the number of slices employed by the envelope tracker
-  with respect to convergence was investigated.
-We found that the optimal slice number is around 400 for the problem addressed
-  here, producing the best trade-off between computational cost and accuracy
-  of the solution of the simulation.
-Similarly, the gun and beam line time step was investigated confirming the
-  convergence of the results.
-
 %This first study shows that the framework is ready to tackle problems arising
@@
 %The number of individuals is the only limiting factor.
-
-The framework was then applied to a larger beam dynamics problem at the AWA.
+In this paper we applied the framework to a beam dynamics problem at the AWA.
 Optimization of the 3D beam size and energy spread was accomplished.

### 2018-08-01 paper/theor-experiment.tex
taking out Ferrario and changing Figure to Fig.

@@
 In this section we present numerical results of the validation benchmark and
-  discuss a proof of concept application in the domain of particle
-  accelerators.
+  discuss optimization of a photoinjector operated in the space charge dominated regime.
 
@@
   $m$ objectives) of the dominated space, relative a chosen origin.
-We visualize this for $2$ objectives in Figure~\ref{fig:hypervolume}.
+We visualize this for $2$ objectives in Fig.~\ref{fig:hypervolume}.
 For further information and details of the implementation see~\cite{whbb:12}.
-Figure~\ref{fig:pisa_bench} and the corresponding hypervolume values in
+Fig.~\ref{fig:pisa_bench} and the corresponding hypervolume values in
   Table~\ref{tbl:bench_rms_error}.
@@
   additional 100 evaluations for the initial population) function evaluations.
-
-\subsection{Ferrario Matching Point}\label{ferrario}
-
-As a verification and proof of concept we reproduce the Ferrario
-  matching point discovered by Ferrario \textit{et~al.}~\cite{fcpr:00},
-  by formulating the problem as a  multi-objective optimization problem.
-Using the low-dimensional and fast nature of their new simulation code
-  Homdyn~\cite{homdyn}, an extensive beam dynamics study was conducted.
-
-One of the results of the study presented in \cite{fcpr:00} was the discovery
-  of a novel working point.
-The authors noticed that the second emittance minimum can profit from the
-  additional emittance compensation in the accelerating traveling wave
-  structure ensuring that the second emittance minimum occurs at a higher
-  energy.
-This property is attained if the beam emittance has a maximum and the root
-  mean square (rms) beam size has a minimum at the entrance of the first
-  accelerating traveling wave structure.
-This behavior is illustrated in Figure~\ref{fig:fer_match}.
-
-\begin{figure}
-  \centering
-  \input{figures/ferrario_illustrated}
-  \caption{Illustration of the Ferrario matching criteria: beam emittance
-  attains a maximum and rms beam size a minimum at the entrance to the first
-  accelerating traveling wave structure.}
-  \label{fig:fer_match}
-\end{figure}
-
-By artificially reproducing this working point as the solution of a
-  multi-objective optimization problem given in equations
-  (\ref{eq:swissfel:p1}) to (\ref{eq:swissfel:lastdvar}),
-  we demonstrate the automation of discovering optimal beam dynamics behaviors
-  given a set of desired objectives.
-
-\begin{align}
-\text{min}  \quad & \left[ \Delta \text{rms}_{x,\text{peak}} = \vert 3.0 -
-\text{rms}_{x,\text{peak}} \vert, \right. \label{eq:swissfel:p1}\\
-                & \Delta \varepsilon_{x,\text{peak}}  = \vert 3.0 -
-                \varepsilon_{x,\text{peak}} \vert, \label{eq:swissfel:p2}\\
-                & \left. \vert \text{rms}_{x, \text{peak\_pos}} -
-                \varepsilon_{x,\text{peak\_pos}} \vert
-                \label{eq:swissfel:p3} \right]^T\\
-\text{subject to} \quad & q = 200 \left[\text{pC}\right] \label{eq:swissfel:firstconstr}\\
-          \quad & \text{Volt}_{\text{RF}} = 100 \left[\text{MV/m}\right] \label{eq:swissfel:lastconstr}\\
-          \quad & \sigma_{L} \leq \sigma_x = \sigma_y \leq \sigma_{U} \label{eq:swissfel:firstdvar}\\
-          \quad & \text{KS}_{L} \leq \text{KS}_{\text{RF}} \leq \text{KS}_{U} \label{eq:swissfel:seconddvar}\\
-          \quad & \text{LAG}_{L} \leq \text{LAG}_{\text{RF}} \leq \text{LAG}_{U} \\
-          \quad & \Delta z_{L\text{KS}} \leq \Delta z_{\text{KS}} \leq \Delta z_{U\text{KS}} \label{eq:swissfel:lastdvar}
-\end{align}
-
-The first two objectives minimize the distance from the position of the current
-  minimum peak to the expected peak location at $3.0$\,m for transverse bunch
-  size (beam waist) and emittance (see Figure~\ref{fig:fer_match}).
-The third objective (\ref{eq:swissfel:p3}) adds a condition preferring
-  solutions that have their emittance and rms peak locations at the same
-  $s$-coordinate.
-Equations (\ref{eq:swissfel:firstconstr}) and (\ref{eq:swissfel:firstdvar})
-  define constraints for initial conditions for the simulation: charge,
-  gun voltage and laser spot size.
-Design variables given in (\ref{eq:swissfel:seconddvar}) to
-  (\ref{eq:swissfel:lastdvar}) correspond to field strengths of the
-  first focusing magnet, its displacement, and the phase of the gun.
-
-In order to compute the peaks, we employed an additional Python script.
-This script was called in the \textsc{OPAL}~input file, after the simulation
-  finished using the \texttt{SYSTEM} functionality.
-Once the peaks (in a given range) were located, the two objectives
-  (\ref{eq:swissfel:p1}) and (\ref{eq:swissfel:p2}) were computed and their
-  values written into corresponding files.
-The custom \texttt{fromFile} functor allows us to access the values stored in
-  the peak finder Python script result files
-%
-%\vspace{0.2cm}
-
-\begin{flushleft}
-\begin{Verbatim}[fontsize=\scriptsize]
-rmsx:  OBJECTIVE, EXPR="statVariableAt("rms_x-err.dat", "var")";
-emitx: OBJECTIVE, EXPR="statVariableAt("emit_x-err.dat", "var")";
-match: OBJECTIVE, EXPR="fabs(statVariableAt("emit_x-peak.dat", "var") -
-statVariableAt("rms_x-peak.dat", "var"))";
-\end{Verbatim}
-\end{flushleft}
-\vspace{0.2cm}
-
-\noindent
-The design variables and the assembly of the multi-objective optimization problem
-  can be included in the \textsc{OPAL}~input file as shown below:
-%\vspace{0.2cm}
-
-\begin{flushleft}
-\begin{Verbatim}[fontsize=\scriptsize]
-d1: DVAR, VARIABLE="SIGX", LOWERBOUND="0.00025", UPPERBOUND="0.00029";
-d2: DVAR, VARIABLE="FIND1_MSOL10_i", LOWERBOUND="110", UPPERBOUND="120";
-d3: DVAR, VARIABLE="D_LAG_RGUN", LOWERBOUND="-0.1", UPPERBOUND="0.1";
-d4: DVAR, VARIABLE="D_SOLPOS", LOWERBOUND="-0.05", UPPERBOUND="0.05";
-
-objs:    OBJECTIVES = (rmsx, emitx);
-dvars:   DVARS = (d1, d2, d3, d4);
-constrs: CONSTRAINTS = ();
-opt:     OPTIMIZE, OBJECTIVES=objs, DVARS=dvars,
-CONSTRAINTS=constrs;
-\end{Verbatim}
-\end{flushleft}
-\vspace{0.2cm}
-
-%All numerical experiments in this sections were executed on the
-%  \textsc{Felsim} cluster at PSI\@.
-%The \textsc{Felsim} cluster consists of 8 dual quad-core Intel Xeon
-%  processors at 3.0 GHz and has $2$ GB memory per core with a total of 128
-%  cores.
-%The nodes are connected via Infiniband network with a total bandwidth of 16
-%  GB/s.
-
-The envelope-tracker, mentioned in the previous section, was used to evaluate
-  the forward problems.
-We performed a beam convergence study in order to tune the simulation input
-  parameters to achieve the best trade-off between simulation accuracy and
-  time to solution.
-These parameters include the number of slices (\texttt{NSLICE}) used in the
-  envelope-tracker simulations, simulation timestep (\texttt{DT}) and gun
-  timestep (\texttt{DTGUN}).
-
-Before the simulation can be executed a number of initial beam optics
-  parameters have to be defined in an input file.
-Table~\ref{tbl:et_params} shows the values of these parameters for the
-  envelope-tracker.
-All simulations were performed up to 12.5~m of the
-  \textsc{SwissFEL} 250 MeV injector~\cite{pedr:10} beam line, with
-  energies reaching  up to 120 MeV.
-
-\begin{figure}%[h!]
-  \centering
-  \includegraphics[width=0.8\linewidth]{Report/dt_scan}
-  \caption{Envelope-tracker with different number of slices and simulation
-    time steps.}
-  \label{fig:et-dt}
-\end{figure}
-
-\begin{table}
-  \begin{center}
-    \caption{Initial conditions for the envelope tracker.}
-    \label{tbl:et_params}
-    \begin{tabular}{ll}
-      \hline\noalign{\smallskip}
-      name & initial value \\
-      \noalign{\smallskip}\hline\noalign{\smallskip}
-        Gun voltage       & $100$ MV\\
-        %Solenoid current & $110.541$ A\\
-        %Laser spot size  & $290 \times 10^{-6}$ m in x and y\\
-        Bunch charge      & $200$ pC\\
-        %DT$_{Gun}$        & $0.06$ ps\\
-        DT$_{\text{Beamline}}$  & $1.5$ ps\\
-        Number of slices  & $400$ \\
-      \noalign{\smallskip}\hline
-    \end{tabular}
-  \end{center}
-\end{table}
-
-The parameter that affects the performance most is the number of slices.
-We scanned the range from $100$ to $1000$ slices to determine the minimal
-  number of slices required for stable results using various timesteps.
-The results (for 100, 400 and 800 slices) of this scan are shown in
-  Figure~\ref{fig:et-dt}.
-Using this data we settled for $400$ slices -- increasing the slice number
-  only minimally improves convergence of the results, therefore using more
-  slices is inefficient.
-
-%\begin{figure}
-   %\centering
-     %\includegraphics[angle=0,width=0.8\linewidth]{Report/sliceNew}
-   %\caption{Scan of the envelope-tracker slice number showing its influence
-            %on the exit emittance values.}
-   %\label{fig:scan_slices}
-%\end{figure}
-
-In a next step the influence of different time steps was examined.
-To that end a series of optimization runs with 100, 400 and 800 slices and
-  varying timestep was performed.
-%Figures \ref{fig:pareto_front_1} and \ref{fig:pareto_front_21} show two Pareto
-Figure~\ref{fig:pareto_front_21} shows the Pareto fronts for 400 slices
-  respectively using different timesteps.
-As expected, increasing the number of slices while lowering the timestep
-  produces more detailed results.
-
-%\begin{figure}
-  %\centering
-    %\includegraphics[width=0.9\linewidth]{Report/Run1slices100a}
-  %\caption{Pareto Front for the $1000$th generation with $40$ individuals
-    %using 100 slices, a simulation timestep of 5 ps and a gun timestep of 0.1
-    %ps.}
-  %\label{fig:pareto_front_1}
-%\end{figure}
-
-\begin{figure}%[h!]
-  \centering
-    \includegraphics[width=0.8\linewidth]{Report/front_plot}
-  \caption{Pareto front for the $1000$th generation with $40$ individuals
-    using 400 slices (interesting region magnified), a simulation timestep
-    of 1.5 ps.
-    The individual 3 was selected for further investigations.}
-  \label{fig:pareto_front_21}
-\end{figure}
-
-\subsubsection{Optimization Results}
-
-Each of the $40$ points on the Pareto front, shown in
-  Figure~\ref{fig:pareto_front_21}, represents an optimal solution, where
-  emittance and beam size values are compromised to achieve the best agreement
-  with the Ferrario matching point.
-We selected individual $3$ based on a comparison of the emittance and beam size
-  characteristics of all solutions and by retaining the feasibility of the
-  beam line optics parameters.
-The design variables, emittance and beam size of the selected solution are
-  shown in Table~\ref{tbl:des_vars} and Figure~\ref{fig:rmsemit}.
-With the multi-objective optimization framework we attain the same working
-  point as reported in~\cite{pedr:10}.
-
-\begin{table}
-  \begin{center}
-    \caption{The design variables for individual $3$.}
-    \label{tbl:des_vars}
-    \begin{tabular}{ll}
-      \hline\noalign{\smallskip}
-      name & value \\
-      \noalign{\smallskip}\hline\noalign{\smallskip}
-        $\sigma_{x}$          & $0.262$ mm \\
-        Solenoid displacement & $28.8467$ mm \\
-        Gun voltage lag       & $0.0159067$ MV\\
-        Solenoid current      & $111.426$ A \\
-      \noalign{\smallskip}\hline
-    \end{tabular}
-  \end{center}
-\end{table}
-
-\begin{figure}%[h!]
-  \centering
-  \includegraphics[width=0.8\linewidth]{Report/iff_plot_emrms}
-  \caption{Beam size and emittance of individual $3$.}
-  \label{fig:rmsemit}
-\end{figure}
-
-Using the input parameters of the selected solution, we performed a stability
-  analysis by varying the slice number and the time step for both the gun and
-  the beam line.
-Figure~\ref{fig:et-dt} shows that the exit emittance stabilizes for 400
-  slices and various time steps.
-No difference between $800$ and $400$ slices is visible as their minimum
-  maximum extension seems to be in the same range of $0.024$ mm~mrad.
-
-For validation purposes we compared the results of the envelope-tracker using
-  the analytical space charge model with the \textsc{OPAL-t} 3D macro particle
-  tracker.
-The benchmark was run on the first 12.5 meters of the \textsc{SwissFEL} 250
-  MeV injector.
-The results for both rms beam size and emittance are shown in
-  Figure~\ref{fig:et-vs-tt}.
-A good agreement between the two codes can be observed.
-The difference of the larger emittance along the solenoids in case of 3D
-  tracker that is not seen by the envelope-tracker is due to the different
-  definition of the particle momenta (canonical vs.~mechanical).
-Both trackers agree within acceptable limits \cite{chao:99}.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.9\linewidth]{Report/iff_plot_emrms_ettt}
-  \caption{Comparison 3D-tracker versus envelope-tracker in case for rms$_{x}$
-    and $\varepsilon_{x}$.}
-  \label{fig:et-vs-tt}
-\end{figure}
-
-%\subsection{IW2: Inverse Problem}
-
-%In order to find cross correlations we try to solve the inverse problem
-  %(15) -- (23)
-%%
-%\begin{align}
-  %\text{min}  \quad & \sqrt{\frac{1}{N} \sum \left( \text{rmx}_{x,s} -
-                      %\text{m}_{x,s} \right)^2 } \text{,}\\
-              %\quad & \sqrt{\frac{1}{N} \sum \left( \text{rmx}_{y,s} -
-                      %\text{m}_{y,s} \right)^2 } \text{,}\\
-              %\quad & \sqrt{\frac{1}{N} \sum \left( \text{rmx}_{z,s} -
-                      %\text{m}_{z,s} \right)^2 } \\
-  %\text{s.t.} \quad & -0.95 \leq \text{R52} \leq -0.65 \label{eq:iw2:fistdvar}\\
-              %\quad & -0.90 \leq \text{R61} \leq -0.50 \\
-              %\quad & 0.0   \leq \text{R62} \leq 0.20 \\
-              %\quad & 0.25 \leq \text{CORR}_x \leq 0.65 \\
-              %\quad & 0.55 \leq \text{CORR}_y \leq 0.95 \\
-              %\quad & 0.10 \leq \text{CORR}_z \leq 0.50 \label{eq:iw2:lastdvar} \text{.}
-%\end{align}
-%%
-%We try to match the beam to measurements from the real machine by minimizing
-  %the sum of $N$ squared measurement ($m_{d,s}$ at a given position
-  %$s$) errors for rmx beam size in each dimensions.
-%The design variables (\ref{eq:iw2:fistdvar}) - (\ref{eq:iw2:lastdvar}) define
-  %the correlation matrix used when generating particles, e.g., R51, R52, R61,
-  %R62 describe limits of correlations between planes.
-%The initial Binomial distribution (with $m = ?$) has the form
-%%
-%\begin{equation*}
-  %\frac{1}{2\pi\sigma_x\sigma_y}exp(-\frac{x^2}{2\sigma_x^2}
-  %-\frac{y^2}{2\sigma_y^2})
-  %\text{.}
-%\end{equation*}
-%%
-
-%Since these correlations cannot be measured we get the real values by solving
-  %the inverse problem mentioned above.
-
-%Currently we run the simulations on a low resolution space charge grid ($8
-  %\times 8 \times 8$) as a proof of concept.
-%In a next step a simple Python script would be applied to iteratively rerun
-  %the optimizer with increasing space-charge resolution when the limits of the
-  %design variables are narrow enough (iteratively diminishing search space).
-%\subsection{IW2: Inverse Problem}
-
-%In order to find cross correlations we try to solve the inverse problem
-  %(15) -- (23)
-%%
-%\begin{align}
-  %\text{min}  \quad & \sqrt{\frac{1}{N} \sum \left( \text{rmx}_{x,s} -
-                      %\text{m}_{x,s} \right)^2 } \text{,}\\
-              %\quad & \sqrt{\frac{1}{N} \sum \left( \text{rmx}_{y,s} -
-                      %\text{m}_{y,s} \right)^2 } \text{,}\\
-              %\quad & \sqrt{\frac{1}{N} \sum \left( \text{rmx}_{z,s} -
-                      %\text{m}_{z,s} \right)^2 } \\
-  %\text{s.t.} \quad & -0.95 \leq \text{R52} \leq -0.65 \label{eq:iw2:fistdvar}\\
-              %\quad & -0.90 \leq \text{R61} \leq -0.50 \\
-              %\quad & 0.0   \leq \text{R62} \leq 0.20 \\
-              %\quad & 0.25 \leq \text{CORR}_x \leq 0.65 \\
-              %\quad & 0.55 \leq \text{CORR}_y \leq 0.95 \\
-              %\quad & 0.10 \leq \text{CORR}_z \leq 0.50 \label{eq:iw2:lastdvar} \text{.}
-%\end{align}
-%%
-%We try to match the beam to measurements from the real machine by minimizing
-  %the sum of $N$ squared measurement ($m_{d,s}$ at a given position
-  %$s$) errors for rmx beam size in each dimensions.
-%The design variables (\ref{eq:iw2:fistdvar}) - (\ref{eq:iw2:lastdvar}) define
-  %the correlation matrix used when generating particles, e.g., R51, R52, R61,
-  %R62 describe limits of correlations between planes.
-%The initial Binomial distribution (with $m = ?$) has the form
-%%
-%\begin{equation*}
-  %\frac{1}{2\pi\sigma_x\sigma_y}exp(-\frac{x^2}{2\sigma_x^2}
-  %-\frac{y^2}{2\sigma_y^2})
-  %\text{.}
-%\end{equation*}
-%%
-
-%Since these correlations cannot be measured we get the real values by solving
-  %the inverse problem mentioned above.
-
-%Currently we run the simulations on a low resolution space charge grid ($8
-  %\times 8 \times 8$) as a proof of concept.
-%In a next step a simple Python script would be applied to iteratively rerun
-  %the optimizer with increasing space-charge resolution when the limits of the
-  %design variables are narrow enough (iteratively diminishing search space). 
-%\vspace{-7em}
 

### 2018-08-01 paper/theor-experiment.tex
spelling out Figure when at beginning of sent.
adding Yves suggestions

@@
 For further information and details of the implementation see~\cite{whbb:12}.
-Fig.~\ref{fig:pisa_bench} and the corresponding hypervolume values in
+Figure~\ref{fig:pisa_bench} and the corresponding hypervolume values in
   Table~\ref{tbl:bench_rms_error}.
@@
 and nonlinear effects such as space charge. There is no existing information
-that accurately predicts where the Pareto fronts will fall. This work is also meaningful in that
-it will guide future operations at the AWA.
+that accurately predicts optimized parameters for this beam line. 
+This work is also meaningful in that it will guide future operations at the AWA.
 
@@
 While the optimization problem and goals were well defined (Subsection \ref{awaproblem}), 
-it was not clear what the best hyper parameters for the NSGA-II would be.
+it was not clear what the best hyper parameters for the genetic algorithm would be.
 These parameters include gene mutation probability, mutation probability, 
@@
 Given the beam line in Fig.~\ref{awa-linac},
-four small optimization experiments were done with varying NSGA-II parameters. 
+four small optimization experiments were done with various NSGA-II parameters. 
 Similar to the time step scan, 

### 2018-09-04 paper/theor-experiment.tex
linda's second round of edits

@@
 Given a point in the Pareto set, we compute the $m$ dimensional volume (for
-  $m$ objectives) of the dominated space, relative a chosen origin.
+  $m$ objectives) of the dominated space, relative to a chosen origin.
 We visualize this for $2$ objectives in Fig.~\ref{fig:hypervolume}.
 For further information and details of the implementation see~\cite{whbb:12}.
+\lsedit{The next sentence is confusing.  If hyper volumes referring to fig. 6, why is there only one value?  Is it an average?}
 Figure~\ref{fig:pisa_bench} and the corresponding hypervolume values in
@@
 \end{figure}
+
+\lsedit{The column descriptors for the table are not clear  - better formatting needed}
 
@@
 The charge of interest, 40 nC, is needed for Two Beam 
-Acceleration (TBA) \cite{gai_power_jing_2012,JING201872} 
-experiments performed at AWA, which motivates this work.
-
+Acceleration (TBA) 
+experiments performed at AWA \cite{gai_power_jing_2012,JING201872}, 
+which motivates this work. 
 Prior experimental results were limited by beam size when the beam passed through small aperture 
@@
 In an attempt to maximize charge transmission in upcoming experiments
-we optimize magnet strengths in the gun and quadrupoles leading into the 
+we optimize magnet strengths of the solenoids and quadrupoles leading into the 
 TBA section of the beam line, shown in Fig.~\ref{awa-tba}.
-The simulation model includes the linac, kicker, and septum. 
-The optimization location is chosen as the longitudinal 
+The simulation model includes from the gun to the septum.
+The optimization location is chosen as the  
 entrance to the first quadrupole on the dog leg ($s_3$), see Fig.~\ref{awa-tba}.
@@
 
-In addition to the physics challenges, we chose this model to demonstrate the ability of the framework to tackle large problems.
+In addition to addressing the challenge of producing an optimized beam, 
+we chose this model to demonstrate the ability of the framework to tackle large problems.
 Six design variables and objectives were used, along with three constraints.
@@
 The design variables include the two gun solenoids and 
-the first four quadrupoles. 
+the first four quadrupoles settings. 
 This problem encompasses high dimensionality 
@@
 that accurately predicts optimized parameters for this beam line. 
-This work is also meaningful in that it will guide future operations at the AWA.
+This work is meaningful in that it will guide future operations at the AWA.
 
@@
 a study on time step and number of particles in the simulation model 
-was done to reduce the time to simulation while 
+was done to reduce the time of the simulation while 
 maintaining the physics of interest. 
@@
 Next several time steps were explored, see Table~\ref{timestep}.
-The largest steps were too big to resolve the physics needed.
+The largest steps were too big to resolve the beam parameters accurately.
 See low fidelity plot in Fig.~\ref{tstep} for $dT=$\num{5E-11} results.
@@
 	\begin{center}
-		\caption{Checkmarks (\cmark) indicate desired physics is resolved at that time step. 
+		\caption{Checkmarks (\cmark) indicate desired beam parameters are resolved at that time step. 
 			An (\xmark) indicates the time step is too large, and results are nonphysical.}
@@
 the mid fidelity simulations for metrics of interest, as shown in 
-Fig.~\ref{tstep}.  Where we consider mid fidelity as a simulation of the 
-beam line using $dT=\num{1E-12}$ everywhere. The
-average run time of each simulation with the adjusted time steps was 1.6~minutes.
+Fig.~\ref{tstep}.  Mid fidelity simulations used steps of  $dT=\num{1E-12}$ everywhere.
+The average run time of each simulation with the adjusted time steps was 1.6~minutes.
 In comparison, the mid fidelity simulation ran for 18~minutes.
@@
 and shortened the simulation time by moving the objectives further 
-upstream to $s_1$ and $s_2$.
+upstream to $s_1$ and $s_2$, the locations before and after the kicker.
+
+\lsedit{Also, I had no idea what you meant by} %\text{rms}_{s}\left(s = s_1\right) until I saw the parameter list.
+I would suggest`t' for time?
+In any case maybe some text specifying what this is when you first mention it would be helpful.}
+
 The objectives include: $\varepsilon_{x}\left(s = s_1\right)\text{, } \varepsilon_{x}\left(s = s_2\right)\text{, } \text{rms}_{s}\left(s = s_1\right)\text{, and }  \text{rms}_{s}\left(s = s_2\right)$.
-\lsnote{You could define $\varepsilon_{x1}$ to be $\varepsilon_{x} (s=s1)$ and similarly in the table and then use going forward to simplify notation}
 The OPAL input file for ex-3 is given as an example to show how optimization and design variables are defined:
@@
 From Table \ref{extable}, we clearly see ex-3 is significantly 
-slower, as it evaluated only 53 generations compared to the max 
-experiment, ex-1 at 96 generations.
+slower, as it evaluated only 53 generations 
+compared to the experiment with the maximum number, ex-1 at 96 generations.
 Perhaps this trade off would be acceptable if the Pareto front was significantly 
@@
 The objectives (beam sizes and energy spread) are calculated at 
-$s_3=19.4$~m. See Fig.~\ref{awa-tba} for location of $s_3$ w.r.t. other 
-beam line elements. 
+$s_3=19.4$~m, located downstream of the septum, see Fig.~\ref{awa-tba}. 
 Given the longitudinal location of $s_3$ (unless otherwise noted), 
@@
 
-The first four objectives, Eqs. (\ref{eq:awa:p1}) to (\ref{eq:awa:p2}),
+The first four objectives, parameters (\ref{eq:awa:p1}) to (\ref{eq:awa:p2}),
 minimize the transverse ($rms_{x,y}$) beam size and transverse momentum ($rms_{px,py}$)
@@
 which ensures better transmission through the wakefield structures downstream. 
-Less divergence in the beam (lower transverse momentum) 
-reduces growth of transverse beam size after the focal point (min beam size).
+Less divergence in the beam (lower transverse momentum spread) 
+reduces growth of transverse beam size after the focal point (location of min beam size).
 This reduces halo by ensuring the beam is not over focused through a hard waist.
-The momentum is also critical to preventing large growth during transport in bending elements. 
+The momentum spread is also critical to preventing large growth during transport in bending elements. 
 All of these factors help with transmission downstream.
 
-The next two objectives in Eq. (\ref{eq:awa:p4}) minimize the 
+The next two objectives in parameter (\ref{eq:awa:p4}) minimize the 
 longitudinal beam size ($rms_s$), and energy spread (dE) at location $s_3$. 
 This helps reduce longitudinal beam size growth in bending elements.
+\lsedit{Why?  If all particles at lightspeed, then long beam size should not change in a dipole magnet}
 A small bunch length ($rms_s$) is also critical to the goals of 
@@
 As multiple generations, the objectives continue to improve.
+\lsedit{the above sentence makes no sense to me}
 
@@
 and the location of interest for objectives is $s_3=19.4$~meters. 
+\lsedit{Do you mean `the objectives are optimized at location s3' in the above sentence?
+`location of interest for objectives' is not clear.
+Also, I think your later text `This is the entrance to the fifth quad in the beam line.
+This location is where the beam should be captured and focused through subsequent elements.' should be moved here.}
 
@@
 This location is where the beam should be captured and focused through subsequent elements.
+\lsedit{as previously mentioned, move above two sentences.}
 After collection of the data, Pareto fronts comparing the objectives were plotted, 
@@
 As expected, the x dimension is impacted by the bending elements, and unable to reach 
-the small beam sizes seen in the y dimension. This suggest objectives in the x 
+the small beam sizes seen in the y dimension. This suggest suggests objectives in the x 
 dimension will drive design variable choices used in operations. 
 However, it is still necessary to 
-include the y dimension in optimization. Early optimization tests showed the y dimension 
-can easily grow out of control if not included in the objectives.
-Those results are not shown here due to the unfeasible solutions they resulted in
+include the y dimension in the optimization. Early optimization tests showed the y dimension 
+can easily grow out of control if it is not included in the objectives.
+Those results are not shown here due to the unfeasible nature of the solutions 
 (i.e. $rms_y$ larger than the beam pipe).
@@
 With these observations in mind, several beam parameters corresponding to
-options on Pareto Front in Fig.~\ref{fig:pareto1} were plotted and compared. 
-A select result is shown in Fig.~\ref{fig:stat}. 
+options on the Pareto Front in Fig.~\ref{fig:pareto1} were plotted and compared. 
+A select result is shown in Fig.~\ref{fig:stat}.  \lsedit{It would be a nice addition to say which point on the pareto front that was, perhaps marking it on the curve}
 The maximum beam sizes are well below the beam pipe aperture limits as shown in Fig.~\ref{fig:stat} (b).
@@
 Overall this solution is satisfactory, and meets all requirements at the AWA.
+\lsedit{Some comments on Fig.
+13: FIrst, is fig 13(a) necessary?
+Why can't you just add a vertical scale to fig.
+13b?
+Also, how about adding more info to the figure caption; is s=0 the position of the cathode?
+If so, put that in the caption.
+You could describe what each curve is in the figure caption for completeness.
+The bottom traces show the optimized beam sizes..
+The top black trace shows..
+including key elements such as the kicker location.
+Why do you start showing the aperture at s=10?
+Is it plenty big before that?
+If so, in the figure caption you could say, the aperture is shown starting at s=10 because the aperture constraints are more acute after that point.}
 

### 2018-09-04 paper/theor-experiment.tex
removing AiF for Christof, and more linda edits

@@
 The location at the entrance of the kicker is $s_1=16.45$~meters, 
-and the location of interest for objectives is $s_3=19.4$~meters. 
-\lsedit{Do you mean `the objectives are optimized at location s3' in the above sentence?
-`location of interest for objectives' is not clear.
-Also, I think your later text `This is the entrance to the fifth quad in the beam line.
-This location is where the beam should be captured and focused through subsequent elements.' should be moved here.}
+and the objectives are optimized at location $s_3=19.4$~meters. 
+This is the entrance to the fifth quad in the beam line. 
+This location is where the beam should be captured and focused through subsequent elements.
 
@@
 we wanted a large population size that would fit evenly on these resources. 
-
 Again, the location of optimization is $s_3=19.4$ [m].
-This is the entrance to the fifth quad in the beam line. 
-This location is where the beam should be captured and focused through subsequent elements.
-\lsedit{as previously mentioned, move above two sentences.}
-After collection of the data, Pareto fronts comparing the objectives were plotted, 
-see Figs.~\ref{fig:pareto1} and \ref{fig:pareto2}.
 

### 2018-09-16 run_opt_params/experiment_comparison_30nC/3D/setup.sh
opal input files for experimental comparison

@@ -1,0 +1,9 @@
+# general of opal
+#rm -rf results *.0 *_0
+#rm -rf tmp
+#mkdir tmp results
+export QUEUE=knlall
+export TEMPLATES=`pwd`/tmpl/
+export TIME=01:00:00
+export OPAL_EXE_PATH=/lcrc/project/AWA-beam-dynamics/software/knl/bin
+export FIELDMAPS=/lcrc/project/AWA-beam-dynamics/FieldFiles/DriveFiles

### 2018-09-16 paper/figures/opt-framework_code.tex
updating framework fig

@@
-\node (ML) [draw, text centered,
+\begin{pgfonlayer}{background}
+	\path (-3,4.5)+(0,0) node (a) {};
+	\path (0,0)+(3,-3) node (c) {};
+
+	\path[fill=white!20,rounded corners, draw=black!50, dashed]
+	(a) rectangle (c);           
+	\path (-2,4)+(-0,0) node (a) {OPAL};
+
+\end{pgfonlayer}
+
+	\node (optimizer) [draw, text centered,
 	text width=12.8em, fill=red!60, fill opacity=0.1, minimum height=2em,
@@
 
-\path (ML.north)+(-1.38,0.8) node (optimizer) [draw, text centered,
+	\path (optimizer.north)+(-1.38,0.8) node (pilot) [draw, text centered,
 	text width=5em, fill=brown, fill opacity=0.1, minimum height=2em,
@@
 
-\path[<->, very thick] (optimizer.east)+(.0,-0.2) edge [bend left] (ML.north);
+	\path[<->, very thick] (pilot.east)+(.0,-0.2) edge [bend left] (optimizer.north);
 
-\path (optimizer)+(-2.5,.8) node (input) [draw, text
+	\path (pilot)+(-2.5,.8) node (input) [draw, text
 	width=2em, fill=olive!60, fill opacity=0.1, minimum height=2em,
-    text opacity=1.0] {\tiny{-\\ -\\ input}};
-\path (optimizer)+(-2.5,-.4) node (obj) [draw, text
-    width=2em, fill=olive!60, fill opacity=0.1, minimum height=2em,
-    text opacity=1.0] {\tiny{-\\ -\\ obj}};
-\path (optimizer)+(-2.5,-1.6) node (constr) [draw, text
-    width=2em, fill=olive!60, fill opacity=0.1, minimum height=2em,
-    text opacity=1.0] {\tiny{-\\ -\\ constr}};
-\path [<-, very thick] (optimizer.west)+(.0,0.2) edge (input.east);
-\path [<-, very thick] (optimizer.west) edge (obj.east);
-\path [<-, very thick] (optimizer.west)+(.0,-0.2) edge (constr.east);
+	text opacity=1.0] {\tiny{input \vspace{0.2em} \\obj\\constr}};
+%	\path (optimizer)+(-2.5,-.4) node (obj) [draw, text
+%	width=2em, fill=olive!60, fill opacity=0.1, minimum height=2em,
+%	text opacity=1.0] {\tiny{-\\ -\\ obj}};
+%	\path (optimizer)+(-2.5,-1.6) node (constr) [draw, text
+%	width=2em, fill=olive!60, fill opacity=0.1, minimum height=2em,
+%	text opacity=1.0] {\tiny{-\\ -\\ constr}};
+	\path [<-, very thick] (pilot.west)+(.0,0.2) edge (input.east);
+%	\path [<-, very thick] (optimizer.west)+(.0,-0.2) edge (constr.east);
 
-\path (optimizer)+(2.0,0.8) node (sims) [draw, text
-    width=2em, fill=orange!60, fill opacity=0.1, minimum height=2em,
-    text opacity=1.0] {\tiny{-\\ -\\ sims}};
+	\path (pilot.east)+(2.0,0.8) node (sims) [draw, text
+	width=3em, fill=orange!60, fill opacity=0.1, minimum height=2em,
+	text opacity=1.0] {\tiny{sim results}};
 
-\path (sims.east)+(1.8,0.6) node (opal) [draw, text centered,
+	\path (pilot.north)+(0.7,1.5) node (opal) [draw, text centered,
 	text width=6em, fill=orange, fill opacity=0.1, minimum height=2em,
@@
 
-\path[<->, very thick] (optimizer.east) edge [bend right] (sims.south);
-\path[<->, very thick] (sims.east) edge [bend left] (opal.west);
+	\path [->, very thick] (pilot.north) edge [bend left] (opal.south);	
+	\path[<-, very thick] (optimizer.east) edge [bend right] (sims.east);
+	\path[<-, very thick] (sims.north) edge [bend right] (opal.east);
 
-\path (ML.south)+(-1.30,-1.8) node (convex) [draw, text centered,
+	\path (optimizer.south)+(-1.30,-1.8) node (convex) [draw, text centered,
 	text width=5em, fill=blue!60, fill opacity=0.1, minimum height=2em,
@@
 
-\path (ML.south)+(1.30,-1.8) node (heuristic) [draw, text centered, text
+	\path (optimizer.south)+(1.30,-1.8) node (heuristic) [draw, text centered, text
 	width=5em, fill=blue!60, fill opacity=0.1, minimum height=4em,
@@
 
-\path[<->, very thick] (convex.north)+(+0.8,0.0) edge [bend right] (ML.south);
-\path[<->, very thick] (heuristic.north)+(-0.8,0.0) edge [bend left] (ML.south);
+	\path[<->, very thick] (convex.north)+(+0.8,0.0) edge [bend right] (optimizer.south);
+	\path[<->, very thick] (heuristic.north)+(-0.8,0.0) edge [bend left] (optimizer.south);

### 2018-09-16 paper/theor-experiment.tex
clean up

@@
 			\hline\noalign{\smallskip}
-			& Gene Mutation Probability & Recombination Probibility & Number of completed generations \\
+			& Gene Mutation Probability & Recombination Probability & Number of completed generations \\
 			\noalign{\smallskip}\hline\noalign{\smallskip}
@@
 \begin{figure}
-	\includegraphics[width=0.5\textwidth]{../pareto_stat_plots/xy_vs_pxy_pareto_front_quads_before_Q5}
+	\includegraphics[width=0.5\textwidth]{../pareto_stat_plots/safehold/xy_vs_pxy_pareto_front_quads_before_Q5}
 	\caption{Pareto front comparing transverse beam sizes ($\sigma_{x,y}$) and transverse momentum ($\sigma_{px,py}$).}
@@
 	\centering
-	\includegraphics[width=0.48\textwidth]{../pareto_stat_plots/dE_vs_zrms_pareto_front_quads_before_Q5_zoomout}%
+	\includegraphics[width=0.48\textwidth]{../pareto_stat_plots/safehold/dE_vs_zrms_pareto_front_quads_before_Q5_zoomout}%
 	\llap{\raisebox{1.9cm}{%  move next graphics to top right corner
-			\includegraphics[height=4.5cm]{../pareto_stat_plots/dE_vs_zrms_pareto_front_quads_before_Q5}%
+			\includegraphics[height=4.5cm]{../pareto_stat_plots/safehold/dE_vs_zrms_pareto_front_quads_before_Q5}%
 	}}
@@
 \begin{figure}
-	\includegraphics[width=0.48\textwidth]{../pareto_stat_plots/xyrms-zrms_newobj}\\
-	\vspace{2em}
-	\includegraphics[width=0.48\textwidth]{../pareto_stat_plots/xy-max-min-zrms_newobj}
+	\includegraphics[width=0.48\textwidth]{../pareto_stat_plots/safehold/xy-max-min-zrms_newobj}
 	\caption{Optimized beam sizes along high charge beam line.}

### 2018-09-16 makemldb.py

@@ -16,7 +16,10 @@ The content of the file is
 #baseFN = 'rand_sample'
 #root   = "/lcrc/project/AWA-beam-dynamics/surrogatemodels/random_sample/surrogate_models_rand_sample_bounds2"
 path    = './databases/'
-baseFN  = ['ex-1', 'ex-2', 'ex-3', 'ex-4']
+#baseFN  = ['ex-1', 'ex-2', 'ex-3', 'ex-4']
+root    = 'paper-run-ex4/results'
+baseFN  = ['paper-run-ex4']
+
 #root   = "/lcrc/project/AWA-beam-dynamics/Nicole/awa-tba/paper-run-1/results"
 #root   = "./ex-4/results"
 

### 2018-09-20 paper/theor-experiment.tex
fixing missing plot

--- 2018-09-04 paper/theor-experiment.tex
@@
 \begin{figure}
-	\includegraphics[width=0.48\textwidth]{../pareto_stat_plots/xyrms-zrms_newobj}\\
-	\vspace{2em}
 	\includegraphics[width=0.48\textwidth]{../pareto_stat_plots/xy-max-min-zrms_newobj}

### 2018-09-24 paper/prab.tex
spelling out Figure when at beginning of sent.
making equation span two columns
linda's second round of edits
remove SwissFEL ties

@@
 %rmp,
-%prstab,
+prstab,
 %prstper,
@@
 \usepackage{graphicx,xcolor,enumitem}
+%\usepackage{cuted}
 \newcommand{\lsnote}[1]{\textsf{{\color{violet}{ LS note:}   #1 }}}
@@
 
-\newcommand{\nrnote}[1]{\textsf{{\color{violet}{ NN note:}   #1 }}}
-
+\newcommand{\nrnote}[1]{\textsf{{\color{blue}{ NN note:}   #1 }}}
+\newcommand{\lsedit}[1]{\textsf{{\color{violet}{ ls note:}   #1 }}}
 \begin{document}
@@
 
-\author{Y. Ineichen }
-\affiliation{% 
-	place holder 1
-}%
-
 \author{A. Adelmann}
 \email{andreas.adelmann@psi.ch}
+\author{Y. Ineichen }
+%\email{yves.ineichen@gmail.com}
 \author{A. Kolano}
@@
 \author{C. Metzger-Kraus}
-\altaffiliation[Also at ]{AiF Projekt GmbH}
 \affiliation{
@@
 
-Here, we will focus on a real world applications arising from Paul Scherrer Institut's (PSI)
-  \textsc{SwissFEL}~\cite{pedr:10} activities, and a high charge photoinjector 
-  at the Argonne Wakefield Accelerator (AWA). Both of which have an immediate and a
-  long-range impact, by optimizing important parameters for rf photoinjectors.
+Here, we will focus on a real world application, the a high charge photoinjector 
+  at the Argonne Wakefield Accelerator (AWA).
+
+  %Both of which have an immediate and a
+  %long-range impact, by optimizing important parameters for rf photoinjectors.
 
@@
   functions for the corresponding genes.
-Fig.~\ref{fig:varsel} schematically depicts the connection of the
+Figure~\ref{fig:varsel} schematically depicts the connection of the
   components introduced above.
@@
 
-\begin{flushleft}
+%\begin{strip}
+	\begin{widetext}
 		\begin{align} \label{eqn:bench}
@@
 		\left(x_3 - \frac{1}{\sqrt{3}} \right)^2 \right)\right), \right. \\
+		\vspace{3em} 
 		& \left. 1 - \exp \left( -1 \left(
@@
 		\left(x_3 + \frac{1}{\sqrt{3}} \right)^2 \right)\right) \right]^T \nonumber \\
+		\vspace{3em} \\
 		\text{s.t.} \quad & \quad -1 \le x_i \le 1, \quad i=1,2,3 \nonumber
@@
 		\end{align}
-\end{flushleft}
+	\end{widetext}
+%\end{strip}
 
@@
 
-\input{theor-experiment} %periment}
+\input{theor-experiment}
 
@@
 
-The authors thank the \textsc{SwissFEL} and AWA teams for contributing to the
+The authors thank the AWA team for contributing to the
   formulation of optimization problems. 

### 2018-09-28 paper/theor-experiment.tex
first round of edits with Dr. Neveu

@@
 For further information and details of the implementation see~\cite{whbb:12}.
-\lsedit{The next sentence is confusing.  If hyper volumes referring to fig. 6, why is there only one value?  Is it an average?}
 Figure~\ref{fig:pisa_bench} and the corresponding hypervolume values in
-  Table~\ref{tbl:bench_rms_error}.
+  Table~\ref{tbl:bench_rms_error}, show expected convergence.
 The reference Pareto front is clearly very well approximated.
@@
 
-\lsedit{The column descriptors for the table are not clear  - better formatting needed}
-
 \begin{table}%[h!]
@@
   \label{tbl:bench_rms_error}
-  \begin{tabular}{lcc}
+  \begin{tabular}{c|c|c}
     \hline\noalign{\smallskip}
@@
     100  &  0.859753 & $3.076 \times 10^{-1}$ \\
-    \noalign{\smallskip}\hline\noalign{\smallskip}
+   % \noalign{\smallskip}\hline\noalign{\smallskip}
     200  &  0.784943 & $1.938 \times 10^{-1}$ \\
@@
 
-\lsedit{Also, I had no idea what you meant by} %\text{rms}_{s}\left(s = s_1\right) until I saw the parameter list.
-I would suggest`t' for time?
-In any case maybe some text specifying what this is when you first mention it would be helpful.}
-
-The objectives include: $\varepsilon_{x}\left(s = s_1\right)\text{, } \varepsilon_{x}\left(s = s_2\right)\text{, } \text{rms}_{s}\left(s = s_1\right)\text{, and }  \text{rms}_{s}\left(s = s_2\right)$.
+The objectives include: $\varepsilon_{x}\left(s = s_1\right)\text{, } \varepsilon_{x}\left(s = s_2\right)$, $\text{rms}_{s}\left(s = s_1\right)\text{, and }  \text{rms}_{s}\left(s = s_2\right)$. 
 The OPAL input file for ex-3 is given as an example to show how optimization and design variables are defined:
@@
 longitudinal beam size ($rms_s$), and energy spread (dE) at location $s_3$. 
-This helps reduce longitudinal beam size growth in bending elements.
-\lsedit{Why?  If all particles at lightspeed, then long beam size should not change in a dipole magnet}
+This helps reduce the transverse beam size growth in bending elements.
 A small bunch length ($rms_s$) is also critical to the goals of 
 TBA experiments. The power generated in the wakefield structures 
-designed for TBA is related to the bunch length \cite{JING201872}.
-\nrnote{need better source for this info} 
-i.e. smaller bunch lengths result in larger wakefields and higher power generation.
+designed for TBA is related to the bunch length \cite{JING201872,PETSeq}.
 
@@
 define three constraints used to guide the algorithm.
-The bounding values may seem large, but this is done to avoid over constraining the 
-problem in early generations. When the constraints were set tighter, 
-optimization runs did not reach the second generation within a 48 hour time limit. 
-In other words, enough satisfactory points were not produced to fill a complete generation in 48 hours. 
-By leaving the value large, a sufficient number of simulations finish
-and subsequent generations are reached in a timely manner. 
-As multiple generations, the objectives continue to improve.
-\lsedit{the above sentence makes no sense to me}
-
+However, it is important to not over-constrain the problem, which would prevent
+the algorithm from converging.
 The difference constraint, Eq.~\ref{eq:awa:c3}, is used to favor nearly round beams.
@@
 %\vspace{-1em}
-As introduced in Section \ref{ferrario}, we define the AWA optimization 
+The AWA 
 design variables, objectives, and constraints in the OPAL input file as shown in
@@
 Overall this solution is satisfactory, and meets all requirements at the AWA.
-\lsedit{Some comments on Fig.
-13: FIrst, is fig 13(a) necessary?
-Why can't you just add a vertical scale to fig.
-13b?
-Also, how about adding more info to the figure caption; is s=0 the position of the cathode?
-If so, put that in the caption.
-You could describe what each curve is in the figure caption for completeness.
-The bottom traces show the optimized beam sizes..
-The top black trace shows..
-including key elements such as the kicker location.
-Why do you start showing the aperture at s=10?
-Is it plenty big before that?
-If so, in the figure caption you could say, the aperture is shown starting at s=10 because the aperture constraints are more acute after that point.}
 
@@
 	\includegraphics[width=0.48\textwidth]{../pareto_stat_plots/xy-max-min-zrms_newobj}
-	\caption{Optimized beam sizes along high charge beam line.}
+	\caption{Optimized beam sizes along high charge beam line. The gun is located at $s=0$, 
+	both x and y beam sizes are shown. The black line represents the relevant beam line aperture, while
+	the green line indicates the location of the optimisation.}
 	\label{fig:stat}

### 2018-09-28 paper/theor-experiment.tex
updating exp tex

@@
 	\centering
-	\includegraphics[width=\linewidth]{Report/timestep_comparison}
+	\includegraphics[width=\linewidth]{Report/timestep_comparison_paper}
 	\caption{Comparison of different fidelity models (dT stands for time step).}
@@
 
-TITLE, STRING="ANL Optimisation";
+TITLE, STRING="ANL Optimization";
 
@@
 Again, the location of optimization is $s_3=19.4$ [m]. 
-
 \begin{figure}
-	\includegraphics[width=0.5\textwidth]{../pareto_stat_plots/xy_vs_pxy_pareto_front_quads_before_Q5}
-	\caption{Pareto front comparing transverse beam sizes ($\sigma_{x,y}$) and transverse momentum ($\sigma_{px,py}$).}
+	\begin{center}		
+		\begin{tikzpicture}[scale=1]
+		\node (fig1) at (0,0)
+		{\includegraphics[width=0.5\textwidth]{../pareto_stat_plots/xy_vs_pxy_pareto_front_quads_before_Q5}};
+		\node[star, star points=5, star point ratio=0.5, fill=yellow, draw](key) at (3.35,-1.7) {};
+		\end{tikzpicture}
+	\end{center} 
+		\caption{Pareto front comparing transverse beam sizes ($\sigma_{x,y}$) and transverse momentum ($\sigma_{px,py}$). The yellow star indicates the 
+		point plotted in Fig.~\ref{fig:stat}}
 	\label{fig:pareto1}
@@
 
+\iffalse
 \begin{figure}
@@
 \end{figure}  
+\fi
 
@@
 options on the Pareto Front in Fig.~\ref{fig:pareto1} were plotted and compared. 
-A select result is shown in Fig.~\ref{fig:stat}.  \lsedit{It would be a nice addition to say which point on the pareto front that was, perhaps marking it on the curve}
+A select result is shown in Fig.~\ref{fig:stat}.  
 The maximum beam sizes are well below the beam pipe aperture limits as shown in Fig.~\ref{fig:stat} (b).
@@
 \begin{figure}
-	\includegraphics[width=0.48\textwidth]{../pareto_stat_plots/xy-max-min-zrms_newobj}
+	\includegraphics[width=0.48\textwidth]{../pareto_stat_plots/xy-max-min-sigma-paper}
 	\caption{Optimized beam sizes along high charge beam line. The gun is located at $s=0$, 
 	both x and y beam sizes are shown. The black line represents the relevant beam line aperture, while
-	the green line indicates the location of the optimisation.}
+	the green line indicates the location of the optimization.}
 	\label{fig:stat}
 \end{figure}
+\begin{table}%[h!]
+	\begin{center}
+		\caption{Input Parameters for large scale TBA optimization runs.}
+		\label{tab:designopt}   
+		\begin{tabular}{l|c|c}
+			\noalign{\smallskip}\hline\noalign{\smallskip}
+			%\rowcolor{blue!30} 
+			\textbf{Design Variable} & \textbf{Unit}	&  \textbf{Value}  \\ 
+			\noalign{\smallskip}\hline\noalign{\smallskip}
+			{Buck Focusing Solenoid} & amps	& 478 \\
+			Matching Solenoid &	amps	& 197	  \\
+			Quadrupole 1& T-m		& -0.8	\\ 
+			Quadrupole 2& T-m		& 0.9	\\
+			Quadrupole 3 & T-m		& 0.8	\\
+			Quadrupole 4 & T-m		& -1.0	\\ 
+			Bunch Length & mm 		& 1.5	\\
+			\noalign{\smallskip}\hline\noalign{\smallskip}
+		\end{tabular}
+	\end{center}
+\end{table}

### 2018-09-28 paper/prab.tex
first round of edits with Dr. Neveu
typo

@@
 \begin{code}[Assembling the optimizer \\ from components]
-typedef  \textsc{OPAL-t} InputFileParser Input_t;
+typedef InputFileParser Input_t;
 typedef PisaVariator        Opt_t;
@@
 
+Outlook, ....
+
 \section{ACKNOWLEDGMENT}

### 2018-09-29 paper/prab.tex
changes to ch 1 and lit

@@
 We developed a modular multi-objective software framework (see
-  Fig.~\ref{fig:framenetwork}) where the core functionality is decoupled from
-  the ``forward solver'' and the optimizer.
+  Fig.~\ref{fig:framenetwork}) where the core functionality of the optimizer is decoupled from
+  the ``beam dynamics'' but fully integrated in the OPAL \cite{opal} framework. 
 To that end, we use a master/slave mechanism where a master process governs a
-  set of slave processes given some computational tasks to complete.
+  set of slave processes given some computational tasks (beam dynamics simulation) to complete.
 This separation allows to easily interchange optimizer algorithms, forward
@@
 A ``pilot'' coordinates all efforts between the optimization algorithm and the
-  forward solver.
+  beam dynamics task. In the sequel we will also use the notion of ``forward solver'' to indicate 
+  the beam dynamics task.
 This forms a robust and general framework for massively parallel
@@
 Currently the framework offers one concrete optimization algorithm, an
-  evolutionary algorithm employing a \textsc{NSGAII} selector \cite{pisa}.
+  evolutionary algorithm employing a \textsc{NSGA-II} selector \cite{pisa}.
 Normally, simulation based approaches are plagued by the trade-of between
   level of detail and time to solution.
-We address this problem by using forward solvers with different time and
+We address this problem later in Section~(\ref{awa:subsection:test}) by using forward solvers with different time and
   resolution complexity.

### 2018-09-29 paper/prab.tex
clarify OPAL integration

@@
   \textsc{Pilot} being handled by $W_j$. Subsequently the result $r_k$ is
-  returned to the requesting \textsc{Optimizer} ($O_i$).}
+  returned to the requesting \textsc{Optimizer} ($O_i$). The work $W_j$ are beam dynamics 
+  simulation within OPAL.}
   \label{fig:opt-framework-layout}
@@
 
-In most cases \textsc{Simulation} implementations are simple wrappers to run
+In most cases forward solver implementations are simple wrappers to run
   an existing ``external'' simulation code using a set of design variables as
-  input.
+  input. In case of the OPAL integration, basically the \texttt{main} function is
+  playing the role of the ``forward solver''. Underlying the general nature of our approach, 
+  in a similar project, we use the described methods for cavity shape optimisation based on \cite{ARBENZ2008381}. 
 As for the \textsc{Optimizer} component there exists a base class, labeled

### 2018-09-29 paper/prab.tex
first round of grammer edits

--- 2018-09-28 paper/prab.tex
@@
 \usepackage{bm}% bold math
-\usepackage{todonotes}
+%\usepackage{todonotes}
 \usepackage{siunitx}
@@
 %\usepackage{multicol}
-\usepackage{color}
+%\usepackage{color}
 \usepackage{algorithm}
@@
 	algorithms and workers running forward solves.}
-\end{figure}\label{fig:framenetwork}
-
-We developed a modular multi-objective software framework (see
+\label{fig:framenetwork}
+\end{figure}
+
+A modular multi-objective software framework was developed (see
   Fig.~\ref{fig:framenetwork}) where the core functionality is decoupled from
@@
   set of slave processes given some computational tasks to complete.
-This separation allows to easily interchange optimizer algorithms, forward
+This separation allows easy interchange of optimization algorithms, forward
   solvers and optimization problems.
@@
 Currently the framework offers one concrete optimization algorithm, an
-  evolutionary algorithm employing a \textsc{NSGAII} selector \cite{pisa}.
+  evolutionary algorithm employing a \textsc{NSGA-II} selector \cite{pisa}.
 Normally, simulation based approaches are plagued by the trade-of between
@@
   \item design and implementation of a modular framework that is simple to use
-        and deploy on large scale computation resources, and
+        and deploy on large scale computational resources, and
   \item demonstrating the usefulness of the proposed framework on a real world
-        application in the domain of particle accelerators.
+        application in the domain of particle accelerators,
+        with the optimization problem set as 
+        the high charge photoinjector at the Argonne Wakefield Accelerator (AWA). 
 \end{enumerate}
-
-Here, we will focus on a real world application, the a high charge photoinjector 
-  at the Argonne Wakefield Accelerator (AWA).
-
-  %Both of which have an immediate and a
-  %long-range impact, by optimizing important parameters for rf photoinjectors.
 
@@
 theory and describes the first implemented optimizer.
-In Section~\ref{sec:framework} we discuss the implementation of the framework.
+In Section~\ref{sec:framework} the implementation of the framework is discussed.
 We introduce the employed forward-solver in Section~\ref{sec:forward-solver}.
@@
   corresponding to extreme values of objectives.
-If more than one objective is present in the optimization problem we call this
+If more than one objective is present in the optimization problem this is called
   a multi-objective optimization problem (MOOP).
@@
 
-Often, we encounter conflicting objectives complicating the concept of
+Often, conflicting objectives are encountered, and this complicates the concept of
   optimality.
@@
 
-Once the shape of the Pareto front has been determined the buyer can
+Once the shape of the Pareto front has been determined, the buyer can
   \textit{specify preference}, balancing the features by observing the
@@
   surface of the search space.
-So far, we used an NSGA-II selector \cite{dpam:02} exhibiting satisfactory
+So far, the NSGA-II selector \cite{dpam:02} has been used and exhibits satisfactory
   convergence performance.
@@
 Simulation based multi-objective optimization problems are omnipresent in
-  research and the industry.
+  research and industry.
 The simulation and optimization problems arising in such problems are in
@@
   \textsc{Simulation} modules.
-
-We implemented the framework in \texttt{C++}, utilizing features like template
+The framework was implemented in \texttt{C++}, utilizing features like template
   parameters to specify the composition of the framework (shown in Listing 1).
@@
 %\end{minipage}
-
 The framework provides ``default'' implementations that can be controlled via
@@
 Upon reception a new message is immediately forwarded to the appropriate
-  handler, the \texttt{onMessage()} method.
+  handler: the \texttt{onMessage()} method.
 The method is called with the \texttt{MPI\_Status} of the received message and
@@
   already implementing the polling protocol for default worker types.
-As shown in the API in Listing 3 the \texttt{Worker} class expects an
+As shown in the API in Listing 3, the \texttt{Worker} class expects an
   implementation to provide implementations for those three methods.
@@
 Subsequently, the \texttt{Worker} calls \texttt{collectResults}, where the
-  \textsc{Simulation} prepares the result data, e.g., parsing output files,
+  \textsc{Simulation} prepares the result data, e.g. parsing output files,
   and stores the requested information in a \texttt{reqVarContainer\_t} data
@@
   specification in the simulation input file by prefixing it with special
-  characters, e.g., as annotations prefixed with a special character.
+  characters, e.g. as annotations prefixed with a special character.
 In some cases it might not be possible to annotate the simulation input file.
@@
 \noindent
-  we implemented an expression parser using Boost
-%  Spirit\footnote{\url{http://boost-spirit.com/}}.
+  we implemented an expression parser using Boost Spirit\footnotemark \footnotetext{test}
+  	%http://boost-spirit.com/}.
 In addition to the parser, we need an evaluator able to evaluate an expression,

### 2018-09-29 paper/prab.tex

@@
 A modular multi-objective software framework was developed (see
-  Fig.~\ref{fig:framenetwork}) where the core functionality is decoupled from
-  the ``forward solver'' and the optimizer.
+ Fig.~\ref{fig:framenetwork}) where the core functionality of the optimizer is decoupled from
+ the ``beam dynamics'' but fully integrated in the OPAL \cite{opal} framework. 
 To that end, we use a master/slave mechanism where a master process governs a
-  set of slave processes given some computational tasks to complete.
+ set of slave processes given some computational tasks (beam dynamics simulation) to complete.
 This separation allows easy interchange of optimization algorithms, forward
@@
   level of detail and time to solution.
-We address this problem by using forward solvers with different time and
+We address this problem later in Section~(\ref{awa:subsection:test}) by using forward solvers with different time and
   resolution complexity.

### 2018-09-29 paper/prab.tex

@@
 \noindent
-  we implemented an expression parser using Boost Spirit\footnotemark \footnotetext{test}
-  	%http://boost-spirit.com/}.
+  we implemented an expression parser using Boost Spirit~\cite{boost}.
 In addition to the parser, we need an evaluator able to evaluate an expression,
@@
 The function arguments specified in the corresponding expression are stored in
-  a \texttt{std::vector} of Boost
-%  variants\footnote{\url{www.boost.org/doc/html/variant.html}} that can be
+  a \texttt{std::vector} of Boost variants~\cite{boost2} that can be
   booleans, strings or floating point values.
@@
 As shown in Listing 5 this is done by creating a collection of Boost
-%  functions\footnote{\url{www.boost.org/libs/function/}} corresponding to the
+  functions~\cite{boost3} corresponding to the
   available custom functions in expressions and passing this to the

### 2018-09-29 paper/prab.tex
fixing commas

@@
   of accelerator facilities is a complex and versatile problem.
-Today, tuning machine parameters, e.g., bunch charge, emission time and
+Today, tuning machine parameters, e.g. bunch charge, emission time and
   various parameters of beamline elements, is most commonly done manually by
@@
   a solution after all possible trade-offs have been presented to us.
-An alternative is to specify preference \textit{a priori}, e.g., by
+An alternative is to specify preference \textit{a priori}, e.g. by
   weighting (specifying preference before solving the problem) and combining
@@
   simple mechanism to define and call custom functions in expressions.
-Using simple functors, e.g., as the one shown in Listing 4 to compute an
+Using simple functors, e.g. as the one shown in Listing 4 to compute an
   average over a set of data points, enriches expressions with custom

### 2018-09-29 paper/prab.tex
eq fix

@@
   functions, is included in the dictionary by default.
-This enables an out of source description of optimization problem containing
+This enables an out of source description of optimization problems containing
   only simple math primitives.
@@
 
-The parallelization will be explained and benchmarked in detail in a
-  forthcoming publication.
 One major disadvantage of the master/slave implementation model is the fast
@@
 
-To that end we implemented a solution propagation based on rumor networks (see
-  e.g.\ \cite{bgps:06,ayss:09}) using only one-sided communication.
+To that end we implemented a solution propagation based on rumor networks 
+(see \cite{bgps:06,ayss:09}) using only one-sided communication.
 This limits the number of messages sent over the already heavily used links
@@
   accelerators with satisfactory parallel performance \cite{akir:09}.
-Recently we introduced a reduced envelope model \cite{iabc:12} into
-  \textsc{OPAL} reducing time to solution by several orders of magnitude.
 
@@
 		\left(x_3 + \frac{1}{\sqrt{3}} \right)^2 \right)\right) \right]^T \nonumber \\
-		\vspace{3em} \\
+		\vspace{3em} \nonumber \\
 		\text{s.t.} \quad & \quad -1 \le x_i \le 1, \quad i=1,2,3 \nonumber
-		\text{.}
+		\text{.} \nonumber
 		\end{align}

### 2018-09-29 paper/theor-experiment.tex
fig ref
starting to edit theor-exp

@@
 
-In this section we present numerical results of the validation benchmark and
-  discuss optimization of a photoinjector operated in the space charge dominated regime.
+In this section a numerical results of the validation benchmark and
+  optimization of a photoinjector operated in the space charge dominated regime is presented.
 
@@
 In the case of bunch length, there are not many options to choose from.
-Ignoring the extreme value on the right, Fig.~\ref{fig:pareto2} shows the 
+Ignoring the extreme value on the right, Fig.~\ref{fig:pareto1} shows the 
 range of optimal bunch lengths fall between 1.39 and 1.5 mm.

### 2018-09-29 paper/theor-experiment.tex
grammer edits to theor-exp

@@
 
-From Table~\ref{tbl:bench_rms_error} we deduce that we achieved satisfactory
+Table~\ref{tbl:bench_rms_error} shows satisfactory
   convergence to the sampled reference Pareto front after 1000 (plus the
@@
 \subsection{AWA Photoinjector Optimization} \label{awaproblem}
-Next we apply the optimization framework to a high charge beam line
+Next the optimization framework is applied to a high charge beam line
  at the Argonne Wakefield Accelerator (AWA) facility. 
@@
 wakefield structures located downstream. 
-In an attempt to maximize charge transmission in upcoming experiments
-we optimize magnet strengths of the solenoids and quadrupoles leading into the 
-TBA section of the beam line, shown in Fig.~\ref{awa-tba}.
+In an attempt to maximize charge transmission in upcoming experiments,
+magnet strengths of the solenoids and quadrupoles leading into the 
+TBA section of the beam line were optimized, shown in Fig.~\ref{awa-tba}.
 The simulation model includes from the gun to the septum.
@@
 In addition to addressing the challenge of producing an optimized beam, 
-we chose this model to demonstrate the ability of the framework to tackle large problems.
+this model was chosen to demonstrate the ability of the framework to tackle large problems.
 Six design variables and objectives were used, along with three constraints.
@@
 The design variables include the two gun solenoids and 
-the first four quadrupoles settings. 
+the first four quadrupoles strengths. 
 This problem encompasses high dimensionality 
@@
 After comparing several options (1,000, 10,000, 20,000, 50,000, 100,000) 
-with a small time step, the number of particles was fixed at ten thousand.
+with a small time step, the number of particles was fixed at 10,000.
 Next several time steps were explored, see Table~\ref{timestep}.
@@
 
-In the drifts and linac tanks, $dT=\num{1E-11}$ was sufficient, 
-but not acceptable near the quadrupoles. 
+In the drifts and linac tanks, $dT=\num{1E-11}$ was sufficient. 
+However, it was not acceptable near the quadrupoles. 
 For all models, the longitudinal parameters (rms$_s$ and energy) 

### 2018-09-29 paper/theor-experiment.tex
grammer edits to theor-exp 2

@@
 In the linac and drift sections $dT=\num{1E-11}$ was used. 
-A time step of $dT=\num{1E-12}$ was used near sensitive elements such as the quadrupoles, kicker, and septum.
-
+Near sensitive elements such as the quadrupoles, kicker, and septum, 
+a time step of $dT=\num{1E-12}$ was used.
 The resulting simulations are low fidelity in most places, but closely approximate 
@@
 Note, a smaller time step, \num{1E-13}, is always used in the gun where the 
-beam is low energy and changing rapidly.
+beam has low energy and changing rapidly.
 %A summary of the parameters used is listed in Table \ref{fidelity}.
@@
 Given the beam line in Fig.~\ref{awa-linac},
-four small optimization experiments were done with various NSGA-II parameters. 
+four small optimization experiments were done with various hyper parameters. 
 Similar to the time step scan, 

### 2018-09-29 paper/theor-experiment.tex
fixing units

@@
 	\caption{Side view of the high charge linac at the AWA. 
-		All hardware in this drawing is currently installed.}
+		All hardware in this drawing is currently installed. 
+	Note locations $s_1$ and $s_2$, before and after the kicker.}
 	\label{awa-linac}
@@
 		This is the proposed two beam acceleration section. 
-		Only the kicker in this drawing is installed}
+		Only the kicker in this drawing is installed. 
+	Note $s_3$, the entrance to the fifth quadrupole on the beam line.
+	This is the optimization location.}
 	\label{awa-tba}
@@
 
-The maximum number of individuals per generation was fixed at 80, 
+The maximum number of individuals per generation was fixed at 80. 
+This number was chosen based on the node architecture, and the 
+to prevent a prohibitive computational cost.  
 Each experiment was allowed to run for twenty four hours, with 
@@
 and shortened the simulation time by moving the objectives further 
-upstream to $s_1$ and $s_2$, the locations before and after the kicker.
+upstream to $s_1$ and $s_2$, the locations before and after the kicker, 
+see Fig.~\ref{awa-tba}.
 
@@
 were compared, including number of generations completed in twenty four hours and
-Pareto fronts at $s_1$ and $s_2$.
+Pareto fronts at $s_1$ and $s_2$, see Fig.~\ref{awa-linac}.
 From Table \ref{extable}, we clearly see ex-3 is significantly 
@@
 improved, but from Fig. \ref{expareto}, we can see this is not the case.
-Similar arguments can be made for ex-2, which evaluated about 15 less generations
-with no clear benefit in either Pareto front.
-The Pareto fronts at $s_1$, are nearly identical. We could expect
+Similar arguments can be made for ex-2, which evaluated about 15 less generations.
+The Pareto fronts at $s_2$, are nearly identical. We could expect
 this trend would continue given more time. 
-When looking at the Pareto front at $s_2$, only ex-4 has a slight 
-edge over the others.
+When looking at the Pareto front at $s_1$, only ex-4 has a slightly 
+larger range compared to the others.
 With ex-2 and ex-3 eliminated due to evaluation time, 
-and a slightly better Pareto front at $s_2$ for ex-4, the hyper parameters in ex-4 were chosen as the default values for subsequent runs.
+and a slightly better Pareto front at $s_1$ for ex-4, 
+the hyper parameters in ex-4 were chosen as the default values for subsequent runs.
 
@@
 & \text{rms}_{s}, \quad dE \label{eq:awa:p4} \\
-\text{constraints} \quad & rms_x < 0.1 \, [m] |_{s=s_1}\label{eq:awa:c1}\\
-\quad & rms_y < 0.1 [m] |_{s=s_1}\, \label{eq:awa:c2}\\
-\quad & |rms_y - rms_x | < 0.005 \, [m] |_{s=s_1}\label{eq:awa:c3}\\
-\text{subject to} \quad & q = 40 \left[\text{nC}\right] \label{eq:awa:firstconstr}\\
-\quad & \text{Volt}_{\text{Gun}} = 64\left[\text{MV/m}\right] \label{eq:awa:lastconstr}\\
-\quad & \text{Volt}_{\text{Linac}} = 24 \, \text{or} \, 25\left[\text{MV/m}\right] \\
-\quad & R_x = R_y = 9 \left[\text{mm}\right] \label{eq:awa:firstdvar}\\
+\text{constraints} \quad & rms_x < 0.1 \, (m) |_{s=s_1}\label{eq:awa:c1}\\
+\quad & rms_y < 0.1\, (m) |_{s=s_1}\, \label{eq:awa:c2}\\
+\quad & |rms_y - rms_x | < 0.005 \, (m) |_{s=s_1}\label{eq:awa:c3}\\
+\text{subject to} \quad & q = 40 \, (nC) \label{eq:awa:firstconstr}\\
+\quad & \text{Volt}_{\text{Gun}} = 64 \, \, (\text{MV/m}) \label{eq:awa:lastconstr}\\
+\quad & \text{Volt}_{\text{Linac}} = 24 \, \text{or} \, 25\,\, (\text{MV/m}) \\
+\quad & R_x = R_y = 9 \, (mm) \label{eq:awa:firstdvar}\\
 \quad & \phi_{\text{gun}} =-20^\circ \label{eq:awa:gphidvar}\\

### 2018-09-29 paper/theor-experiment.tex
finishing grammer edits

@@
 minimize the transverse ($rms_{x,y}$) beam size and transverse momentum ($rms_{px,py}$)
-at the location of interest in the beam line ($s_3$).
-%Where $s_3$ is the longitudinal entrance of the fifth quadrupole. 
+at the location of interest in the beam line ($s_3$, see Fig.~\ref{awa-tba}). 
 Minimizing the beam size at this location is essential to 
@@
 This reduces halo by ensuring the beam is not over focused through a hard waist.
-The momentum spread is also critical to preventing large growth during transport in bending elements. 
+The momentum spread is also critical to preventing large growth during transport. 
 All of these factors help with transmission downstream.
@@
 This prevents one dimension from becoming disproportionately large compared to the other.
-At the AWA, there is some room in the beam pipe to allow the y dimension to grow, but round beams 
-are preferred for easier data analysis.
+At the AWA, there is some room in the beam pipe to allow the y dimension to grow, but round beams are preferred.
 
@@
 Design variables include the currents in two gun solenoids (IBF and IM), 
-and four quadrupole strengths (KQ1-KQ2). The objectives include
+and four quadrupole strengths (KQ1-KQ4). The objectives include
 beam size (transverse and longitudinal), transverse momentum, and energy spread as
@@
 cluster provided by the Laboratory Computing Resource Center (LCRC)
-at Argonne National Laboratory (ANL). We used Intel Knights Landing 
+at Argonne National Laboratory (ANL). Intel Knights Landing 
 (KNL) processors at 1.3 GHz with 128 GB of memory 
-and 64 cores per node. There are 352 compute nodes available on 
+and 64 cores per node were used for all runs. 
+There are 352 compute nodes available on 
 Bebop, with a total of 22,528 cores. All jobs were run and compared 
@@
 Since each simulation takes 8 cores, and there are 64 cores per KNL node, 
-we wanted a large population size that would fit evenly on these resources. 
+a large population size that would fit evenly on these resources was chosen. 
 Again, the location of optimization is $s_3=19.4$ [m]. 
@@
 the small beam sizes seen in the y dimension. This suggest suggests objectives in the x 
-dimension will drive design variable choices used in operations. 
+dimension will drive design variable choices used during operations. 
 However, it is still necessary to 
@@
 In the case of bunch length, there are not many options to choose from.
-Ignoring the extreme value on the right, Fig.~\ref{fig:pareto1} shows the 
-range of optimal bunch lengths fall between 1.39 and 1.5 mm.
 
@@
 A select result is shown in Fig.~\ref{fig:stat}.  
-The maximum beam sizes are well below the beam pipe aperture limits as shown in Fig.~\ref{fig:stat} (b).
+The maximum beam sizes are well below the beam pipe aperture limits as shown in Fig.~\ref{fig:stat}.
 The solution is nearly round, which will increase changes of keeping the beam nearly round

### 2018-09-29 paper/prab.tex
starting to edit theor-exp
conclusion edit

@@
 
-We presented a general-purpose framework for solving multi-objective
-  optimization problems.
+A general-purpose framework for solving multi-objective
+  optimization problems was presented.
 Its modular design simplifies the application to simulation-based optimization
@@
 %The number of individuals is the only limiting factor.
-In this paper we applied the framework to a beam dynamics problem at the AWA.
-Optimization of the 3D beam size and energy spread was accomplished.
+The framework was integrated into OPAL, and used 
+to study a beam dynamics problem at the AWA.
 A scan of time step and hyper parameters was done to determine computational settings.
 Then a full scale physics optimization was performed.
-The resulting beam tune can and will be used in future TBA experiments at the AWA.
-This problem also took advantage of the frameworks massively parallel capabilities by
-running on 2624 processes on Bebop at LCRC.
+Optimization of the 3D beam size and energy spread was accomplished.
+The TBA beam line presented is currently being installed at the AWA.
+Once installation is complete, 
+the results shown here will guide future experiments at the AWA.
+%This problem also took advantage of the frameworks massively parallel capabilities by
+%running on 2624 processes on Bebop at LCRC.
 
@@
   design and operation of particle accelerators.
-
-Outlook, ....
 

### 2018-09-29 paper/prab.tex
remove cite
add linenumbers
taking out we's

@@
   algorithms which also facilitate a parallel deployment.
-In order to compute solutions in a meaningful time frame we require a fast
-  and scalable software framework.
+In order to compute solutions in a meaningful time frame a fast 
+  and scalable software framework is required.
 In this paper, we present the implementation of such a general-purpose
@@
 Using evolutionary algorithms and \textsc{OPAL}~simulations as optimizer and
-  forward solver in our framework, we present validation experiments and first
+  forward solver in our framework, validation experiments and first
   results of multi-objective optimization problems in the domain of beam
-  dynamics.
+  dynamics is presented.
 
@@
 A ``pilot'' coordinates all efforts between the optimization algorithm and the
-  beam dynamics task. In the sequel we will also use the notion of ``forward solver'' to indicate 
-  the beam dynamics task.
+  beam dynamics task. In the sequel we will also use the notion of ``forward solver'' to indicate the beam dynamics task.
 This forms a robust and general framework for massively parallel
@@
   level of detail and time to solution.
-We address this problem later in Section~(\ref{awa:subsection:test}) by using forward solvers with different time and
+This problem is addressed later in Section~(\ref{awa:subsection:test}) by using forward solvers with different time and
   resolution complexity.
@@
   effect on the optimality criteria, converging to the preferred solution.
-This is called \textit{a posteriori} preference specification since we select
-  a solution after all possible trade-offs have been presented to us.
+This is called \textit{a posteriori} preference specification since 
+  a solution is selected after all possible trade-offs have been presented to us.
 An alternative is to specify preference \textit{a priori}, e.g. by
@@
   and many more~\cite{domc:96,cati:02,kara:05,hoss:09}.
-In the next section we briefly introduce the theory of evolutionary algorithms
+In the next section, we briefly introduce the theory of evolutionary algorithms
   used in the present work.
@@
 Since there already exist plenty of implementations of evolutionary algorithms,
-  we decided to incorporate the PISA library \cite{pisa} into our
+  it was decided to incorporate the PISA library \cite{pisa} into our
   framework.
@@
   this one individual in order to continue to generate and evaluate offspring.
-To counteract this effect we call the selector already when two individuals
+To counteract this effect, the selector is already called when two individuals
   have finished evaluating their fitness, lifting the boundaries between
@@
   optimization problems that should be handled by such a general framework.
-As an example, we show how \textsc{Pisa} \cite{pisa}, an existing evolutionary
+As an example, it is shown how \textsc{Pisa} \cite{pisa}, an existing evolutionary
   algorithm library, was integrated with ease.
@@
 
-The basic assumption in simulation-based optimization is that we need to
-  call an expensive simulation software component present in the
-  constraints or objectives.
-We divide the framework in three exchangeable components, as shown in
+The basic assumption in simulation-based optimization is that a
+  call to an expensive simulation software component present in the
+  constraints or objectives is needed.
+The framework is divided in three exchangeable components, as shown in
   Fig.~\ref{fig:opt-framework-layout}, to encapsulate the major behavioral
@@
   playing the role of the ``forward solver''. Underlying the general nature of our approach, 
-  in a similar project, we use the described methods for cavity shape optimisation based on \cite{ARBENZ2008381}. 
+  in a similar project, the described methods are used for cavity shape optimisation based on \cite{ARBENZ2008381}. 
 As for the \textsc{Optimizer} component there exists a base class, labeled
@@
 \noindent
-  we implemented an expression parser using Boost Spirit~\cite{boost}.
+  An expression parser using Boost Spirit~\cite{boost} was implemented.
 In addition to the parser, we need an evaluator able to evaluate an expression,
@@
 
-To improve the expressive power of objectives and constraints we introduced a
-  simple mechanism to define and call custom functions in expressions.
+To improve the expressive power of objectives and constraints, a
+  simple mechanism to define and call custom functions in expressions was introduced.
 Using simple functors, e.g. as the one shown in Listing 4 to compute an
@@
   optimization algorithm.
-In a recent work, we successfully implemented and integrated another
-  optimization algorithm, originally presented in~\cite{pesc:11}, into our
-  framework.
+%In a recent work, we successfully implemented and integrated another
+  %optimization algorithm, originally presented in~\cite{pesc:11}, into our
+ % framework.
 The flexibility of being able to adapt both ends of the optimization

### 2018-09-29 paper/submission/theor-experiment.tex
for Physrev AB and arxiv

--- 2018-09-29 paper/theor-experiment.tex
@@
 
-To ensure that the optimizer works correctly we solved the benchmark
-  problem (\ref{eqn:bench}).
+To ensure that the optimizer works correctly the benchmark
+  problem (\ref{eqn:bench}) was solved.
 To that end, we use a metric for comparing the quality of a Pareto
@@
   $m$ objectives) of the dominated space, relative to a chosen origin.
-We visualize this for $2$ objectives in Fig.~\ref{fig:hypervolume}.
+This is visualized for $2$ objectives in Fig.~\ref{fig:hypervolume}.
 For further information and details of the implementation see~\cite{whbb:12}.
@@
 For all models, the longitudinal parameters (rms$_s$ and energy) 
-are calculated correctly, but we see discrepancies in the transverse 
+are calculated correctly, but discrepancies are seen in the transverse 
 (rms$_x$ and $\epsilon_x$) for low fidelity results. This discrepancy is 
@@
 Perhaps this trade off would be acceptable if the Pareto front was significantly 
-improved, but from Fig. \ref{expareto}, we can see this is not the case.
+improved, but from Fig. \ref{expareto}, but this is not the case.
 Similar arguments can be made for ex-2, which evaluated about 15 less generations.
-The Pareto fronts at $s_2$, are nearly identical. We could expect
+The Pareto fronts at $s_2$, are nearly identical. It is expected
 this trend would continue given more time. 

### 2018-09-29 paper/submission/figures/ga_explained_big.tex
adding figures to submission folder

\path (0.0, 4.0) node (population) [draw, text centered,
    text width=19.5em, fill=red, fill opacity=0.1, minimum height=6em,
    rounded corners, very thick, draw=red, text opacity=1.0]
    {};
\path (0.0, 4.8) node {\textsc{Population}};

\draw [dashed, very thick, draw=gray!90!white]
  (-0.2,3.6) circle (14pt)
  node {$\mathcal{I}_1$};
\draw [dashed, very thick, draw=gray!90!white]
  (1.2,3.9) circle (14pt)
  node {$\mathcal{I}_k$};
\draw [dashed, very thick, draw=gray!90!white]
  (2.4,4.2) circle (14pt)
  node {$\mathcal{I}_2$};
\draw [dashed, very thick, draw=gray!90!white]
  (-1.4,4.3) circle (14pt)
  node {$\mathcal{I}_3$};
\draw [dashed, very thick, draw=gray!90!white]
  (-2.7,3.8) circle (14pt)
  node {$\mathcal{I}_4$};

\path (population.south)+(-2.0, -3.0) node (selector) [draw, text centered,
    text width=10.5em, fill=orange, fill opacity=0.1, minimum height=15em,
    rounded corners, very thick, draw=orange, text opacity=1.0]
    {};
\path (-2.0, 1.7) node {\textsc{Selector}};
\path (-2.0, 1.0) node
  {1. $\mathcal{I}_4$};
\path (-2.0, 0.5) node
  {2. $\mathcal{I}_k$};
\path (-2.0, 0.0) node
  {3. $\mathcal{I}_2$};
\path (-2.0, -0.5) node
  {4. $\mathcal{I}_3$};
\draw [thick,brown!90!white]
  (-3.4,-0.74) rectangle (-0.6,-0.76);
\path (-2.0, -1.0) node
  {5. $\mathcal{I}_1$};
\path (-2.0, -1.5) node
  {$\ldots$};
\path (-2.0, -2.0) node
  {$n$. $\mathcal{I}_n$};

\draw [very thick,gray,decorate,decoration={brace,amplitude=3pt},
       xshift=-0pt,yshift=-0pt]
      (-1.5, 1.1)  -- (-1.5, 0.4)
      node {};
\path[->, very thick] (-1.3,0.75) edge (1.1, 1.1);

\draw [very thick,gray,decorate,decoration={brace,amplitude=3pt},
       xshift=-0pt,yshift=-0pt]
      (-1.5, 0.1)  -- (-1.5, -0.6)
      node {};
\path[->, very thick] (-1.3,-0.25) edge (1.1, -0.25);

\draw [very thick,gray,decorate,decoration={brace,amplitude=3pt},
       xshift=-0pt,yshift=-0pt]
      (-1.5, -0.9)  -- (-1.5, -2.1)
      node[right, xshift=0pt, yshift=10pt] {removed};

\path (selector.east)+(3.0, 0.0) node (variator) [draw, text centered,
    text width=11.5em, fill=brown, fill opacity=0.1, minimum height=12em,
    rounded corners, very thick, draw=brown, text opacity=1.0]
    {};
\path (3.0, 1.7) node {\textsc{Variator}};
\path (1.1, 1.1) node[right]
  {$\mathcal{I}_4 \cdot \mathcal{I}_k = \mathcal{I}_{n+1}$: };

\draw [thick, brown!90!white, fill=green, opacity=0.4]
  (1.8,0.4) rectangle (2.0,0.8);
\draw [thick, brown!90!white, fill=green, opacity=0.4] (1.8,0.4)
  rectangle (1.6,0.8);
\draw [thick, brown!90!white, fill=green, opacity=0.4] (1.6,0.4)
  rectangle (1.4,0.8);
\draw [thick, brown!90!white, fill=green, opacity=0.4] (1.4,0.4)
  rectangle (1.2,0.8);
\draw [very thick] (2.2,0.6) circle (2pt);

\draw [thick, brown!90!white, fill=cyan, opacity=0.4]
  (3.0,0.4) rectangle (3.2,0.8);
\draw [thick, brown!90!white, fill=cyan, opacity=0.4]
  (2.8,0.4) rectangle (3.0,0.8);
\draw [thick, brown!90!white, fill=cyan, opacity=0.4]
  (2.6,0.4) rectangle (2.8,0.8);
\draw [thick, brown!90!white, fill=cyan, opacity=0.4]
  (2.4,0.4) rectangle (2.6,0.8);
\draw (3.4,0.55) node {$=$};

\draw [thick, brown!90!white, fill=yellow, opacity=0.4]
  (4.2,0.4) rectangle (4.4,0.8);
\draw [thick, brown!90!white, fill=cyan, opacity=0.4]
  (4.0,0.4) rectangle (4.2,0.8);
\draw [thick, brown!90!white, fill=green, opacity=0.4]
  (3.8,0.4) rectangle (4.0,0.8);
\draw [thick, brown!90!white, fill=green, opacity=0.4]
  (3.6,0.4) rectangle (3.8,0.8);

\path (1.1, -0.25) node[right]
  {$\mathcal{I}_2 \cdot \mathcal{I}_3 = \mathcal{I}_{n+2}$: };

\begin{scope}[
     yshift=-38]
\draw [thick, brown!90!white, fill=orange, opacity=0.4]
  (1.8,0.4) rectangle (2.0,0.8);
\draw [thick, brown!90!white, fill=orange, opacity=0.4] (1.8,0.4)
  rectangle (1.6,0.8);
\draw [thick, brown!90!white, fill=orange, opacity=0.4] (1.6,0.4)
  rectangle (1.4,0.8);
\draw [thick, brown!90!white, fill=orange, opacity=0.4] (1.4,0.4)
  rectangle (1.2,0.8);
\draw [very thick] (2.2,0.6) circle (2pt);

\draw [thick, brown!90!white, fill=magenta, opacity=0.4]
  (3.0,0.4) rectangle (3.2,0.8);
\draw [thick, brown!90!white, fill=magenta, opacity=0.4]
  (2.8,0.4) rectangle (3.0,0.8);
\draw [thick, brown!90!white, fill=magenta, opacity=0.4]
  (2.6,0.4) rectangle (2.8,0.8);
\draw [thick, brown!90!white, fill=magenta, opacity=0.4]
  (2.4,0.4) rectangle (2.6,0.8);
\draw (3.4,0.55) node {$=$};

\draw [thick, brown!90!white, fill=magenta, opacity=0.4]
  (4.2,0.4) rectangle (4.4,0.8);
\draw [thick, brown!90!white, fill=magenta, opacity=0.4]
  (4.0,0.4) rectangle (4.2,0.8);
\draw [thick, brown!90!white, fill=yellow, opacity=0.4]
  (3.8,0.4) rectangle (4.0,0.8);
\draw [thick, brown!90!white, fill=orange, opacity=0.4]
  (3.6,0.4) rectangle (3.8,0.8);
\end{scope}

% individuals to selector
\path[->, very thick]
  (-0.4, 3.3) edge [bend left, out=0, in=-130] (selector.north);
\path[very thick] (-1.4, 4.0) edge [bend left, out=0, in=-130] (-1.4, 2.75);
\path[very thick] (-2.5, 3.5) edge [bend left, out=0, in=-190] (-1.4, 2.75);
\path[very thick] (1.0, 3.6) edge [bend left, out=30, in=130] (-1.4, 2.75);
\path[very thick] (2.2, 3.9) edge [bend left, out=20, in=130] (-1.4, 2.75);

\path[->, very thick, dashed]
  (4.4, 0.85) edge [bend right] (3.65, 3.5);
\draw [dashed, very thick, draw=gray!90!white]
  (3.95,2.5) circle (14pt)
  node {$\mathcal{I}_{n+1}$};

\path[->, very thick, dashed]
  (4.4, -0.45) edge [bend right] (3.65, 4.5);
\draw [dashed, very thick, draw=gray!90!white]
  (4.4,4.15) circle (14pt)
  node {$\mathcal{I}_{n+2}$};

### 2018-09-29 paper/submission/figures/opt-framework_code.tex
adding figures to submission folder

--- 2018-09-16 paper/figures/opt-framework_code.tex
@@
 	\path (pilot.north)+(0.7,1.5) node (opal) [draw, text centered,
-	text width=6em, fill=orange, fill opacity=0.1, minimum height=2em,
+	text width=8em, fill=orange, fill opacity=0.1, minimum height=2em,
 	rounded corners, very thick, draw=orange, text opacity=1.0]
-	{\textsc{Simulation}};
+	{\textsc{Beam Dynamics}};
 

### 2018-09-29 paper/submission/prab.tex
adding figures to submission folder

--- 2018-09-29 paper/prab.tex
@@
 \documentclass[%
-reprint,
+preprint,
 %superscriptaddress,
@@
 %frontmatterverbose, 
-%preprint,
+preprint,
+linenumbers,
 %showpacs,preprintnumbers,
@@
 Today, tuning machine parameters, e.g. bunch charge, emission time and
-  various parameters of beamline elements, is most commonly done manually by
+  various parameters of beam line elements, is most commonly done manually by
   running simulation codes to scan the parameter space.

### 2018-09-29 paper/submission/theor-experiment.tex
adding figures to submission folder

@@
 	\node (fig1) at (0,0)
-	{\includegraphics[width=\textwidth]{Report/awa-drawing}};
+	{\includegraphics[width=\textwidth]{figures/awa-drawing}};
 	\node[fill=white, inner sep=2pt] (txt2) at (0,\gunheight) {\large Gun};
@@
 	\node (fig2) at (0,0)
-	{\includegraphics[width=\textwidth]{Report/tba_dogleg}};
+	{\includegraphics[width=\textwidth]{figures/tba_dogleg}};
 	\node[fill=white, inner sep=2pt] (txt2) at (3,\sheight) {\large $s_1$};
@@
 	\centering
-	\includegraphics[width=\linewidth]{Report/timestep_comparison_paper}
+	\includegraphics[width=\linewidth]{figures/timestep_comparison_paper}
 	\caption{Comparison of different fidelity models (dT stands for time step).}
@@
 \end{figure}
-
-\iffalse
-\begin{table}%[h!]
-	\begin{center}
-		\caption{Low and mid fidelity simulation parameters.}
-		\label{fidelity}
-		\begin{tabular*}{0.48\textwidth}{l @{\extracolsep{\fill}} C c D }
-			\hline\noalign{\smallskip}
-			& Number of particles & dT (seconds) & Time to simulation (minutes)\\
-			\noalign{\smallskip}\hline\noalign{\smallskip}
-			low fidelity  			&  10,000   & $5 \times10^{-11}$  &  2.6 \\
-			adjusted low fidelity  	&  10,000   & $2 \times 10^{-12}$, $1 \times 10^{-11}$ & 1.6 \\
-			mid fidelity 			&  100,000  & $1 \times 10^{-12}$ &  18\\
-			\noalign{\smallskip}\hline
-		\end{tabular*}
-	\end{center}
-\end{table}
-\fi
 
@@
 		\centering
-		\includegraphics[width=\textwidth]{Report/ex-pareto1}
+		\includegraphics[width=\textwidth]{figures/ex-pareto1}
 		(a) Pareto fronts for ex-1 through ex-4 at $s_1$.
@@
 		\centering
-		\includegraphics[width=\textwidth]{Report/ex-pareto2}
+		\includegraphics[width=\textwidth]{figures/ex-pareto2}
 		(b) Pareto fronts for ex-1 through ex-4 at $s_2$.
@@
 		\node (fig1) at (0,0)
-		{\includegraphics[width=0.5\textwidth]{../pareto_stat_plots/xy_vs_pxy_pareto_front_quads_before_Q5}};
+		{\includegraphics[width=0.5\textwidth]{figures/xy_vs_pxy_pareto_front_quads_before_Q5}};
 		\node[star, star points=5, star point ratio=0.5, fill=yellow, draw](key) at (3.35,-1.7) {};
@@
 \end{figure}
-
-\iffalse
-\begin{figure}
-	\centering
-	\includegraphics[width=0.48\textwidth]{../pareto_stat_plots/dE_vs_zrms_pareto_front_quads_before_Q5_zoomout}%
-	\llap{\raisebox{1.9cm}{%  move next graphics to top right corner
-			\includegraphics[height=4.5cm]{../pareto_stat_plots/dE_vs_zrms_pareto_front_quads_before_Q5}%
-	}}
-	\caption{Pareto front comparing energy spread (dE) and bunch length ($\sigma_z$). \nrnote{add tikz arrows to point to left side of curve?}}
-	\label{fig:pareto2}
-\end{figure}  
-\fi
 
@@
 \begin{figure}
-	\includegraphics[width=0.48\textwidth]{../pareto_stat_plots/xy-max-min-sigma-paper}
+	\includegraphics[width=0.48\textwidth]{figures/xy-max-min-sigma-paper}
 	\caption{Optimized beam sizes along high charge beam line. The gun is located at $s=0$, 

### 2018-09-29 paper/prab.tex
adding to abstract
fix abstarct

@@
   optimization tasks.
-Using evolutionary algorithms and \textsc{OPAL}~simulations as optimizer and
-  forward solver in our framework, validation experiments and first
+Using evolutionary algorithms as the optimizer and \textsc{OPAL} as the 
+  forward solver, validation experiments and 
  results of multi-objective optimization problems in the domain of beam
-  dynamics is presented.
+  dynamics are presented. The high charge beam line at the Argonne Wakefield 
+  Accelerator Facility was used as the beam dynamics model. The 3D beam size, 
+  transverse momentum, and energy spread were optimized.
 

### 2018-09-29 paper/theor-experiment.tex
fixing spacing for one sided doc

@@
 
-\def \gunheight {25}
+\def \gunheight {25}  %25} %double sided number
 \def \quadheight {35}
-\def \quadleft {127}
-\def \kickerleft {160}
+\def \quadleft {115}  %127} %double sided number
+\def \kickerleft {145}  %160} % two sided number
 \def \leftarrow{10}
@@
 	\node (fig1) at (0,0)
-	{\includegraphics[width=\textwidth]{Report/awa-drawing}};
+	{\includegraphics[width=\textwidth]{figures/awa-drawing}};
 	\node[fill=white, inner sep=2pt] (txt2) at (0,\gunheight) {\large Gun};
 	\node[fill=white, inner sep=2pt] (txt2) at (20,\gunheight) {\large Accelerating Cavities};
-	\node[fill=white, inner sep=2pt] (txt2) at (\quadleft,\quadheight) {\large Quadrupoles};
+	\node[fill=white, inner sep=2pt] (txt2) at (\quadleft-5,\quadheight) {\large Quadrupoles};
 	\draw [blue, ->, line width=1] (\quadleft+\leftarrow,\topofarrows) -- (\quadleft+\leftarrow, \bottomofarrows);
@@
 	\label{awa-linac}
-	\vspace{-7em}
+	%\vspace{-7em}
 \end{figure*}
@@
 \def \septheight {65}
-\def \bottomarrow {57}
+\def \bottomarrow {55} %57}
 \def \kleft {13}
-\def \sleft {41.5}
-\def \sheight {47}
+\def \sleft {38}%41.5}
+\def \sheight {45}%47}
 \def \beam {35}
@@
 	\node (fig2) at (0,0)
-	{\includegraphics[width=\textwidth]{Report/tba_dogleg}};
+	{\includegraphics[width=\textwidth]{figures/tba_dogleg}};
 	\node[fill=white, inner sep=2pt] (txt2) at (3,\sheight) {\large $s_1$};
 	\node[fill=white, inner sep=2pt] (txt2) at (20,\sheight) {\large $s_2$};
-	\node[fill=white, inner sep=2pt] (txt2) at (46,45) {\large $s_3$};
+	\node[fill=white, inner sep=2pt] (txt2) at (41,40) {\large $s_3$}; %(46,45)
 	\node[fill=white, inner sep=2pt] (txt2) at (33,\septheight) {\large Septum};

### 2018-10-03 paper/submission/prab.tex
adding Christof's changes to prab paper

--- 2018-09-29 paper/prab.tex
@@
 \documentclass[%
-reprint,
 %superscriptaddress,
@@
 %frontmatterverbose, 
-%preprint,
+preprint,
+linenumbers,
+%twocolumn,
 %showpacs,preprintnumbers,
@@
 We introduce the employed forward-solver in Section~\ref{sec:forward-solver}.
-A validation and a proof of concept application in the two beam dynamics problems 
+A validation and a proof of concept application in the beam dynamics problems 
 mentioned above is discussed in Section~\ref{sec:experiments}.
@@
   input. In case of the OPAL integration, basically the \texttt{main} function is
-  playing the role of the ``forward solver''. Underlying the general nature of our approach, 
+  playing the role of the ``forward solver''. To underline the general nature of our approach, 
   in a similar project, the described methods are used for cavity shape optimisation based on \cite{ARBENZ2008381}. 
@@
 
+\begin{samepage}
 	\begin{flushleft}
@@
 	\end{flushleft}
-%\vspace{0.2cm}
+\end{samepage}
 
@@
   process, the forward solver and the optimization algorithm simultaneously
-  not only leads to broad applicability but it facilitates the ability to
-  tailor the optimization strategy to the optimization problem as well.
+  not only leads to broad applicability but it facilitates
+  tailoring the optimization strategy to the optimization problem as well.
 

### 2018-10-03 paper/submission/theor-experiment.tex
adding Christof's changes to prab paper

@@
 	\node[fill=white, inner sep=2pt] (txt2) at (20,\gunheight) {\large Accelerating Cavities};
-	\node[fill=white, inner sep=2pt] (txt2) at (\quadleft,\quadheight) {\large Quadrupoles};
+	\node[fill=white, inner sep=2pt] (txt2) at (\quadleft-5,\quadheight) {\large Quadrupoles};
 	\draw [blue, ->, line width=1] (\quadleft+\leftarrow,\topofarrows) -- (\quadleft+\leftarrow, \bottomofarrows);
@@
 	\node[fill=white, inner sep=2pt] (txt2) at (20,\sheight) {\large $s_2$};
-	\node[fill=white, inner sep=2pt] (txt2) at (46,45) {\large $s_3$};
+	\node[fill=white, inner sep=2pt] (txt2) at (41,40) {\large $s_3$}; %(46,45)
 	\node[fill=white, inner sep=2pt] (txt2) at (33,\septheight) {\large Septum};
@@
 The OPAL input file for ex-3 is given as an example to show how optimization and design variables are defined:
-%
 
 %\vspace{0.2cm}
+\begin{samepage}
 	\begin{Verbatim}[fontsize=\scriptsize]
@@
 	\end{Verbatim}
+\end{samepage}
+
 %\vspace{0.2cm}
@@
 %\vspace{0.2cm}
+\begin{samepage}
 	\begin{Verbatim}[fontsize=\scriptsize]
@@
 
-//Kicker apeture
+	//Constraints
 	c1: CONSTRAINT, EXPR="fabs(statVariableAt('rms_x',16.5))<0.1";
@@
 	\end{Verbatim}
-\vspace{0.2cm}
+\end{samepage}
 
@@
 As expected, the x dimension is impacted by the bending elements, and unable to reach 
-the small beam sizes seen in the y dimension. This suggest suggests objectives in the x 
+the small beam sizes seen in the y dimension. This suggest objectives in the x 
 dimension will drive design variable choices used during operations. 

### 2018-12-13 paper/submission/ZW10157-response-1.tex
response to editors

\documentclass{article}
\usepackage{latexsym}
\usepackage{color}
\setlength{\parskip}{3mm}
\setlength{\parindent}{0pt}

\newcommand{\TODO}[1]{\color{green}\noindent[{\bf TODO: #1}]\color{black}}
\newcommand{\atline}[1]{\color{red} Lines: #1\color{blue}}
\begin{document}
\title {Paper  \#ZW10157}
\author {N. Neveu, et. al}

\maketitle
Dear reviewers and editors,

Thank you for considering the manuscript.
We appreciate the constructive criticism. It helped improve the quality of this manuscript.

We have carefully answered all your questions and implemented your suggestions to the best of our knowledge.\ The details can be found in the following pages.

With the best regards  \\[3mm]

Nicole Neveu, et. al

\pagebreak

{\bf Problems with the manuscript:}

Figure(s) [10,11]
Please remove background grid and/or shading from your figures.

* Please provide a figure file (.ps, .eps, .pdf, .jpg, or .png format)
that does not require tikz commands in the text source file to
display properly. Figure files should be self-contained and we do
not support the tikz format in the production process. We will also
need a revised text source file.

{\bf My response:} {\color{blue} The grid has been removed from Figures 10 and 11.
PDF versions of the tikz pictures have been made. All updated figures are provided 
along with an updated source file.}

{\bf Referee A (Remarks to Author)}

1) Remove the sections of code from the text. This adds no value to
the paper and should be left for a User’s Manual.

{\bf My response:} {\color{blue} The code sections are now removed.}

2) Provide a stronger physics basis for the AWA optimization. Why is
this problem of beam squeeze challenging enough to warrant solution
with such a massively capable solver? Could the same solution have
been arrived at with something simpler? Describe the important
component of physics that come into play in the beam squeeze, whatever
they are – space charge, etc. After all, this is primarily a physics
journal so the physics context for the application needs to be clear.

{\bf My response:} {\color{blue} XXXXX.}

REFEREE B - ZW10157

First, optimization systems based on PISA have been in use in
accelerator design since 2005, and NSGA-II’s use dates from that time
too. References to early PISA-based systems and NSGAII applications
are missing from the authors’ reference list, and the authors must
correct this. Three groups of references are provided to assist in
addressing these omissions: 1) early PISAbased systems; 2) a small
sample of NSGA-II applications and implementations (there are MANY
more as the NSGA-II algorithm is easy to understand and fairly
straight forward to implement); and 3) a survey of accelerator physics
and genetic and evolutionary application usage as of 2013.

1) References for 4 PISA-based optimization systems:

I.V. Bazarov and C.K. Sinclair. "Multivariate optimization of a high
brightness dc gun photoinjector," Phys. Rev. ST Accel. Beams 8,
034202, 2005

Y.C. Chao et al. "TRIUMF-VECC Electron Linac Beam Dynamics
Optimization," ICAP09, San Francisco, 2009, THPSC012

A. Hofler et al. "Optimizing SRF Gun Cavity Profiles in a Genetic
Algorithm Framework," ICAP09, San Francisco, 2009, THPSC020

M. Marchetto et al. "Beam Dynamics Optimization of the TRIUMF ELINAC
Injector," PAC09, Vancouver, BC, Canada, 2009, TH6PFP097

A. Hofler and P. Evtushenko. “Optimizing RF Gun Cavity Geometry within
an Automated Injector Design System,” NAPAC11, New York, 2011, TUODS6

I.V. Bazarov et al., "Comparison of dc and superconducting rf
photoemission guns for high brightness high average current beam
production", Phys. Rev. ST Accel. Beams 14, 072001, 2011

A. Hofler, “Optimization Framework for a Radio Frequency Gun Based
Injector,” Ph.D. thesis, Old Dominion University, Norfolk, Virginia,
USA, 2012

C. Gong and Y.C. Chao, "The TRIUMF Optimization Platform and
Application to the E-LINAC Injector", ICAP2012, Rostock-Warnemunde,
Germany, 2012, TUABI1

A. Hofler et al., "Innovative applications of genetic algorithms to
problems in accelerator physics", Phys. Rev. ST Accel. Beams 16,
010101, 2013

B. Terzic et al., "Simultaneous optimization of the cavity heat load
and trip rates in linacs using a genetic algorithm", Phys. Rev. ST
Accel. Beams 17, 101003, 2014

C. Gong, A Novel Optimization Platform and Its Applications to the
TRIUMF Energy Recovery Linac, Ph.D. thesis, The University of
Columbia, October 2015

C. Gong and Y.C. Chao, "The TRIUMF Optimization Platform and
Application to the E-LINAC Injector", ICAP2015, Shanghai, China, 2015,
THCWC4

C. Gulliford et al., "Multiobjective optimizations of a novel
cryocooled dc gun based ultrafast electron diffraction beam line",
Phys. Rev. Accel. Beams 19, 093402, 2016

C. Gulliford et al., "Multiobjective optimization design of an rf gun
based electron diffraction beam line", Phys. Rev. Accel. Beams 20,
033401, 2017

2) Optimization systems using NSGA-II (a few example references):

L. Emery. PAC 2005, Knoxville, TN, USA, May 2005, RPPP047

M. Borland et al. PAC 2009, Vancouver, BC, Canada, May 2009, TH6PFP062

Pulsar Physics. General Particle Tracer, http://www.pulsar.nl/gpt

3) Survey with various references showing GA/EA usage in Accelerator
Physics: A. Hofler. “Genetic Algorithms and Their Applications in
Accelerator Physics,” NAPAC2013, Pasadena, CA, USA, 2013, THTB1

{\bf My response:} {\color{blue} XXXXX.}

Second, due to the thoroughness and success of Bazarov and Sinclair’s
optimization (PRSTAB 2005 provided above), genetic and evolutionary
algorithm-based optimizations are standard practice in accelerator
design, and researchers are now looking at ways to use machine
learning and AI techniques in accelerator design and optimization.
Manual parameter scans, as mentioned in Section I lines 17-19, are
useful, but they are by no means the sole optimization technique in
use today. The statement made in lines 17-19 was true prior to 2005
but not now. The authors should consider providing a different and
more compelling motivator to encourage users to consider the system
they have developed.

{\bf My response:} {\color{blue} XXXXX.}

Third, several of the features of this system are available is
existing systems but are not acknowledged:

- parallel/distributed computation: the survey article mentioned above
provides references to several examples

- Section II lines 115-125 blurring generations: APISA and General
Particle Tracer’s optimization system start evaluating the next
generation before all individuals in the present generation complete,
too.

- Section III subsection D lines 229-231 Geometry optimization. With
PISA-based systems, Bazarov and Hofler have done this (see PISA-based
reference list). Others have performed geometry optimization with
different GA/EA based systems (again the survey reference mentions
several.)

{\bf My response:} {\color{blue} XXXXX.}

That said, a general-purpose optimization system is a useful addition
to the design tools for accelerators. The way to entice prospective
users through PRAB is to introduce the system with a very brief
general overview and then focus on the results obtained using the
system. The detailed discussion of the design and implementation with
code snippets should be provided as Supplemental Material. PRAB is not
a computer journal. Salient implementation or design points if
necessary can be summarized in short Appendices; the main discussion
of the paper should be the optimization results not the details of the
implementation and design. For example, in the main text, it is
reasonable to say that the optimization system provides a flexible and
extensible meta-language for setting up optimization problems (covered
in detail in Section III subsection E) and then direct the reader to
an Appendix or the Supplemental Material for the details provided in
Section III subsection E. Bear in mind, though, that several of the
PISA-based systems mentioned above, also, provide expression
capabilities and should be referenced. The one presented here is more
flexible and has the advantage of being easily extended. Both are
distinguishing features. The authors need to emphasize what
differentiates their system from 13+ years of development in the area
of GA/EA-based optimization in accelerator design and then demonstrate
that the results produced are exemplary or could not have been
produced otherwise. Or they should focus on how their system advances
the application of the target AWA machine (the Gulliford references
use this approach).

Following are comments/suggestions/questions organized by paper
section.

Abstract:

In this paper, we present the implementation of such a general-purpose
framework for simulation-based multi-objective optimization methods
that allows the automatic investigation of optimal sets of machine
parameters. The implementation is based on a master/slave paradigm,
employing several masters that govern a set of slaves executing
simulations and performing optimization tasks. -> In this paper, we
present a general-purpose framework for simulation-based
multi-objective optimization methods that allows the automatic
investigation of optimal sets of machine parameters.

The high charge beam line at the Argonne Wakefield Accelerator
Facility was used as the beam dynamics model. The 3D beam size,
transverse momentum, and energy spread were optimized. Please state
the significance of the optimization. Is the solution found better
than the original design? Then provide a comparison with the baseline
solution as Bazarov and Sinclair did in their 2005 paper. Is it the
first such solution for the AWA? Then make that clear. Has this
solution been used in the machine? Then provide a comparison between
prediction and operational experience.

Section I

line 35: trade of -> trade off

{\bf My response:} {\color{blue} This typo is corrected in the updated manuscript.}

Section II

lines 53-74. The car example is from Deb’s book but not cited. This
example can probably be removed as EA/GA methodology is established
practice now.

Section III

subsection A

Needs to be updated to reflect developments in accelerator physics.

subsections B-F

Replace with a brief overview and put the details in Supplemental
Material

Section VI

Code and input file details should be in Supplemental Material

Section V

subsection B

Code and input file details should be in Supplemental Material

subsubsection 3

line 427 to to -> to

{\bf My response:} {\color{blue} This typo is corrected in the updated manuscript.}

subsubsection 4

FIGS. 11/12 The discussed case in FIG. 12 is not on either front in
FIG. 11. Explain why a nonfront solution is used otherwise the
optimization exercise is moot.

TABLE IV is provided and not discussed. Are these the settings for the
solution in FIG. 12? The table’s title is confusing. If the table
contents are input parameters for an optimization, shouldn’t they have
ranges of values? If the values are a selected solution, shouldn’t the
title state that directly?

{\it Your manuscript, "On Uncertainty Quantification in Particle Accelerator Modelling," has completed this round of review. The AE and first two reviewers are positive about the main concept of the article - UQ for charged particle accelerators - but have issues with the paper. The manuscript is a narrow in its focus on UQ and the tie to particle accelerator applications is difficult to follow.

The AE's suggestion to better motivate the use UQ methods is a good one. I like the suggestion of the AE and reviewer 2 to focus on a particular application of using a charged particle accelerator, describing the details so that a general audience can understand, and clearly motivating the need for UQ. This will give you the opportunity to show how UQ makes the science better. If the application is very compelling, there is not a need to be using novel UQ methodology. In this case, it's the application that is novel. A genuine example/application, involving real data, would help help make the case for the need for UQ in this area. }

{\bf My response: }{\color{blue} In the revised version I added a contribution to an ongoing design effort (DAE$\delta$ALUS/IsoDAR) where UQ was used. For this the new section 5 is introduced and the section 4 is renamed to {\em APPLICATION OF THE UQ FRAMEWORK to a MODEL PROBLEM}. I also elaborate more in detail why the 
particular selection of a Cyclotron, is a very general example of a particle accelerator (\atline{281-299}), that justifies the general title and, hopefully refute the claim, that the paper has a  narrow scope.}

{\bf Associate Editor (Remarks to the Author): }

{\it The authors appear to have the goal of providing a broad paper illustrating issues pertaining to uncertainty quantification to the community of scientists modeling particle accelerators. This is a laudatory and timely goal.
Unfortunately, by trying to achieve this breadth, the authors provided a discussion of surrogate models and sensitivity analysis that is fairly standard in the UQ community without adequately demonstrating its novelty for particle accelerator modeling or more general applications. The first and second reviewers both note that the necessity for computing a PCE surrogate, which can be used for subsequent sensitivity analysis, needs to be better motivated for this application. Moreover, statements that the framework provides a template for other computationally intensive applications need to be mollified or better motivated. Both reviewers also note that the discussion regarding extrapolation needs to be better motivated.}

{\bf My response: }{\color{blue}  In section 3 (\atline{281-299}), I added a  discussion of the general Hamiltonian that is the base of the selected Cyclotron as an example.\ This will better motivate the choice of the example.}

{\it The second reviewer discusses two possible directions in which a revision might be considered. The first would be to more adequately introduce UQ to the community of particle accelerator models. The second would be to focus the scope while addressing the concerns raised by all three reviewers. The latter is closer to the present scope of the paper. }

{\bf My response: }{\color{blue} I modify the paper according the second direction}

{\it If the authors choose to revise the paper by providing a more focused case study, I would encourage them to devote more details illustrating the techniques for a specific application where they can more completely relate the mathematics and statistics to relevant physics. }

{\bf My response:} {\color{blue}I indeed add a more focused case study in section 5.}

{\bf Referee \#1 (Remarks to the Author): }

{\it The work presented in the manuscript lacks a development or findings that have impact on either theory of UQ and its application. Discussion of the UQ approach and associated methods is not new, and numerical results presented are of demonstration value and well expected. The technical content boils down to construction of PC-based surrogate models. In demonstrating the surrogate construction approach, it is important to establish a range of applicability (e.g., depending on physics model properties/ nonlinearity, dependency of parameters).

The "claim to present a problem that can be recognised as a template for many high intensity modelling attempts, and beyond" is poorly substantiated. The demonstration is performed for a fairly limited case, with three uncertain independent parameters. Furthermore, the physics problem is largely treated as black box. 
}

{\bf My response: }{\color{blue} I motived the {\it general nature} of the presented model problem at \atline{281-299}. I did not elaborate more on the physics of the model problem, but hope to achieve a better understanding of the physics problem by 
introducing the new section 5.}

{\it  The first figure (Fig 1) is perhaps the most important one in the manuscript, as it points to a (potential) novelty of the work presented; (in option 2) when the high fidelity model u* in D* is used to construct surrogate models.

The last figure (Fig 12) shows the numerical result, that the surrogate models predict several "extrapolation" points (it is unclear are those outside the high-fidelity domain D*). Unfortunately, the figures are either too general (Fig 1) or implicit (Fig 12) for a reader to relate the two, and appreciate how far is the "extrapolation". If the physics remains in the same regime, there is no surprise that the surrogate models can capture the "extrapolation". For example, it would be useful to provide a clear demonstration of performance and limitations of the surrogate model in the domain beyond D*. }

{\bf My response: }{\color{blue}  Also due to other comments, I will not use the term "extrapolation" but instead I use "prediction". I also partially rewrite 2.1 to accommodate your suggestions \atline{107-131}. \\

Option 1: the red points in figure 12 would correspond to x in Fig 1, hence a point outside the training set and found to be a desired/optimal working point. With the surrogate model
we are doing (work in progress) multi objective optimisation in order to find such points.

Option 2: In a similar way I map out D* with the help of the cheep surrogate model, such that the D* is sufficiently small to be accessible with expensive high fidelity simulations.

In case the surrogate model is sufficiently close to the high fidelity model, option 2 does need not to be considered. In the new section 5, figure 17 is showing such a case.

}

{\bf Referee \#2 (Remarks to the Author): }

{\it Overall Summary: 
This paper describes 
* how a response surface can be constructed using polynomial chaos, 
* how sensitivity (Sobol') inidicies can be computed from this, and 
* a stylized example that applies these methods to analize a cyclotron 
model.

While the title is broad, the actual focus of the paper is pretty narrow, 
focusing on PCE-based sensitivity analysis and response surface 
building. Also, the details, purpose, and motivation of the sylized 
example are not brought out very well. I can envision a paper that would 
be important for introducing UQ to the particle accelerator community 
eventually coming from this manuscript, but it's a long way off now. 
}

{\bf My response: }{\color{blue} I motived the {\it general nature} of the presented model problem at \atline{281-299}\ and added section 5, where this Ansatz is
used in an ongoing physics design effort. }

{\it

A successful revision of this paper would have to go into one of two 
directions. It could either try to be a paper that a) intoduces UQ to this 
community of particle accerator modelers, or (b) it could be a focused case 
study, with some note about how such approaches could be used in other 
particle accelerator applicatios. I think the paper is much closer to (b) 
in its current form. A general paper would be quite an undertaking since 
it would have to survey potential problems in accelerator science as well 
as survey UQ methods for sensitivity analysis, inverse problems, optimal 
design / control, etc. If (b) is the appropriate route, then a real 
example would be great. }

{\bf My response: }{\color{blue} I follow direction b) and added a real example in section 5. }

Comments:

{\it I like the general idea of demonstrating the utility of modern UQ 
methods for the application area of charged particle accelerators. I think 
such a paper could be very influential. However I think the paper has 
some key issues that need to be corrected:

The details of the stylized problem are not well laid out. Because of this 
I'm not very clear on why a response surface is being generated, on why 
sensitivity inidicies are being calculated, and what advantage was gained 
by the effort described in the paper. I'm sure there is an advantage; it's 
just not brought out effectively. For example, why are the controllable 
parameters assigned independent uniform distributions? I would have 
expected that you'd want to set these parameters so that the resulting 
beam properties are good for some future experiment or data collection. 
As it stands now, I can't follow the goal of this example. 
}

{\bf My response: }{\color{blue}

I added in section 5 an example of a real design study that should better motivate the gain 
by the effort described. Just before 3.1 \atline{300-310},  I also address more carefully  the 
benefits of surrogate models and sensitivity analysis.

We use uniform distribution to construct the response surface in order to best 
represent the variability of the selected physics parameters. All of them can be
varied in the real accelerator according to an uniform distribution.

}

{\it 
The UQ methodology focuses solely on the (non-intrusive) PCE approach 
to emulate the code output (QoI's) and to produce sensitivity indicies. 
So it seems to focus on a specific approach to propagate uncertainty from 
inputs to outputs. That's fine, but the title "UQ in particle accelerator 
modeling" implies something much broader. A title that indicates this focus 
would be more appropriate. }

{\bf My response: }{\color{blue} I agree the promises in reading the title is too much, the title is adjusted to {\bf On Non-Intrusive Uncertainty Quantification and Surrogate Model Construction in Particle Accelerator Modelling}}

{\it 
Also, a more focused paper could essentially 
be a case study, so that the general introductions to UQ and particle 
accelerator modeling could be altered to focus on a specific problem 
where the goals of the effort are more concrete. If you go down this 
path, then an actual example would be great. 
}

{\bf My response: }{\color{blue} I added a real example in the new section 5}

{\it 
If you want to make this a more general paper as the title suggests, 
then a much broader survey of problems and UQ methods will be needed. 
For example, are there interesting inverse problems or control 
problems in this field that UQ could be applied to? Could such features 
be brought out in a stylized problem? 
}

{\bf My response: }{\color{blue} At this point I would like to avoid inverse problems. This I think is 
a perfect subject for future work, and will be mentioned in the outlook  \atline{633-635}}

Specific comments

{\it 
To assess the quality of the response surface, I think it'll be more 
appropriate to use "holdout" model runs, and compare the accuracy of the 
response surface to these model runs. All of the figures 4-9 seem to 
be using the training data to show the quality of the PC-based response 
surface. Maybe you could use something like a collection of 100 model 
runs at inputs chosen uniformly over the input space for this. 
}

{\bf My response: }{\color{blue} In the design example of section 5 I use a hold out model of $N_{rs} = 100$ uniform samples over the model parameter domain. I mention in 4.6 (\atline{497-499}) that a random sample of  $N_{rs} = 100$ was used to verify the accuracy of the response surface.}

{\it 
The "extrapolation" points are difficult for me to understand. Are these 
just prediction of the code response? Are they extrapolations because 
the inputs are far away from the training set? [I doubt this because 
polynomials would be crummy for this purpose]. If they're just "prediction" 
points used for a holdout test of the response surface? If so, I think 
the term "extrapolation" is unwarrented. 
}
{\bf My response: }{\color{blue} I agree the "extrapolation" could imply points outside of the domain of $\mathbf{\lambda}$. The title of 4.7 is changed to "Predictions"}

{\it 
The work of Lee et al. (2006) seems to be dealing with estimation 
and uncertainties in a charged particle accelerator. How does this 
relate to this paper? Some mention of the distinction should be 
given. 
Lee, Herbert KH, et al. "Inferring particle distribution in a 
proton accelerator experiment." Bayesian Analysis 1.2 (2006): 249-264. 
}

{\bf My response: }{\color{blue} Lee et al. treating a classical inverse problem, by using an emulator $\mathcal{M}$, measurements (projections of the distribution) and 
infer initial conditions (initial distributions).  While, in principe, with the UQ Ansatz inverse problems can be covered, I will not yet open this box. I will distinct Lee et al in the introduction \atline{53-62}.}

{\it 
For Fig 12, are the 95\% uncertainties of the response surface are computed 
using an assumption of independent, identically distributed errors for 
the difference between the response surface surrogate and the actual 
code? I suspect so, but this is not an appropriate assumption - the 
errors are going to be very structured as a function of xi. I'd be tempted 
to go without this plot since it is trying to advertise something that I 
don't think is correct. Standard regression uncertainties all assume 
iid errors which are not the case here when one is using a polynomial surface 
to approximate a smooth model response. 
}

{\bf My response: }{\color{blue} From my surrogate model I can calculate the 95 CL.
In Fig 12 I simply show that predictions red points (before I called them Extrapolation) are within 95 CL. The prediction are based on iid of the model parameters over the 
full domain.

I think I do not understand what you mean with $\xi$ are very structured and what the implication is.

At the moment I would like to stay with that figure.
}

{\bf Referee \#3 (Remarks to the Author): }

{\it The paper reflects some misunderstanding concerning fundamental probabilistic concepts. For instance, on one 129, reference is made to stochastic processes, when in reality these expansions are for random variables. }

{\bf My response: }{\color{blue} I corrected this mistake and use the proper term random variable  \atline{137}.}

{\it Also, on line 150-155, it is stated that intrusive methods are P times more computationally expensive than the non-intrusive methods. This is also incorrect. The P equations in intrusive methods are coupled. Non-intrusive methods involve solving deterministic equations a large number of times. The comparison, as given in the paper, is thus completely baseless.}

{\bf My response: }{\color{blue}  I will only mention the need for modification and drop the statements w.r.t. explicit computational complexity, see  \atline{169-170} }

{\it The procedure, as described in the paper has been automated and described in many other publications. The insight provided following the computations is lacking and hindered by lack of sufficient perspective on probabilistic models. }

{\bf My response: }{\color{blue} The aim of this paper is to apply known methods/procedures to the field of charged particle
accelerators. I significantly modified the paper along these lines.

 \end{document}

### 2018-12-14 paper/submission/ZW10157-response-1.tex
removing copied text

@@
 Thank you for considering the manuscript.
-We appreciate the constructive criticism. It helped improve the quality of this manuscript.
+We appreciate the constructive criticism. 
+It helped improve the quality of this manuscript.
 
@@
 
-Figure(s) [10,11]
+{ Figure(s) [10,11] 
 	Please remove background grid and/or shading from your figures.
@@
 not support the tikz format in the production process. We will also
-need a revised text source file.
+need a revised text source file.}
 
@@
 
-{\bf My response:} {\color{blue} The code sections are now removed.}
+{\bf My response:} {\color{blue} The code sections have been removed.}
 
@@
 
-{\it Your manuscript, "On Uncertainty Quantification in Particle Accelerator Modelling," has completed this round of review.
-The AE and first two reviewers are positive about the main concept of the article - UQ for charged particle accelerators - but have issues with the paper.
-The manuscript is a narrow in its focus on UQ and the tie to particle accelerator applications is difficult to follow.
-
-The AE's suggestion to better motivate the use UQ methods is a good one.
-I like the suggestion of the AE and reviewer 2 to focus on a particular application of using a charged particle accelerator, describing the details so that a general audience can understand, and clearly motivating the need for UQ.
-This will give you the opportunity to show how UQ makes the science better.
-If the application is very compelling, there is not a need to be using novel UQ methodology.
-In this case, it's the application that is novel.
-A genuine example/application, involving real data, would help help make the case for the need for UQ in this area.
-}
-
-{\bf My response: }{\color{blue} In the revised version I added a contribution to an ongoing design effort (DAE$\delta$ALUS/IsoDAR) where UQ was used.
-For this the new section 5 is introduced and the section 4 is renamed to {\em APPLICATION OF THE UQ FRAMEWORK to a MODEL PROBLEM}.
-I also elaborate more in detail why the
-particular selection of a Cyclotron, is a very general example of a particle accelerator (\atline{281-299}), that justifies the general title and, hopefully refute the claim, that the paper has a  narrow scope.}
-
-{\bf Associate Editor (Remarks to the Author): }
-
-{\it The authors appear to have the goal of providing a broad paper illustrating issues pertaining to uncertainty quantification to the community of scientists modeling particle accelerators.
-This is a laudatory and timely goal.
-Unfortunately, by trying to achieve this breadth, the authors provided a discussion of surrogate models and sensitivity analysis that is fairly standard in the UQ community without adequately demonstrating its novelty for particle accelerator modeling or more general applications.
-The first and second reviewers both note that the necessity for computing a PCE surrogate, which can be used for subsequent sensitivity analysis, needs to be better motivated for this application.
-Moreover, statements that the framework provides a template for other computationally intensive applications need to be mollified or better motivated.
-Both reviewers also note that the discussion regarding extrapolation needs to be better motivated.}
-
-{\bf My response: }{\color{blue}  In section 3 (\atline{281-299}), I added a  discussion of the general Hamiltonian that is the base of the selected Cyclotron as an example.\ This will better motivate the choice of the example.}
-
-{\it The second reviewer discusses two possible directions in which a revision might be considered.
-The first would be to more adequately introduce UQ to the community of particle accelerator models.
-The second would be to focus the scope while addressing the concerns raised by all three reviewers.
-The latter is closer to the present scope of the paper.
-}
-
-{\bf My response: }{\color{blue} I modify the paper according the second direction}
-
-{\it If the authors choose to revise the paper by providing a more focused case study, I would encourage them to devote more details illustrating the techniques for a specific application where they can more completely relate the mathematics and statistics to relevant physics.
-}
-
-{\bf My response:} {\color{blue}I indeed add a more focused case study in section 5.}
-
-{\bf Referee \#1 (Remarks to the Author): }
-
-{\it The work presented in the manuscript lacks a development or findings that have impact on either theory of UQ and its application.
-Discussion of the UQ approach and associated methods is not new, and numerical results presented are of demonstration value and well expected.
-The technical content boils down to construction of PC-based surrogate models.
-In demonstrating the surrogate construction approach, it is important to establish a range of applicability (e.g., depending on physics model properties/ nonlinearity, dependency of parameters).
-
-The "claim to present a problem that can be recognised as a template for many high intensity modelling attempts, and beyond" is poorly substantiated.
-The demonstration is performed for a fairly limited case, with three uncertain independent parameters.
-Furthermore, the physics problem is largely treated as black box.
-}
-
-{\bf My response: }{\color{blue} I motived the {\it general nature} of the presented model problem at \atline{281-299}.
-I did not elaborate more on the physics of the model problem, but hope to achieve a better understanding of the physics problem by
-introducing the new section 5.}
-
-{\it  The first figure (Fig 1) is perhaps the most important one in the manuscript, as it points to a (potential) novelty of the work presented; (in option 2) when the high fidelity model u* in D* is used to construct surrogate models.
-
-The last figure (Fig 12) shows the numerical result, that the surrogate models predict several "extrapolation" points (it is unclear are those outside the high-fidelity domain D*).
-Unfortunately, the figures are either too general (Fig 1) or implicit (Fig 12) for a reader to relate the two, and appreciate how far is the "extrapolation".
-If the physics remains in the same regime, there is no surprise that the surrogate models can capture the "extrapolation".
-For example, it would be useful to provide a clear demonstration of performance and limitations of the surrogate model in the domain beyond D*.
-}
-
-{\bf My response: }{\color{blue}  Also due to other comments, I will not use the term "extrapolation" but instead I use "prediction".
-I also partially rewrite 2.1 to accommodate your suggestions \atline{107-131}.
-\\
-
-Option 1: the red points in figure 12 would correspond to x in Fig 1, hence a point outside the training set and found to be a desired/optimal working point. With the surrogate model
-we are doing (work in progress) multi objective optimisation in order to find such points.
-
-Option 2: In a similar way I map out D* with the help of the cheep surrogate model, such that the D* is sufficiently small to be accessible with expensive high fidelity simulations.
-
-In case the surrogate model is sufficiently close to the high fidelity model, option 2 does need not to be considered. In the new section 5, figure 17 is showing such a case.
-
-}
-
-{\bf Referee \#2 (Remarks to the Author): }
-
-{\it Overall Summary: 
-This paper describes 
-* how a response surface can be constructed using polynomial chaos, 
-* how sensitivity (Sobol') inidicies can be computed from this, and 
-* a stylized example that applies these methods to analize a cyclotron 
-model.
-
-While the title is broad, the actual focus of the paper is pretty narrow, 
-focusing on PCE-based sensitivity analysis and response surface 
-building. Also, the details, purpose, and motivation of the sylized 
-example are not brought out very well. I can envision a paper that would 
-be important for introducing UQ to the particle accelerator community 
-eventually coming from this manuscript, but it's a long way off now. 
-}
-
-{\bf My response: }{\color{blue} I motived the {\it general nature} of the presented model problem at \atline{281-299}\ and added section 5, where this Ansatz is
-used in an ongoing physics design effort. }
-
-{\it
-
-A successful revision of this paper would have to go into one of two 
-directions. It could either try to be a paper that a) intoduces UQ to this 
-community of particle accerator modelers, or (b) it could be a focused case 
-study, with some note about how such approaches could be used in other 
-particle accelerator applicatios. I think the paper is much closer to (b) 
-in its current form. A general paper would be quite an undertaking since 
-it would have to survey potential problems in accelerator science as well 
-as survey UQ methods for sensitivity analysis, inverse problems, optimal 
-design / control, etc. If (b) is the appropriate route, then a real 
-example would be great. }
-
-{\bf My response: }{\color{blue} I follow direction b) and added a real example in section 5. }
-
-Comments:
-
-{\it I like the general idea of demonstrating the utility of modern UQ 
-methods for the application area of charged particle accelerators. I think 
-such a paper could be very influential. However I think the paper has 
-some key issues that need to be corrected:
-
-The details of the stylized problem are not well laid out. Because of this 
-I'm not very clear on why a response surface is being generated, on why 
-sensitivity inidicies are being calculated, and what advantage was gained 
-by the effort described in the paper. I'm sure there is an advantage; it's 
-just not brought out effectively. For example, why are the controllable 
-parameters assigned independent uniform distributions? I would have 
-expected that you'd want to set these parameters so that the resulting 
-beam properties are good for some future experiment or data collection. 
-As it stands now, I can't follow the goal of this example. 
-}
-
-{\bf My response: }{\color{blue}
-
-I added in section 5 an example of a real design study that should better motivate the gain 
-by the effort described. Just before 3.1 \atline{300-310},  I also address more carefully  the 
-benefits of surrogate models and sensitivity analysis.
-
-We use uniform distribution to construct the response surface in order to best 
-represent the variability of the selected physics parameters. All of them can be
-varied in the real accelerator according to an uniform distribution.
-
-}
-
-{\it 
-The UQ methodology focuses solely on the (non-intrusive) PCE approach 
-to emulate the code output (QoI's) and to produce sensitivity indicies. 
-So it seems to focus on a specific approach to propagate uncertainty from 
-inputs to outputs. That's fine, but the title "UQ in particle accelerator 
-modeling" implies something much broader. A title that indicates this focus 
-would be more appropriate. }
-
-{\bf My response: }{\color{blue} I agree the promises in reading the title is too much, the title is adjusted to {\bf On Non-Intrusive Uncertainty Quantification and Surrogate Model Construction in Particle Accelerator Modelling}}
-
-{\it 
-Also, a more focused paper could essentially 
-be a case study, so that the general introductions to UQ and particle 
-accelerator modeling could be altered to focus on a specific problem 
-where the goals of the effort are more concrete. If you go down this 
-path, then an actual example would be great. 
-}
-
-{\bf My response: }{\color{blue} I added a real example in the new section 5}
-
-{\it 
-If you want to make this a more general paper as the title suggests, 
-then a much broader survey of problems and UQ methods will be needed. 
-For example, are there interesting inverse problems or control 
-problems in this field that UQ could be applied to? Could such features 
-be brought out in a stylized problem? 
-}
-
-{\bf My response: }{\color{blue} At this point I would like to avoid inverse problems. This I think is 
-a perfect subject for future work, and will be mentioned in the outlook  \atline{633-635}}
-
-Specific comments
-
-{\it 
-To assess the quality of the response surface, I think it'll be more 
-appropriate to use "holdout" model runs, and compare the accuracy of the 
-response surface to these model runs. All of the figures 4-9 seem to 
-be using the training data to show the quality of the PC-based response 
-surface. Maybe you could use something like a collection of 100 model 
-runs at inputs chosen uniformly over the input space for this. 
-}
-
-{\bf My response: }{\color{blue} In the design example of section 5 I use a hold out model of $N_{rs} = 100$ uniform samples over the model parameter domain.
-I mention in 4.6 (\atline{497-499}) that a random sample of  $N_{rs} = 100$ was used to verify the accuracy of the response surface.}
-
-{\it 
-The "extrapolation" points are difficult for me to understand. Are these 
-just prediction of the code response? Are they extrapolations because 
-the inputs are far away from the training set? [I doubt this because 
-polynomials would be crummy for this purpose]. If they're just "prediction" 
-points used for a holdout test of the response surface? If so, I think 
-the term "extrapolation" is unwarrented. 
-}
-{\bf My response: }{\color{blue} I agree the "extrapolation" could imply points outside of the domain of $\mathbf{\lambda}$. The title of 4.7 is changed to "Predictions"}
-
-{\it 
-The work of Lee et al. (2006) seems to be dealing with estimation 
-and uncertainties in a charged particle accelerator. How does this 
-relate to this paper? Some mention of the distinction should be 
-given. 
-Lee, Herbert KH, et al. "Inferring particle distribution in a 
-proton accelerator experiment." Bayesian Analysis 1.2 (2006): 249-264. 
-}
-
-{\bf My response: }{\color{blue} Lee et al. treating a classical inverse problem, by using an emulator $\mathcal{M}$, measurements (projections of the distribution) and 
-infer initial conditions (initial distributions).
-While, in principe, with the UQ Ansatz inverse problems can be covered, I will not yet open this box.
-I will distinct Lee et al in the introduction \atline{53-62}.}
-
-{\it 
-For Fig 12, are the 95\% uncertainties of the response surface are computed 
-using an assumption of independent, identically distributed errors for 
-the difference between the response surface surrogate and the actual 
-code? I suspect so, but this is not an appropriate assumption - the 
-errors are going to be very structured as a function of xi. I'd be tempted 
-to go without this plot since it is trying to advertise something that I 
-don't think is correct. Standard regression uncertainties all assume 
-iid errors which are not the case here when one is using a polynomial surface 
-to approximate a smooth model response. 
-}
-
-{\bf My response: }{\color{blue} From my surrogate model I can calculate the 95 CL.
-In Fig 12 I simply show that predictions red points (before I called them Extrapolation) are within 95 CL. The prediction are based on iid of the model parameters over the 
-full domain.
-
-I think I do not understand what you mean with $\xi$ are very structured and what the implication is.
-
-At the moment I would like to stay with that figure.
-}
-
-{\bf Referee \#3 (Remarks to the Author): }
-
-{\it The paper reflects some misunderstanding concerning fundamental probabilistic concepts.
-For instance, on one 129, reference is made to stochastic processes, when in reality these expansions are for random variables.
-}
-
-{\bf My response: }{\color{blue} I corrected this mistake and use the proper term random variable  \atline{137}.}
-
-{\it Also, on line 150-155, it is stated that intrusive methods are P times more computationally expensive than the non-intrusive methods.
-This is also incorrect.
-The P equations in intrusive methods are coupled.
-Non-intrusive methods involve solving deterministic equations a large number of times.
-The comparison, as given in the paper, is thus completely baseless.}
-
-{\bf My response: }{\color{blue}  I will only mention the need for modification and drop the statements w.r.t. explicit computational complexity, see  \atline{169-170} }
-
-{\it The procedure, as described in the paper has been automated and described in many other publications.
-The insight provided following the computations is lacking and hindered by lack of sufficient perspective on probabilistic models.
-}
-
-{\bf My response: }{\color{blue} The aim of this paper is to apply known methods/procedures to the field of charged particle
-accelerators. I significantly modified the paper along these lines.
-
  \end{document}

### 2018-12-21 paper/submission/theor-experiment.tex
removing grids from plots in figure 10

@@
 
+\iffalse
 %\vspace{0.2cm}
@@
 \end{samepage}
-
+\fi
 %\vspace{0.2cm}
@@
 		\centering
-		\includegraphics[width=\textwidth]{figures/ex-pareto1}
+		\includegraphics[width=\textwidth]{figures/ex-pareto1-paperedit}
 		(a) Pareto fronts for ex-1 through ex-4 at $s_1$.
@@
 		%\label{expareto1}
-		\vspace{2em}
+		%\vspace{2em}
 	\end{minipage}
@@
 		\centering
-		\includegraphics[width=\textwidth]{figures/ex-pareto2}
+		\includegraphics[width=\textwidth]{figures/ex-pareto2-paperedit}
 		(b) Pareto fronts for ex-1 through ex-4 at $s_2$.
@@
 %\vspace{0.2cm}
+\iffalse
 \begin{samepage}
@@
 \end{samepage}
+\fi
 

### 2018-12-21 paper/submission/ZW10157-response-1.tex
fixing figure names in paper

@@
 \setlength{\parindent}{0pt}
+\usepackage[margin=1in]{geometry}
 
@@
 
-We have carefully answered all your questions and implemented your suggestions to the best of our knowledge.\ The details can be found in the following pages.
+We have carefully answered all your questions and implemented your suggestions to the best of our knowledge.
+The details can be found in the following pages.
 

### 2018-12-21 paper/submission/ZW10157-response-1.tex
more responses added

@@
 
-{\bf My response:} {\color{blue} The grid has been removed from Figures 10 and 11.
+{\bf Our response:} {\color{blue} The grid has been removed from Figures 10 and 11.
 PDF versions of the tikz pictures have been made. All updated figures are provided 
@@
 
-{\bf Referee A (Remarks to Author)}
+{\bf REFEREE A (Remarks to Author)}
 
@@
 
-{\bf My response:} {\color{blue} The code sections have been removed.}
+{\bf Our response:} {\color{blue} The code sections have been removed.}
 
@@
 
-{\bf My response:} {\color{blue} XXXXX.}
+{\bf Our response:} {\color{blue} XXXXX.}
 
-REFEREE B - ZW10157
+{\bf REFEREE B (Remarks to Author)}
 
@@
 
-{\bf My response:} {\color{blue} XXXXX.}
+{\bf Our response:} {\color{blue} XXXXX.}
 
@@
 
-line 35: trade of -> trade off
+line 35: trade of -$>$ trade off
 
-{\bf My response:} {\color{blue} This typo is corrected in the updated manuscript.}
+{\bf Our response:} {\color{blue} This typo is corrected in the updated manuscript.}
 
@@
 
-subsubsection 3
+{\bf Our response:} {\color{blue} The code has been removed from the updated manuscript. Interested parties can refer to the repository.}
 
-line 427 to to -> to
+subsubsection 3:
+line 427 to to -$>$ to
 
-{\bf My response:} {\color{blue} This typo is corrected in the updated manuscript.}
+{\bf Our response:} {\color{blue} This typo is corrected in the updated manuscript.}
 
-subsubsection 4
-
+subsubsection 4:
 FIGS. 11/12 The discussed case in FIG. 12 is not on either front in
@@
 optimization exercise is moot.
+
+{\bf Our response:} {\color{blue} This was a plotting mistake, and has been corrected in the updated Fig. 11.}
 
@@
 
+{\bf Our response:} {\color{blue} This table shows input parameters for one optimized solution (the solution in Fig. 12). 
+The table title has been changed to the following: "Input Parameters for the optimized solution shown in Figures~11 and 12."}
+
  \end{document}

### 2018-12-21 paper/submission/ZW10157-response-1.tex
updating bib

@@
 
-{\bf Our response:} {\color{blue} The code sections have been removed.}
+{\bf Our response:} {\color{blue} The code examples in sections IV-V have been removed.}
 
@@
 
-{\bf Our response:} {\color{blue} XXXXX.}
+{\bf Our response:} {\color{blue} We agree that some references of import were missing and should have been included.
+Especially, the following:
+
+I.V. Bazarov and C.K. Sinclair. "Multivariate optimization of a high
+brightness dc gun photoinjector," Phys. Rev. ST Accel. Beams 8,
+034202, 2005
+
+A. Hofler et al., "Innovative applications of genetic algorithms to
+problems in accelerator physics", Phys. Rev. ST Accel. Beams 16,
+010101, 2013
+
+}
 
@@
 
-Section VI
-
+Section VI: 
 Code and input file details should be in Supplemental Material
 
-Section V
-
-subsection B
-
+Section V, subsection B:
 Code and input file details should be in Supplemental Material
 
-{\bf Our response:} {\color{blue} The code has been removed from the updated manuscript. Interested parties can refer to the repository.}
+{\bf Our response:} {\color{blue} The code examples in sections VI-V has been removed from the updated manuscript. 
+	A sentence and link to the repository have been provided. Interested parties can refer to the repository.}
 
@@
 {\bf Our response:} {\color{blue} This table shows input parameters for one optimized solution (the solution in Fig. 12). 
-The table title has been changed to the following: "Input Parameters for the optimized solution shown in Figures~11 and 12."}
+The table title has been changed to the following: ``Input Parameters for the optimized solution shown in Figures~11 and 12."}
 

### 2018-12-21 paper/submission/prab.tex
removing grids from plots in figure 10
updating bib

@@
   evolutionary algorithm employing a \textsc{NSGA-II} selector \cite{pisa}.
-Normally, simulation based approaches are plagued by the trade-of between
+Normally, simulation based approaches are plagued by the trade off between
   level of detail and time to solution.
@@
 In general, it is not possible to get the maximal performance for the lowest
-  price and a trade-off decision between performance and price has to be
+  price and a trade off decision between performance and price has to be
   reached (see Fig.~\ref{fig:tradeoff}).
@@
   $x_4$ costs as much as $x_2^*$ but offers less performance), we pick
-  trade-offs (red points) that are essentially ``equally optimal'' in both
+  trade offs (red points) that are essentially ``equally optimal'' in both
   conflicting objectives, meaning, we cannot improve one point without hurting
@@
 This is called \textit{a posteriori} preference specification since 
-  a solution is selected after all possible trade-offs have been presented to us.
+  a solution is selected after all possible trade offs have been presented to us.
 An alternative is to specify preference \textit{a priori}, e.g. by
@@
   understanding of the solution space.
-The Pareto front can be explored and the impact of a trade-off decision then
+The Pareto front can be explored and the impact of a trade off decision then
   becomes visible.
@@
 \textsc{OPAL} provides different trackers for cyclotrons and linear
-  accelerators with satisfactory parallel performance \cite{akir:09}.
+  accelerators with satisfactory parallel performance. % \cite{akir:09}.
 
@@
 %\vspace{0.2cm}
-
+\iffalse
 \begin{samepage}

### 2018-12-21 paper/submission/theor-experiment.tex
fixing figure names in paper
updating bib

@@
 		\label{extable}
-		\begin{tabular*}{0.48\textwidth}{l @{\extracolsep{\fill}} C C D }
+		\begin{tabular*}{0.48\textwidth}{l @{\extracolsep{\fill}}| C | C | D }
 			\hline\noalign{\smallskip}
@@
 The objectives include: $\varepsilon_{x}\left(s = s_1\right)\text{, } \varepsilon_{x}\left(s = s_2\right)$, $\text{rms}_{s}\left(s = s_1\right)\text{, and }  \text{rms}_{s}\left(s = s_2\right)$. 
-The OPAL input file for ex-3 is given as an example to show how optimization and design variables are defined:
+The OPAL input file for ex-3, and subsequent optimization runs in this paper, can be found at in following repository: 
+\url{https://github.com/nneveu/awa-tba}.
+%is given as an example to show how optimization and design variables are defined:
 
@@
 & \text{rms}_{px}, \quad \text{rms}_{py}, \label{eq:awa:p2}\\
-& \text{rms}_{s}, \quad dE \label{eq:awa:p4} \\
-\text{constraints} \quad & rms_x < 0.1 \, (m) |_{s=s_1}\label{eq:awa:c1}\\
-\quad & rms_y < 0.1\, (m) |_{s=s_1}\, \label{eq:awa:c2}\\
-\quad & |rms_y - rms_x | < 0.005 \, (m) |_{s=s_1}\label{eq:awa:c3}\\
-\text{subject to} \quad & q = 40 \, (nC) \label{eq:awa:firstconstr}\\
+& \text{rms}_{s}, \quad \text{dE} \label{eq:awa:p4} \\
+\text{constraints} \quad & \text{rms}_x < 0.1 \, (\text{m}) |_{s=s_1}\label{eq:awa:c1}\\
+\quad & \text{rms}_y < 0.1\, (m) |_{s=s_1}\, \label{eq:awa:c2}\\
+\quad & |\text{rms}_y - \text{rms}_x | < 0.005 \, (\text{m}) |_{s=s_1}\label{eq:awa:c3}\\
+\text{subject to} \quad & q = 40 \, (\text{nC}) \label{eq:awa:firstconstr}\\
 \quad & \text{Volt}_{\text{Gun}} = 64 \, \, (\text{MV/m}) \label{eq:awa:lastconstr}\\
 \quad & \text{Volt}_{\text{Linac}} = 24 \, \text{or} \, 25\,\, (\text{MV/m}) \\
-\quad & R_x = R_y = 9 \, (mm) \label{eq:awa:firstdvar}\\
+\quad & R_x = R_y = 9 \, (\text{mm}) \label{eq:awa:firstdvar}\\
 \quad & \phi_{\text{gun}} =-20^\circ \label{eq:awa:gphidvar}\\
@@
 	\begin{center}		
-		\begin{tikzpicture}[scale=1]
-		\node (fig1) at (0,0)
-		{\includegraphics[width=0.5\textwidth]{figures/xy_vs_pxy_pareto_front_quads_before_Q5}};
-		\node[star, star points=5, star point ratio=0.5, fill=yellow, draw](key) at (3.35,-1.7) {};
-		\end{tikzpicture}
+		\includegraphics[width=0.65\textwidth]{figures/paperedit_pareto_front_Q5_xy_vs_pxpy}
 	\end{center} 
-		\caption{Pareto front comparing transverse beam sizes ($\sigma_{x,y}$) and transverse momentum ($\sigma_{px,py}$). The yellow star indicates the 
+		\caption{Pareto front comparing transverse beam sizes (rms$_{x,y}$) and transverse momentum (rms$_{px,py}$). The yellow star indicates the 
 		point plotted in Fig.~\ref{fig:stat}}
@@
 \begin{figure}
-	\includegraphics[width=0.48\textwidth]{figures/xy-max-min-sigma-paper}
+	\includegraphics[width=0.65\textwidth]{figures/xy-max-min-sigma-paper}
 	\caption{Optimized beam sizes along high charge beam line. The gun is located at $s=0$, 
@@
 	\begin{center}
-		\caption{Input Parameters for large scale TBA optimization runs.}
+		\caption{Input Parameters for the optimized solution shown in Figures~\ref{fig:pareto1} and \ref{fig:stat}.}
 		\label{tab:designopt}   

### 2018-12-21 paper/submission/ZW10157-response-1.tex
adding in Ref B suggestions to abstract, etc

@@
 employing several masters that govern a set of slaves executing
-simulations and performing optimization tasks. -> In this paper, we
+simulations and performing optimization tasks. $->$ In this paper, we
 present a general-purpose framework for simulation-based
@@
 
+{\bf Our Response:} {\color{blue} The suggested edit above has been incorporated into the updated manuscript. }
+
 The high charge beam line at the Argonne Wakefield Accelerator
 Facility was used as the beam dynamics model. The 3D beam size,
-transverse momentum, and energy spread were optimized. Please state
+transverse momentum, and energy spread were optimized.
+
+Please state
 the significance of the optimization. Is the solution found better
@@
 
-Section I
-
-line 35: trade of -$>$ trade off
+Section I, line 35: trade of -$>$ trade off
 
@@
 
-Section II
-
+Section II:
 lines 53-74. The car example is from Deb’s book but not cited. This
@@
 
-Section III
+{\bf Our response:} {\color{blue} This example has been removed.}
 
-subsection A
-
+Section III, subsection A:
 Needs to be updated to reflect developments in accelerator physics.
 
-subsections B-F
+{\bf Our response:} {\color{blue} XXX}
 
+subsections B-F:
 Replace with a brief overview and put the details in Supplemental
 Material
+
+{\bf Our response: } {\color{blue} XXX}
 

### 2018-12-21 paper/submission/prab.tex
adding in Ref B suggestions to abstract, etc

@@
   and scalable software framework is required.
-In this paper, we present the implementation of such a general-purpose
-  framework for simulation-based multi-objective optimization methods that
-  allows the automatic investigation of optimal sets of machine parameters.
-The implementation is based on a master/slave paradigm, employing several
-  masters that govern a set of slaves executing simulations and performing
-  optimization tasks.
+In this paper, we
+present a general-purpose framework for simulation-based
+multi-objective optimization methods that allows the automatic
+investigation of optimal sets of machine parameters.
 Using evolutionary algorithms as the optimizer and \textsc{OPAL} as the 
@@
   optimality.
+
+  \iffalse
 To illustrate this, let us consider the problem of buying a car.
@@
   at least one other solution.
+  \fi
 This is known as \textit{Pareto optimality}.

### 2019-01-15 paper/submission/ZW10157-response-1.tex
more small edits to review response 1

@@
 
-First, optimization systems based on PISA have been in use in
-accelerator design since 2005, and NSGA-II’s use dates from that time
-too. References to early PISA-based systems and NSGAII applications
+References to early PISA-based systems and NSGAII applications
 are missing from the authors’ reference list, and the authors must
@@
 
-1) References for 4 PISA-based optimization systems:
+{\bf Our response:} {\color{blue} We agree that some references of import were missing and should have been included.
+	Especially the following:
 
@@
 
-Y.C. Chao et al. "TRIUMF-VECC Electron Linac Beam Dynamics
-Optimization," ICAP09, San Francisco, 2009, THPSC012
+	A. Hofler et al., "Innovative applications of genetic algorithms to
+	problems in accelerator physics", Phys. Rev. ST Accel. Beams 16,
+	010101, 2013
+
+	We thank the reviewer for the list of references. 
+	References described or referenced by A. Hofler in the above were excluded from 
+	the bibliography. 
+}
+
+1) References for 4 PISA-based optimization systems:
+
+{\color{blue}{Included in updated bib:}}
+
+I.V. Bazarov and C.K. Sinclair. "Multivariate optimization of a high
+brightness dc gun photoinjector," Phys. Rev. ST Accel. Beams 8,
+034202, 2005
+
+{\color{blue}{Exluded from bib, because  they are in A. Hofler 13':}}
 
@@
 Algorithm Framework," ICAP09, San Francisco, 2009, THPSC020
+
+Y.C. Chao et al. "TRIUMF-VECC Electron Linac Beam Dynamics
+Optimization," ICAP09, San Francisco, 2009, THPSC012
 
@@
 
-{\bf Our response:} {\color{blue} We agree that some references of import were missing and should have been included.
-Especially, the following:
-
-I.V. Bazarov and C.K. Sinclair. "Multivariate optimization of a high
-brightness dc gun photoinjector," Phys. Rev. ST Accel. Beams 8,
-034202, 2005
-
-A. Hofler et al., "Innovative applications of genetic algorithms to
-problems in accelerator physics", Phys. Rev. ST Accel. Beams 16,
-010101, 2013
-
-}
-
-Second, due to the thoroughness and success of Bazarov and Sinclair’s
-optimization (PRSTAB 2005 provided above), genetic and evolutionary
-algorithm-based optimizations are standard practice in accelerator
-design, and researchers are now looking at ways to use machine
-learning and AI techniques in accelerator design and optimization.
 Manual parameter scans, as mentioned in Section I lines 17-19, are

### 2019-01-15 paper/submission/theor-experiment.tex
more small edits to review response 1

@@
 
-\iffalse
-%\vspace{0.2cm}
-\begin{samepage}
-	\begin{Verbatim}[fontsize=\scriptsize]
-	OPTION, ECHO=FALSE;
-	OPTION, INFO=TRUE;
-
-	TITLE, STRING="ANL Optimization";
-
-	dv0: DVAR, VARIABLE="IBF",    LOWERBOUND=200.0, UPPERBOUND=500.0;
-	dv1: DVAR, VARIABLE="IM",     LOWERBOUND=170.0, UPPERBOUND=260.0;
-	dv2: DVAR, VARIABLE="GPHASE", LOWERBOUND=-30.0, UPPERBOUND=0.0;
-	dv3: DVAR, VARIABLE="FWHM",   LOWERBOUND=1.5,   UPPERBOUND=10.0;
-
-	// Quad values
-	dv4: DVAR, VARIABLE="KQ1", LOWERBOUND=-8.0, UPPERBOUND=8.0;
-	dv5: DVAR, VARIABLE="KQ2", LOWERBOUND=-8.0, UPPERBOUND=8.0;
-	dv6: DVAR, VARIABLE="KQ3", LOWERBOUND=-8.0, UPPERBOUND=8.0;
-	dv7: DVAR, VARIABLE="KQ4", LOWERBOUND=-8.0, UPPERBOUND=8.0;
-
-	rmss1:  OBJECTIVE,EXPR="fabs(statVariableAt('rms_s',16.5))";
-	emitx1: OBJECTIVE,EXPR="fabs(statVariableAt('emit_x',16.5))";
-
-	rmss2:  OBJECTIVE,EXPR="fabs(statVariableAt('rms_s',18.5))";
-	emitx2: OBJECTIVE,EXPR="fabs(statVariableAt('emit_x',18.5))";
-
-	c1: CONSTRAINT, EXPR="fabs(statVariableAt('rms_x',16.5))<1.0e-1";
-	c2: CONSTRAINT, EXPR="fabs(statVariableAt('rms_y',16.5))<1.0e-1";
-
-	OPTIMIZE, INPUT="tmpl/optLinac_40nC.tmpl",
-	OUTPUT="optLinac_40nC",
-	OUTDIR="results",
-	OBJECTIVES = {rmss1, emitx1, rmss2, emitx2},
-	DVARS = {dv0, dv1, dv2, dv3, dv4, dv5, dv6, dv7},
-	CONSTRAINTS = {c1, c2},
-	INITIALPOPULATION=80,
-	MAXGENERATIONS=100,
-	NUM_MASTERS=1,
-	NUM_COWORKERS=8,
-	SIMTMPDIR="tmp",
-	TEMPLATEDIR="tmpl",
-	\end{Verbatim}
-\end{samepage}
-\fi
-%\vspace{0.2cm}
-
 After collection of the data for all four experiments, several metrics
@@
 %\vspace{0.2cm}
-\iffalse
-\begin{samepage}
-	\begin{Verbatim}[fontsize=\scriptsize]
-
-	// Gun variables 
-	dv0: DVAR, VARIABLE="IBF",    LOWERBOUND=300.0, UPPERBOUND=500.0;
-	dv1: DVAR, VARIABLE="IM",     LOWERBOUND=180.0, UPPERBOUND=280.0;
-
-	// Quad variables 
-	dv4: DVAR, VARIABLE="KQ1", LOWERBOUND=-8.0, UPPERBOUND=8.0;
-	dv5: DVAR, VARIABLE="KQ2", LOWERBOUND=-8.0, UPPERBOUND=8.0;
-	dv6: DVAR, VARIABLE="KQ3", LOWERBOUND=-8.0, UPPERBOUND=8.0;
-	dv7: DVAR, VARIABLE="KQ4", LOWERBOUND=-8.0, UPPERBOUND=8.0;
-
-	//Objectives
-	de3: OBJECTIVE,EXPR="fabs(statVariableAt('dE',19.4))";
-	rmss3: OBJECTIVE,EXPR="fabs(statVariableAt('rms_s',19.4))";
-	rmsx3: OBJECTIVE,EXPR="fabs(statVariableAt('rms_x',19.4))";
-	rmsy3: OBJECTIVE,EXPR="fabs(statVariableAt('rms_y',19.4))";
-	rmspx3: OBJECTIVE,EXPR="fabs(statVariableAt('rms_px',19.4))";
-	rmspy3: OBJECTIVE,EXPR="fabs(statVariableAt('rms_py',19.4))";
-
-	//Constraints
-	c1: CONSTRAINT, EXPR="fabs(statVariableAt('rms_x',16.5))<0.1";
-	c2: CONSTRAINT, EXPR="fabs(statVariableAt('rms_y',16.5))<0.1";
-	c3: CONSTRAINT, EXPR="fabs(statVariableAt('rms_y',16.5)
-	-statVariableAt('rms_x',16.5))<0.005";
-
-	OPTIMIZE, INPUT="tmpl/optLinac-40nC.tmpl",
-	OUTPUT="optLinac-40nC",
-	OUTDIR="results",
-	OBJECTIVES = {rmss3, rmsx3, rmsy3, rmspx3, rmspy3, de3},
-	DVARS = {dv0, dv1, dv4, dv5, dv6, dv7},
-	CONSTRAINTS = {c1, c2, c3},
-	INITIALPOPULATION=656,
-	MAXGENERATIONS=200,
-	NUM_MASTERS=1,
-	NUM_COWORKERS=8,
-	SIMTMPDIR="tmp",
-	TEMPLATEDIR="tmpl",
-	FIELDMAPDIR="fieldmaps",
-	NUM_IND_GEN=328,
-	GENE_MUTATION_PROBABILITY=0.01,
-	MUTATION_PROBABILITY=0.01,
-	RECOMBINATION_PROBABILITY=0.09;
-	QUIT;
-	\end{Verbatim}
-\end{samepage}
-\fi
 

### 2019-01-16 paper/submission/ZW10157-response-1.tex
add suggestions for 2 answers

@@
 
-{\bf Our response:} {\color{blue} XXXXX.}
+{\bf Our response:} {\color{red} The AWA is a high charge charge accelerator. The strong non-linearities
+justifying the full 3D approach. At the same time AWA is a facility where many different accelerator research experiments take
+place. Therefore it is very desirable, and was one of the important research objectives, to come up with a precise, e.g. 3D
+model embedded into a multi-objective optimisation framework. The OPAL framework, differentiates itself, being massively paralle,
+full 3D and, and simple to use i.e.\ user friendly.}
 
@@
 
-{\bf Our response:} {\color{blue} XXXXX.}
+{\bf Our response:} {\color{red} The statements on the lines  17-19 of our initial submission are misleading, as
+the referee correctly recognised. We replace them with the following:
 
-Third, several of the features of this system are available is
+Despite the great success of on-line models, and various model dependent and model independent tuning and 
+optimisation techniques, in research facilities such as AWA empirical tuning is still one of the methods used. Due to the 
+non-linear problem mainly from space charge, simple and fast models are applicable only in a very 
+restricted manner. When it comes to multi-objective optimisation then the situation is even more complicated.
+}
+
+Third, several of the features of this system are available in
 existing systems but are not acknowledged:

### 2019-01-17 paper/submission/ZW10157-response-1.tex
add an other suggestions for an answer
more edits to response 1

--- 2019-01-15 paper/submission/ZW10157-response-1.tex
@@
 
-With the best regards  \\[3mm]
+With the best regards,  \\[3mm]
 
@@
 
-{\bf Our response:} {\color{blue} The code examples in sections IV-V have been removed.}
+{\bf Our response:} {\color{blue} The code examples in sections IV-V have been removed.
+A link to the repository was provided, interested parties can see the code examples there.}
 
@@
 
-{\bf Our response:} {\color{blue} XXXXX.}
+{\bf Our response:} {\color{blue} 
+	To address this concern, the following was added on lines XX-XX in the updated manuscript:
+	The AWA facility operates at both low and high charge charge (up to 100 nC). Strong non-linearities
+at high charge justify using a full 3D space charge approach. Finding optics solutions in this regime and 
+with the tight aperture constraints specific to two beam acceleration at the AWA is not trivial.
+
+At the same time, AWA is a facility where many different accelerator research experiments take
+place. Therefore it is very desirable, and was an important research objective, to develop a precise, e.g. 3D
+model embedded into a multi-objective optimization framework. In this way, optimization of various 
+machine configurations can be done at different charge levels.
+While other codes such as GPT~\cite{gpt} and ELEGANT~\cite{borl:00}, also have integrated genetic optimization algorithms; the OPAL framework, differentiates itself by being open source (i.e.
+free to use), massively parallel, and fully 3D.
+}
 
@@
 {\bf Our response:} {\color{blue} We agree that some references of import were missing and should have been included.
-	Especially the following:
+	Especially the following: }
 
@@
 
-	We thank the reviewer for the list of references. 
-	References described or referenced by A. Hofler in the above were excluded from 
-	the bibliography. 
+{\bf Our response:} {\color{blue} 	We thank the reviewer for the list of references. 
+	Next, one by one in the list, we indicate which references were included in the updated bibliography: 
 }
 
-1) References for 4 PISA-based optimization systems:
+{\color{blue}{Included in updated bibliography (in addition to two references above):}}
 
-{\color{blue}{Included in updated bib:}}
+B. Terzic et al., "Simultaneous optimization of the cavity heat load
+and trip rates in linacs using a genetic algorithm", Phys. Rev. ST
+Accel. Beams 17, 101003, 2014
 
-I.V. Bazarov and C.K. Sinclair. "Multivariate optimization of a high
-brightness dc gun photoinjector," Phys. Rev. ST Accel. Beams 8,
-034202, 2005
+C. Gulliford et al., "Multiobjective optimizations of a novel
+cryocooled dc gun based ultrafast electron diffraction beam line",
+Phys. Rev. Accel. Beams 19, 093402, 2016
 
-{\color{blue}{Exluded from bib, because  they are in A. Hofler 13':}}
+C. Gulliford et al., "Multiobjective optimization design of an rf gun
+based electron diffraction beam line", Phys. Rev. Accel. Beams 20,
+033401, 2017
+
+M. Borland. ELEGANT: A flexible SDDS-compliant code for accelerator simulation, 2000-2018.
+{\color{blue}{(slightly updated this reference)}}
+
+Pulsar Physics. General Particle Tracer, http://www.pulsar.nl/gpt
+
+{\color{blue}{Exluded from updated bibliography, because  they are in A. Hofler 13':}}
 
@@
 Algorithm Framework," ICAP09, San Francisco, 2009, THPSC020
-
-Y.C. Chao et al. "TRIUMF-VECC Electron Linac Beam Dynamics
-Optimization," ICAP09, San Francisco, 2009, THPSC012
-
-M. Marchetto et al. "Beam Dynamics Optimization of the TRIUMF ELINAC
-Injector," PAC09, Vancouver, BC, Canada, 2009, TH6PFP097
 
@@
 
+{\color{blue}{Excluded because of similarity to other references or scope of paper:}}
+
+Y.C. Chao et al. "TRIUMF-VECC Electron Linac Beam Dynamics
+Optimization," ICAP09, San Francisco, 2009, THPSC012
+
+M. Marchetto et al. "Beam Dynamics Optimization of the TRIUMF ELINAC
+Injector," PAC09, Vancouver, BC, Canada, 2009, TH6PFP097
+
 C. Gong and Y.C. Chao, "The TRIUMF Optimization Platform and
@@
 Germany, 2012, TUABI1
-
-A. Hofler et al., "Innovative applications of genetic algorithms to
-problems in accelerator physics", Phys. Rev. ST Accel. Beams 16,
-010101, 2013
-
-B. Terzic et al., "Simultaneous optimization of the cavity heat load
-and trip rates in linacs using a genetic algorithm", Phys. Rev. ST
-Accel. Beams 17, 101003, 2014
 
@@
 
-C. Gulliford et al., "Multiobjective optimizations of a novel
-cryocooled dc gun based ultrafast electron diffraction beam line",
-Phys. Rev. Accel. Beams 19, 093402, 2016
-
-C. Gulliford et al., "Multiobjective optimization design of an rf gun
-based electron diffraction beam line", Phys. Rev. Accel. Beams 20,
-033401, 2017
-
-2) Optimization systems using NSGA-II (a few example references):
-
 L. Emery. PAC 2005, Knoxville, TN, USA, May 2005, RPPP047
 
-M. Borland et al. PAC 2009, Vancouver, BC, Canada, May 2009, TH6PFP062
+A. Hofler. “Genetic Algorithms and Their Applications in
+Accelerator Physics,” NAPAC2013, Pasadena, CA, USA, 2013, THTB1
 
-Pulsar Physics. General Particle Tracer, http://www.pulsar.nl/gpt
-
-3) Survey with various references showing GA/EA usage in Accelerator
-Physics: A. Hofler. “Genetic Algorithms and Their Applications in
-Accelerator Physics,” NAPAC2013, Pasadena, CA, USA, 2013, THTB1
+\vspace{5em}
 
@@
 
-{\bf Our response:} {\color{blue} XXXXX.}
+{\bf Our response:} {\color{blue} The statements on the lines  17-19 of our initial submission are misleading, as
+the referee correctly recognized. We replace them with the following:
 
-Third, several of the features of this system are available is
+Despite the success of on-line models in some facilities[ref here], and various model dependent and model independent tuning and optimization techniques, in research facilities like the AWA, empirical tuning by operators is still one of the common methods used.
+Due to the non-linear problem mainly from space charge, simple and fast models are applicable only in a very restricted manner.
+When it comes to multi-objective optimization, the situation is even more complicated.
+}
+
+Third, several of the features of this system are available in
 existing systems but are not acknowledged:
@@
 
-{\bf Our response:} {\color{blue} XXXXX.}
+{\bf Our response:} {\color{blue} We hope we have addressed these comments with the additional references included above, correction of lines 17-19, 
+	and the additions provided in response to Referee A's remarks.}
 
@@
 of the paper should be the optimization results not the details of the
-implementation and design. For example, in the main text, it is
+implementation and design.
+
+{\bf Our response:} {\color{blue} 
+	Respectfully, we point out Referee A's comments that 
+	"Computing and algorithms" is listed under PRAB's scope. 
+	However, for those interested in physics and not implementation details (i.e. user of code not developer), 
+	we had hoped the AWA optimization problem would 
+	provide a meaningful and tangible use case for the framework.
+	It seems we did not present that part of the paper strongly enough. 
+	We hope some of the additions above have helped in this area.
+	However, would also like to keep some computational details for those who 
+	may be interested in code development specifically for accelerator optimization.
+}
+
+For example, in the main text, it is
 reasonable to say that the optimization system provides a flexible and
@@
 PISA-based systems mentioned above, also, provide expression
-capabilities and should be referenced. The one presented here is more
+capabilities and should be referenced.
+
+{\bf Our response:}{\color{blue} 	
+	We have removed all opal related code, and shortened these sections.
+	Additional references now point out ELEGANT and GPT have built in genetic optimization.
+}
+
+The one presented here is more
 flexible and has the advantage of being easily extended. Both are
@@
 use this approach).
+
+{\bf Our response:}{\color{blue} 	
+	We hope the additions above are addressing these issues. }
 
@@
 
-{\bf Our response: } {\color{blue} XXX}
+{\bf Our response: } {\color{red} This section has been shortened. However we would like to 
+leave the existing description, in order to drive home the fact that the framework can be 
+easily extended with other optimization algorithms. Something that you can not find in most of the 
+existing codes.}
 

### 2019-01-17 paper/submission/prab.tex
more edits to response 1

@@
 \begin{figure}%[h!]
-%\begin{center}%\normalsize
-	\scalebox{0.8}{
-	\pgfdeclarelayer{background}
-	\pgfsetlayers{background,main}
-	\begin{tikzpicture}[text=black]%[scale=0.05]%, transform shape]
-	\input{figures/opt-framework_code.tex}
-	\end{tikzpicture}
-}
-%\end{center}
+	\center
+\includegraphics[width=0.5\textwidth]{figures/opt-framework_code}
 \caption{Multi-objective framework: the pilot (master) solves the
@@
   optimality.
-
-  \iffalse
-To illustrate this, let us consider the problem of buying a car.
-Naturally, we try to bargain the lowest price for the best performance,
-  e.g.\ maximal horsepower or minimal fuel consumption.
-This can be formulated as MOOP (\ref{eq:car-moop}).
-%
-\begin{equation}
-  \begin{array}{cl}
-  \min          & \quad \left[ \text{price}, -\text{performance} \right]^T \\
-    \text{s.t.} & \quad \text{low}_\text{pr} \leq \text{price} \leq \text{high}_\text{pr}\\
-                & \quad \text{low}_\text{pe} \leq \text{performance} \leq \text{high}_\text{pe}
-  \end{array}
-  \label{eq:car-moop}
-\end{equation}
-
-\begin{figure}
-  \begin{center}
-    \begin{tikzpicture}[scale=1.3, transform shape]
-      \input{figures/car-trade-off}
-    \end{tikzpicture}
-  \end{center}
-  \caption{Two competing objectives can not be optimal at the same time.
-    Red dots represent Pareto optimal points, while the green square $x_4$ is
-    dominated (exhibits a worse price per performance ratio than e.g. $x_2^*$)
-    by all points on the blue curve (Pareto front).
-  }
-  \label{fig:tradeoff}
-\end{figure}
-
-In general, it is not possible to get the maximal performance for the lowest
-  price and a trade off decision between performance and price has to be
-  reached (see Fig.~\ref{fig:tradeoff}). 
-Since not every choice is equally profitable for the buyer (for example, car
-  $x_4$ costs as much as $x_2^*$ but offers less performance), we pick
-  trade offs (red points) that are essentially ``equally optimal'' in both
-  conflicting objectives, meaning, we cannot improve one point without hurting
-  at least one other solution.
-  \fi
 This is known as \textit{Pareto optimality}.

### 2019-01-17 paper/submission/ZW10157-response-1.tex
more edits to response 1
cosmetics

@@
 machine configurations can be done at different charge levels.
-While other codes such as GPT~\cite{gpt} and ELEGANT~\cite{borl:00}, also have integrated genetic optimization algorithms; the OPAL framework, differentiates itself by being open source (i.e.
+While other codes such as GPT  and ELEGANT, also have integrated genetic optimization algorithms; the OPAL framework, differentiates itself by being open source (i.e.
 free to use), massively parallel, and fully 3D.
@@
 
-\vspace{5em}
+\vspace{1em}
 
@@
 
-{\bf Our response:}{\color{blue} 	
-	We have removed all opal related code, and shortened these sections.
-	Additional references now point out ELEGANT and GPT have built in genetic optimization.
-}
+{\bf Our response: }{\color{blue} We have removed all opal related code, and shortened these sections.
+	Additional references now point out ELEGANT and GPT have built in genetic optimization.}
 
@@
 
-{\bf Our response:}{\color{blue} 	
+{\bf Our response: }{\color{blue} 	
 	We hope the additions above are addressing these issues. }
+
+Following are comments/suggestions/questions organized by paper
+section.
+
+Abstract:
+
+In this paper, we present the implementation of such a general-purpose
+framework for simulation-based multi-objective optimization methods
+that allows the automatic investigation of optimal sets of machine
+parameters. The implementation is based on a master/slave paradigm,
+employing several masters that govern a set of slaves executing
+simulations and performing optimization tasks. $->$ In this paper, we
+present a general-purpose framework for simulation-based
+multi-objective optimization methods that allows the automatic
+investigation of optimal sets of machine parameters.
+
+{\bf Our Response:} {\color{blue} The suggested edit above has been incorporated into the updated manuscript. }
+
+The high charge beam line at the Argonne Wakefield Accelerator
+Facility was used as the beam dynamics model. The 3D beam size,
+transverse momentum, and energy spread were optimized.
+
+Please state
+the significance of the optimization. Is the solution found better
+than the original design? Then provide a comparison with the baseline
+solution as Bazarov and Sinclair did in their 2005 paper. Is it the
+first such solution for the AWA? Then make that clear. Has this
+solution been used in the machine? Then provide a comparison between
+prediction and operational experience.
+
+Section I, line 35: trade of -$>$ trade off
+
+{\bf Our response:} {\color{blue} This typo is corrected in the updated manuscript.}
+
+Section II:
+lines 53-74. The car example is from Deb’s book but not cited. This
+example can probably be removed as EA/GA methodology is established
+practice now.
+
+{\bf Our response:} {\color{blue} This example has been removed.}
+
+Section III, subsection A:
+Needs to be updated to reflect developments in accelerator physics.
+
+{\bf Our response:} {\color{blue} New references were added to address this.}
+
+subsections B-F:
+Replace with a brief overview and put the details in Supplemental
+Material
+
+{\bf Our response: } {\color{blue} This section has been shortened. However we would like to 
+leave the existing description, in order to drive home the fact that the framework can be 
+easily extended with other optimization algorithms. Something that you can not find in most of the 
+existing codes.}
+
+Section VI: 
+Code and input file details should be in Supplemental Material
+
+Section V, subsection B:
+Code and input file details should be in Supplemental Material
+
+{\bf Our response:} {\color{blue} The code examples in sections VI-V has been removed from the updated manuscript. 
+	A sentence and link to the repository have been provided. Interested parties can refer to the repository.}
+
+subsubsection 3:
+line 427 to to -$>$ to
+
+{\bf Our response:} {\color{blue} This typo is corrected in the updated manuscript.}
+
+subsubsection 4:
+FIGS. 11/12 The discussed case in FIG. 12 is not on either front in
+FIG. 11. Explain why a nonfront solution is used otherwise the
+optimization exercise is moot.
+
+{\bf Our response:} {\color{blue} This was a plotting mistake, and has been corrected in the updated Fig. 11.}
+
+TABLE IV is provided and not discussed. Are these the settings for the
+solution in FIG. 12? The table’s title is confusing. If the table
+contents are input parameters for an optimization, shouldn’t they have
+ranges of values? If the values are a selected solution, shouldn’t the
+title state that directly?
+
+{\bf Our response:} {\color{blue} This table shows input parameters for one optimized solution (the solution in Fig. 12). 
+The table title has been changed to the following: ``Input Parameters for the optimized solution shown in Figures~11 and 12."}
+
+ \end{document}
+
+=======
+\documentclass{article}
+\usepackage{latexsym}
+\usepackage{color}
+\setlength{\parskip}{3mm}
+\setlength{\parindent}{0pt}
+\usepackage[margin=1in]{geometry}
+
+\newcommand{\TODO}[1]{\color{green}\noindent[{\bf TODO: #1}]\color{black}}
+\newcommand{\atline}[1]{\color{red} Lines: #1\color{blue}}
+\begin{document}
+\title {Paper  \#ZW10157}
+\author {N. Neveu, et. al}
+
+\maketitle
+Dear reviewers and editors,
+
+Thank you for considering the manuscript.
+We appreciate the constructive criticism. 
+It helped improve the quality of this manuscript.
+
+We have carefully answered all your questions and implemented your suggestions to the best of our knowledge.
+The details can be found in the following pages.
+
+With the best regards  \\[3mm]
+
+Nicole Neveu, et. al
+
+\pagebreak
+
+{\bf Problems with the manuscript:}
+
+{ Figure(s) [10,11] 
+	Please remove background grid and/or shading from your figures.
+
+* Please provide a figure file (.ps, .eps, .pdf, .jpg, or .png format)
+that does not require tikz commands in the text source file to
+display properly. Figure files should be self-contained and we do
+not support the tikz format in the production process. We will also
+need a revised text source file.}
+
+{\bf Our response:} {\color{blue} The grid has been removed from Figures 10 and 11.
+PDF versions of the tikz pictures have been made. All updated figures are provided 
+along with an updated source file.}
+
+{\bf REFEREE A (Remarks to Author)}
+
+1) Remove the sections of code from the text. This adds no value to
+	the paper and should be left for a User’s Manual.
+
+{\bf Our response:} {\color{blue} The code examples in sections IV-V have been removed.}
+
+2) Provide a stronger physics basis for the AWA optimization. Why is
+this problem of beam squeeze challenging enough to warrant solution
+with such a massively capable solver? Could the same solution have
+been arrived at with something simpler? Describe the important
+component of physics that come into play in the beam squeeze, whatever
+they are – space charge, etc. After all, this is primarily a physics
+journal so the physics context for the application needs to be clear.
+
+{\bf Our response:} {\color{red} The AWA is a high charge charge accelerator. The strong non-linearities
+justifying the full 3D approach. At the same time AWA is a facility where many different accelerator research experiments take
+place. Therefore it is very desirable, and was one of the important research objectives, to come up with a precise, e.g. 3D
+model embedded into a multi-objective optimisation framework. The OPAL framework, differentiates itself, being massively paralle,
+full 3D and, and simple to use i.e.\ user friendly.}
+
+{\bf REFEREE B (Remarks to Author)}
+
+References to early PISA-based systems and NSGAII applications
+are missing from the authors’ reference list, and the authors must
+correct this. Three groups of references are provided to assist in
+addressing these omissions: 1) early PISAbased systems; 2) a small
+sample of NSGA-II applications and implementations (there are MANY
+more as the NSGA-II algorithm is easy to understand and fairly
+straight forward to implement); and 3) a survey of accelerator physics
+and genetic and evolutionary application usage as of 2013.
+
+{\bf Our response:} {\color{blue} We agree that some references of import were missing and should have been included.
+	Especially the following:
+
+	I.V. Bazarov and C.K. Sinclair. "Multivariate optimization of a high
+	brightness dc gun photoinjector," Phys. Rev. ST Accel. Beams 8,
+	034202, 2005
+
+	A. Hofler et al., "Innovative applications of genetic algorithms to
+	problems in accelerator physics", Phys. Rev. ST Accel. Beams 16,
+	010101, 2013
+
+	We thank the reviewer for the list of references. 
+	References described or referenced by A. Hofler in the above were excluded from 
+	the bibliography. 
+}
+
+1) References for 4 PISA-based optimization systems:
+
+{\color{blue}{Included in updated bib:}}
+
+I.V. Bazarov and C.K. Sinclair. "Multivariate optimization of a high
+brightness dc gun photoinjector," Phys. Rev. ST Accel. Beams 8,
+034202, 2005
+
+{\color{blue}{Exluded from bib, because  they are in A. Hofler 13':}}
+
+A. Hofler et al. "Optimizing SRF Gun Cavity Profiles in a Genetic
+Algorithm Framework," ICAP09, San Francisco, 2009, THPSC020
+
+Y.C. Chao et al. "TRIUMF-VECC Electron Linac Beam Dynamics
+Optimization," ICAP09, San Francisco, 2009, THPSC012
+
+M. Marchetto et al. "Beam Dynamics Optimization of the TRIUMF ELINAC
+Injector," PAC09, Vancouver, BC, Canada, 2009, TH6PFP097
+
+A. Hofler and P. Evtushenko. “Optimizing RF Gun Cavity Geometry within
+an Automated Injector Design System,” NAPAC11, New York, 2011, TUODS6
+
+I.V. Bazarov et al., "Comparison of dc and superconducting rf
+photoemission guns for high brightness high average current beam
+production", Phys. Rev. ST Accel. Beams 14, 072001, 2011
+
+A. Hofler, “Optimization Framework for a Radio Frequency Gun Based
+Injector,” Ph.D. thesis, Old Dominion University, Norfolk, Virginia,
+USA, 2012
+
+C. Gong and Y.C. Chao, "The TRIUMF Optimization Platform and
+Application to the E-LINAC Injector", ICAP2012, Rostock-Warnemunde,
+Germany, 2012, TUABI1
+
+A. Hofler et al., "Innovative applications of genetic algorithms to
+problems in accelerator physics", Phys. Rev. ST Accel. Beams 16,
+010101, 2013
+
+B. Terzic et al., "Simultaneous optimization of the cavity heat load
+and trip rates in linacs using a genetic algorithm", Phys. Rev. ST
+Accel. Beams 17, 101003, 2014
+
+C. Gong, A Novel Optimization Platform and Its Applications to the
+TRIUMF Energy Recovery Linac, Ph.D. thesis, The University of
+Columbia, October 2015
+
+C. Gong and Y.C. Chao, "The TRIUMF Optimization Platform and
+Application to the E-LINAC Injector", ICAP2015, Shanghai, China, 2015,
+THCWC4
+
+C. Gulliford et al., "Multiobjective optimizations of a novel
+cryocooled dc gun based ultrafast electron diffraction beam line",
+Phys. Rev. Accel. Beams 19, 093402, 2016
+
+C. Gulliford et al., "Multiobjective optimization design of an rf gun
+based electron diffraction beam line", Phys. Rev. Accel. Beams 20,
+033401, 2017
+
+2) Optimization systems using NSGA-II (a few example references):
+
+L. Emery. PAC 2005, Knoxville, TN, USA, May 2005, RPPP047
+
+M. Borland et al. PAC 2009, Vancouver, BC, Canada, May 2009, TH6PFP062
+
+Pulsar Physics. General Particle Tracer, http://www.pulsar.nl/gpt
+
+3) Survey with various references showing GA/EA usage in Accelerator
+Physics: A. Hofler. “Genetic Algorithms and Their Applications in
+Accelerator Physics,” NAPAC2013, Pasadena, CA, USA, 2013, THTB1
+
+Manual parameter scans, as mentioned in Section I lines 17-19, are
+useful, but they are by no means the sole optimization technique in
+use today. The statement made in lines 17-19 was true prior to 2005
+but not now. The authors should consider providing a different and
+more compelling motivator to encourage users to consider the system
+they have developed.
+
+{\bf Our response:} {\color{red} The statements on the lines  17-19 of our initial submission are misleading, as
+the referee correctly recognised. We replace them with the following:
+
+Despite the great success of on-line models, and various model dependent and model independent tuning and 
+optimisation techniques, in research facilities such as AWA empirical tuning is still one of the methods used. Due to the 
+non-linear problem mainly from space charge, simple and fast models are applicable only in a very 
+restricted manner. When it comes to multi-objective optimisation then the situation is even more complicated.
+}
+
+Third, several of the features of this system are available in
+existing systems but are not acknowledged:
+
+- parallel/distributed computation: the survey article mentioned above
+provides references to several examples
+
+- Section II lines 115-125 blurring generations: APISA and General
+Particle Tracer’s optimization system start evaluating the next
+generation before all individuals in the present generation complete,
+too.
+
+- Section III subsection D lines 229-231 Geometry optimization. With
+PISA-based systems, Bazarov and Hofler have done this (see PISA-based
+reference list). Others have performed geometry optimization with
+different GA/EA based systems (again the survey reference mentions
+several.)
+
+{\bf Our response:} {\color{blue} XXXXX.}
+
+That said, a general-purpose optimization system is a useful addition
+to the design tools for accelerators. The way to entice prospective
+users through PRAB is to introduce the system with a very brief
+general overview and then focus on the results obtained using the
+system. The detailed discussion of the design and implementation with
+code snippets should be provided as Supplemental Material. PRAB is not
+a computer journal. Salient implementation or design points if
+necessary can be summarized in short Appendices; the main discussion
+of the paper should be the optimization results not the details of the
+implementation and design. For example, in the main text, it is
+reasonable to say that the optimization system provides a flexible and
+extensible meta-language for setting up optimization problems (covered
+in detail in Section III subsection E) and then direct the reader to
+an Appendix or the Supplemental Material for the details provided in
+Section III subsection E. Bear in mind, though, that several of the
+PISA-based systems mentioned above, also, provide expression
+capabilities and should be referenced. The one presented here is more
+flexible and has the advantage of being easily extended. Both are
+distinguishing features. The authors need to emphasize what
+differentiates their system from 13+ years of development in the area
+of GA/EA-based optimization in accelerator design and then demonstrate
+that the results produced are exemplary or could not have been
+produced otherwise. Or they should focus on how their system advances
+the application of the target AWA machine (the Gulliford references
+use this approach).
 
@@
 
-{\bf Our response: } {\color{red} This section has been shortened. However we would like to 
+{\bf Our response: } {\color{red} This section has being shortened. However we would like to 
 leave the existing description, in order to drive home the fact that the framework can be 
-easily extended with other optimization algorithms. Something that you can not find in most of the 
-existing codes.}
+easily extended with other optimisation algorithms. Something that you can not find in most of the 
+existing codes.}`
 

### 2019-01-29 paper/submission/ZW10157-response-1.tex
adding some of linda's edits to response.

@@
 We appreciate the constructive criticism. 
-It helped improve the quality of this manuscript.
+It helped improve the quality of the manuscript.
 
@@
 	To address this concern, the following was added on lines XX-XX in the updated manuscript:
-	The AWA facility operates at both low and high charge charge (up to 100 nC). Strong non-linearities
-at high charge justify using a full 3D space charge approach. Finding optics solutions in this regime and 
-with the tight aperture constraints specific to two beam acceleration at the AWA is not trivial.
 
-At the same time, AWA is a facility where many different accelerator research experiments take
-place. Therefore it is very desirable, and was an important research objective, to develop a precise, e.g. 3D
-model embedded into a multi-objective optimization framework. In this way, optimization of various 
-machine configurations can be done at different charge levels.
-While other codes such as GPT  and ELEGANT, also have integrated genetic optimization algorithms; the OPAL framework, differentiates itself by being open source (i.e.
-free to use), massively parallel, and fully 3D.
+A hallmark of the AWA facility is the flexibility to swap physical
+components in the beamlines, which enables different, often novel,
+accelerator research experiments to take place.  Not only do the
+physical machine components change, the beam characteristics also vary
+considerably to meet different needs.  The facility operates at both low
+and high charge (up to 100 nC), and at high charge strong nonlinearities
+require a full 3D space charge approach in simulations for modeling.  
+Finding optics solutions in this regime, especially when
+there are additional constraints such as the small aperture two-beam
+accelerating structures, is challenging even without the quick
+turnaround of the beamline configurations.  Therefore, it has been an
+important research objective to develop a precise, e.g. 3D model
+embedded into a multi-objective optimization framework that may be used
+as a flexible platform for optimization of changing machine
+configurations operated at different charge levels. While other codes
+such as GPT [updated ref here] and ELEGANT [updated ref here], also have
+integrated genetic optimization algorithms; the OPAL framework,
+differentiates itself by being open source (i.e. free to use), massively
+parallel, and fully 3D.
 }

### 2019-01-29 paper/submission/prab.tex
adding some of linda's edits to response.

@@
 
-%Unfortunately, the island parallelization approach is not well suited for
-  %running search algorithms in the massively parallel environment.
-%The decision how many processors are assigned to an island is non-trivial.
-%\todo{PA: what are roles?}
-%Parallel performance is sensitive to placement and assignment of roles to
-  %processors of such frameworks and therefore should be considered carefully.
-%Especially the master thread on an island (used to exchange individuals
-  %between the islands and aggregate solutions) can be overwhelmed with
-  %messages from slaves evaluating individuals.
-%This creates hotspots on the network and as a result the network performance
-  %suffers.
-
 Additionally, as with simulation based multi-objective optimization, we can
@@
 
-%
-Using the default expression primitives this can be stated in an input file
-  as:
-%
-%\vspace{0.2cm}
-\iffalse
-\begin{samepage}
-	\begin{flushleft}
-		\begin{Verbatim}[fontsize=\scriptsize]
-		d1: DVAR, VARIABLE="x1", LOWERBOUND="-1.0", UPPERBOUND="1.0";
-		d2: DVAR, VARIABLE="x2", LOWERBOUND="-1.0", UPPERBOUND="1.0";
-		d3: DVAR, VARIABLE="x3", LOWERBOUND="-1.0", UPPERBOUND="1.0";
-
-		obj1: OBJECTIVE,
-		EXPR="1- exp(-1 * (sq(x1 - 1/sqrt(3)) 
-		+ sq(x2 - 1/sqrt(3)) + sq(x3 - 1/sqrt(3))))";
-		obj2: OBJECTIVE,
-		EXPR="1- exp(-1 * (sq(x1 + 1/sqrt(3)) 
-		+ sq(x2 + 1/sqrt(3)) + sq(x3 + 1/sqrt(3))))";
-
-		objs:    OBJECTIVES = (obj1, obj2);
-		dvars:   DVARS = (d1, d2, d3);
-		constrs: CONSTRAINTS = ();
-		opt: OPTIMIZE, OBJECTIVES=objs, DVARS=dvars, CONSTRAINTS=constrs;
-		\end{Verbatim}
-	\end{flushleft}
-\end{samepage}
-\fi
-
 \input{theor-experiment}
@@
   optimization algorithm.
-%In a recent work, we successfully implemented and integrated another
-  %optimization algorithm, originally presented in~\cite{pesc:11}, into our
- % framework.
 The flexibility of being able to adapt both ends of the optimization
@@
 
-%This first study shows that the framework is ready to tackle problems arising
-%  in the domain of beam dynamics.
-%
-%Interestingly, the computation of a good approximation of the Pareto front is
-%  already feasible on a small cluster using only a modest number of MPI
-%  processes.
-%  
-%For 1000 generations consisting of 2048 feasible and 8354 infeasible function
-%  evaluations (simulations) the optimizer needed $845$ minutes on the
-%  \textsc{Felsim} cluster on $16$ processes.
-%
-%When we double the number of processes to $32$ (\textsc{Felsim} allows a
-%  maximum of $64$ processes per job) the runtime improves to $302$ minutes (2048
-%  accepted and 5426 infeasible individuals).
-%Notice that the runtime can vary due to the random nature of the process.
-%Nevertheless we see a reasonable speeduo when using more cores to solve the
-%  optimization problem. %and the parallel performance will be further evaluated
-%  in a forthcoming publication.
-%The number of individuals is the only limiting factor.
 The framework was integrated into OPAL, and used 
@@
 the results shown here will guide future experiments at the AWA.
-%This problem also took advantage of the frameworks massively parallel capabilities by
-%running on 2624 processes on Bebop at LCRC.
 

### 2019-01-30 paper/submission/ZW10157-response-1.tex
changes on mac that I didn't commit, response and main text

--- 2019-01-17 paper/submission/ZW10157-response-1.tex
@@
 machine configurations can be done at different charge levels.
-While other codes such as GPT  and ELEGANT, also have integrated genetic optimization algorithms; the OPAL framework, differentiates itself by being open source (i.e.
+While other codes such as GPT [updated ref here] and ELEGANT [updated ref here], also have integrated genetic optimization algorithms; the OPAL framework, differentiates itself by being open source (i.e.
 free to use), massively parallel, and fully 3D.
@@
 {\bf Our response:} {\color{blue} The statements on the lines  17-19 of our initial submission are misleading, as
-the referee correctly recognized. We replace them with the following:
+the referee correctly recognized. We replace them with the following on lines 18-27 of the updated manuscript:
 
-Despite the success of on-line models in some facilities[ref here], and various model dependent and model independent tuning and optimization techniques, in research facilities like the AWA, empirical tuning by operators is still one of the common methods used.
-Due to the non-linear problem mainly from space charge, simple and fast models are applicable only in a very restricted manner.
+Despite the success of on-line models in some facilities [ref here], 
+and various model dependent and model independent tuning and optimization techniques, 
+empirical tuning by operators a common method used at many research facilities.
+When the beam dynamics is non-linear, as is the case with space charge, 
+simple and fast models are applicable only in a very restricted manner. 
 When it comes to multi-objective optimization, the situation is even more complicated.
+In order to be able to reliably identify optimal configurations of
+accelerators, we solve large multi-objective design optimization
+problems to automate the investigation for an optimal set of tuning parameters.
+This approach has been used in the past [updated refs here] with much success.
+The difference here being the code implementation and the application to a novel
+problem at the Argonne Wakefield Accelerator Facility (AWA).
 }
@@
 
+{\bf Our response:} {\color{blue} New references were added, as mentioned above.}
+
 - Section II lines 115-125 blurring generations: APISA and General
@@
 too.
+
+{\bf Our response:} {\color{blue} A line has been here added indicating this capability in GPT too.}
 
@@
 {\bf Our response:} {\color{blue} 
-	Respectfully, we point out Referee A's comments that 
+	Respectfully, we point out Referee A's comment that 
 	"Computing and algorithms" is listed under PRAB's scope. 
@@
 
-The high charge beam line at the Argonne Wakefield Accelerator
-Facility was used as the beam dynamics model. The 3D beam size,
-transverse momentum, and energy spread were optimized.
-
 Please state
@@
 prediction and operational experience.
+
+{\bf Our Response:} {\color{blue} This optimization was used for design of 
+an experiment. There is not an alternative base line, i.e. this is the 
+"first such solution for the AWA". They points have not been operationally measured yet.
+The following line was added to the abstract:
+
+"Optimized solutions found by the framework were used to finish the design 
+of a two beam acceleration experiment."
+}
 

### 2019-01-30 paper/submission/prab.tex
changes on mac that I didn't commit, response and main text

--- 2019-01-17 paper/submission/prab.tex
@@
   algorithms which also facilitate a parallel deployment.
-In order to compute solutions in a meaningful time frame a fast 
+In order to compute solutions in a meaningful time frame, a fast 
   and scalable software framework is required.
@@
   dynamics are presented. The high charge beam line at the Argonne Wakefield 
-  Accelerator Facility was used as the beam dynamics model. The 3D beam size, 
-  transverse momentum, and energy spread were optimized.
+  Accelerator Facility was used as the beam dynamics model. 
+  Optimized solutions found by the framework were used to finish the design 
+  of a two beam acceleration experiment.
 
@@
   of accelerator facilities is a complex and versatile problem.
-Today, tuning machine parameters, e.g. bunch charge, emission time and
-  various parameters of beamline elements, is most commonly done manually by
-  running simulation codes to scan the parameter space.
-This approach is tedious, time consuming and can be error prone.
+
+Despite the success of on-line models in some facilities [ref here], 
+and various model dependent and model independent tuning and optimization techniques, 
+empirical tuning by operators a common method used at many research facilities.
+When the beam dynamics is non-linear, as is the case with space charge, 
+simple and fast models are applicable only in a very restricted manner. 
+When it comes to multi-objective optimization, the situation is even more complicated.
 In order to be able to reliably identify optimal configurations of
-  accelerators we propose to solve large multi-objective design optimization
-  problems to automate the investigation for an optimal set of tuning
-  parameters.
-Observe that multiple and conflicting optimality criteria call for a
-  multi-objective approach.
+  accelerators, we solve large multi-objective design optimization
+  problems to automate the investigation for an optimal set of tuning parameters.
+  This approach has been used in the past [] with much success.
+The difference here being the implementation and application to a novel
+problem at the Argonne Wakefield Accelerator Facility (AWA).
 
@@
   and $\bf x$ the design variables (\ref{eq:moop:dvar}).
-
 Often, conflicting objectives are encountered, and this complicates the concept of
-  optimality.
-This is known as \textit{Pareto optimality}.
-The set of Pareto optimal points (blue curve) forms the Pareto front or
+  optimality. \textit{Pareto optimality} is often used in such situations [].
+The set of Pareto optimal points forms the Pareto front or
   surface.
 All points on this surface are considered to be Pareto optimal.
-
-Once the shape of the Pareto front has been determined, the buyer can
-  \textit{specify preference}, balancing the features by observing the
-  effect on the optimality criteria, converging to the preferred solution.
-This is called \textit{a posteriori} preference specification since 
-  a solution is selected after all possible trade offs have been presented to us.
-An alternative is to specify preference \textit{a priori}, e.g. by
-  weighting (specifying preference before solving the problem) and combining
-  all objectives into one and applying a single-objective method to solve the
-  problem (yielding only one solution).
-In many situations preference is not known \textit{a priori} and an
-  \textit{a posteriori} preference specification helps conveying a deeper
-  understanding of the solution space.
-The Pareto front can be explored and the impact of a trade off decision then
-  becomes visible.
-
 Sampling Pareto fronts is far from trivial.
@@
   implementations of evolutionary algorithms.
-In the worst case some MPI processes are taking a long time to compute the
+In the worst case, some MPI processes are taking a long time to compute the
   fitness of the last individual in the pool of individuals to evaluate.
@@
 On the other hand, calling the selector more often is computationally more
-  expensive.
+  expensive. Note this capability is also present in GPT's~\cite{gpt} optimization system.
 
-Our variator implementation uses the master/slave architecture, presented in
+The variator implementation uses the master/slave architecture, presented in
   the next section, to run as many function evaluations as possible in parallel.
@@
   simple set of functions.
-
-%Unfortunately, the island parallelization approach is not well suited for
-  %running search algorithms in the massively parallel environment.
-%The decision how many processors are assigned to an island is non-trivial.
-%\todo{PA: what are roles?}
-%Parallel performance is sensitive to placement and assignment of roles to
-  %processors of such frameworks and therefore should be considered carefully.
-%Especially the master thread on an island (used to exchange individuals
-  %between the islands and aggregate solutions) can be overwhelmed with
-  %messages from slaves evaluating individuals.
-%This creates hotspots on the network and as a result the network performance
-  %suffers.
 

### 2019-01-30 paper/submission/ZW10157-response-1.tex

@@
 free to use), massively parallel, and fully 3D.
+
+A hallmark of the AWA facility is the flexibility to swap physical
+components in the beamlines, which enables different, often novel,
+accelerator research experiments to take place.  Not only do the
+physical machine components change, the beam characteristics also vary
+considerably to meet different needs.  The facility operates at both low
+and high charge (up to 100 nC), and at high charge strong nonlinearities
+require a full 3D space charge approach in simulations for modeling.  
+Finding optics solutions in this regime, especially when
+there are additional constraints such as the small aperture two-beam
+accelerating structures, is challenging even without the quick
+turnaround of the beamline configurations.  Therefore, it has been an
+important research objective to develop a precise, e.g. 3D model
+embedded into a multi-objective optimization framework that may be used
+as a flexible platform for optimization of changing machine
+configurations operated at different charge levels. While other codes
+such as GPT [updated ref here] and ELEGANT [updated ref here], also have
+integrated genetic optimization algorithms; the OPAL framework,
+differentiates itself by being open source (i.e. free to use), massively
+parallel, and fully 3D.
+
 }
@@
  \end{document}
-
-=======
-\documentclass{article}
-\usepackage{latexsym}
-\usepackage{color}
-\setlength{\parskip}{3mm}
-\setlength{\parindent}{0pt}
-\usepackage[margin=1in]{geometry}
-
-\newcommand{\TODO}[1]{\color{green}\noindent[{\bf TODO: #1}]\color{black}}
-\newcommand{\atline}[1]{\color{red} Lines: #1\color{blue}}
-\begin{document}
-\title {Paper  \#ZW10157}
-\author {N. Neveu, et. al}
-
-\maketitle
-Dear reviewers and editors,
-
-Thank you for considering the manuscript.
-We appreciate the constructive criticism. 
-It helped improve the quality of this manuscript.
-
-We have carefully answered all your questions and implemented your suggestions to the best of our knowledge.
-The details can be found in the following pages.
-
-With the best regards  \\[3mm]
-
-Nicole Neveu, et. al
-
-\pagebreak
-
-{\bf Problems with the manuscript:}
-
-{ Figure(s) [10,11] 
-	Please remove background grid and/or shading from your figures.
-
-* Please provide a figure file (.ps, .eps, .pdf, .jpg, or .png format)
-that does not require tikz commands in the text source file to
-display properly. Figure files should be self-contained and we do
-not support the tikz format in the production process. We will also
-need a revised text source file.}
-
-{\bf Our response:} {\color{blue} The grid has been removed from Figures 10 and 11.
-PDF versions of the tikz pictures have been made. All updated figures are provided 
-along with an updated source file.}
-
-{\bf REFEREE A (Remarks to Author)}
-
-1) Remove the sections of code from the text. This adds no value to
-	the paper and should be left for a User’s Manual.
-
-{\bf Our response:} {\color{blue} The code examples in sections IV-V have been removed.}
-
-2) Provide a stronger physics basis for the AWA optimization. Why is
-this problem of beam squeeze challenging enough to warrant solution
-with such a massively capable solver? Could the same solution have
-been arrived at with something simpler? Describe the important
-component of physics that come into play in the beam squeeze, whatever
-they are – space charge, etc. After all, this is primarily a physics
-journal so the physics context for the application needs to be clear.
-
-{\bf Our response:} {\color{red} The AWA is a high charge charge accelerator. The strong non-linearities
-justifying the full 3D approach. At the same time AWA is a facility where many different accelerator research experiments take
-place. Therefore it is very desirable, and was one of the important research objectives, to come up with a precise, e.g. 3D
-model embedded into a multi-objective optimisation framework. The OPAL framework, differentiates itself, being massively paralle,
-full 3D and, and simple to use i.e.\ user friendly.}
-
-{\bf REFEREE B (Remarks to Author)}
-
-References to early PISA-based systems and NSGAII applications
-are missing from the authors’ reference list, and the authors must
-correct this. Three groups of references are provided to assist in
-addressing these omissions: 1) early PISAbased systems; 2) a small
-sample of NSGA-II applications and implementations (there are MANY
-more as the NSGA-II algorithm is easy to understand and fairly
-straight forward to implement); and 3) a survey of accelerator physics
-and genetic and evolutionary application usage as of 2013.
-
-{\bf Our response:} {\color{blue} We agree that some references of import were missing and should have been included.
-	Especially the following:
-
-	I.V. Bazarov and C.K. Sinclair. "Multivariate optimization of a high
-	brightness dc gun photoinjector," Phys. Rev. ST Accel. Beams 8,
-	034202, 2005
-
-	A. Hofler et al., "Innovative applications of genetic algorithms to
-	problems in accelerator physics", Phys. Rev. ST Accel. Beams 16,
-	010101, 2013
-
-	We thank the reviewer for the list of references. 
-	References described or referenced by A. Hofler in the above were excluded from 
-	the bibliography. 
-}
-
-1) References for 4 PISA-based optimization systems:
-
-{\color{blue}{Included in updated bib:}}
-
-I.V. Bazarov and C.K. Sinclair. "Multivariate optimization of a high
-brightness dc gun photoinjector," Phys. Rev. ST Accel. Beams 8,
-034202, 2005
-
-{\color{blue}{Exluded from bib, because  they are in A. Hofler 13':}}
-
-A. Hofler et al. "Optimizing SRF Gun Cavity Profiles in a Genetic
-Algorithm Framework," ICAP09, San Francisco, 2009, THPSC020
-
-Y.C. Chao et al. "TRIUMF-VECC Electron Linac Beam Dynamics
-Optimization," ICAP09, San Francisco, 2009, THPSC012
-
-M. Marchetto et al. "Beam Dynamics Optimization of the TRIUMF ELINAC
-Injector," PAC09, Vancouver, BC, Canada, 2009, TH6PFP097
-
-A. Hofler and P. Evtushenko. “Optimizing RF Gun Cavity Geometry within
-an Automated Injector Design System,” NAPAC11, New York, 2011, TUODS6
-
-I.V. Bazarov et al., "Comparison of dc and superconducting rf
-photoemission guns for high brightness high average current beam
-production", Phys. Rev. ST Accel. Beams 14, 072001, 2011
-
-A. Hofler, “Optimization Framework for a Radio Frequency Gun Based
-Injector,” Ph.D. thesis, Old Dominion University, Norfolk, Virginia,
-USA, 2012
-
-C. Gong and Y.C. Chao, "The TRIUMF Optimization Platform and
-Application to the E-LINAC Injector", ICAP2012, Rostock-Warnemunde,
-Germany, 2012, TUABI1
-
-A. Hofler et al., "Innovative applications of genetic algorithms to
-problems in accelerator physics", Phys. Rev. ST Accel. Beams 16,
-010101, 2013
-
-B. Terzic et al., "Simultaneous optimization of the cavity heat load
-and trip rates in linacs using a genetic algorithm", Phys. Rev. ST
-Accel. Beams 17, 101003, 2014
-
-C. Gong, A Novel Optimization Platform and Its Applications to the
-TRIUMF Energy Recovery Linac, Ph.D. thesis, The University of
-Columbia, October 2015
-
-C. Gong and Y.C. Chao, "The TRIUMF Optimization Platform and
-Application to the E-LINAC Injector", ICAP2015, Shanghai, China, 2015,
-THCWC4
-
-C. Gulliford et al., "Multiobjective optimizations of a novel
-cryocooled dc gun based ultrafast electron diffraction beam line",
-Phys. Rev. Accel. Beams 19, 093402, 2016
-
-C. Gulliford et al., "Multiobjective optimization design of an rf gun
-based electron diffraction beam line", Phys. Rev. Accel. Beams 20,
-033401, 2017
-
-2) Optimization systems using NSGA-II (a few example references):
-
-L. Emery. PAC 2005, Knoxville, TN, USA, May 2005, RPPP047
-
-M. Borland et al. PAC 2009, Vancouver, BC, Canada, May 2009, TH6PFP062
-
-Pulsar Physics. General Particle Tracer, http://www.pulsar.nl/gpt
-
-3) Survey with various references showing GA/EA usage in Accelerator
-Physics: A. Hofler. “Genetic Algorithms and Their Applications in
-Accelerator Physics,” NAPAC2013, Pasadena, CA, USA, 2013, THTB1
-
-Manual parameter scans, as mentioned in Section I lines 17-19, are
-useful, but they are by no means the sole optimization technique in
-use today. The statement made in lines 17-19 was true prior to 2005
-but not now. The authors should consider providing a different and
-more compelling motivator to encourage users to consider the system
-they have developed.
-
-{\bf Our response:} {\color{red} The statements on the lines  17-19 of our initial submission are misleading, as
-the referee correctly recognised. We replace them with the following:
-
-Despite the great success of on-line models, and various model dependent and model independent tuning and 
-optimisation techniques, in research facilities such as AWA empirical tuning is still one of the methods used. Due to the 
-non-linear problem mainly from space charge, simple and fast models are applicable only in a very 
-restricted manner. When it comes to multi-objective optimisation then the situation is even more complicated.
-}
-
-Third, several of the features of this system are available in
-existing systems but are not acknowledged:
-
-- parallel/distributed computation: the survey article mentioned above
-provides references to several examples
-
-- Section II lines 115-125 blurring generations: APISA and General
-Particle Tracer’s optimization system start evaluating the next
-generation before all individuals in the present generation complete,
-too.
-
-- Section III subsection D lines 229-231 Geometry optimization. With
-PISA-based systems, Bazarov and Hofler have done this (see PISA-based
-reference list). Others have performed geometry optimization with
-different GA/EA based systems (again the survey reference mentions
-several.)
-
-{\bf Our response:} {\color{blue} XXXXX.}
-
-That said, a general-purpose optimization system is a useful addition
-to the design tools for accelerators. The way to entice prospective
-users through PRAB is to introduce the system with a very brief
-general overview and then focus on the results obtained using the
-system. The detailed discussion of the design and implementation with
-code snippets should be provided as Supplemental Material. PRAB is not
-a computer journal. Salient implementation or design points if
-necessary can be summarized in short Appendices; the main discussion
-of the paper should be the optimization results not the details of the
-implementation and design. For example, in the main text, it is
-reasonable to say that the optimization system provides a flexible and
-extensible meta-language for setting up optimization problems (covered
-in detail in Section III subsection E) and then direct the reader to
-an Appendix or the Supplemental Material for the details provided in
-Section III subsection E. Bear in mind, though, that several of the
-PISA-based systems mentioned above, also, provide expression
-capabilities and should be referenced. The one presented here is more
-flexible and has the advantage of being easily extended. Both are
-distinguishing features. The authors need to emphasize what
-differentiates their system from 13+ years of development in the area
-of GA/EA-based optimization in accelerator design and then demonstrate
-that the results produced are exemplary or could not have been
-produced otherwise. Or they should focus on how their system advances
-the application of the target AWA machine (the Gulliford references
-use this approach).
-
-Following are comments/suggestions/questions organized by paper
-section.
-
-Abstract:
-
-In this paper, we present the implementation of such a general-purpose
-framework for simulation-based multi-objective optimization methods
-that allows the automatic investigation of optimal sets of machine
-parameters. The implementation is based on a master/slave paradigm,
-employing several masters that govern a set of slaves executing
-simulations and performing optimization tasks. $->$ In this paper, we
-present a general-purpose framework for simulation-based
-multi-objective optimization methods that allows the automatic
-investigation of optimal sets of machine parameters.
-
-{\bf Our Response:} {\color{blue} The suggested edit above has been incorporated into the updated manuscript. }
-
-The high charge beam line at the Argonne Wakefield Accelerator
-Facility was used as the beam dynamics model. The 3D beam size,
-transverse momentum, and energy spread were optimized.
-
-Please state
-the significance of the optimization. Is the solution found better
-than the original design? Then provide a comparison with the baseline
-solution as Bazarov and Sinclair did in their 2005 paper. Is it the
-first such solution for the AWA? Then make that clear. Has this
-solution been used in the machine? Then provide a comparison between
-prediction and operational experience.
-
-Section I, line 35: trade of -$>$ trade off
-
-{\bf Our response:} {\color{blue} This typo is corrected in the updated manuscript.}
-
-Section II:
-lines 53-74. The car example is from Deb’s book but not cited. This
-example can probably be removed as EA/GA methodology is established
-practice now.
-
-{\bf Our response:} {\color{blue} This example has been removed.}
-
-Section III, subsection A:
-Needs to be updated to reflect developments in accelerator physics.
-
-{\bf Our response:} {\color{blue} XXX}
-
-subsections B-F:
-Replace with a brief overview and put the details in Supplemental
-Material
-
-{\bf Our response: } {\color{red} This section has being shortened. However we would like to 
-leave the existing description, in order to drive home the fact that the framework can be 
-easily extended with other optimisation algorithms. Something that you can not find in most of the 
-existing codes.}`
-
-Section VI: 
-Code and input file details should be in Supplemental Material
-
-Section V, subsection B:
-Code and input file details should be in Supplemental Material
-
-{\bf Our response:} {\color{blue} The code examples in sections VI-V has been removed from the updated manuscript. 
-	A sentence and link to the repository have been provided. Interested parties can refer to the repository.}
-
-subsubsection 3:
-line 427 to to -$>$ to
-
-{\bf Our response:} {\color{blue} This typo is corrected in the updated manuscript.}
-
-subsubsection 4:
-FIGS. 11/12 The discussed case in FIG. 12 is not on either front in
-FIG. 11. Explain why a nonfront solution is used otherwise the
-optimization exercise is moot.
-
-{\bf Our response:} {\color{blue} This was a plotting mistake, and has been corrected in the updated Fig. 11.}
-
-TABLE IV is provided and not discussed. Are these the settings for the
-solution in FIG. 12? The table’s title is confusing. If the table
-contents are input parameters for an optimization, shouldn’t they have
-ranges of values? If the values are a selected solution, shouldn’t the
-title state that directly?
-
-{\bf Our response:} {\color{blue} This table shows input parameters for one optimized solution (the solution in Fig. 12). 
-The table title has been changed to the following: ``Input Parameters for the optimized solution shown in Figures~11 and 12."}
-
- \end{document}

### 2019-01-30 paper/submission/ZW10157-response-1.tex
adding some of Linda's edits

@@
 	To address this concern, the following was added on lines XX-XX in the updated manuscript:
-	The AWA facility operates at both low and high charge charge (up to 100 nC). Strong non-linearities
-at high charge justify using a full 3D space charge approach. Finding optics solutions in this regime and 
-with the tight aperture constraints specific to two beam acceleration at the AWA is not trivial.
-
-At the same time, AWA is a facility where many different accelerator research experiments take
-place. Therefore it is very desirable, and was an important research objective, to develop a precise, e.g. 3D
-model embedded into a multi-objective optimization framework. In this way, optimization of various 
-machine configurations can be done at different charge levels.
-While other codes such as GPT [updated ref here] and ELEGANT [updated ref here], also have integrated genetic optimization algorithms; the OPAL framework, differentiates itself by being open source (i.e.
-free to use), massively parallel, and fully 3D.
 
@@
 and various model dependent and model independent tuning and optimization techniques, 
-empirical tuning by operators a common method used at many research facilities.
+empirical tuning by operators is a common method used at many research facilities.
 When the beam dynamics is non-linear, as is the case with space charge, 
@@
 When it comes to multi-objective optimization, the situation is even more complicated.
-In order to be able to reliably identify optimal configurations of
+In order to reliably identify optimal configurations of
 accelerators, we solve large multi-objective design optimization
@@
 
-{\bf Our response:} {\color{blue} New references were added, as mentioned above.}
+{\bf Our response:} {\color{blue} New references were added, as detailed above.}
 
@@
 
-{\bf Our response:} {\color{blue} A line has been here added indicating this capability in GPT too.}
+{\bf Our response:} {\color{blue} A line XX has been added indicating this capability in GPT too.}
 
@@
 	Respectfully, we point out Referee A's comment that 
-	"Computing and algorithms" is listed under PRAB's scope. 
+	``Computing and algorithms'' is listed under PRAB's scope. 
 	However, for those interested in physics and not implementation details (i.e. user of code not developer), 
@@
 an experiment. There is not an alternative base line, i.e. this is the 
-"first such solution for the AWA". They points have not been operationally measured yet.
+``first such solution for the AWA''. They points have not been operationally measured yet.
 The following line was added to the abstract:

### 2019-01-30 paper/submission/ZW10157-response-1.tex
small grammer edits to response

@@
 an experiment. There is not an alternative base line, i.e. this is the 
-``first such solution for the AWA''. They points have not been operationally measured yet.
-The following line was added to the abstract:
+``first such solution for the AWA''. The points have not been operationally measured yet.
+The following line was added to the abstract to address this:
 
-"Optimized solutions found by the framework were used to finish the design 
-of a two beam acceleration experiment."
+``Optimized solutions found by the framework were used to finish the design 
+of a two beam acceleration experiment.''
 }
@@
 leave the existing description, in order to drive home the fact that the framework can be 
-easily extended with other optimization algorithms. Something that you can not find in most of the 
-existing codes.}
+easily extended with other optimization algorithms.}
 
@@
 
-{\bf Our response:} {\color{blue} The code examples in sections VI-V has been removed from the updated manuscript. 
+{\bf Our response:} {\color{blue} The code examples in sections VI-V have been removed from the updated manuscript. 
 	A sentence and link to the repository have been provided. Interested parties can refer to the repository.}

### 2019-01-31 paper/submission/ZW10157-response-1.tex
finished adding in Linda's edits

@@
-\documentclass{article}
+~\cite{hofler13,bazarov05,yrss:09,jefferson,gull1,gull2} \documentclass{article}
 \usepackage{latexsym}
@@
 {\bf Our response:} {\color{blue} 
-	To address this concern, the following was added on lines XX-XX in the updated manuscript:
+	To address this concern, the following was added on lines 28-41 in the updated manuscript:
 
@@
 {\bf Our response:} {\color{blue} The statements on the lines  17-19 of our initial submission are misleading, as
-the referee correctly recognized. We replace them with the following on lines 18-27 of the updated manuscript:
+the referee correctly recognized. We replace them with the following on lines 17-27 of the updated manuscript:
 

### 2019-01-31 paper/submission/prab.tex
finished adding in Linda's edits

@@
-\documentclass[%
-%superscriptaddress,
-%groupedaddress,
-%unsortedaddress,
-%runinaddress,
-%frontmatterverbose, 
-preprint,
-linenumbers,
-%twocolumn,
-%showpacs,preprintnumbers,
-%nofootinbib,
-%nobibnotes,
-%bibnotes,
-amsmath,amssymb,
-aps,
-%pra,
-%prb,
-%rmp,
-prstab,
-%prstper,
-%floatfix,
-]{revtex4-1}
+\documentclass[preprint,linenumbers,amsmath,amssymb,aps,prstab]{revtex4-1}%
 
@@
 \usepackage{bm}% bold math
-%\usepackage{todonotes}
 \usepackage{siunitx}
@@
 \usepackage{fancyvrb}
-\usepackage{booktabs}
-%\usepackage{cite}
-\usepackage{amsmath}
-\usepackage{amsfonts}
+%\usepackage{booktabs}
+%\usepackage{amsmath}
+%\usepackage{amsfonts}
 \usepackage{url}
-%\usepackage{footmisc}
-%\usepackage{multicol}
-%\usepackage{color}
-\usepackage{algorithm}
-\usepackage{algorithmic}
-\usepackage{tikz}
-\usetikzlibrary{shapes,arrows,snakes,backgrounds}
-\usetikzlibrary{mindmap,trees}
-\usetikzlibrary{decorations.pathreplacing}
-\usetikzlibrary{plotmarks}
+%\usepackage{algorithm}
+%\usepackage{algorithmic}
 \usepackage{listings}
@@
 \setcounter{lstmain}{1}
-
 \usepackage{graphicx,xcolor,enumitem}
-%\usepackage{cuted}
-\newcommand{\lsnote}[1]{\textsf{{\color{violet}{ LS note:}   #1 }}}
+\usepackage{booktabs}
 
@@
 
-\usepackage{array}
-\newcolumntype{C}{ >{\centering\arraybackslash} m{2.5cm} }
-\newcolumntype{D}{ >{\centering\arraybackslash} m{3cm} }
-
-\newcommand{\nrnote}[1]{\textsf{{\color{blue}{ NN note:}   #1 }}}
-\newcommand{\lsedit}[1]{\textsf{{\color{violet}{ ls note:}   #1 }}}
 \begin{document}
@@
   with Application To Electron Beam Dynamics}
-%\thanks{A footnote to the article title}%
 
@@
 Particle accelerators are invaluable tools for research in the basic and
-  applied sciences, in fields such as materials science, chemistry,
+  applied sciences, such as materials science, chemistry,
   the biosciences, particle physics, nuclear physics and medicine.
@@
 
-\pacs{Valid PACS appear here}% PACS, the Physics and Astronomy
-% Classification Scheme.
-%\keywords{Suggested keywords}%Use showkeys class option if keyword
-%display desired
 \maketitle
@@
   physics, nuclear physics and medicine depend on reliable and effective
-  particle accelerators, both as research but as well as practical tools.
+  particle accelerators, both as research and practical tools.
 Achieving the required performance in the design, commissioning, and operation
   of accelerator facilities is a complex and versatile problem.
-
-Despite the success of on-line models in some facilities [ref here], 
+Despite the success of on-line models in some facilities~\cite{xiaobiao}, 
 and various model dependent and model independent tuning and optimization techniques, 
-empirical tuning by operators a common method used at many research facilities.
+empirical tuning by operators is a common method used at many research facilities.
 When the beam dynamics is non-linear, as is the case with space charge, 
@@
   problems to automate the investigation for an optimal set of tuning parameters.
-  This approach has been used in the past [] with much success.
-The difference here being the implementation and application to a novel
+  This approach has been used in the past with much success~\cite{hofler13,bazarov05,yrss:09,jefferson,gull1,gull2}.
+The difference here being the implementation and application to a 
 problem at the Argonne Wakefield Accelerator Facility (AWA).
+
+A hallmark of the AWA facility is the flexibility to swap physical
+components in the beamlines, which enables different, often novel,
+accelerator research experiments to take place.  Not only do the
+physical machine components change, the beam characteristics also vary
+considerably to meet different needs.  The facility operates at both low
+and high charge (up to 100 nC), and at high charge strong nonlinearities
+require a full 3D space charge approach in simulations for modeling.  
+Finding optics solutions in this regime, especially when
+there are additional constraints such as the small aperture two-beam
+accelerating structures, is challenging even without the quick
+turnaround of the beamline configurations.  Therefore, it has been an
+important research objective to develop a precise, e.g. 3D model
+embedded into a multi-objective optimization framework that may be used
+as a flexible platform for optimization of changing machine
+configurations operated at different charge levels. While other codes,
+such as GPT~\cite{gpt} and ELEGANT~\cite{elegant}, also have
+integrated genetic optimization algorithms; the OPAL~\cite{opal} framework
+differentiates itself by being open source (i.e. free to use), massively
+parallel, and fully 3D.
 
@@
  Fig.~\ref{fig:framenetwork}) where the core functionality of the optimizer is decoupled from
- the ``beam dynamics'' but fully integrated in the OPAL \cite{opal} framework. 
+ the ``beam dynamics'' but fully integrated in the OPAL framework. 
 To that end, we use a master/slave mechanism where a master process governs a
@@
 A ``pilot'' coordinates all efforts between the optimization algorithm and the
-  beam dynamics task. In the sequel we will also use the notion of ``forward solver'' to indicate the beam dynamics task.
+  beam dynamics task. In the following sections, we will also use the notion of ``forward solver'' to indicate the beam dynamics task.
 This forms a robust and general framework for massively parallel
@@
         and deploy on large scale computational resources, and
-  \item demonstrating the usefulness of the proposed framework on a real world
-        application in the domain of particle accelerators,
+  \item demonstration of the usefulness of the proposed framework on a real world
+        application in the domain of particle accelerators. This is done
         with the optimization problem set as 
@@
 theory and describes the first implemented optimizer.
-In Section~\ref{sec:framework} the implementation of the framework is discussed.
+In Section~\ref{sec:framework}, the implementation of the framework is discussed.
 We introduce the employed forward-solver in Section~\ref{sec:forward-solver}.
@@
     \centering
-    \scalebox{1}{
-    \begin{tikzpicture}[scale=0.8, transform shape, text=black]
-    \input{figures/ga_explained_big.tex}
-    \end{tikzpicture}
-	}
+    \includegraphics[width=0.6\textwidth]{figures/ga_explained_big}
   \caption{Schematic view of interplay between selector and variator. The
@@
   \centering
-  \scalebox{0.85}{
-  \begin{tikzpicture}[text=black]
-  \input{figures/opt-framework-layout.tex}
-  \end{tikzpicture}
-}
-
+  \includegraphics[width=0.7\linewidth]{figures/opt-framework-layout}
   \caption{Schematic view of messages passed within the network between the
@@
 \textsc{OPAL} provides different trackers for cyclotrons and linear
-  accelerators with satisfactory parallel performance. % \cite{akir:09}.
+  accelerators with satisfactory parallel performance.
 
@@
 
-\bibliographystyle{abbrv}
 \bibliography{paper}

### 2019-01-31 paper/submission/theor-experiment.tex
finished adding in Linda's edits

@@
     \centering
-    \begin{tikzpicture}[text=black]
-      \input{figures/hypervolume.tex}
-    \end{tikzpicture}
+      \includegraphics[width=0.4\linewidth]{figures/hypervolume}
   \caption{The hypervolume for a two-objective optimization problem
@@
 
-\def \gunheight {25}  %25} %double sided number
-\def \quadheight {35}
-\def \quadleft {115}  %127} %double sided number
-\def \kickerleft {145}  %160} % two sided number
-\def \leftarrow{10}
-\def \bottomofarrows {29}
-\def \topofarrows {34}
 \begin{figure*}
-	\begin{tikzpicture}[every node/.style={anchor=south west,inner sep=0pt},x=1mm, y=1mm,]   
-	\node (fig1) at (0,0)
-	{\includegraphics[width=\textwidth]{figures/awa-drawing}};
-	\node[fill=white, inner sep=2pt] (txt2) at (0,\gunheight) {\large Gun};
-	\node[fill=white, inner sep=2pt] (txt2) at (20,\gunheight) {\large Accelerating Cavities};
-	\node[fill=white, inner sep=2pt] (txt2) at (\quadleft-5,\quadheight) {\large Quadrupoles};
-	\draw [blue, ->, line width=1] (\quadleft+\leftarrow,\topofarrows) -- (\quadleft+\leftarrow, \bottomofarrows);
-	\node[fill=white, inner sep=2pt] (txt2) at (\kickerleft,20) {\large $s_1$};
-	\node[fill=white, inner sep=2pt] (txt2) at (\kickerleft+8,20) {\large $s_2$};
-	\node[fill=white, inner sep=2pt] (txt2) at (\kickerleft,\quadheight) {\large Kicker};
-	\draw [blue, ->, line width=1] (\kickerleft+\leftarrow-3,\topofarrows) -- (\kickerleft+\leftarrow-3, \bottomofarrows);	
-	\draw [black, ->, line width=1] (0,-2) -- (100, -2);
-	\node[fill=white, inner sep=2pt] (txt2) at (50,0) {\large Beam Direction};
-	\end{tikzpicture}
+\includegraphics[width=0.9\linewidth]{figures/awa-drawing}
 	\caption{Side view of the high charge linac at the AWA. 
@@
 
-\def \septheight {65}
-\def \bottomarrow {55} %57}
-\def \kleft {13}
-\def \sleft {38}%41.5}
-\def \sheight {45}%47}
-\def \beam {35}
 \begin{figure*}
-	\begin{tikzpicture}[every node/.style={anchor=south west,inner sep=0pt},x=1mm, y=1mm,]   
-	\node (fig2) at (0,0)
-	{\includegraphics[width=\textwidth]{figures/tba_dogleg}};
-	\node[fill=white, inner sep=2pt] (txt2) at (3,\sheight) {\large $s_1$};
-	\node[fill=white, inner sep=2pt] (txt2) at (20,\sheight) {\large $s_2$};
-	\node[fill=white, inner sep=2pt] (txt2) at (41,40) {\large $s_3$}; %(46,45)
-	\node[fill=white, inner sep=2pt] (txt2) at (33,\septheight) {\large Septum};
-	\draw [blue, ->, line width=1] (\sleft,\septheight) -- (\sleft, \bottomarrow);	
-	\node[fill=white, inner sep=2pt] (txt2) at (7,\septheight) {\large Kicker};
-	\draw [blue, ->, line width=1] (\kleft,\septheight) -- (\kleft, \bottomarrow);
-	\draw [black, ->, line width=1] (0,\beam) -- (100,\beam);
-	\node[fill=white, inner sep=2pt] (txt2) at (50,\beam+2) {\large Beam Direction};
-	\end{tikzpicture}
-	\vspace{-12em}
+\includegraphics[width=0.9\linewidth]{figures/tba_dogleg2}
 	\caption{Continuation of the high charge beam line layout at the AWA, top view. 
@@
 		\label{timestep}
-		\begin{tabular*}{0.48\textwidth}{c @{\extracolsep{\fill}} C c D }
+		\begin{tabular*}{0.48\textwidth}{cccc}
 			\hline\noalign{\smallskip}
@@
 		\label{extable}
-		\begin{tabular*}{0.48\textwidth}{l @{\extracolsep{\fill}}| C | C | D }
-			\hline\noalign{\smallskip}
+		\begin{tabular*}{0.48\textwidth}{l ccc}
 			& Gene Mutation Probability & Recombination Probability & Number of completed generations \\
-			\noalign{\smallskip}\hline\noalign{\smallskip}
 			ex-1 &  0.1  & 0.9  &  96 \\
@@
 			ex-4 &  0.01 & 0.09 &  95 \\
-			\noalign{\smallskip}\hline
 		\end{tabular*}
@@
 \url{https://github.com/nneveu/awa-tba}.
-%is given as an example to show how optimization and design variables are defined:
 
@@
 		(a) Pareto fronts for ex-1 through ex-4 at $s_1$.
-		%\caption{(a) Pareto fronts at $s_1$.}
-		%\label{expareto1}
 		%\vspace{2em}
@@
 		(b) Pareto fronts for ex-1 through ex-4 at $s_2$.
-		%\caption{(b) Pareto fronts at $s_2$.}
 		%\label{expareto2}
@@
 that must be defined, but do not vary during the optimization.
-%\vspace{-1em}
-The AWA 
-design variables, objectives, and constraints in the OPAL input file as shown in
-the following code: %equations (\ref{eq:awa:p1}) to (\ref{eq:awa:lastdvar}). 
+The AWA design variables, objectives, and constraints in the OPAL input file as shown in
+the repository.
 %\vspace{0.2cm}
@@
 		\label{tab:designopt}   
-		\begin{tabular}{l|c|c}
-			\noalign{\smallskip}\hline\noalign{\smallskip}
-			%\rowcolor{blue!30} 
+		\begin{tabular}{ccc}
+			\toprule
 			\textbf{Design Variable} & \textbf{Unit}	&  \textbf{Value}  \\ 
-			\noalign{\smallskip}\hline\noalign{\smallskip}
+			\midrule
 			{Buck Focusing Solenoid} & amps	& 478 \\
@@
 			Bunch Length & mm 		& 1.5	\\
-			\noalign{\smallskip}\hline\noalign{\smallskip}
+			\bottomrule
 		\end{tabular}

### 2019-01-31 paper/submission/prab.tex
incorporating Linda's edits to abstract

@@
 \begin{abstract}
-Particle accelerators are invaluable tools for research in the basic and
-  applied sciences, such as materials science, chemistry,
-  the biosciences, particle physics, nuclear physics and medicine.
-The design, commissioning, and operation of accelerator facilities is a
-  non-trivial task, due to the large number of control parameters and the
-  complex interplay of several conflicting design goals.
-We propose to tackle this problem by means of multi-objective optimization
-  algorithms which also facilitate a parallel deployment.
-In order to compute solutions in a meaningful time frame, a fast 
-  and scalable software framework is required.
-In this paper, we
-present a general-purpose framework for simulation-based
-multi-objective optimization methods that allows the automatic
-investigation of optimal sets of machine parameters.
-Using evolutionary algorithms as the optimizer and \textsc{OPAL} as the 
-  forward solver, validation experiments and 
- results of multi-objective optimization problems in the domain of beam
-  dynamics are presented. The high charge beam line at the Argonne Wakefield 
-  Accelerator Facility was used as the beam dynamics model. 
-  Optimized solutions found by the framework were used to finish the design 
+Particle accelerators are invaluable tools for research in the basic and applied sciences, such as materials science, chemistry,
+  the biosciences, particle physics, nuclear physics and medicine. The design, commissioning, and operation of accelerator facilities is a
+  non-trivial task, due to the large number of control parameters and the complex interplay of several conflicting design goals.
+  The Argonne Wakefield Accelerator facility has some unique challenges resulting from its purpose to carry out advanced accelerator R\&D.
+  Individual experiments often have challenging beam requirements, and the physical configuration of the beamlines is often changed
+  to accommodate the variety of supported experiments. The need for rapid deployment of different operational settings
+  further complicates the optimization work that must be done for multiple constraints and challenging operational regimes. 
+  One example of this is an independently staged two-beam acceleration experiment which requires the construction 
+  of an additional beamline (this is now in progress).  The high charge drive beam, well into the space charge regime, must be threaded
+  through small aperture (\SI{17.6}{mm}) decelerating structures.  
+  In addition, the bunch length must be sufficiently short to maximize power generation in the decelerator.  
+We propose to tackle this problem by means of multi-objective optimization algorithms which also facilitate a parallel deployment.
+In order to compute solutions in a meaningful time frame, a fast and scalable software framework is required.
+In this paper, we present a general-purpose framework for simulation-based
+multi-objective optimization methods that allows the automatic investigation of optimal sets of machine parameters.
+Using evolutionary algorithms as the optimizer and \textsc{OPAL} as the forward solver, validation experiments and 
+ results of multi-objective optimization problems in the domain of beam dynamics are presented. 
+  Optimized solutions for the new high charge drive beamline found by the framework were used to finish the design 
   of a two beam acceleration experiment.
+  The selected solution along with the associated beam parameters is presented.
 

### 2019-01-31 paper/submission/ZW10157-response-1.tex
adding text about new abstract

@@
-~\cite{hofler13,bazarov05,yrss:09,jefferson,gull1,gull2} \documentclass{article}
+\documentclass{article}
 \usepackage{latexsym}
@@
 {\bf Our response:} {\color{blue} 
-	To address this concern, the following was added on lines 28-41 in the updated manuscript:
+	Several changes were made in the paper to address this concern. 
+	 abstract to explain the AWA problem. 
+	Here is the new abstract in it's entirety:
+
+	Particle accelerators are invaluable tools for research in the basic and applied sciences, such as materials science, chemistry,
+	the biosciences, particle physics, nuclear physics and medicine. The design, commissioning, and operation of accelerator facilities is a
+	non-trivial task, due to the large number of control parameters and the complex interplay of several conflicting design goals.
+	The Argonne Wakefield Accelerator facility has some unique challenges resulting from its purpose to carry out advanced accelerator R\&D.
+	Individual experiments often have challenging beam requirements, and the physical configuration of the beamlines is often changed
+	to accommodate the variety of supported experiments. The need for rapid deployment of different operational settings
+	further complicates the optimization work that must be done for multiple constraints and challenging operational regimes. 
+	One example of this is an independently staged two-beam acceleration experiment which requires the construction 
+	of an additional beamline (this is now in progress).  The high charge drive beam, well into the space charge regime, must be threaded
+	through small aperture (17.6mm) decelerating structures.  
+	In addition, the bunch length must be sufficiently short to maximize power generation in the decelerator.  
+	We propose to tackle this problem by means of multi-objective optimization algorithms which also facilitate a parallel deployment.
+	In order to compute solutions in a meaningful time frame, a fast and scalable software framework is required.
+	In this paper, we present a general-purpose framework for simulation-based
+	multi-objective optimization methods that allows the automatic investigation of optimal sets of machine parameters.
+	Using evolutionary algorithms as the optimizer and \textsc{OPAL} as the forward solver, validation experiments and 
+	results of multi-objective optimization problems in the domain of beam dynamics are presented. 
+	Optimized solutions for the new high charge drive beamline found by the framework were used to finish the design 
+	of a two beam acceleration experiment.
+	The selected solution along with the associated beam parameters is presented.
+
+	The following was added on lines 28-41 in the updated manuscript:
 
@@
 ``first such solution for the AWA''. The points have not been operationally measured yet.
-The following line was added to the abstract to address this:
-
-``Optimized solutions found by the framework were used to finish the design 
-of a two beam acceleration experiment.''
+Several sentences were added to the abstract to explain this. 
+Please see new abstract used in response to Referee A, or updated manuscript.
 }

### 2019-01-31 paper/submission/theor-experiment.tex
adding Linda's edit to inclue beam size

@@
   \centering
-    \includegraphics[width=0.7\linewidth]{figures/valid_front}
+    \includegraphics[width=0.6\linewidth]{figures/valid_front}
   \caption{Variator benchmark after $1100$ function evaluations using binary
@@
     \hline\noalign{\smallskip}
-    tot.\ function  & hyper volume & relative error\\
+    tot.\ function  & hypervolume & relative error\\
     evaluations    & & \\
@@
 		\label{timestep}
-		\begin{tabular*}{0.48\textwidth}{cccc}
+		\begin{tabular*}{0.48\textwidth}{c|c|c|c}
 			\hline\noalign{\smallskip}
-			Time Step (dT) & Linac & Drift & Quadrupoles \\
+			Time Step, dT (s) \quad & Linac & Drift & Quadrupoles \\
 			\noalign{\smallskip}\hline\noalign{\smallskip}
@@
 As expected, the x dimension is impacted by the bending elements, and unable to reach 
-the small beam sizes seen in the y dimension. This suggest objectives in the x 
+the small beam sizes seen in the y dimension. This suggests objectives in the x 
 dimension will drive design variable choices used during operations. 
@@
 as it travels to the last triplet in Fig.~\ref{awa-tba}.
-Overall this solution is satisfactory, and meets all requirements at the AWA.
+Overall this solution is satisfactory, and meets all requirements for the new TBA beamline at the AWA.
+The PETS (Power Extractor and Transfer Structure) is the physical device putting the tightest constraints on the beam parameters.  
+At this location the aperture diameter is \SI{17.6}{mm}, and the desired bunch length is \SI{1.5}{m}.  
+The optimization meets all requirements in general; and specifically at the PETS location, 
+the beam parameters are $\sigma_x=\sigma_y=2.5$mm, with aa bunch length of XXXXX.
+
+ Although the simulation results at the PETS location cannot yet be checked since the beamline is not yet completely installed, some checks have been possible for the partially completed beamline.
+Simulations of the partial beamline have been done with good agreement to measurement.
+For example, beam images were taken on the YAG screen located downstream of the kicker and the extracted beam sizes at different kicker angles compared to simulation.
+Measurements showed an asymmetry between the x and y beam size that was also shown in simulation (see Fig.
+).
+This is likely due to the gun voltage since that had the most noticeable impact on the simulated asymmetry (the best match was at a gun voltage of 55 MV/m).
+When it becomes possible to test the complete simulation solution, it is expected that there will not be perfect agreement with simulation; for example there may be errors in the fields of beamline elements.
+However, the simulation can be a tool to track down the source of discrepancies, such as understanding the effect of the gun field on the beam symmetry.
+More importantly, the optimization results should provide significant improvement in efficiency for achieving a good operational regime.
 
@@
 		\label{tab:designopt}   
-		\begin{tabular}{ccc}
+		\begin{tabular}{lcc}
 			\toprule
-			\textbf{Design Variable} & \textbf{Unit}	&  \textbf{Value}  \\ 
+			\textbf{Design Variable} \qquad \qquad & \textbf{Unit}	\quad&  \textbf{Value}  \\ 
 			\midrule
-			{Buck Focusing Solenoid} & amps	& 478 \\
+			{Buck Focusing Solenoid} \qquad \qquad & amps	\quad & 478 \\
 			Matching Solenoid &	amps	& 197	  \\

### 2019-01-31 paper/submission/theor-experiment.tex
adding Linda's edits to pg 23, end of tba section Added beam sizes at the pets location, reference to thesis

@@
     100  &  0.859753 & $3.076 \times 10^{-1}$ \\
-   % \noalign{\smallskip}\hline\noalign{\smallskip}
     200  &  0.784943 & $1.938 \times 10^{-1}$ \\
@@
 		\label{extable}
-		\begin{tabular*}{0.48\textwidth}{l ccc}
-			& Gene Mutation Probability & Recombination Probability & Number of completed generations \\
+		\begin{tabular*}{0.48\textwidth}{l c|c|c}
+			& Gene Mutation \qquad& Recombination \qquad& Number of completed\vspace{-0.75em}\\
+			& Probability \qquad& Probability \qquad&  generations \\
+			\midrule
 			ex-1 &  0.1  & 0.9  &  96 \\
@@
 see Fig.~\ref{awa-tba}.  
-
 The objectives include: $\varepsilon_{x}\left(s = s_1\right)\text{, } \varepsilon_{x}\left(s = s_2\right)$, $\text{rms}_{s}\left(s = s_1\right)\text{, and }  \text{rms}_{s}\left(s = s_2\right)$. 
-The OPAL input file for ex-3, and subsequent optimization runs in this paper, can be found at in following repository: 
-\url{https://github.com/nneveu/awa-tba}.
+The OPAL input file for these cases and all subsequent optimization runs in this paper, 
+can be found at in following repository: \url{https://github.com/nneveu/awa-tba}.
 
@@
 Overall this solution is satisfactory, and meets all requirements for the new TBA beamline at the AWA.
-The PETS (Power Extractor and Transfer Structure) is the physical device putting the tightest constraints on the beam parameters.  
-At this location the aperture diameter is \SI{17.6}{mm}, and the desired bunch length is \SI{1.5}{m}.  
-The optimization meets all requirements in general; and specifically at the PETS location, 
-the beam parameters are $\sigma_x=\sigma_y=2.5$mm, with aa bunch length of XXXXX.
+A Power Extractor and Transfer Structure (PETS) will be located after the septum and quadrupoles in Fig.~\ref{awa-tba}.
+This device is putting the tightest constraints on the beam parameters.  
+The aperture diameter is \SI{17.6}{mm}, and bunch length should be below \SI{2}{mm}
+to facilitate large power extraction~\cite{PETSeq}.
 
- Although the simulation results at the PETS location cannot yet be checked since the beamline is not yet completely installed, some checks have been possible for the partially completed beamline.
-Simulations of the partial beamline have been done with good agreement to measurement.
-For example, beam images were taken on the YAG screen located downstream of the kicker and the extracted beam sizes at different kicker angles compared to simulation.
-Measurements showed an asymmetry between the x and y beam size that was also shown in simulation (see Fig.
-).
-This is likely due to the gun voltage since that had the most noticeable impact on the simulated asymmetry (the best match was at a gun voltage of 55 MV/m).
-When it becomes possible to test the complete simulation solution, it is expected that there will not be perfect agreement with simulation; for example there may be errors in the fields of beamline elements.
-However, the simulation can be a tool to track down the source of discrepancies, such as understanding the effect of the gun field on the beam symmetry.
+The optimization results shown here were used in part to meet all TBA requirements. 
+After adjustments to include 3D rf field maps and CSR in the dipoles~\cite{neveuthesis}, 
+the max beamsizes at the PETS location were below \SI{10}{mm} with a bunch length of $rms_z=\SI{1.6}{mm}$. 
+Although the simulation results at the PETS location cannot yet be verified, since the beamline is not yet completely installed, 
+some checks have been possible for the partially completed beamline.  
+Simulations of the partial beamline have been done.
+For example, beam images were taken on the YAG screen located downstream of the kicker and 
+the extracted beam sizes at different kicker angles compared to simulation~\cite{neveuthesis}.  
+When it becomes possible to test the complete simulation solution, it is expected that there will not be perfect agreement with simulation;
+for example there may be errors in the fields of beamline elements.  However, the simulation can be a tool to track down the source of
+discrepancies, such as understanding the effect of the gun field on the beam symmetry.  
 More importantly, the optimization results should provide significant improvement in efficiency for achieving a good operational regime.

### 2019-01-31 paper/submission/ZW10157-response-1.tex
added Linda's edit to TBA section

@@
 	Several changes were made in the paper to address this concern. 
-	 abstract to explain the AWA problem. 
+	The abstract was edited to explain the AWA problem. 
 	Here is the new abstract in it's entirety:
@@
 parallel, and fully 3D.
+
+The following information was added on lines 479-496:
+
+Overall this solution is satisfactory, and meets all requirements for the new TBA beamline at the AWA.
+A Power Extractor and Transfer Structure (PETS) will be located after the septum and quadrupoles in Fig. 7.
+This device is putting the tightest constraints on the beam parameters.  
+The aperture diameter is 17.6 mm and bunch length should be below 2 mm
+to facilitate large power extraction [new ref here].
+
+The optimization results shown here were used in part to meet all TBA requirements. 
+After adjustments to include 3D rf field maps and CSR in the dipoles[new ref here] 
+the max beamsizes at the PETS location were below 10 mm with a bunch length of rmsz=1.6 mm. 
+Although the simulation results at the PETS location cannot yet be verified, since the beamline is not yet completely installed, 
+some checks have been possible for the partially completed beamline.  
+Simulations of the partial beamline have been done.
+For example, beam images were taken on the YAG screen located downstream of the kicker and 
+the extracted beam sizes at different kicker angles compared to simulation [new ref here].  
+When it becomes possible to test the complete simulation solution, it is expected that there will not be perfect agreement with simulation;
+for example there may be errors in the fields of beamline elements.  However, the simulation can be a tool to track down the source of
+discrepancies, such as understanding the effect of the gun field on the beam symmetry.  
+More importantly, the optimization results should provide significant improvement in efficiency for achieving a good operational regime.
 

### 2019-01-31 paper/submission/theor-experiment.tex
new bib, small changes to paper

@@
 This problem encompasses high dimensionality 
-and nonlinear effects such as space charge. There is no existing information
-that accurately predicts optimized parameters for this beam line. 
-This work is meaningful in that it will guide future operations at the AWA.
+and nonlinear effects such as space charge. 
+Using this model it was possible to find good solutions that meet the 
+operational goals for the new beamline.  One of these solutions is 
+presented in the next section.
 

### 2019-02-01 paper/submission/ZW10157-response-1.tex
lot's of small edits, mostly commas

@@
 
-{\bf Our response:} {\color{blue} A line XX has been added indicating this capability in GPT too.}
+{\bf Our response:} {\color{blue} Line 123 in the new manuscript indicates this capability is in GPT too.}
 
@@
 {\bf Our response:} {\color{blue} 
-	Respectfully, we point out Referee A's comment that 
-	``Computing and algorithms'' is listed under PRAB's scope. 
-	However, for those interested in physics and not implementation details (i.e. user of code not developer), 
-	we had hoped the AWA optimization problem would 
-	provide a meaningful and tangible use case for the framework.
-	It seems we did not present that part of the paper strongly enough. 
-	We hope some of the additions above have helped in this area.
-	However, would also like to keep some computational details for those who 
-	may be interested in code development specifically for accelerator optimization.
+	Additions were made to the text to enhance the discussion of the 
+	physical problem and extend the discussion of the results.  For example, 
+	the abstract was extended, and additional discussion was added to the 
+	optimization results section. The code snippets were moved out of the 
+	main body of the paper.  However, we would also like to keep some 
+	computational details for those who may be interested in code 
+	development specifically for accelerator optimization.  Hopefully this 
+	is justified since "Computing and algorithms" is listed under PRAB's 
+	scope.
 }
@@
 {\bf Our response: }{\color{blue} 	
-	We hope the additions above are addressing these issues. }
+	We hope the additions above (including response to Ref. A) are addressing these issues.}
 

### 2019-02-01 paper/submission/prab.tex
new bib, small changes to paper
lot's of small edits, mostly commas

@@
   of an additional beamline (this is now in progress).  The high charge drive beam, well into the space charge regime, must be threaded
-  through small aperture (\SI{17.6}{mm}) decelerating structures.  
+  through small aperture (17.6 mm) decelerating structures.  
   In addition, the bunch length must be sufficiently short to maximize power generation in the decelerator.  
@@
 empirical tuning by operators is a common method used at many research facilities.
-When the beam dynamics is non-linear, as is the case with space charge, 
+When the beam dynamics is nonlinear, as is the case with space charge, 
 simple and fast models are applicable only in a very restricted manner. 
-When it comes to multi-objective optimization, the situation is even more complicated.
+This further complicates any mult-objective optimization by complicating the model. 
 In order to be able to reliably identify optimal configurations of
@@
   problems to automate the investigation for an optimal set of tuning parameters.
-  This approach has been used in the past with much success~\cite{hofler13,bazarov05,yrss:09,jefferson,gull1,gull2}.
+  This approach has been used in the past with much success~\cite{hofler13,bazarov05,yrss:09,jefferson,gull1,gull2,marija}.
 The difference here being the implementation and application to a 
@@
 and high charge (up to 100 nC), and at high charge strong nonlinearities
-require a full 3D space charge approach in simulations for modeling.  
+require a full 3D space charge approach in simulations.  
 Finding optics solutions in this regime, especially when
@@
         with the optimization problem set as 
-        the high charge photoinjector at the Argonne Wakefield Accelerator (AWA). 
+        the high charge photoinjector at the AWA. 
 \end{enumerate}
@@
 Often, conflicting objectives are encountered, and this complicates the concept of
-  optimality. \textit{Pareto optimality} is often used in such situations [].
+  optimality. \textit{Pareto optimality} is often used in such situations.
 The set of Pareto optimal points forms the Pareto front or
@@
   representing one location in the search space.
-In a next step the population is processed by the selector
+In the next step, the population is processed by the selector
   determining the $k$ fittest individuals according to their fitness values.
@@
   research and industry.
-The simulation and optimization problems arising in such problems are in
+These simulation and optimization problems are in
   general very big and computationally demanding.
@@
   e.g.\ only providing evolutionary algorithms as optimizers.
-Users can merely specify optimization problems, but cannot change the
+Users can specify optimization problems, but cannot change the
   optimization algorithm.
@@
   optimization problems that should be handled by such a general framework.
-As an example, it is shown how \textsc{Pisa} \cite{pisa}, an existing evolutionary
+As an example, it is shown how \textsc{Pisa}~\cite{pisa}, an existing evolutionary
   algorithm library, was integrated with ease.
@@
   MPI processes to exploit parallelism.
-As shown in Fig.~\ref{fig:opt-framework-layout} the \textsc{Pilot} is used
+As shown in Fig.~\ref{fig:opt-framework-layout}, the \textsc{Pilot} is used
   to coordinate all ``information requests'' between the \textsc{Optimizer}
@@
 
-After a process gets appointed a role it starts a polling loop asynchronously
-  checking for appropriate incoming requests.
+After a process gets appointed a role, it starts a polling loop to asynchronously
+  check for appropriate incoming requests.
 To that end a \textsc{Poller} interface helper class has been introduced.
@@
 A special set of communicator groups serves as communication channels to the
-  \textsc{Pilot} and its job queue and if existing to processes supporting the
+  \textsc{Pilot}, its job queue, and processes supporting the
   \textsc{Optimizer} component.
@@
 
-In most cases forward solver implementations are simple wrappers to run
+In most cases, forward solver implementations are simple wrappers to run
   an existing ``external'' simulation code using a set of design variables as
-  input. In case of the OPAL integration, basically the \texttt{main} function is
+  input. In the case of the OPAL integration, the \texttt{main} function is
   playing the role of the ``forward solver''. To underline the general nature of our approach, 
@@
 
-First, upon receiving a new job, the \texttt{Worker} will call the
-  \texttt{run} method on the \textsc{Simulation} implementation.
+First, upon receiving a new job, the \texttt{Worker} will call the \texttt{run} 
+method on the \textsc{Simulation} implementation.
 This expects the \textsc{Simulation} implementation to run the simulation in a 
@@
 \textsc{Simulation} prepares the result data, e.g. parsing output files,
-  and stores the requested information in a \texttt{reqVarContainer\_t} data
-  structure.
-Finally, the results obtained with \texttt{getResults} are sent to the
-  \textsc{Pilot}.
-As before, the serialized data is exchanged using MPI point-to-point
-  communication using a specific set of communicators.
+and stores the requested information in a \texttt{reqVarContainer\_t} data structure.
+Finally, the results obtained with \texttt{getResults} are sent to the \textsc{Pilot}. 
+As before, the serialized data is exchanged using MPI point-to-point communication using a specific set of communicators.
 
@@
 
-We aimed at an easy and expressive way for users to specify multi-objective
-  optimization problems.
-Following the principle of keeping metadata (optimization and simulation
-  input data) together, we decided to embed the optimization problem
-  specification in the simulation input file by prefixing it with special
-  characters, e.g. as annotations prefixed with a special character.
-In some cases it might not be possible to annotate the simulation input file.
-By providing an extra input file parser, optimization problems can be read
-  from stand-alone files.
-
+We aimed at an easy and expressive way for users to specify multi-objective optimization problems.
+Following the principle of keeping metadata (optimization and simulation input data) together, 
+we decided to embed the optimization problem specification in the simulation input file by 
+prefixing it with special characters, e.g. as annotations prefixed with a special character.
+In some cases, it might not be possible to annotate the simulation input file.
+By providing an extra input file parser, optimization problems can be read from stand-alone files.
 To allow arbitrary constraints and objective expressions, such as
@@
 to booleans or floating point values.
-The parse tree, also denoted abstract syntax tree (AST), is constructed
-  recursively while an expression is parsed.
-Upon evaluation, all unknown variables are replaced with values, either
-  obtained from simulation results or provided by other subtrees in the AST.
+The parse tree, also denoted abstract syntax tree (AST), is constructed recursively while an expression is parsed.
+Upon evaluation, all unknown variables are replaced with values, 
+either obtained from simulation results or provided by other subtrees in the AST.
 In this stage, the AST can be evaluated bottom-up and the desired result is
@@
   simple mechanism to define and call custom functions in expressions was introduced.
-Using simple functors, e.g. as the one shown in Listing 4 to compute an
+Using simple functors, e.g. as the one shown in Listing 4, to compute an
   average over a set of data points, enriches expressions with custom
@@
   with increasing number of workers that are attached to one master process.
-Clearly, the limiting factor is the number of outgoing links of a node in the
-  network topology and already for a few workers the links surrounding a
-  master process are subject to congestions.
+The limiting factor is the number of outgoing links of a node in the
+  network topology. For a few workers, the links surrounding a
+  master process are subject to congestion.
 This effect is amplified further by large message sizes.
@@
 This limits the number of messages sent over the already heavily used links
-  surrounding the master node and at the same time helps to prevent the use of
-  global communication.
-Using information about the interconnection network topology and the
-  application communication graph the task of assigning roles helps to further
+surrounding the master node and helps to prevent the use of
+global communication. Using information about the interconnection network topology and the
+application communication graph, the task of assigning roles helps to further
 improve the parallel performance.
@@
 The framework contains a wrapper implementing the API mentioned in
-  Listing 3 for using \textsc{OPAL} \cite{opal} as the forward solver.
+  Listing 3 for using \textsc{OPAL}~\cite{opal} as the forward solver.
 \textsc{OPAL} provides different trackers for cyclotrons and linear
   accelerators with satisfactory parallel performance. 
-
-With access to the \textsc{OPAL} forward solver the framework is able to
+With access to the \textsc{OPAL} forward solver, the framework is able to
   tackle a multitude of optimization problems arising in the domain of
@@
 
-If the objectives and constraints are simple arithmetical expressions, the
-  \texttt{FunctionEvaluator} simulator can be used.
-Using functors and the default expression primitives already powerful
-  multi-objective optimization problems can be specified, i.e.\ the benchmark
-  problem presented in \cite{hbwh:05}:
+If the objectives and constraints are simple arithmetical expressions, 
+the \texttt{FunctionEvaluator} simulator can be used.
+Using functors and the default expression primitives, 
+multi-objective optimization problems can be specified, 
+i.e.\ the benchmark problem presented in \cite{hbwh:05}:
 %
 
-%\begin{strip}
 	\begin{widetext}

### 2019-02-01 paper/submission/theor-experiment.tex
lot's of small edits, mostly commas

@@
 
-In this section a numerical results of the validation benchmark and
-  optimization of a photoinjector operated in the space charge dominated regime is presented.
+In this section numerical results of the validation benchmark and optimization 
+of a photoinjector operated in the space charge dominated regime is presented.
 
@@
 
-To ensure that the optimizer works correctly the benchmark
+To ensure that the optimizer works correctly, the benchmark
   problem (\ref{eqn:bench}) was solved.
-To that end, we use a metric for comparing the quality of a Pareto
-  front.
+To that end, we use a metric for comparing the quality of a Pareto front.
 Given a point in the Pareto set, we compute the $m$ dimensional volume (for
@@
 Figure~\ref{fig:pisa_bench} and the corresponding hypervolume values in
-  Table~\ref{tbl:bench_rms_error}, show expected convergence.
+  Table~\ref{tbl:bench_rms_error} show expected convergence.
 The reference Pareto front is clearly very well approximated.
@@
   \begin{tabular}{c|c|c}
-    \hline\noalign{\smallskip}
+	\cline{1-3}
     tot.\ function  & hypervolume & relative error\\
     evaluations    & & \\
-    \noalign{\smallskip}\hline\noalign{\smallskip}
+	\cline{1-3}
     100  &  0.859753 & $3.076 \times 10^{-1}$ \\
@@
     1100 &  0.657615 & $1.749 \times 10^{-4}$ \\
-    \noalign{\smallskip}\hline
+	\cline{1-3}
   \end{tabular}
@@
 See low fidelity plot in Fig.~\ref{tstep} for $dT=$\num{5E-11} results.  
-
 \begin{table}%[h!]
@@
 		\begin{tabular*}{0.48\textwidth}{c|c|c|c}
-			\hline\noalign{\smallskip}
+	\cline{1-4}
 			Time Step, dT (s) \quad & Linac & Drift & Quadrupoles \\
-			\noalign{\smallskip}\hline\noalign{\smallskip}
+	\cline{1-4}
 			$5 \times10^{-10}$  & \xmark & \xmark & \xmark \\
@@
 			$1 \times10^{-12}$  & \cmark & \cmark & \cmark \\
-			\noalign{\smallskip}\hline
+	\cline{1-4}
 		\end{tabular*}
@@
 	\centering
-	\includegraphics[width=\linewidth]{figures/timestep_comparison_paper}
+	\includegraphics[width=0.8\linewidth]{figures/timestep_comparison_paper}
 	\caption{Comparison of different fidelity models (dT stands for time step).}
@@
 \label{extable}
-		\begin{tabular*}{0.48\textwidth}{l c|c|c}
-			& Gene Mutation \qquad& Recombination \qquad& Number of completed\vspace{-0.75em}\\
-			& Probability \qquad& Probability \qquad&  generations \\
-			\midrule
+\begin{tabular}{c|c|c|c}
+\cline{1-4}
+& Gene Mutation \qquad& Recombination \qquad & Number of completed \vspace{-0.75em}\\
+Experiment & Probability & Probability &  generations \\ 
+\cline{1-4}
 ex-1 &  0.1  & 0.9  &  96 \\
@@
 ex-4 &  0.01 & 0.09 &  95 \\ 
-		\end{tabular*}
+\cline{1-4}
+\end{tabular}
 \end{center}
@@
 		\label{tab:designopt}   
-		\begin{tabular}{lcc}
-			\toprule
+		\begin{tabular}{l|c|c}
+			\cline{1-3}
 			\textbf{Design Variable} \qquad \qquad & \textbf{Unit}	\quad&  \textbf{Value}  \\ 
-			\midrule
+			\cline{1-3}
 			{Buck Focusing Solenoid} \qquad \qquad & amps	\quad & 478 \\
@@
 			Bunch Length & mm 		& 1.5	\\
-			\bottomrule
+			\cline{1-3}
 		\end{tabular}

### 2019-02-01 paper/submission/prab.tex
Removed code listing 1 and 4

@@
 The framework was implemented in \texttt{C++}, utilizing features like template
-  parameters to specify the composition of the framework (shown in Listing 1).
-
-%\noindent\begin{minipage}{0.48\textwidth}
-%\noindent
-\begin{code}[Assembling the optimizer \\ from components]
-typedef InputFileParser	Input_t;
-typedef PisaVariator	Opt_t;
-typedef OpalSimulation	Sim_t;
-
-typedef Pilot< Input_t, Opt_t, Sim_t > Pilot_t;
-\end{code}
-%\end{minipage}
-The framework provides ``default'' implementations that can be controlled via
-  command line options.
+parameters to specify the composition of the framework.
+``Default'' implementations are provided that can be controlled via command line options.
 Due to its modular design, all components can be completely customized.
@@
   simple mechanism to define and call custom functions in expressions was introduced.
-Using simple functors, e.g. as the one shown in Listing 4, to compute an
+Using simple functors, to compute an
   average over a set of data points, enriches expressions with custom
@@
   booleans, strings or floating point values.
-
-\begin{code}[Simple Average Functor]
-struct avg {
-
-    double operator()(
-      client::function::arguments_t args) const {
-
-        double limit = boost::get<double>(args[0]);
-        std::string filename =
-          boost::get<std::string>(args[1]);
-
-        double sum = 0.0;
-        for(int i = 0; i < limit; i++)
-            sum += getDataFromFile(filename, i);
-
-        return sum / limit;
-    }
-};
-\end{code}
 
@@
 search for the Pareto optimal solutions.
-Finally, combining the presented multi-objective optimization framework with
-  a physicist long standing experience in the field provides a solid basis
-  for better understanding and improving the decision making process in the
-  design and operation of particle accelerators.
+Finally, combining a multi-objective optimization framework such as 
+the one presented with practical experience in the field should expedite 
+the decision making process in the design and operation of particle 
+accelerators.
 

### 2019-02-01 paper/submission/ZW10157-response-1.tex
adding Linda's last edits

@@
 
-The following information was added on lines 479-496:
+The following information was added on lines 401-404:
+
+These structures are called Power Extractor and Transfer Structure (PETS), 
+and will be located after the septum and quadrupoles in Fig.~7.
+This device is putting the tightest constraints on the beam parameters.  
+The aperture diameter is 17.6 mm and the bunch length should be below 2 mm
+to facilitate large power extraction~[new ref here]
+
+The following information was added on lines 457-475:
 
 Overall this solution is satisfactory, and meets all requirements for the new TBA beamline at the AWA.
-A Power Extractor and Transfer Structure (PETS) will be located after the septum and quadrupoles in Fig. 7.
-This device is putting the tightest constraints on the beam parameters.  
-The aperture diameter is 17.6 mm and bunch length should be below 2 mm
-to facilitate large power extraction [new ref here].
 
-The optimization results shown here were used in part to meet all TBA requirements. 
-After adjustments to include 3D rf field maps and CSR in the dipoles[new ref here] 
-the max beamsizes at the PETS location were below 10 mm with a bunch length of rmsz=1.6 mm. 
-Although the simulation results at the PETS location cannot yet be verified, since the beamline is not yet completely installed, 
-some checks have been possible for the partially completed beamline.  
-Simulations of the partial beamline have been done.
-For example, beam images were taken on the YAG screen located downstream of the kicker and 
-the extracted beam sizes at different kicker angles compared to simulation [new ref here].  
-When it becomes possible to test the complete simulation solution, it is expected that there will not be perfect agreement with simulation;
-for example there may be errors in the fields of beamline elements.  However, the simulation can be a tool to track down the source of
-discrepancies, such as understanding the effect of the gun field on the beam symmetry.  
-More importantly, the optimization results should provide significant improvement in efficiency for achieving a good operational regime.
+The TBA line under construction includes a kicker and septum combination to route one bunch train to its own PETS, 
+while the other bunch train is undeflected and goes to a different PETS.  
+The optimization results shown here start at the gun and go through to the first quadrupole after the septum (s3=19.4~(m)).  
+These results were used as the basis for the full solution up to the PETS [new ref here].
+After adjustments to include 3D rf field maps and CSR in the dipoles~[new ref here], 
+the maximum beam sizes at the PETS location were below 10mm with a bunch length of rmsz = 1.6mm.  
+Although the simulation results at the PETS location cannot yet be verified, 
+since the beamline is not yet completely installed, some checks have been possible for the partially completed beamline. 
+For example, beam images were taken on the YAG screen located downstream of the kicker, 
+and it was found that the extracted beam sizes at different kicker angles 
+were in good agreement with simulation results~[new ref here]. 
+When it becomes possible to test the complete simulation solution, 
+it is expected that there will not be perfect agreement with simulation; 
+for example there may be errors in the fields of beamline elements. 
+However, the simulation can be a tool to track down the source of discrepancies, 
+such as understanding the effect of the gun field on the beam symmetry. 
+More importantly, the optimization results should provide significant improvement 
+in efficiency for achieving a good operational regime.
 

### 2019-02-01 paper/submission/prab.tex
adding Linda's last edits

@@
 The TBA beam line presented is currently being installed at the AWA.
-Once installation is complete, 
-the results shown here will guide future experiments at the AWA.
+Once installation is complete, the results shown here will guide future experiments at the AWA.
 
@@
 Even in cases where the mathematical model of the forward solver is not known
-exactly, fixed or on the real time measurements can be used to guide the
+exactly, fixed or real time measurements can be used to guide the
 search for the Pareto optimal solutions.
-Finally, combining a multi-objective optimization framework such as 
-the one presented with practical experience in the field should expedite 
-the decision making process in the design and operation of particle 
-accelerators.
+Finally, combining a multi-objective optimization framework, such as 
+the one presented, with practical experience in the field should expedite 
+the decision making process in the design and operation of particle accelerators.
 

### 2019-02-01 paper/submission/theor-experiment.tex
adding Linda's last edits

@@
  computed by sampling the solution provided in~\cite{hbwh:05}.
-
 \begin{figure}
@@
 \end{figure}
-
 \begin{table}%[h!]
@@
 \end{table}
-
 Table~\ref{tbl:bench_rms_error} shows satisfactory
@@
 \subsection{AWA Photoinjector Optimization} \label{awaproblem}
-Next the optimization framework is applied to a high charge beam line
+Next the optimization framework is applied to the high charge beam line
  at the Argonne Wakefield Accelerator (AWA) facility. 
 The goal of this optimization is to produce beams of electrons that meet 
-design specifications; this includes number of particles (charge), energy, and particle distribution (characterized by beam sizes and energy spread).
+design specifications; this includes number of particles (charge), energy, 
+and particle distribution (characterized by beam sizes and energy spread).
 As shown in Fig.~\ref{awa-linac}, the installed portion of the the 
@@
 followed by four quadrupoles and a stripline kicker. 
-The charge of interest, 40 nC, is needed for Two Beam 
-Acceleration (TBA) 
-experiments performed at AWA \cite{gai_power_jing_2012,JING201872}, 
+The charge of interest, 40 nC, is needed for two beam acceleration (TBA) 
+experiments performed at the AWA~\cite{gai_power_jing_2012,JING201872}, 
 which motivates this work. 
@@
 Note, a smaller time step, \num{1E-13}, is always used in the gun where the 
-beam has low energy and changing rapidly.
-%A summary of the parameters used is listed in Table \ref{fidelity}.
-
-\begin{figure}%[h]
+beam has low energy and is changing rapidly.
+\begin{figure}
 	\centering
@@
 With computational and hyper parameters set, 
-the full optimization problem of interest is explored.
+the optimization problem of interest is explored.
 The objectives (beam sizes and energy spread) are calculated at 
@@
 which ensures better transmission through the wakefield structures downstream.
+These structures are called Power Extractor and Transfer Structure (PETS), 
+and will be located after the septum and quadrupoles in Fig.~\ref{awa-tba}.
+This device is putting the tightest constraints on the beam parameters.  
+The aperture diameter is \SI{17.6}{mm} and the bunch length should be below \SI{2}{mm}
+to facilitate large power extraction~\cite{PETSeq}.   
 Less divergence in the beam (lower transverse momentum spread) 
@@
 designed for TBA is related to the bunch length \cite{JING201872,PETSeq}.
-
 Eqs.~\ref{eq:awa:c1} to \ref{eq:awa:c3} 
@@
 At the AWA, there is some room in the beam pipe to allow the y dimension to grow, but round beams are preferred.
-
 Equations (\ref{eq:awa:firstconstr}) to
@@
 laser radius, gun phase, and linac cavity phases (in that order). 
-These are parameters in the simulation 
-that must be defined, but do not vary during the optimization.
-The AWA design variables, objectives, and constraints in the OPAL input file as shown in
-the repository.
-%\vspace{0.2cm}
+These are parameters in the simulation that must be defined, but do not vary during the optimization.
+For setup of the AWA design variables, objectives, and constraints in the OPAL input file, 
+refer to the the repository above.
 
@@
 defined in Eqs. (\ref{eq:awa:p1}) to (\ref{eq:awa:p4}). 
-The location at the entrance of the kicker is $s_1=16.45$~meters, 
-and the objectives are optimized at location $s_3=19.4$~meters. 
+The location at the entrance of the kicker is $s_1=16.45$~(m), 
+and the objectives are optimized at location $s_3=19.4$~(m). 
 This is the entrance to the fifth quad in the beam line. 
@@
 With the time steps and hyper parameters set by the work in Section \ref{awa:subsection:test}, 
-the full optimization problem described in \ref{awaproblem} was run for 200 generations.
+the optimization problem described in \ref{awaproblem} was run for 200 generations.
 The initial number of individuals was fixed at 656, 
@@
 a large population size that would fit evenly on these resources was chosen. 
-Again, the location of optimization is $s_3=19.4$ [m]. 
+Again, the location of optimization is $s_3=19.4$~(m). 
 \begin{figure}
@@
 (i.e. $rms_y$ larger than the beam pipe).
-In the case of bunch length, there are not many options to choose from.
-
+In the case of bunch length, there are not many options to choose from, as the phase was not varied.
 With these observations in mind, several beam parameters corresponding to
@@
 A select result is shown in Fig.~\ref{fig:stat}.  
-The maximum beam sizes are well below the beam pipe aperture limits as shown in Fig.~\ref{fig:stat}.
-The solution is nearly round, which will increase changes of keeping the beam nearly round
+The maximum beam sizes are well below the beam pipe aperture limits, also shown in Fig.~\ref{fig:stat}.
+The solution is nearly round, which will increase chances of keeping the beam nearly round
 as it travels to the last triplet in Fig.~\ref{awa-tba}.
 Overall this solution is satisfactory, and meets all requirements for the new TBA beamline at the AWA.
-A Power Extractor and Transfer Structure (PETS) will be located after the septum and quadrupoles in Fig.~\ref{awa-tba}.
-This device is putting the tightest constraints on the beam parameters.  
-The aperture diameter is \SI{17.6}{mm}, and bunch length should be below \SI{2}{mm}
-to facilitate large power extraction~\cite{PETSeq}.
 
-The optimization results shown here were used in part to meet all TBA requirements. 
+The TBA line under construction includes a kicker and septum combination to route one bunch train to its own PETS, 
+while the other bunch train is undeflected and goes to a different PETS.  
+The optimization results shown here start at the gun and go through to the first quadrupole after the septum ($s_3=19.4$~(m)).  
+These results were used as the basis for the full solution up to the PETS~\cite{neveuthesis}.
 After adjustments to include 3D rf field maps and CSR in the dipoles~\cite{neveuthesis}, 
-the max beamsizes at the PETS location were below \SI{10}{mm} with a bunch length of $rms_z=\SI{1.6}{mm}$. 
-Although the simulation results at the PETS location cannot yet be verified, since the beamline is not yet completely installed, 
-some checks have been possible for the partially completed beamline.  
-Simulations of the partial beamline have been done.
-For example, beam images were taken on the YAG screen located downstream of the kicker and 
-the extracted beam sizes at different kicker angles compared to simulation~\cite{neveuthesis}.  
-When it becomes possible to test the complete simulation solution, it is expected that there will not be perfect agreement with simulation;
-for example there may be errors in the fields of beamline elements.  However, the simulation can be a tool to track down the source of
-discrepancies, such as understanding the effect of the gun field on the beam symmetry.  
-More importantly, the optimization results should provide significant improvement in efficiency for achieving a good operational regime.
+the maximum beam sizes at the PETS location were below 10mm with a bunch length of rmsz = 1.6mm.  
+Although the simulation results at the PETS location cannot yet be verified, 
+since the beamline is not yet completely installed, some checks have been possible for the partially completed beamline. 
+For example, beam images were taken on the YAG screen located downstream of the kicker, 
+and it was found that the extracted beam sizes at different kicker angles 
+were in good agreement with simulation results~\cite{neveuthesis}. 
+When it becomes possible to test the complete simulation solution, 
+it is expected that there will not be perfect agreement with simulation; 
+for example there may be errors in the fields of beamline elements. 
+However, the simulation can be a tool to track down the source of discrepancies, 
+such as understanding the effect of the gun field on the beam symmetry. 
+More importantly, the optimization results should provide significant improvement 
+in efficiency for achieving a good operational regime.
 

### 2019-02-01 paper/submission/prab.tex
fixing bib for resubmission
adding bib to tex file and moving figures

@@
 	\center
-\includegraphics[width=0.5\textwidth]{figures/opt-framework_code}
+\includegraphics[width=0.5\textwidth]{opt-framework_code}
 \caption{Multi-objective framework: the pilot (master) solves the
@@
     \centering
-    \includegraphics[width=0.6\textwidth]{figures/ga_explained_big}
+    \includegraphics[width=0.6\textwidth]{ga_explained_big}
   \caption{Schematic view of interplay between selector and variator. The
@@
   \centering
-  \includegraphics[width=0.7\linewidth]{figures/opt-framework-layout}
+  \includegraphics[width=0.7\linewidth]{opt-framework-layout}
   \caption{Schematic view of messages passed within the network between the
@@
 	\end{widetext}
-%\end{strip}
 
@@
 
-% AA: this is too much for Phys Rev. AB
-
-% \appendix
-
-%\section{Forward Solver Implementation}
-%
-%A simple implementation, e.g.\ using a Python forward solver, is given below
-%  in Listing 6.
-%We assume the Python script executes a simulation and dumps results in the
-%  \textsc{SDDS} file format~\cite{borl:00}.
-%Utility classed are used to parse the result data and fill the appropriate
-%  structures returned to the optimizer algorithm.
-%
-%\begin{code}[Simple Simulation Wrapper]
-%#include <map>
-%#include <string>
-%#include <vector>
-%
-%#include "Util/Types.h"
-%#include "Util/CmdArguments.h"
-%#include "Simulation/Simulation.h"
-%
-%#include "boost/smart_ptr.hpp"
-%
-%class SimpleSimulation : public Simulation {
-%
-%public:
-%
-%    SimpleSimulation(Expressions::Named_t objectives,
-%                     Expressions::Named_t constraints,
-%                     Param_t params, std::string name, MPI_Comm comm,
-%                     CmdArguments_t args);
-%
-%    ~SimpleSimulation();
-%
-%    /// Calls simulation through Python wrapper and returns when simulation
-%    /// has either failed or finished.
-%    void run() {
-%        // user implements wrappers
-%        prepare_input_file();
-%        run_python_simulation();
-%    }
-%
-%    /// Parse SDDS stat file and build up requested variable dictionary.
-%    void collectResults(){
-%
-%        Expressions::Named_t::iterator it;
-%        for(it = objectives_.begin(); it != objectives_.end(); it++) {
-%
-%            Expressions::Expr_t *objective = it->second;
-%
-%            // find out which variables we need in order to evaluate the
-%            // objective
-%            variableDictionary_t variable_dictionary;
-%            std::set<std::string> req_vars = objective->getReqVars();
-%
-%            if(req_vars.size() != 0) {
-%
-%                boost::scoped_ptr<SDDSReader> sddsr(new SDDSReader(fn));
-%
-%                try {
-%                    sddsr->parseFile();
-%                } catch(OptPilotException &e) {
-%                    std::cout << "Exception while parsing SDDS file: "
-%                        << e.what() << std::endl;
-%                    break;
-%                }
-%
-%                // get all the required variable values from the stat file
-%                foreach(std::string req_var, req_vars) {
-%                    if(variable_dictionary.count(req_var) == 0) {
-%
-%                        try {
-%                            double value = 0.0;
-%                            sddsr->getValue(1 /*atTime*/, req_var, value);
-%                            variable_dictionary.insert(
-%                                std::pair<std::string, double>(req_var, value));
-%                        } catch(OptPilotException &e) {
-%                            std::cout << "Exception while getting value "
-%                                      << "from SDDS file: " << e.what()
-%                                      << std::endl;
-%                        }
-%                    }
-%                }
-%            }
-%
-%            // and evaluate the expression using the built dictionary of
-%            // variable values
-%            Expressions::Result_t result =
-%                objective->evaluate(variable_dictionary);
-%
-%            std::vector<double> values;
-%            values.push_back(boost::get<0>(result));
-%            bool is_valid = boost::get<1>(result);
-%
-%            reqVarInfo_t tmps = {EVALUATE, values, is_valid};
-%            requestedVars_.insert(
-%                std::pair<std::string, reqVarInfo_t>(it->first, tmps));
-%
-%        }
-%    }
-%
-%    /// returns container containing all requested variables with results
-%    reqVarContainer_t getResults() { return requestedVars_; }
-%
-%private:
-%
-%    /// holds solutions returned to the optimizer
-%    reqVarContainer_t requestedVars_;
-%
-%    Expressions::Named_t objectives_;
-%    Expressions::Named_t constraints_;
-%
-%    MPI_Comm comm_;
-%};
-%
-%#endif
-%\end{code}
-
-\bibliography{paper}
-
+%\bibliography{paper}
+\providecommand{\SortNoop}[1]{}
+\begin{thebibliography}{37}%
+	\makeatletter
+	\providecommand \@ifxundefined [1]{%
+		\@ifx{#1\undefined}
+	}%
+	\providecommand \@ifnum [1]{%
+		\ifnum #1\expandafter \@firstoftwo
+		\else \expandafter \@secondoftwo
+		\fi
+	}%
+	\providecommand \@ifx [1]{%
+		\ifx #1\expandafter \@firstoftwo
+		\else \expandafter \@secondoftwo
+		\fi
+	}%
+	\providecommand \natexlab [1]{#1}%
+	\providecommand \enquote  [1]{``#1''}%
+	\providecommand \bibnamefont  [1]{#1}%
+	\providecommand \bibfnamefont [1]{#1}%
+	\providecommand \citenamefont [1]{#1}%
+	\providecommand \href@noop [0]{\@secondoftwo}%
+	\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
+	\providecommand \@href[1]{\@@startlink{#1}\@@href}%
+	\providecommand \@@href[1]{\endgroup#1\@@endlink}%
+	\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
+		`\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
+	\providecommand \@@startlink[1]{}%
+	\providecommand \@@endlink[0]{}%
+	\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
+	\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
+	\providecommand \urlprefix  [0]{URL }%
+	\providecommand \Eprint [0]{\href }%
+	\providecommand \doibase [0]{http://dx.doi.org/}%
+	\providecommand \selectlanguage [0]{\@gobble}%
+	\providecommand \bibinfo  [0]{\@secondoftwo}%
+	\providecommand \bibfield  [0]{\@secondoftwo}%
+	\providecommand \translation [1]{[#1]}%
+	\providecommand \BibitemOpen [0]{}%
+	\providecommand \bibitemStop [0]{}%
+	\providecommand \bibitemNoStop [0]{.\EOS\space}%
+	\providecommand \EOS [0]{\spacefactor3000\relax}%
+	\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
+	\let\auto@bib@innerbib\@empty
+	%</preamble>
+\bibitem [{\citenamefont {Huang}(2018)}]{xiaobiao}%
+\BibitemOpen
+\bibfield  {author} {\bibinfo {author} {\bibfnamefont {X.}~\bibnamefont
+		{Huang}},\ }\href {\doibase 10.1103/PhysRevAccelBeams.21.104601} {\bibfield
+	{journal} {\bibinfo  {journal} {Phys. Rev. Accel. Beams}\ }\textbf {\bibinfo
+		{volume} {21}},\ \bibinfo {pages} {104601} (\bibinfo {year}
+	{2018})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Hofler}\ \emph {et~al.}(2013)\citenamefont {Hofler},
+	\citenamefont {Terzic}, \citenamefont {Kramer}, \citenamefont {Zvezdin},
+	\citenamefont {Morozov}, \citenamefont {Roblin}, \citenamefont {Lin},\ and\
+	\citenamefont {Jarvis}}]{hofler13}%
+\BibitemOpen
+\bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+		{Hofler}}, \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Terzic}},
+	\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Kramer}}, \bibinfo
+	{author} {\bibfnamefont {A.}~\bibnamefont {Zvezdin}}, \bibinfo {author}
+	{\bibfnamefont {V.}~\bibnamefont {Morozov}}, \bibinfo {author} {\bibfnamefont
+		{Y.}~\bibnamefont {Roblin}}, \bibinfo {author} {\bibfnamefont
+		{F.}~\bibnamefont {Lin}}, \ and\ \bibinfo {author} {\bibfnamefont
+		{C.}~\bibnamefont {Jarvis}},\ }\href {\doibase 10.1103/PhysRevSTAB.16.010101}
+{\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. ST Accel. Beams}\
+	}\textbf {\bibinfo {volume} {16}},\ \bibinfo {pages} {010101} (\bibinfo
+	{year} {2013})}\BibitemShut {NoStop}%
+%%CITATION = PRSTA,16,010101;%%
+\bibitem [{\citenamefont {Bazarov}\ and\ \citenamefont
+	{Sinclair}(2005)}]{bazarov05}%
+\BibitemOpen
+\bibfield  {author} {\bibinfo {author} {\bibfnamefont {I.~V.}\ \bibnamefont
+		{Bazarov}}\ and\ \bibinfo {author} {\bibfnamefont {C.~K.}\ \bibnamefont
+		{Sinclair}},\ }\href {\doibase 10.1103/PhysRevSTAB.8.034202} {\bibfield
+	{journal} {\bibinfo  {journal} {Phys. Rev. ST Accel. Beams}\ }\textbf
+	{\bibinfo {volume} {8}},\ \bibinfo {pages} {034202} (\bibinfo {year}
+	{2005})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Yang}\ \emph {et~al.}(2009)\citenamefont {Yang},
+	\citenamefont {Robin}, \citenamefont {Sannibale}, \citenamefont {Steier},\
+	and\ \citenamefont {Wan}}]{yrss:09}%
+\BibitemOpen
+\bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+		{Yang}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Robin}},
+	\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Sannibale}}, \bibinfo
+	{author} {\bibfnamefont {C.}~\bibnamefont {Steier}}, \ and\ \bibinfo {author}
+	{\bibfnamefont {W.}~\bibnamefont {Wan}},\ }\href {\doibase
+	10.1016/j.nima.2009.08.027} {\bibfield  {journal} {\bibinfo  {journal} {Nucl.
+			Instrum. Methods Phys. Res. A}\ }\textbf {\bibinfo {volume} {609}},\ \bibinfo
+	{pages} {50} (\bibinfo {year} {2009})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Terzi\ifmmode~\acute{c}\else \'{c}\fi{}}\ \emph
+	{et~al.}(2014)\citenamefont {Terzi\ifmmode~\acute{c}\else \'{c}\fi{}},
+	\citenamefont {Hofler}, \citenamefont {Reeves}, \citenamefont {Khan},
+	\citenamefont {Krafft}, \citenamefont {Benesch}, \citenamefont {Freyberger},\
+	and\ \citenamefont {Ranjan}}]{jefferson}%
+\BibitemOpen
+\bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.~c.~v.}\
+		\bibnamefont {Terzi\ifmmode~\acute{c}\else \'{c}\fi{}}}, \bibinfo {author}
+	{\bibfnamefont {A.~S.}\ \bibnamefont {Hofler}}, \bibinfo {author}
+	{\bibfnamefont {C.~J.}\ \bibnamefont {Reeves}}, \bibinfo {author}
+	{\bibfnamefont {S.~A.}\ \bibnamefont {Khan}}, \bibinfo {author}
+	{\bibfnamefont {G.~A.}\ \bibnamefont {Krafft}}, \bibinfo {author}
+	{\bibfnamefont {J.}~\bibnamefont {Benesch}}, \bibinfo {author} {\bibfnamefont
+		{A.}~\bibnamefont {Freyberger}}, \ and\ \bibinfo {author} {\bibfnamefont
+		{D.}~\bibnamefont {Ranjan}},\ }\href {\doibase 10.1103/PhysRevSTAB.17.101003}
+{\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. ST Accel. Beams}\
+	}\textbf {\bibinfo {volume} {17}},\ \bibinfo {pages} {101003} (\bibinfo
+	{year} {2014})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Gulliford}\ \emph {et~al.}(2016)\citenamefont
+	{Gulliford}, \citenamefont {Bartnik},\ and\ \citenamefont {Bazarov}}]{gull1}%
+\BibitemOpen
+\bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
+		{Gulliford}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Bartnik}},
+	\ and\ \bibinfo {author} {\bibfnamefont {I.}~\bibnamefont {Bazarov}},\ }\href
+{\doibase 10.1103/PhysRevAccelBeams.19.093402} {\bibfield  {journal}
+	{\bibinfo  {journal} {Phys. Rev. Accel. Beams}\ }\textbf {\bibinfo {volume}
+		{19}},\ \bibinfo {pages} {093402} (\bibinfo {year} {2016})}\BibitemShut
+{NoStop}%
+\bibitem [{\citenamefont {Gulliford}\ \emph {et~al.}(2017)\citenamefont
+	{Gulliford}, \citenamefont {Bartnik}, \citenamefont {Bazarov},\ and\
+	\citenamefont {Maxson}}]{gull2}%
+\BibitemOpen
+\bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
+		{Gulliford}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Bartnik}},
+	\bibinfo {author} {\bibfnamefont {I.}~\bibnamefont {Bazarov}}, \ and\
+	\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Maxson}},\ }\href
+{\doibase 10.1103/PhysRevAccelBeams.20.033401} {\bibfield  {journal}
+	{\bibinfo  {journal} {Phys. Rev. Accel. Beams}\ }\textbf {\bibinfo {volume}
+		{20}},\ \bibinfo {pages} {033401} (\bibinfo {year} {2017})}\BibitemShut
+{NoStop}%
+\bibitem [{\citenamefont {Kranjčević}\ \emph {et~al.}(2019)\citenamefont
+	{Kranjčević}, \citenamefont {Adelmann}, \citenamefont {Arbenz},
+	\citenamefont {Citterio},\ and\ \citenamefont {Stingelin}}]{marija}%
+\BibitemOpen
+\bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+		{Kranjčević}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+		{Adelmann}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Arbenz}},
+	\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Citterio}}, \ and\
+	\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Stingelin}},\ }\href
+{\doibase https://doi.org/10.1016/j.nima.2018.12.066} {\bibfield  {journal}
+	{\bibinfo  {journal} {Nucl. Instrum. Methods Phys. Res. A}\ }\textbf
+	{\bibinfo {volume} {920}},\ \bibinfo {pages} {106 } (\bibinfo {year}
+	{2019})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Physics}(2018)}]{gpt}%
+\BibitemOpen
+\bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+		{Physics}},\ }\href@noop {} {\enquote {\bibinfo {title} {{General Particle
+				Tracer (GPT)}},}\ } (\bibinfo {year} {1996-2018}),\ \Eprint
+{http://arxiv.org/abs/\url{http://www.pulsar.nl/gpt}}
+{\url{http://www.pulsar.nl/gpt}} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Borland}(2018)}]{elegant}%
+\BibitemOpen
+\bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+		{Borland}},\ }\href@noop {} {\emph {\bibinfo {title} {Elegant: A flexible
+			SDDS-compliant code for accelerator simulation}}},\ \bibinfo {type} {Tech.
+	Rep.}\ \bibinfo {number} {LS-287}\ (\bibinfo  {institution} {Argonne National
+	Laboratory},\ \bibinfo {year} {2000-2018})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Adelmann}\ \emph {et~al.}(2018)\citenamefont
+	{Adelmann}, \citenamefont {Baumgarten}, \citenamefont {Frey}, \citenamefont
+	{Gsell}, \citenamefont {Rizzoglio}, \citenamefont {Snuverink}, \citenamefont
+	{Metzger-Kraus}, \citenamefont {Ineichen}, \citenamefont {Russell},
+	\citenamefont {Wang}, \citenamefont {Sheehy}, \citenamefont {Rogers},\ and\
+	\citenamefont {Winklehner}}]{opal}%
+\BibitemOpen
+\bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+		{Adelmann}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
+		{Baumgarten}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Frey}},
+	\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Gsell}}, \bibinfo
+	{author} {\bibfnamefont {V.}~\bibnamefont {Rizzoglio}}, \bibinfo {author}
+	{\bibfnamefont {J.}~\bibnamefont {Snuverink}}, \bibinfo {author}
+	{\bibfnamefont {C.}~\bibnamefont {Metzger-Kraus}}, \bibinfo {author}
+	{\bibfnamefont {Y.}~\bibnamefont {Ineichen}}, \bibinfo {author}
+	{\bibfnamefont {S.}~\bibnamefont {Russell}}, \bibinfo {author} {\bibfnamefont
+		{C.}~\bibnamefont {Wang}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+		{Sheehy}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Rogers}}, \
+	and\ \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Winklehner}},\
+}\href@noop {} {\emph {\bibinfo {title} {The {OPAL} (Object Oriented Parallel
+			Accelerator Library) Framework}}},\ \bibinfo {type} {Tech. Rep.}\ \bibinfo
+{number} {PSI-PR-08-02}\ (\bibinfo  {institution} {Paul Scherrer Institut},\
+\bibinfo {year} {2008-2018})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Bleuler}\ \emph {et~al.}(2003)\citenamefont
+	{Bleuler}, \citenamefont {Laumanns}, \citenamefont {Thiele},\ and\
+	\citenamefont {Zitzler}}]{pisa}%
+\BibitemOpen
+\bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+		{Bleuler}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Laumanns}},
+	\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Thiele}}, \ and\ \bibinfo
+	{author} {\bibfnamefont {E.}~\bibnamefont {Zitzler}},\ }in\ \href@noop {}
+{\emph {\bibinfo {booktitle} {{E}volutionary {M}ulti-{C}riterion
+			{O}ptimization}}},\ \bibinfo {editor} {edited by\ \bibinfo {editor}
+	{\bibfnamefont {C.~M.}\ \bibnamefont {Fonseca}}, \bibinfo {editor}
+	{\bibfnamefont {P.~J.}\ \bibnamefont {Fleming}}, \bibinfo {editor}
+	{\bibfnamefont {E.}~\bibnamefont {Zitzler}}, \bibinfo {editor} {\bibfnamefont
+		{L.}~\bibnamefont {Thiele}}, \ and\ \bibinfo {editor} {\bibfnamefont
+		{K.}~\bibnamefont {Deb}}}\ (\bibinfo  {publisher} {Springer},\ \bibinfo
+{address} {Berlin, Heidelberg},\ \bibinfo {year} {2003})\ pp.\ \bibinfo
+{pages} {494--508}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Deb}(2009)}]{deb:09}%
+\BibitemOpen
+\bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
+		{Deb}},\ }\href@noop {} {\emph {\bibinfo {title} {{M}ulti-{O}bjective
+			{O}ptimization {U}sing {E}volutionary {A}lgorithms}}}\ (\bibinfo  {publisher}
+{Wiley},\ \bibinfo {year} {2009})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Kirkpatrick}\ \emph {et~al.}(1983)\citenamefont
+	{Kirkpatrick}, \citenamefont {Gelatt},\ and\ \citenamefont
+	{Vecchi}}]{kigv:83}%
+\BibitemOpen
+\bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+		{Kirkpatrick}}, \bibinfo {author} {\bibfnamefont {C.~D.}\ \bibnamefont
+		{Gelatt}}, \ and\ \bibinfo {author} {\bibfnamefont {M.~P.}\ \bibnamefont
+		{Vecchi}},\ }\href {\doibase 10.1126/science.220.4598.671} {\bibfield
+	{journal} {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo {volume}
+		{220}},\ \bibinfo {pages} {671} (\bibinfo {year} {1983})}\BibitemShut
+{NoStop}%
+\bibitem [{\citenamefont {Kennedy}\ and\ \citenamefont
+	{Eberhart}(1995)}]{keeb:95}%
+\BibitemOpen
+\bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+		{Kennedy}}\ and\ \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
+		{Eberhart}},\ }in\ \href {\doibase 10.1109/ICNN.1995.488968} {\emph {\bibinfo
+		{booktitle} {Proc. of ICNN}}},\ Vol.~\bibinfo {volume} {4}\ (\bibinfo {year}
+{1995})\ pp.\ \bibinfo {pages} {1942--1948}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Dorigo}\ \emph {et~al.}(1996)\citenamefont {Dorigo},
+	\citenamefont {Maniezzo},\ and\ \citenamefont {Colorni}}]{domc:96}%
+\BibitemOpen
+\bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+		{Dorigo}}, \bibinfo {author} {\bibfnamefont {V.}~\bibnamefont {Maniezzo}}, \
+	and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Colorni}},\
+}\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {IEEE Trans. Syst.
+			Man. Cy. B}\ }\textbf {\bibinfo {volume} {26}},\ \bibinfo {pages} {29}
+	(\bibinfo {year} {1996})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {De~Castro}\ and\ \citenamefont
+	{Timmis}(2002)}]{cati:02}%
+\BibitemOpen
+\bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+		{De~Castro}}\ and\ \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+		{Timmis}},\ }\href@noop {} {\emph {\bibinfo {title} {Artificial immune
+			systems: a new computational intelligence approach}}}\ (\bibinfo  {publisher}
+{Springer},\ \bibinfo {year} {2002})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Karaboga}(2005)}]{kara:05}%
+\BibitemOpen
+\bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
+		{Karaboga}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+		{Techn. Rep. TR06, Erciyes Univ. Press, Erciyes}\ } (\bibinfo {year}
+	{2005})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Shah-Hosseini}(2009)}]{hoss:09}%
+\BibitemOpen
+\bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
+		{Shah-Hosseini}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+		{Int. J. Bio-Inspir. Com.}\ }\textbf {\bibinfo {volume} {1}},\ \bibinfo
+	{pages} {71} (\bibinfo {year} {2009})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Deb}\ \emph {et~al.}(2002)\citenamefont {Deb},
+	\citenamefont {Pratap}, \citenamefont {Agarwal},\ and\ \citenamefont
+	{Meyarivan}}]{dpam:02}%
+\BibitemOpen
+\bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
+		{Deb}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Pratap}},
+	\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Agarwal}}, \ and\
+	\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Meyarivan}},\ }\href
+{\doibase 10.1109/4235.996017} {\bibfield  {journal} {\bibinfo  {journal}
+		{IEEE Trans. Evol. Comp.}\ }\textbf {\bibinfo {volume} {6}},\ \bibinfo
+	{pages} {182} (\bibinfo {year} {2002})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Filipi\v{c}}\ and\ \citenamefont
+	{Depolli}(2009)}]{fide:09}%
+\BibitemOpen
+\bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
+		{Filipi\v{c}}}\ and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+		{Depolli}},\ }in\ \href {\doibase 10.1007/978-1-84882-409-6\_7} {\emph
+	{\bibinfo {booktitle} {Parallel Computing}}},\ \bibinfo {editor} {edited by\
+	\bibinfo {editor} {\bibfnamefont {R.}~\bibnamefont {Trobec}}, \bibinfo
+	{editor} {\bibfnamefont {M.}~\bibnamefont {Vajter\v{s}ic}}, \ and\ \bibinfo
+	{editor} {\bibfnamefont {P.}~\bibnamefont {Zinterhof}}}\ (\bibinfo
+{publisher} {Springer},\ \bibinfo {year} {2009})\ pp.\ \bibinfo {pages}
+{217--240}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Le\'{o}n}\ \emph {et~al.}(2009)\citenamefont
+	{Le\'{o}n}, \citenamefont {Miranda},\ and\ \citenamefont {Segura}}]{lems:09}%
+\BibitemOpen
+\bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
+		{Le\'{o}n}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Miranda}}, \
+	and\ \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Segura}},\ }\href
+{\doibase 10.1142/S0218213009000275} {\bibfield  {journal} {\bibinfo
+		{journal} {Int. J. Artif. Intell. Tools}\ }\textbf {\bibinfo {volume} {18}},\
+	\bibinfo {pages} {569} (\bibinfo {year} {2009})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Liefooghe}\ \emph {et~al.}(2007)\citenamefont
+	{Liefooghe}, \citenamefont {Basseur}, \citenamefont {Jourdan},\ and\
+	\citenamefont {Talbi}}]{lbjt:07}%
+\BibitemOpen
+\bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+		{Liefooghe}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Basseur}},
+	\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Jourdan}}, \ and\
+	\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Talbi}},\ }in\ \href@noop
+{} {\emph {\bibinfo {booktitle} {Evolutionary Multi-Criterion
+			Optimization}}}\ (\bibinfo {organization} {Springer},\ \bibinfo {year}
+{2007})\ pp.\ \bibinfo {pages} {386--400}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Durillo}\ \emph {et~al.}(2006)\citenamefont
+	{Durillo}, \citenamefont {Nebro}, \citenamefont {Luna}, \citenamefont
+	{Dorronsoro},\ and\ \citenamefont {Alba}}]{dnld:06}%
+\BibitemOpen
+\bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+		{Durillo}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Nebro}},
+	\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Luna}}, \bibinfo {author}
+	{\bibfnamefont {B.}~\bibnamefont {Dorronsoro}}, \ and\ \bibinfo {author}
+	{\bibfnamefont {E.}~\bibnamefont {Alba}},\ }\href@noop {} {\emph {\bibinfo
+		{title} {jMetal: a java framework for developing multi-objective optimization
+			metaheuristics}}},\ \bibinfo {type} {Tech. Rep.}\ \bibinfo {number}
+{ITI-2006-10}\ (\bibinfo  {institution} {University of M{\'a}laga, ETSI
+	Inform{\'a}tica, Campus de Teatinos},\ \bibinfo {year} {2006})\BibitemShut
+{NoStop}%
+\bibitem [{\citenamefont {Arbenz}\ and\ \citenamefont
+	{Chinellato}(2008)}]{ARBENZ2008381}%
+\BibitemOpen
+\bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+		{Arbenz}}\ and\ \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont
+		{Chinellato}},\ }\href {\doibase 10.1016/j.apnum.2007.01.019} {\bibfield
+	{journal} {\bibinfo  {journal} {Appl. Numer. Math.}\ }\textbf {\bibinfo
+		{volume} {58}},\ \bibinfo {pages} {381} (\bibinfo {year} {2008})}\BibitemShut
+{NoStop}%
+\bibitem [{boo(2015)}]{boost}%
+\BibitemOpen
+\href@noop {} {\enquote {\bibinfo {title} {{The Boost Spirit Home Page}},}\ }
+(\bibinfo {year} {2015}),\ \bibinfo {note}
+{\url{http://boost-spirit.com/}}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {{ E. Friedman and I. Maman }}(2003)}]{boost2}%
+\BibitemOpen
+\bibfield  {author} {\bibinfo {author} {\bibnamefont {{ E. Friedman and I.
+				Maman }}},\ }\href@noop {} {\enquote {\bibinfo {title} {{Chapter 45.
+				Boost.Variant}},}\ } (\bibinfo {year} {2003}),\ \bibinfo {note}
+{\url{www.boost.org/doc/html/variant.html}}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Gregor}(2004)}]{boost3}%
+\BibitemOpen
+\bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
+		{Gregor}},\ }\href@noop {} {\enquote {\bibinfo {title} {{Chapter 15.
+				Boost.Function}},}\ } (\bibinfo {year} {2004}),\ \bibinfo {note}
+{\url{www.boost.org/libs/function/}}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Balaji}\ \emph {et~al.}(2009)\citenamefont {Balaji},
+	\citenamefont {Chan}, \citenamefont {Thakur}, \citenamefont {Gropp},\ and\
+	\citenamefont {Lusk}}]{bctg:09}%
+\BibitemOpen
+\bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+		{Balaji}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Chan}},
+	\bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Thakur}}, \bibinfo
+	{author} {\bibfnamefont {W.}~\bibnamefont {Gropp}}, \ and\ \bibinfo {author}
+	{\bibfnamefont {E.~L.}\ \bibnamefont {Lusk}},\ }\href {\doibase
+	http://dx.doi.org/10.1007/s00450-009-0095-3} {\bibfield  {journal} {\bibinfo
+		{journal} {Computer Science - Research and Development}\ }\textbf {\bibinfo
+		{volume} {24}},\ \bibinfo {pages} {11} (\bibinfo {year} {2009})}\BibitemShut
+{NoStop}%
+\bibitem [{\citenamefont {Boyd}\ \emph {et~al.}(2006)\citenamefont {Boyd},
+	\citenamefont {Ghosh}, \citenamefont {Prabhakar},\ and\ \citenamefont
+	{Shah}}]{bgps:06}%
+\BibitemOpen
+\bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+		{Boyd}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Ghosh}},
+	\bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Prabhakar}}, \ and\
+	\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Shah}},\ }\href@noop {}
+{\bibfield  {journal} {\bibinfo  {journal} {IEEE Trans. Inform. Theory}\
+	}\textbf {\bibinfo {volume} {52}},\ \bibinfo {pages} {2508} (\bibinfo {year}
+	{2006})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Aysal}\ \emph {et~al.}(2009)\citenamefont {Aysal},
+	\citenamefont {Yildiz}, \citenamefont {Sarwate},\ and\ \citenamefont
+	{Scaglione}}]{ayss:09}%
+\BibitemOpen
+\bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+		{Aysal}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Yildiz}},
+	\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Sarwate}}, \ and\
+	\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Scaglione}},\ }\href@noop
+{} {\bibfield  {journal} {\bibinfo  {journal} {IEEE Trans. Signal Process.}\
+	}\textbf {\bibinfo {volume} {57}},\ \bibinfo {pages} {2748} (\bibinfo {year}
+	{2009})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Huband}\ \emph {et~al.}(2005)\citenamefont {Huband},
+	\citenamefont {Barone}, \citenamefont {While},\ and\ \citenamefont
+	{Hingston}}]{hbwh:05}%
+\BibitemOpen
+\bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+		{Huband}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Barone}},
+	\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {While}}, \ and\ \bibinfo
+	{author} {\bibfnamefont {P.}~\bibnamefont {Hingston}},\ }in\ \href {\doibase
+	10.1007/978-3-540-31880-4_20} {\emph {\bibinfo {booktitle} {Proc. of Intl.
+			Conf. Evol. Multi-Criterion Optimization}}}\ (\bibinfo  {publisher}
+{Springer-Verlag},\ \bibinfo {address} {Berlin, Heidelberg},\ \bibinfo {year}
+{2005})\ pp.\ \bibinfo {pages} {280--295}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {While}\ \emph {et~al.}(2012)\citenamefont {While},
+	\citenamefont {Bradstreet},\ and\ \citenamefont {Barone}}]{whbb:12}%
+\BibitemOpen
+\bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+		{While}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Bradstreet}}, \
+	and\ \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Barone}},\
+}\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {IEEE Trans. Evol.
+			Comput.}\ }\textbf {\bibinfo {volume} {16}},\ \bibinfo {pages} {86} (\bibinfo
+	{year} {2012})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Gai}\ \emph {et~al.}(2012)\citenamefont {Gai},
+	\citenamefont {Power},\ and\ \citenamefont {Jing}}]{gai_power_jing_2012}%
+\BibitemOpen
+\bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.}~\bibnamefont
+		{Gai}}, \bibinfo {author} {\bibfnamefont {J.~G.}\ \bibnamefont {Power}}, \
+	and\ \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Jing}},\ }\href
+{\doibase 10.1017/S0022377812000037} {\bibfield  {journal} {\bibinfo
+		{journal} {Journal of Plasma Physics}\ }\textbf {\bibinfo {volume} {78}},\
+	\bibinfo {pages} {339–345} (\bibinfo {year} {2012})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Jing}\ \emph {et~al.}(2018)\citenamefont {Jing} \emph
+	{et~al.}}]{JING201872}%
+\BibitemOpen
+\bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
+		{Jing}} \emph {et~al.},\ }\href {\doibase
+	https://doi.org/10.1016/j.nima.2018.05.007} {\bibfield  {journal} {\bibinfo
+		{journal} {Nucl. Instrum. Methods Phys. Res. A}\ }\textbf {\bibinfo {volume}
+		{898}},\ \bibinfo {pages} {72 } (\bibinfo {year} {2018})}\BibitemShut
+{NoStop}%
+\bibitem [{\citenamefont {Gao}\ \emph {et~al.}(2008)\citenamefont {Gao},
+	\citenamefont {Conde}, \citenamefont {Gai}, \citenamefont {Jing},
+	\citenamefont {Konecny}, \citenamefont {Liu}, \citenamefont {Power},
+	\citenamefont {Wong},\ and\ \citenamefont {Yusof}}]{PETSeq}%
+\BibitemOpen
+\bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
+		{Gao}}, \bibinfo {author} {\bibfnamefont {M.~E.}\ \bibnamefont {Conde}},
+	\bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Gai}}, \bibinfo {author}
+	{\bibfnamefont {C.}~\bibnamefont {Jing}}, \bibinfo {author} {\bibfnamefont
+		{R.}~\bibnamefont {Konecny}}, \bibinfo {author} {\bibfnamefont
+		{W.}~\bibnamefont {Liu}}, \bibinfo {author} {\bibfnamefont {J.~G.}\
+		\bibnamefont {Power}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+		{Wong}}, \ and\ \bibinfo {author} {\bibfnamefont {Z.}~\bibnamefont {Yusof}},\
+}\href {\doibase 10.1103/PhysRevSTAB.11.041301} {\bibfield  {journal}
+	{\bibinfo  {journal} {Phys. Rev. ST Accel. Beams}\ }\textbf {\bibinfo
+		{volume} {11}},\ \bibinfo {pages} {041301} (\bibinfo {year}
+	{2008})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Neveu}(2018)}]{neveuthesis}%
+\BibitemOpen
+\bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
+		{Neveu}},\ }\emph {\bibinfo {title} {Beam Line Design for Fully Staged Two
+		Beam Acceleration at the Argonne Wakefield Accelerator Facility}},\
+\href@noop {} {Ph.D. thesis},\ \bibinfo  {school} {Illinois Institute of
+	Technology} (\bibinfo {year} {2018})\BibitemShut {NoStop}%
+\end{thebibliography}%
 \end{document}

### 2019-02-01 paper/submission/theor-experiment.tex
adding bib to tex file and moving figures

@@
     \centering
-      \includegraphics[width=0.4\linewidth]{figures/hypervolume}
+      \includegraphics[width=0.4\linewidth]{hypervolume}
   \caption{The hypervolume for a two-objective optimization problem
@@
   \centering
-    \includegraphics[width=0.6\linewidth]{figures/valid_front}
+    \includegraphics[width=0.6\linewidth]{valid_front}
   \caption{Variator benchmark after $1100$ function evaluations using binary
@@
 \begin{figure*}
-\includegraphics[width=0.9\linewidth]{figures/awa-drawing}
+\includegraphics[width=0.9\linewidth]{awa-drawing}
 	\caption{Side view of the high charge linac at the AWA. 
@@
 \begin{figure*}
-\includegraphics[width=0.9\linewidth]{figures/tba_dogleg2}
+\includegraphics[width=0.9\linewidth]{tba_dogleg2}
 	\caption{Continuation of the high charge beam line layout at the AWA, top view. 
@@
 	\centering
-	\includegraphics[width=0.8\linewidth]{figures/timestep_comparison_paper}
+	\includegraphics[width=0.8\linewidth]{timestep_comparison_paper}
 	\caption{Comparison of different fidelity models (dT stands for time step).}
@@
 		\centering
-		\includegraphics[width=\textwidth]{figures/ex-pareto1-paperedit}
+		\includegraphics[width=\textwidth]{ex-pareto1-paperedit}
 		(a) Pareto fronts for ex-1 through ex-4 at $s_1$.
@@
 		\centering
-		\includegraphics[width=\textwidth]{figures/ex-pareto2-paperedit}
+		\includegraphics[width=\textwidth]{ex-pareto2-paperedit}
 		(b) Pareto fronts for ex-1 through ex-4 at $s_2$.
@@
 	\begin{center}		
-		\includegraphics[width=0.65\textwidth]{figures/paperedit_pareto_front_Q5_xy_vs_pxpy}
+		\includegraphics[width=0.65\textwidth]{paperedit_pareto_front_Q5_xy_vs_pxpy}
 	\end{center} 
@@
 \begin{figure}
-	\includegraphics[width=0.65\textwidth]{figures/xy-max-min-sigma-paper}
+	\includegraphics[width=0.65\textwidth]{xy-max-min-sigma-paper}
 	\caption{Optimized beam sizes along high charge beam line. The gun is located at $s=0$, 

### 2019-03-19 paper/submission/ZW10157-response-2.tex
edits to address reviewers second round of comments

\documentclass{article}
\usepackage{latexsym}
\usepackage{color}
\setlength{\parskip}{3mm}
\setlength{\parindent}{0pt}
\usepackage[margin=1in]{geometry}

\newcommand{\TODO}[1]{\color{green}\noindent[{\bf TODO: #1}]\color{black}}
\newcommand{\atline}[1]{\color{red} Lines: #1\color{blue}}
\begin{document}
\title {Paper  \#ZW10157}
\author {N. Neveu, et. al}

\maketitle
Dear reviewer and editors,

Thank you for the additional comments.
We have moved all code implementation details to appendices.
In addition, further revisions have been made as suggested.
We hope to show we value the constructive criticism provided.
The details can be found in the following pages.

With the best regards,  \\[3mm]

Nicole Neveu, et. al

\pagebreak

{\bf REFEREE B (Remarks to Author), Version 2}

My thanks, also, to the authors for updating the cited references.
When blocks of references are provided, conventionally, they are
listed chronologically to properly recognize the contributions of
pioneers, and the authors should reorder their citations to follow
this convention.

{\bf Our response:} {\color{blue} The references have been 
	reordered chronologically, to recognize contribution order.}

For the Evolutionary Algorithm/Genetic Algorithm
(EA/GA)-based systems used in accelerator physics, I would ask them to
reconsider their choice to omit references by C. Gong and Y.C. Chao as
that optimization package allows users to define problems that use
multiple simulation programs in parallel and in series with various
interdependencies and execution times and manages all the complexity
for the user. Based on my understanding of the authors' system, this
is a common feature of both. The goal of publication is to introduce
new work to the community and to also recognize similar contributions
of others for comparison purposes.

{\bf Our response:} {\color{blue} The following references provided in the 
	referees first comments were added to the updated manuscript:

Y.C. Chao et al. "TRIUMF-VECC Electron Linac Beam Dynamics
Optimization," ICAP09, San Francisco, 2009, THPSC012

C. Gong and Y.C. Chao, "The TRIUMF Optimization Platform and
Application to the E-LINAC Injector", ICAP2012, Rostock-Warnemunde,
Germany, 2012, TUABI1

C. Gong, A Novel Optimization Platform and Its Applications to the
TRIUMF Energy Recovery Linac, Ph.D. thesis, The University of
Columbia, October 2015

C. Gong and Y.C. Chao, "The TRIUMF Optimization Platform and
Application to the E-LINAC Injector", ICAP2015, Shanghai, China, 2015,
THCWC4}

I recognize the authors moved some of the source code listings to a
GitHub repository (may not comply with PRAB publishing practices as
PRAB provides Supplemental Materials storage and access on its web
site for each paper providing Supplemental Materials).

{\bf Our response:} {\color{blue} The github link was removed,
	and Appendix B was added to provide an example OPAL 
	optimization input file.}

I stand by my
initial assessment and believe more can be summarized with details
moved to Appendices or Supplemental Materials without diminishing the
authors' accomplishments. It is true that ``computing and algorithms''
are listed under PRAB's scope, but keeping the quite detailed
explanations of the implementation and software listings risks losing
readers interested in optimization systems in general. It would
behoove the authors to note that both reviewers commented on this in
different ways and that the recommendations were made with the goal of
increasing readership and readability. The authors' choice to ignore
the advice is shortsighted as it is possible to describe the
complexity and novel features of the system to readers who are and are
not adept computer programmers.

As an aside to the authors, I believe ``computing and algorithms''
were originally included in PRAB's scope to allow publications
discussing novel or new software requirements or
implementation details as they relate to applications specific to the
accelerator physics community such as field solvers, beam dynamics
codes, beam diagnostic data analysis, distributed control system
designs and communication protocols, etc. Some examples that do so
without detailed software implementation discussions include for
distributed processing for EA/GAs Bazarov and Sinclair's 2005 paper
and for methods for simulating coherent synchrotron radiation
Borland's 2001 and Agoh and Yokoya's 2004 papers. The ``rumor
network'' for message passing the authors employed may fall in the
category of new or novel for its use in accelerator physics
applications, but master/slave, C$++$ classes, inheritance, and
functors do not. As suggested in my initial review, much of the latter
can be summarized with the details moved to an Appendix or
Supplemental Materials. Readers who are truly interested in that level
of detail will go to the Appendices or Supplemental Materials. I
recommend to the authors a question that managers often have to ask
themselves: Is it more important to be right or effective? Do you want
to be right on a technicality about ``computing and algorithms,'' or
do you want to be effective in reaching as many readers as possible?

Sundry proofreading corrections listed by section.

I.

paragraph 3
NSGA-II is mentioned but not cited.

II. A.

paragraph 4
By calling the selector --> Calling the selector

paragraph 4
also present in GPT's [ref] optimization system --> also
present in Cornell's [2005 PRSTAB] and GPT's [ref] optimization
systems
(Note to the authors: Cornell's implementation in APISA pre-dates ALL
of GPT's work with EA/GA's.)

III. A.

paragraph 2
search algorithm to get stuck --> search algorithm getting
stuck

III. B.

paragraph 3
checking for idle WORKER --> checking for idle WORKERs

Fig. 3 caption
$r_k$ --> $r_1$

Fig. 3 caption
The work $W_j$ are beam dynamics simulation within OPAL.
--> $W_j$ performs beam dynamics simulations within OPAL.

III. C.

paragraph 1
shown in Listing 2 --> shown in Listing 1

III. D.

paragraph 1
The author's use of ``approach'' is ambiguous because it could be
interpreted as applying EA/GA multi-objective optimization to cavity
geometries since the emphasis of the paper is on providing a flexible
interface to EA/GAs or approach could mean the framework's software
design which is what, I think, they meant to convey. The authors
should make clear which ``approach'' they want the reader to consider.
A suggested change is:

general nature of our approach --> general nature of our
framework's software design

paragraph 1
the API in Listing 3 --> the API in Listing 2

paragraph 1
for those three --> for three

III. E.

paragraph 1
An expression parser --> an expression parser
(Note to authors: ``an expression parser'' is a continuation of the
sentence started before the code example introduced as an example.)

paragraph 3
As shown in Listing 5 --> As shown in Listing 3

IV.

paragraph 1
in Listing 3 --> in Listing 1

V. B. 2

paragraph 2
, and the to prevent --> and to prevent

Table III description, paragraph 2, and paragraph 3
twenty four --> twenty-four

paragraph 3
but from Fig. 9, but this is --> but from Fig. 9, this is

paragraph 3
15 less --> 15 fewer

V. B. 3
paragraph 2 (reported as corrected but is not in the version provided
to reviewers)
to to --> to

V. B. 4
Fig. 11 Vertical axis units are missing.

{\bf REFEREE B (Remarks to Author), Version 1}

\vspace{1em}

That said, a general-purpose optimization system is a useful addition
to the design tools for accelerators. The way to entice prospective
users through PRAB is to introduce the system with a very brief
general overview and then focus on the results obtained using the
system. The detailed discussion of the design and implementation with
code snippets should be provided as Supplemental Material. PRAB is not
a computer journal. Salient implementation or design points if
necessary can be summarized in short Appendices; the main discussion
of the paper should be the optimization results not the details of the
implementation and design.

subsections B-F:
Replace with a brief overview and put the details in Supplemental
Material

{\bf Our response: } {\color{blue} This section has been shortened. However we would like to 
leave the existing description, in order to drive home the fact that the framework can be 
easily extended with other optimization algorithms.}

Section VI: 
Code and input file details should be in Supplemental Material

Section V, subsection B:
Code and input file details should be in Supplemental Material

{\bf Our response:} {\color{blue} The code examples in sections VI-V have been removed from the updated manuscript. 
	A sentence and link to the repository have been provided. Interested parties can refer to the repository.}

 \end{document}

### 2019-03-19 paper/submission/prab.tex
resubmitted paper
edits to address reviewers second round of comments

--- 2019-02-01 paper/submission/prab.tex
@@
   problems to automate the investigation for an optimal set of tuning parameters.
-  This approach has been used in the past with much success~\cite{hofler13,bazarov05,yrss:09,jefferson,gull1,gull2,marija}.
+  This approach has been used in the past with much 
+  success~\cite{bazarov05,yrss:09,chao09, hofler13,jefferson,gong15, gongthesis15,gull1,gull2,marija}.
 The difference here being the implementation and application to a 
@@
 
-Several similar frameworks, e.g.~\cite{fide:09,lems:09,lbjt:07,dnld:06}, have
+Several similar frameworks, e.g.~\cite{dnld:06, lbjt:07, fide:09,lems:09}, have
   been proposed.
@@
 
-% AA: this is too much for Phys Rev. AB
-
-% \appendix
-
-%\section{Forward Solver Implementation}
-%
-%A simple implementation, e.g.\ using a Python forward solver, is given below
-%  in Listing 6.
-%We assume the Python script executes a simulation and dumps results in the
-%  \textsc{SDDS} file format~\cite{borl:00}.
-%Utility classed are used to parse the result data and fill the appropriate
-%  structures returned to the optimizer algorithm.
-%
-%\begin{code}[Simple Simulation Wrapper]
-%#include <map>
-%#include <string>
-%#include <vector>
-%
-%#include "Util/Types.h"
-%#include "Util/CmdArguments.h"
-%#include "Simulation/Simulation.h"
-%
-%#include "boost/smart_ptr.hpp"
-%
-%class SimpleSimulation : public Simulation {
-%
-%public:
-%
-%    SimpleSimulation(Expressions::Named_t objectives,
-%                     Expressions::Named_t constraints,
-%                     Param_t params, std::string name, MPI_Comm comm,
-%                     CmdArguments_t args);
-%
-%    ~SimpleSimulation();
-%
-%    /// Calls simulation through Python wrapper and returns when simulation
-%    /// has either failed or finished.
-%    void run() {
-%        // user implements wrappers
-%        prepare_input_file();
-%        run_python_simulation();
-%    }
-%
-%    /// Parse SDDS stat file and build up requested variable dictionary.
-%    void collectResults(){
-%
-%        Expressions::Named_t::iterator it;
-%        for(it = objectives_.begin(); it != objectives_.end(); it++) {
-%
-%            Expressions::Expr_t *objective = it->second;
-%
-%            // find out which variables we need in order to evaluate the
-%            // objective
-%            variableDictionary_t variable_dictionary;
-%            std::set<std::string> req_vars = objective->getReqVars();
-%
-%            if(req_vars.size() != 0) {
-%
-%                boost::scoped_ptr<SDDSReader> sddsr(new SDDSReader(fn));
-%
-%                try {
-%                    sddsr->parseFile();
-%                } catch(OptPilotException &e) {
-%                    std::cout << "Exception while parsing SDDS file: "
-%                        << e.what() << std::endl;
-%                    break;
-%                }
-%
-%                // get all the required variable values from the stat file
-%                foreach(std::string req_var, req_vars) {
-%                    if(variable_dictionary.count(req_var) == 0) {
-%
-%                        try {
-%                            double value = 0.0;
-%                            sddsr->getValue(1 /*atTime*/, req_var, value);
-%                            variable_dictionary.insert(
-%                                std::pair<std::string, double>(req_var, value));
-%                        } catch(OptPilotException &e) {
-%                            std::cout << "Exception while getting value "
-%                                      << "from SDDS file: " << e.what()
-%                                      << std::endl;
-%                        }
-%                    }
-%                }
-%            }
-%
-%            // and evaluate the expression using the built dictionary of
-%            // variable values
-%            Expressions::Result_t result =
-%                objective->evaluate(variable_dictionary);
-%
-%            std::vector<double> values;
-%            values.push_back(boost::get<0>(result));
-%            bool is_valid = boost::get<1>(result);
-%
-%            reqVarInfo_t tmps = {EVALUATE, values, is_valid};
-%            requestedVars_.insert(
-%                std::pair<std::string, reqVarInfo_t>(it->first, tmps));
-%
-%        }
-%    }
-%
-%    /// returns container containing all requested variables with results
-%    reqVarContainer_t getResults() { return requestedVars_; }
-%
-%private:
-%
-%    /// holds solutions returned to the optimizer
-%    reqVarContainer_t requestedVars_;
-%
-%    Expressions::Named_t objectives_;
-%    Expressions::Named_t constraints_;
-%
-%    MPI_Comm comm_;
-%};
-%
-%#endif
-%\end{code}
-
 \bibliography{paper}

### 2019-03-19 paper/submission/prab.tex
edits to new bib entries

@@
   This approach has been used in the past with much 
-  success~\cite{bazarov05,yrss:09,chao09, hofler13,jefferson,gong15, gongthesis15,gull1,gull2,marija}.
+  success~\cite{bazarov05,yrss:09,chao09,gong12,hofler13,jefferson,gong15,gongthesis15,gull1,gull2,marija}.
 The difference here being the implementation and application to a 

### 2019-03-19 paper/submission/ZW10157-response-2.tex
edits to new bib entries
small grammer edits

@@
 
-I stand by my
-initial assessment and believe more can be summarized with details
+I stand by my initial assessment and believe more can be summarized with details
 moved to Appendices or Supplemental Materials without diminishing the
@@
 
+{\bf Our response:} {\color{blue} }
+
 Sundry proofreading corrections listed by section.
+I. paragraph 3: NSGA-II is mentioned but not cited.
 
-I.
+{\bf Our response:} {\color{blue} The citation has been added.}
 
-paragraph 3
-NSGA-II is mentioned but not cited.
+II. A. paragraph 4: By calling the selector --$>$ Calling the selector
 
-II. A.
-
-paragraph 4
-By calling the selector --> Calling the selector
+{\bf Our response:} {\color{blue} This correction is in the new manuscript on line xxx.}
 
@@
 also present in GPT's [ref] optimization system --> also
-present in Cornell's [2005 PRSTAB] and GPT's [ref] optimization
-systems
+present in Cornell's [2005 PRSTAB] and GPT's [ref] optimization systems
 (Note to the authors: Cornell's implementation in APISA pre-dates ALL
@@
 
-III. A.
+{\bf Our response:} {\color{blue} The reference to Cornell was added.}
 
-paragraph 2
+III. A: paragraph 2
 search algorithm to get stuck --> search algorithm getting
@@
 
-III. B.
+{\bf Our response:} {\color{blue} This correction is in the new manuscript on line xxx.}
 
-paragraph 3
+III. B. paragraph 3
 checking for idle WORKER --> checking for idle WORKERs
+
+{\bf Our response:} {\color{blue} This correction is in the new manuscript on line xxx.}
 
@@
 $r_k$ --> $r_1$
-
-Fig. 3 caption
 The work $W_j$ are beam dynamics simulation within OPAL.
@@
 
-III. C.
+{\bf Our response:} {\color{blue} The figure caption has been corrected.}
 
-paragraph 1
+III. C. paragraph 1
 shown in Listing 2 --> shown in Listing 1

### 2019-03-19 paper/submission/prab.tex
starting to add appendix
small grammer edits

@@
 Currently the framework offers one concrete optimization algorithm, an
-  evolutionary algorithm employing a \textsc{NSGA-II} selector \cite{pisa}.
+  evolutionary algorithm employing a \textsc{NSGA-II} selector~\cite{dpam:02,pisa}.
 Normally, simulation based approaches are plagued by the trade off between
@@
   surface of the search space.
-So far, the NSGA-II selector \cite{dpam:02} has been used and exhibits satisfactory
+So far, the NSGA-II selector~\cite{dpam:02} has been used and exhibits satisfactory
   convergence performance.
@@
   work on the next fitness evaluation.
-By calling the selector more frequently (already after two offspring
+Calling the selector more frequently (already after two offspring
   individuals have been evaluated) results in better populations since bad
@@
 On the other hand, calling the selector more often is computationally more
-  expensive. Note this capability is also present in GPT's~\cite{gpt} optimization system.
+  expensive. Note this capability is also present in Cornell's~\cite{bazarov05} 
+  and GPT's~\cite{gpt} optimization system.
 
@@
   population are exchanged.
-This is especially useful to prevent the search algorithm to get stuck in
+This is especially useful to prevent the search algorithm getting stuck in
   a local minimum.
@@
   The dashed cyan path describes a request (job $j_1$) sent from $O_i$ to the
-  \textsc{Pilot} being handled by $W_j$. Subsequently the result $r_k$ is
-  returned to the requesting \textsc{Optimizer} ($O_i$). The work $W_j$ are beam dynamics 
-  simulation within OPAL.}
+  \textsc{Pilot} being handled by $W_j$. Subsequently the result $r_1$ is
+  returned to the requesting \textsc{Optimizer} ($O_i$). $W_j$ are beam dynamics 
+  simulations within OPAL.}
   \label{fig:opt-framework-layout}
@@
   (e.g.~function evaluation or derivative).
-The \textsc{Pilot} keeps checking for idle \textsc{Worker} and assigns jobs
+The \textsc{Pilot} keeps checking for idle \textsc{Worker}s and assigns jobs
   in the queue to any free \textsc{Worker}.
@@
 
-% AA: this is too much for Phys Rev. AB  
-% By abiding to the API from Listing 3 it becomes trivial to add new forward
-% solvers to the framework (see Appendix A).
-
 If the objectives and constraints are simple arithmetical expressions, 
@@
 
+\appendix
+
+\section{Code Implementation}
+
+\section{Example Optimization File}
+
+This examples serves to show how a user can 
+set up a multiobjective optimization run 
+within an OPAL input file.
+
+The code that follows was used to perfrom ex-1 in Section~\ref{sec:experiments}.
+
 \bibliography{paper}

### 2019-03-19 paper/submission/ZW10157-response-2.tex
small grammer and typo edits

@@
 
-{\bf Our response:} {\color{blue} This correction is in the new manuscript on line xxx.}
+{\bf Our response:} {\color{blue} This is corrected in the updated manuscript.}
 
@@
 
-{\bf Our response:} {\color{blue} This correction is in the new manuscript on line xxx.}
+{\bf Our response:} {\color{blue} This grammar error is corrected in the updated manuscript.}
 
@@
 
-{\bf Our response:} {\color{blue} This correction is in the new manuscript on line xxx.}
+{\bf Our response:} {\color{blue} This typo is corrected in the updated manuscript.}
 
@@
 
-III. D.
-
-paragraph 1
+III. D. paragraph 1
 The author's use of ``approach'' is ambiguous because it could be
@@
 
-paragraph 1
-the API in Listing 3 --> the API in Listing 2
+{\bf Our response:} {\color{blue} This suggestion was used on line xx.}
 
-paragraph 1
-for those three --> for three
+paragraph 1: the API in Listing 3 --$>$ the API in Listing 2
 
-III. E.
+paragraph 1: for those three --$>$ for three
 
-paragraph 1
+{\bf Our response:} {\color{blue} This was corrected in the updated manuscript.}
+
+III. E. paragraph 1:
 An expression parser --> an expression parser
@@
 
-IV.
-
-paragraph 1
+IV. paragraph 1:
 in Listing 3 --> in Listing 1
 
-V. B. 2
-
-paragraph 2
+V. B. 2 paragraph 2:
 , and the to prevent --> and to prevent
@@
 \vspace{1em}
-
 That said, a general-purpose optimization system is a useful addition

### 2019-03-19 paper/submission/runbib.sh
bibscript

@@ -1,0 +1,7 @@
+#!/bin/bash
+pdflatex prab.tex
+bibtex prab.aux
+bibtex prab.aux
+bibtex prab.aux
+pdflatex prab.tex
+

### 2019-03-19 paper/submission/ZW10157-response-2.tex
small edits done?

@@
 In addition, further revisions have been made as suggested.
-We hope to show we value the constructive criticism provided.
 The details can be found in the following pages.
@@
 
-My thanks, also, to the authors for updating the cited references.
 When blocks of references are provided, conventionally, they are
@@
 III. A: paragraph 2
-search algorithm to get stuck --> search algorithm getting
+search algorithm to get stuck --$>$ search algorithm getting
 stuck
 
-{\bf Our response:} {\color{blue} This grammar error is corrected in the updated manuscript.}
-
 III. B. paragraph 3
-checking for idle WORKER --> checking for idle WORKERs
-
-{\bf Our response:} {\color{blue} This typo is corrected in the updated manuscript.}
+checking for idle WORKER --$>$ checking for idle WORKERs
 
 Fig. 3 caption
-$r_k$ --> $r_1$
+$r_k$ --$>$ $r_1$
 The work $W_j$ are beam dynamics simulation within OPAL.
---> $W_j$ performs beam dynamics simulations within OPAL.
-
-{\bf Our response:} {\color{blue} The figure caption has been corrected.}
+--$>$ $W_j$ performs beam dynamics simulations within OPAL.
 
 III. C. paragraph 1
-shown in Listing 2 --> shown in Listing 1
+shown in Listing 2 --$>$ shown in Listing 1
 
@@
 
-general nature of our approach --> general nature of our
+general nature of our approach --$>$ general nature of our
 framework's software design
-
-{\bf Our response:} {\color{blue} This suggestion was used on line xx.}
 
@@
 paragraph 1: for those three --$>$ for three
-
-{\bf Our response:} {\color{blue} This was corrected in the updated manuscript.}
 
@@
 paragraph 3
-As shown in Listing 5 --> As shown in Listing 3
+As shown in Listing 5 --$>$ As shown in Listing 3
 
 IV. paragraph 1:
-in Listing 3 --> in Listing 1
+in Listing 3 --$>$ in Listing 1
 
 V. B. 2 paragraph 2:
-, and the to prevent --> and to prevent
+, and the to prevent --$>$ and to prevent
 
@@
 paragraph 3
-but from Fig. 9, but this is --> but from Fig. 9, this is
+but from Fig. 9, but this is --$>$ but from Fig. 9, this is
 
 paragraph 3
-15 less --> 15 fewer
+15 less --$>$ 15 fewer
+
+{\bf Our response:} {\color{blue} All typos/corrections above should be incorporated into the updated manuscript.}
 
@@
 to reviewers)
-to to --> to
+to to --$>$ to
+
+{\bf Our response:} {\color{blue} 
+	We were unable to locate this typo. Can the reviewer please provide a line number?}
 

### 2019-03-19 paper/submission/prab.tex
small grammer and typo edits
small edits done?

@@
 All \textsc{Optimizer} implementations have to respect the API shown in
-Listing 2.
+Listing 1.
 
@@
   input. In the case of the OPAL integration, the \texttt{main} function is
-  playing the role of the ``forward solver''. To underline the general nature of our approach, 
+  playing the role of the ``forward solver''. To underline the general nature of our framework's software design, 
   in a similar project, the described methods are used for cavity shape optimisation based on \cite{ARBENZ2008381}. 
@@
   already implementing the polling protocol for default worker types.
-As shown in the API in Listing 3, the \texttt{Worker} class expects an
-  implementation to provide implementations for those three methods.
+As shown in the API in Listing 2, the \texttt{Worker} class expects an
+  implementation to provide implementations for three methods.
 
@@
 \noindent
-An expression parser using Boost Spirit~\cite{boost} was implemented.
+an expression parser using Boost Spirit~\cite{boost} was implemented.
 In addition to the parser, we need an evaluator able to evaluate an expression,
@@
   function calls in their AST.
-As shown in Listing 5 this is done by creating a collection of Boost
+As shown in Listing 3 this is done by creating a collection of Boost
   functions~\cite{boost3} corresponding to the
@@
 The framework contains a wrapper implementing the API mentioned in
-  Listing 3 for using \textsc{OPAL}~\cite{opal} as the forward solver.
+  Listing 1 for using \textsc{OPAL}~\cite{opal} as the forward solver.
 \textsc{OPAL} provides different trackers for cyclotrons and linear
@@
 
-\section{Example Optimization File}
+\section{Example Optimization File}\label{ap:inputfile}
 

### 2019-03-19 paper/submission/theor-experiment.tex
small edits done?

@@
 \begin{center}
-\caption{Input Parameters for initial twenty four hour AWA optimization experiments. 
+\caption{Input Parameters for initial twenty-four hour AWA optimization experiments. 
 The gene mutation probability was equal to the mutation probability (not shown) in all four experiments. 
@@
 The maximum number of individuals per generation was fixed at 80. 
-This number was chosen based on the node architecture, and the 
+This number was chosen based on the node architecture, and  
 to prevent a prohibitive computational cost.  
-Each experiment was allowed to run for twenty four hours, with 
+Each experiment was allowed to run for twenty-four hours, with 
 a maximum generation limit of 100. 
@@
 The objectives include: $\varepsilon_{x}\left(s = s_1\right)\text{, } \varepsilon_{x}\left(s = s_2\right)$, $\text{rms}_{s}\left(s = s_1\right)\text{, and }  \text{rms}_{s}\left(s = s_2\right)$. 
-The OPAL input file for these cases and all subsequent optimization runs in this paper, 
-can be found at in following repository: \url{https://github.com/nneveu/awa-tba}.
+An example OPAL input file, used to perform the optimization in ex-1, 
+can be found in Supplemental Material at [URL will be inserted by publisher].
+All other optimization runs in the paper use this input file format.
 
 After collection of the data for all four experiments, several metrics
-were compared, including number of generations completed in twenty four hours and
+were compared, including number of generations completed in twenty-four hours and
 Pareto fronts at $s_1$ and $s_2$, see Fig.~\ref{awa-linac}.
@@
 Perhaps this trade off would be acceptable if the Pareto front was significantly 
-improved, but from Fig. \ref{expareto}, but this is not the case.
-Similar arguments can be made for ex-2, which evaluated about 15 less generations.
+improved, but from Fig. \ref{expareto}, this is not the case.
+Similar arguments can be made for ex-2, which evaluated about 15 fewer generations.
 The Pareto fronts at $s_2$, are nearly identical. It is expected

### 2019-03-21 paper/submission/ZW10157-response-2.tex
removing code sections

@@
 Thank you for the additional comments.
-We have moved all code implementation details to appendices.
-In addition, further revisions have been made as suggested.
+We have moved all code implementation details to Supplemental Materials.
+In addition, further revisions and corrections have been made as suggested.
 The details can be found in the following pages.
@@
 {\bf Our response:} {\color{blue} The github link was removed,
-	and Appendix B was added to provide an example OPAL 
-	optimization input file.}
+	and a section in the Supplemental Materials file
+	was added to provide an example of an OPAL optimization input file.}
 
@@
 
+{\bf Our response: } {\color{blue} All code and an input file example 
+	have been moved to a Supplemental Materials file. 
+	The Referee's initial comments (see pg. 4) were used to 
+	decide which sections would be moved. }
+
 {\bf Our response:} {\color{blue} }
@@
 paragraph 4
-also present in GPT's [ref] optimization system --> also
+also present in GPT's [ref] optimization system --$>$ also
 present in Cornell's [2005 PRSTAB] and GPT's [ref] optimization systems
@@
 
-{\bf Our response: } {\color{blue} This section has been shortened. However we would like to 
-leave the existing description, in order to drive home the fact that the framework can be 
-easily extended with other optimization algorithms.}
-
 Section VI: 
@@
 
-{\bf Our response:} {\color{blue} The code examples in sections VI-V have been removed from the updated manuscript. 
-	A sentence and link to the repository have been provided. Interested parties can refer to the repository.}
+{\bf Our response: } {\color{blue} All code and the input file example referenced above have been moved 
+					to a Supplemental Materials file.}
 

### 2019-03-21 paper/submission/prab.tex
removing code sections

--- 2019-03-19 paper/submission/prab.tex
@@
 
-\title{A Parallel General Purpose Multi-Objective Optimization Framework,
-  with Application To Electron Beam Dynamics}
+\title{A parallel general purpose multi-objective optimization framework,
+	with application to electron beam dynamics}
 
@@
   technology.
-Fields, such as material science, chemistry, the biosciences, particle
+Fields such as material science, chemistry, the biosciences, particle
   physics, nuclear physics and medicine depend on reliable and effective
@@
   accelerators, we solve large multi-objective design optimization
-  problems to automate the investigation for an optimal set of tuning parameters.
+  problems to automate the investigation for an ideal set of tuning parameters.
   This approach has been used in the past with much 
@@
 A ``pilot'' coordinates all efforts between the optimization algorithm and the
-  beam dynamics task. In the following sections, we will also use the notion of ``forward solver'' to indicate the beam dynamics task.
-This forms a robust and general framework for massively parallel
+  beam dynamics task. Details of the code implementation, e.g. framework components, 
+  optimizer and forward solver implementation, and parallelization, can be found in the 
+  Supplemental Material at [URL will be inserted by publisher].
+In combination, this forms a robust and general framework for massively parallel
   multi-objective optimization.
@@
   level of detail and time to solution.
-This problem is addressed later in Section~(\ref{awa:subsection:test}) by using forward solvers with different time and
-  resolution complexity.
+This problem is addressed later in Section~(\ref{awa:subsection:test}) by using forward solvers with different time and resolution complexity.
 
-The framework discussed here, incorporates the following three contributions:
+The framework used here, incorporates the following three contributions:
 %
@@
 
-\subsection{Components}
-
-The basic assumption in simulation-based optimization is that a
-  call to an expensive simulation software component present in the
-  constraints or objectives is needed.
-The framework is divided in three exchangeable components, as shown in
-  Fig.~\ref{fig:opt-framework-layout}, to encapsulate the major behavioral
-  patterns of the framework.
-%
-\begin{figure}
-  \centering
-  \includegraphics[width=0.7\linewidth]{opt-framework-layout}
-  \caption{Schematic view of messages passed within the network between the
-    three roles.
-  The dashed cyan path describes a request (job $j_1$) sent from $O_i$ to the
-  \textsc{Pilot} being handled by $W_j$. Subsequently the result $r_1$ is
-  returned to the requesting \textsc{Optimizer} ($O_i$). $W_j$ are beam dynamics 
-  simulations within OPAL.}
-  \label{fig:opt-framework-layout}
-\end{figure}
-
-%
-The \textsc{Pilot} component acts as a bridge between the optimizer and
-  forward solvers, providing the necessary functionality to handle passing
-  requests and results between the \textsc{Optimizer} and the
-  \textsc{Simulation} modules.
-The framework was implemented in \texttt{C++}, utilizing features like template
-parameters to specify the composition of the framework.
-``Default'' implementations are provided that can be controlled via command line options.
-Due to its modular design, all components can be completely customized.
-
-Every available MPI process will take up one of the three available roles (see
-  Fig.~\ref{fig:framenetwork}):  one process acts as \textsc{Pilot}, the
-  remaining processes are divided amongst \textsc{Worker} and
-  \textsc{Optimizer} roles.
-Both, the \textsc{Worker} and the \textsc{Optimizer} can consist of multiple
-  MPI processes to exploit parallelism.
-As shown in Fig.~\ref{fig:opt-framework-layout}, the \textsc{Pilot} is used
-  to coordinate all ``information requests'' between the \textsc{Optimizer}
-  and the \textsc{Worker}.
-An information request is a job that consists of a set of design variables
-  (e.g.~the genes of an individual) and a type of information it requests
-  (e.g.~function evaluation or derivative).
-The \textsc{Pilot} keeps checking for idle \textsc{Worker}s and assigns jobs
-  in the queue to any free \textsc{Worker}.
-Once the \textsc{Worker} has computed and evaluated the request its results
-  are returned to the \textsc{Optimizer} that originally requested the
-  information.
-
-After a process gets appointed a role, it starts a polling loop to asynchronously
-  check for appropriate incoming requests.
-To that end a \textsc{Poller} interface helper class has been introduced.
-The \textsc{Poller} interface consists of an infinite loop that checks
-  periodically for new MPI messages.
-Upon reception a new message is immediately forwarded to the appropriate
-  handler: the \texttt{onMessage()} method.
-The method is called with the \texttt{MPI\_Status} of the received message and
-  a \texttt{size\_t} value specifying different values depending on the value
-  of the \texttt{MPI\_Tag}.
-The \textsc{Poller} interface allows the implementation of special methods
-  (denoted \textit{hooks}) determining the behavior of the polling process,
-  e.g.\ for actions that need to be taken after a message has been handled.
-Every \textsc{Poller} terminates the loop upon receiving a special MPI tag.
-
-\subsection{Implementing an Optimizer}
-
-All \textsc{Optimizer} implementations have to respect the API shown in
-Listing 2.
-
-%\noindent\begin{minipage}{0.48\textwidth}
-\begin{code}[Optimizer API]
-virtual void initialize() = 0;
-
-// Poller hooks
-virtual void setupPoll() = 0;
-virtual void prePoll() = 0;
-virtual void postPoll() = 0;
-virtual void onStop() = 0;
-virtual bool onMessage(MPI_Status status,
-                       size_t length) = 0;
-\end{code}
-%\end{minipage}
-
-All processors running an \textsc{Optimizer} component call the
-  \texttt{initialize} entry point after role assignment in the
-  \textsc{Pilot}.
-The implementation of \texttt{initialize} must set up and start the poller and
-  the optimization code.
-Since an optimizer derives from the \texttt{Poller} interface, predefined
-  hooks can be used to determine the polling procedure.
-Hooks can be implemented as empty methods, but the \texttt{onMessage}
-  implementation should reflect the optimization part of the protocol for
-  handling events from the \textsc{Pilot}.
-A special set of communicator groups serves as communication channels to the
-  \textsc{Pilot}, its job queue, and processes supporting the
-  \textsc{Optimizer} component.
-
-\subsection{Implementing a Forward Solver}
-
-In most cases, forward solver implementations are simple wrappers to run
-  an existing ``external'' simulation code using a set of design variables as
-  input. In the case of the OPAL integration, the \texttt{main} function is
-  playing the role of the ``forward solver''. To underline the general nature of our approach, 
-  in a similar project, the described methods are used for cavity shape optimisation based on \cite{ARBENZ2008381}. 
-As for the \textsc{Optimizer} component there exists a base class, labeled
-  \texttt{Simulation} as common basis for all \textsc{Simulation}
-  implementations.
-In addition, this component also inherits from the \texttt{Worker} class,
-  already implementing the polling protocol for default worker types.
-As shown in the API in Listing 3, the \texttt{Worker} class expects an
-  implementation to provide implementations for those three methods.
-
-\begin{code}[Simulation API]
-virtual void run() = 0;
-virtual void collectResults() = 0;
-virtual reqVarContainer_t getResults() = 0;
-\end{code}
-
-First, upon receiving a new job, the \texttt{Worker} will call the \texttt{run} 
-method on the \textsc{Simulation} implementation.
-This expects the \textsc{Simulation} implementation to run the simulation in a 
-\textit{blocking} fashion, meaning the method call blocks and does not return
-until the simulation has terminated.
-Subsequently, the \texttt{Worker} calls \texttt{collectResults}, where the
-\textsc{Simulation} prepares the result data, e.g. parsing output files,
-and stores the requested information in a \texttt{reqVarContainer\_t} data structure.
-Finally, the results obtained with \texttt{getResults} are sent to the \textsc{Pilot}. 
-As before, the serialized data is exchanged using MPI point-to-point communication using a specific set of communicators.
-
-\subsection{Specifying the Optimization Problem}
-
-We aimed at an easy and expressive way for users to specify multi-objective optimization problems.
-Following the principle of keeping metadata (optimization and simulation input data) together, 
-we decided to embed the optimization problem specification in the simulation input file by 
-prefixing it with special characters, e.g. as annotations prefixed with a special character.
-In some cases, it might not be possible to annotate the simulation input file.
-By providing an extra input file parser, optimization problems can be read from stand-alone files.
-To allow arbitrary constraints and objective expressions, such as
-%
-%{0.2cm}
-\begin{Verbatim}[fontsize=\scriptsize]
-  name: OBJECTIVE,
-        EXPR="5 * average(42.0, "measurement.dat") + ENERGY";
-\end{Verbatim}
-%\vspace{0.2cm}
-%
-\noindent
-An expression parser using Boost Spirit~\cite{boost} was implemented.
-In addition to the parser, we need an evaluator able to evaluate an expression,
-given a parse tree and variable assignments to an actual value.
-Expressions arising in multi-objective optimization problems usually evaluate
-to booleans or floating point values.
-The parse tree, also denoted abstract syntax tree (AST), is constructed recursively while an expression is parsed.
-Upon evaluation, all unknown variables are replaced with values, 
-either obtained from simulation results or provided by other subtrees in the AST.
-In this stage, the AST can be evaluated bottom-up and the desired result is
-  returned after processing the root of the tree.
-
-To improve the expressive power of objectives and constraints, a
-  simple mechanism to define and call custom functions in expressions was introduced.
-Using simple functors, to compute an
-  average over a set of data points, enriches expressions with custom
-  functions.
-Custom function implementations overload the \texttt{()} parenthesis operator.
-The function arguments specified in the corresponding expression are stored in
-  a \texttt{std::vector} of Boost variants~\cite{boost2} that can be
-  booleans, strings or floating point values.
-
-All custom functions are registered with expression objects.
-This is necessary to ensure that expressions know how they can resolve
-  function calls in their AST.
-As shown in Listing 5 this is done by creating a collection of Boost
-  functions~\cite{boost3} corresponding to the
-  available custom functions in expressions and passing this to the
-  \textsc{Pilot}.
-
-%\noindent\begin{minipage}{\textwidth}
-\begin{code}[Creating function pointer for registering functor]
-functionDictionary_t funcs;
-client::function::type ff;
-ff = average();
-funcs.insert(std::pair<std::string, 
-		client::function::type> 
-       		("my_average_name", ff));
-\end{code}
-%\end{minipage}
-
-A set of default operators, corresponding to a mapping to \texttt{C} math
-  functions, is included in the dictionary by default.
-This enables an out of source description of optimization problems containing
-  only simple math primitives.
-
-\subsection{Parallelization} \label{sec:parallelization}
-
-The parallelization is defined by a mapping of the roles introduced above to
-  available cores.
-Command-line options allow the user to steer the number of processors used in
-  worker and optimizer groups.
-Here, we mainly use the command-line options to steer the number of processors
-  running a forward solver.
-
-One major disadvantage of the master/slave implementation model is the fast
-  saturation of the network links surrounding the master node.
-In \cite{bctg:09} authors observe an exponential increase in hot-spot latency
-  with increasing number of workers that are attached to one master process.
-The limiting factor is the number of outgoing links of a node in the
-  network topology. For a few workers, the links surrounding a
-  master process are subject to congestion.
-This effect is amplified further by large message sizes.
-
-To that end we implemented a solution propagation based on rumor networks 
-(see \cite{bgps:06,ayss:09}) using only one-sided communication.
-This limits the number of messages sent over the already heavily used links
-surrounding the master node and helps to prevent the use of
-global communication. Using information about the interconnection network topology and the
-application communication graph, the task of assigning roles helps to further
-improve the parallel performance.
-
-\section{FORWARD SOLVER} \label{sec:forward-solver}
-
-The framework contains a wrapper implementing the API mentioned in
-  Listing 3 for using \textsc{OPAL}~\cite{opal} as the forward solver.
-\textsc{OPAL} provides different trackers for cyclotrons and linear
-  accelerators with satisfactory parallel performance. 
-With access to the \textsc{OPAL} forward solver, the framework is able to
-  tackle a multitude of optimization problems arising in the domain of
-  particle accelerators.
-  The framework is also integrated into \textsc{OPAL} so that users can 
-  define optimization problems within an input file, requiring no 
-  additional knowledge or installation of the API to use it.
-
-If the objectives and constraints are simple arithmetical expressions, 
-the \texttt{FunctionEvaluator} simulator can be used.
-Using functors and the default expression primitives, 
-multi-objective optimization problems can be specified, 
-i.e.\ the benchmark problem presented in \cite{hbwh:05}:
-%
-
-	\begin{widetext}
-		\begin{align} \label{eqn:bench}
-		\text{min} & \left[ 1 - \exp \left( -1 \left(
-		\left(x_1 - \frac{1}{\sqrt{3}} \right)^2 +
-		\left(x_2 - \frac{1}{\sqrt{3}} \right)^2 +
-		\left(x_3 - \frac{1}{\sqrt{3}} \right)^2 \right)\right), \right. \\
-		\vspace{3em} 
-		& \left. 1 - \exp \left( -1 \left(
-		\left(x_1 + \frac{1}{\sqrt{3}} \right)^2 +
-		\left(x_2 + \frac{1}{\sqrt{3}} \right)^2 +
-		\left(x_3 + \frac{1}{\sqrt{3}} \right)^2 \right)\right) \right]^T \nonumber \\
-		\vspace{3em} \nonumber \\
-		\text{s.t.} \quad & \quad -1 \le x_i \le 1, \quad i=1,2,3 \nonumber
-		\text{.} \nonumber
-		\end{align}
-	\end{widetext}
-
 \input{theor-experiment}
@@
 
-\appendix
-
-\section{Code Implementation}
-
-\section{Example Optimization File}
-
-This examples serves to show how a user can 
-set up a multiobjective optimization run 
-within an OPAL input file.
-
-The code that follows was used to perfrom ex-1 in Section~\ref{sec:experiments}.
-
 \bibliography{paper}

### 2019-03-21 paper/submission/supplemental_material.tex
adding supp material file

--- 2018-09-29 paper/prab.tex
@@
-\documentclass[%
-reprint,
-%superscriptaddress,
-%groupedaddress,
-%unsortedaddress,
-%runinaddress,
-%frontmatterverbose, 
-%preprint,
-%showpacs,preprintnumbers,
-%nofootinbib,
-%nobibnotes,
-%bibnotes,
-amsmath,amssymb,
-aps,
-%pra,
-%prb,
-%rmp,
-prstab,
-%prstper,
-%floatfix,
-]{revtex4-1}
+\documentclass[preprint,linenumbers,amsmath,amssymb,aps,prstab]{revtex4-1}%
 
@@
 
-\usepackage{array}
-\newcolumntype{C}{ >{\centering\arraybackslash} m{2.5cm} }
-\newcolumntype{D}{ >{\centering\arraybackslash} m{3cm} }
-
-\newcommand{\nrnote}[1]{\textsf{{\color{blue}{ NN note:}   #1 }}}
-\newcommand{\lsedit}[1]{\textsf{{\color{violet}{ ls note:}   #1 }}}
 \begin{document}
 
-\title{A Parallel General Purpose Multi-Objective Optimization Framework,
-  with Application To Electron Beam Dynamics}
-%\thanks{A footnote to the article title}%
+\title{A parallel general purpose multi-objective optimization framework,
+  with application to electron beam dynamics}
 
@@
 
-\begin{abstract}
-Particle accelerators are invaluable tools for research in the basic and
-  applied sciences, in fields such as materials science, chemistry,
-  the biosciences, particle physics, nuclear physics and medicine.
-The design, commissioning, and operation of accelerator facilities is a
-  non-trivial task, due to the large number of control parameters and the
-  complex interplay of several conflicting design goals.
-We propose to tackle this problem by means of multi-objective optimization
-  algorithms which also facilitate a parallel deployment.
-In order to compute solutions in a meaningful time frame a fast 
-  and scalable software framework is required.
-In this paper, we present the implementation of such a general-purpose
-  framework for simulation-based multi-objective optimization methods that
-  allows the automatic investigation of optimal sets of machine parameters.
-The implementation is based on a master/slave paradigm, employing several
-  masters that govern a set of slaves executing simulations and performing
-  optimization tasks.
-Using evolutionary algorithms and \textsc{OPAL}~simulations as optimizer and
-  forward solver in our framework, validation experiments and first
-  results of multi-objective optimization problems in the domain of beam
-  dynamics is presented.
-
-\end{abstract}
-
-\pacs{Valid PACS appear here}% PACS, the Physics and Astronomy
-% Classification Scheme.
-%\keywords{Suggested keywords}%Use showkeys class option if keyword
-%display desired
 \maketitle
 
-\section{INTRODUCTION} \label{sec:introduction}
+\section{Supplemental Material} \label{sec:introduction}
 
-Particle accelerators play a significant role in many aspects of science and
-  technology.
-Fields, such as material science, chemistry, the biosciences, particle
-  physics, nuclear physics and medicine depend on reliable and effective
-  particle accelerators, both as research but as well as practical tools.
-Achieving the required performance in the design, commissioning, and operation
-  of accelerator facilities is a complex and versatile problem.
-Today, tuning machine parameters, e.g. bunch charge, emission time and
-  various parameters of beamline elements, is most commonly done manually by
-  running simulation codes to scan the parameter space.
-This approach is tedious, time consuming and can be error prone.
-In order to be able to reliably identify optimal configurations of
-  accelerators we propose to solve large multi-objective design optimization
-  problems to automate the investigation for an optimal set of tuning
-  parameters.
-Observe that multiple and conflicting optimality criteria call for a
-  multi-objective approach.
+The following information provides additional details about the code implementation
+used in the paper above. In the following sections, we will also use the notion of ``forward solver'' to indicate the beam dynamics simulation (i.e. task).
 
-\begin{figure}%[h!]
-%\begin{center}%\normalsize
-	\scalebox{0.8}{
-	\pgfdeclarelayer{background}
-	\pgfsetlayers{background,main}
-	\begin{tikzpicture}[text=black]%[scale=0.05]%, transform shape]
-	\input{figures/opt-framework_code.tex}
-	\end{tikzpicture}
-}
-%\end{center}
-\caption{Multi-objective framework: the pilot (master) solves the
-	optimization problem specified in the input file by coordinating optimizer
-	algorithms and workers running forward solves.}
-\label{fig:framenetwork}
-\end{figure}
-
-A modular multi-objective software framework was developed (see
- Fig.~\ref{fig:framenetwork}) where the core functionality of the optimizer is decoupled from
- the ``beam dynamics'' but fully integrated in the OPAL \cite{opal} framework. 
-To that end, we use a master/slave mechanism where a master process governs a
- set of slave processes given some computational tasks (beam dynamics simulation) to complete.
-This separation allows easy interchange of optimization algorithms, forward
-  solvers and optimization problems.
-A ``pilot'' coordinates all efforts between the optimization algorithm and the
-  beam dynamics task. In the sequel we will also use the notion of ``forward solver'' to indicate the beam dynamics task.
-This forms a robust and general framework for massively parallel
-  multi-objective optimization.
-Currently the framework offers one concrete optimization algorithm, an
-  evolutionary algorithm employing a \textsc{NSGA-II} selector \cite{pisa}.
-Normally, simulation based approaches are plagued by the trade-of between
-  level of detail and time to solution.
-This problem is addressed later in Section~(\ref{awa:subsection:test}) by using forward solvers with different time and
-  resolution complexity.
-
-The framework discussed here, incorporates the following three contributions:
-%
-\begin{enumerate}
-  \item Implementation of a scalable optimization algorithm capable of
-        approximating Pareto fronts in high dimensional spaces,
-  \item design and implementation of a modular framework that is simple to use
-        and deploy on large scale computational resources, and
-  \item demonstrating the usefulness of the proposed framework on a real world
-        application in the domain of particle accelerators,
-        with the optimization problem set as 
-        the high charge photoinjector at the Argonne Wakefield Accelerator (AWA). 
-\end{enumerate}
-
-The next section introduces the notation of multi-objective optimization
-theory and describes the first implemented optimizer.
-In Section~\ref{sec:framework} the implementation of the framework is discussed.
-We introduce the employed forward-solver in Section~\ref{sec:forward-solver}.
-A validation and a proof of concept application in the two beam dynamics problems 
-mentioned above is discussed in Section~\ref{sec:experiments}.
-
-\section{MULTI-OBJECTIVE OPTIMIZATION} \label{sec:optimization}
-
-Optimization problems deal with finding one or more feasible solutions
-  corresponding to extreme values of objectives.
-If more than one objective is present in the optimization problem this is called
-  a multi-objective optimization problem (MOOP).
-A MOOP is defined as
-%
-\begin{align}
-  \text{ min} \quad & \quad f_m({\bf x}), ~& m &= 1, \dots, M, \label{eq:moop:obj}\\
-  \text{s.t.} \quad & \quad g_j({\bf x}) \geq 0, & j &= 0, \dots, J,
-  \label{eq:moop:constr}\\
-  \quad & \quad  x_i^L \leq {\bf x}=x_i \leq x_i^U,& i &=0, \dots, n
-  \label{eq:moop:dvar} \text{,}
-\end{align}
-%
-where $\bf f$ denotes the objectives (\ref{eq:moop:obj}),
-  $\bf g$ the constraints (\ref{eq:moop:constr}),
-  and $\bf x$ the design variables (\ref{eq:moop:dvar}).
-
-Often, conflicting objectives are encountered, and this complicates the concept of
-  optimality.
-To illustrate this, let us consider the problem of buying a car.
-Naturally, we try to bargain the lowest price for the best performance,
-  e.g.\ maximal horsepower or minimal fuel consumption.
-This can be formulated as MOOP (\ref{eq:car-moop}).
-%
-\begin{equation}
-  \begin{array}{cl}
-  \min          & \quad \left[ \text{price}, -\text{performance} \right]^T \\
-    \text{s.t.} & \quad \text{low}_\text{pr} \leq \text{price} \leq \text{high}_\text{pr}\\
-                & \quad \text{low}_\text{pe} \leq \text{performance} \leq \text{high}_\text{pe}
-  \end{array}
-  \label{eq:car-moop}
-\end{equation}
-
-\begin{figure}
-  \begin{center}
-    \begin{tikzpicture}[scale=1.3, transform shape]
-      \input{figures/car-trade-off}
-    \end{tikzpicture}
-  \end{center}
-  \caption{Two competing objectives can not be optimal at the same time.
-    Red dots represent Pareto optimal points, while the green square $x_4$ is
-    dominated (exhibits a worse price per performance ratio than e.g. $x_2^*$)
-    by all points on the blue curve (Pareto front).
-  }
-  \label{fig:tradeoff}
-\end{figure}
-
-In general, it is not possible to get the maximal performance for the lowest
-  price and a trade-off decision between performance and price has to be
-  reached (see Fig.~\ref{fig:tradeoff}).
-Since not every choice is equally profitable for the buyer (for example, car
-  $x_4$ costs as much as $x_2^*$ but offers less performance), we pick
-  trade-offs (red points) that are essentially ``equally optimal'' in both
-  conflicting objectives, meaning, we cannot improve one point without hurting
-  at least one other solution.
-This is known as \textit{Pareto optimality}.
-The set of Pareto optimal points (blue curve) forms the Pareto front or
-  surface.
-All points on this surface are considered to be Pareto optimal.
-
-Once the shape of the Pareto front has been determined, the buyer can
-  \textit{specify preference}, balancing the features by observing the
-  effect on the optimality criteria, converging to the preferred solution.
-This is called \textit{a posteriori} preference specification since 
-  a solution is selected after all possible trade-offs have been presented to us.
-An alternative is to specify preference \textit{a priori}, e.g. by
-  weighting (specifying preference before solving the problem) and combining
-  all objectives into one and applying a single-objective method to solve the
-  problem (yielding only one solution).
-In many situations preference is not known \textit{a priori} and an
-  \textit{a posteriori} preference specification helps conveying a deeper
-  understanding of the solution space.
-The Pareto front can be explored and the impact of a trade-off decision then
-  becomes visible.
-
-Sampling Pareto fronts is far from trivial.
-A number of approaches have been proposed,
-  e.g.\ evolutionary algorithms~\cite{deb:09},
-  simulated annealing~\cite{kigv:83},
-  swarm methods~\cite{keeb:95},
-  and many more~\cite{domc:96,cati:02,kara:05,hoss:09}.
-In the next section, we briefly introduce the theory of evolutionary algorithms
-  used in the present work.
-
-\subsection{Evolutionary Algorithms}
-
-Evolutionary algorithms are loosely based on nature's evolutionary
-  principles to guide a population of individuals towards an improved solution
-  by honoring the ``survival of the fittest'' principle.
-This ``simulated'' evolutionary process preserves entropy (or diversity in
-  biological terms) by applying genetic operators, such as mutation and
-  crossover, to remix the fittest individuals in a population.
-Maintaining diversity is a crucial feature for the success of all evolutionary
-  algorithms.
-
-In general, a generic evolutionary algorithm consists of the following
-  components:
-%
-\begin{itemize}
-  \item \textit{Genes}: traits defining an individual,
-  \item \textit{Fitness}: a mapping from genes to a fitness value for each
-    individual,
-  \item \textit{Selector}: selecting the $k$ fittest individuals of a
-    population based on some sort of ordering,
-  \item \textit{Variator}: recombination (mutations and crossover) operators
-    for offspring generation.
-\end{itemize}
-
-\begin{figure}
-    \centering
-    \scalebox{1}{
-    \begin{tikzpicture}[scale=0.8, transform shape, text=black]
-    \input{figures/ga_explained_big.tex}
-    \end{tikzpicture}
-	}
-  \caption{Schematic view of interplay between selector and variator. The
-  selector ranks all individuals in the population according to fitness and
-  subsequently the variator uses the fittest individuals to produces new
-  offspring. Finally, the new children are reintroduced in the population.}
-  \label{fig:varsel}
-\end{figure}
-
-Applied to multi-objective optimization problems, genes correspond to
-  design variables.
-The fitness of an individual is loosely related to the value of the objective
-  functions for the corresponding genes.
-Figure~\ref{fig:varsel} schematically depicts the connection of the
-  components introduced above.
-The process starts with an initially random population of individuals, each
-  individual with a unique set of genes and corresponding fitness,
-  representing one location in the search space.
-In a next step the population is processed by the selector
-  determining the $k$ fittest individuals according to their fitness values.
-While the $k$ fittest individuals are passed to the variator, the
-  remaining $n-k$ individuals are eliminated from the population.
-The \textsc{Variator} mates and recombines the $k$ fittest individuals to
-  generate new offspring.
-After evaluating the fitness of all the freshly born individuals a
-  \textit{generation} cycle has completed and the process can start anew.
-
-Since there already exist plenty of implementations of evolutionary algorithms,
-  it was decided to incorporate the PISA library \cite{pisa} into our
-  framework.
-One of the advantages of PISA is that it separates variator from selector,
-  rendering the library expandable and configurable.
-Implementing a variator was enough to use PISA in our framework and
-  retain access to all available PISA selectors.
-As shown in Fig.~\ref{fig:varsel}, the selector is in charge of ordering a
-  set of $d$-dimensional vectors and selecting the $k$ fittest individuals
-  currently in the population.
-The performance of a selector depends on the number of objectives and the
-  surface of the search space.
-So far, the NSGA-II selector \cite{dpam:02} has been used and exhibits satisfactory
-  convergence performance.
-
-The task of the variator is to generate offspring and ensure diversity in the
-  population.
-The variator can start generating offspring once the fitness of every
-  individual of the population has been evaluated.
-This explicit synchronization point defines an obvious bottleneck for parallel
-  implementations of evolutionary algorithms.
-In the worst case some MPI processes are taking a long time to compute the
-  fitness of the last individual in the pool of individuals to evaluate.
-During this time all other resources are idle and wait for the result of
-  this one individual in order to continue to generate and evaluate offspring.
-To counteract this effect, the selector is already called when two individuals
-  have finished evaluating their fitness, lifting the boundaries between
-  generations and evaluating the performance of individuals.
-New offspring will be generated and MPI processes can immediately return to
-  work on the next fitness evaluation.
-By calling the selector more frequently (already after two offspring
-  individuals have been evaluated) results in better populations since bad
-  solutions are rejected earlier.
-On the other hand, calling the selector more often is computationally more
-  expensive.
-
-Our variator implementation uses the master/slave architecture, presented in
-  the next section, to run as many function evaluations as possible in parallel.
-Additionally, various crossover and mutation policies are available for tuning
-  the algorithm to the optimization problem.
-
-\section{THE FRAMEWORK} \label{sec:framework}
-
-Simulation based multi-objective optimization problems are omnipresent in
-  research and industry.
-The simulation and optimization problems arising in such problems are in
-  general very big and computationally demanding.
-This motivated us to design a massively parallel general purpose framework.
-The key traits of such a design can be summarized as:
-%
-\begin{itemize}
-  \item support any multi-objective optimization method,
-  \item support any function evaluator: simulation code or measurements,
-  \item offer a general description/specification of objectives, constraints
-        and design variables,
-  \item run efficiently in parallel on current large-scale high-end clusters
-        and supercomputers.
-\end{itemize}
-%
-
-\subsection{Related Work}
-
-Several similar frameworks, e.g.~\cite{fide:09,lems:09,lbjt:07,dnld:06}, have
-  been proposed.
-Commonly these frameworks are tightly coupled to an optimization algorithm,
-  e.g.\ only providing evolutionary algorithms as optimizers.
-Users can merely specify optimization problems, but cannot change the
-  optimization algorithm.
-Our framework follows a more general approach, providing a user-friendly way
-  to introduce new or choose from existing built-in multi-objective
-  optimization algorithms.
-Tailoring the optimization algorithm to the optimization problem at hand is
-  an important feature due to the many different characteristics of
-  optimization problems that should be handled by such a general framework.
-As an example, it is shown how \textsc{Pisa} \cite{pisa}, an existing evolutionary
-  algorithm library, was integrated with ease.
-Similarly, other multi-objective algorithms could be incorporated and
-  used to solve optimization problems.
-
-The framework presented in \cite{lems:09} resembles our implementation the
-  most, aside from their tight coupling with an evolutionary algorithm
-  optimization strategy.
-The authors propose a plug-in based framework employing an island
-  parallelization model, where multiple populations are evaluated concurrently
-  and independently up to a point where some number of individuals of the
-  population are exchanged.
-This is especially useful to prevent the search algorithm to get stuck in
-  a local minimum.
-A set of default plug-ins for genetic operators, selectors and other
-  components of the algorithms are provided by their framework.
-User-based plug-ins can be incorporated into the framework by implementing a
-  simple set of functions.
-
-%Unfortunately, the island parallelization approach is not well suited for
-  %running search algorithms in the massively parallel environment.
-%The decision how many processors are assigned to an island is non-trivial.
-%\todo{PA: what are roles?}
-%Parallel performance is sensitive to placement and assignment of roles to
-  %processors of such frameworks and therefore should be considered carefully.
-%Especially the master thread on an island (used to exchange individuals
-  %between the islands and aggregate solutions) can be overwhelmed with
-  %messages from slaves evaluating individuals.
-%This creates hotspots on the network and as a result the network performance
-  %suffers.
-
-Additionally, as with simulation based multi-objective optimization, we can
-  exploit the fact that both the optimizer and simulation part of the process
-  use a certain amount of resources.
-The ratio of work between optimizer and simulation costs can be reflected in
-  the ratio of number of processors assigned to each task.
-This not only provides users with  great flexibility in using any simulation
-  or optimizer, but renders influencing the role assignment easy as well.
-
-\subsection{Components}
+\subsection{Components of the Framework}
 
@@
   \centering
-  \scalebox{0.85}{
-  \begin{tikzpicture}[text=black]
-  \input{figures/opt-framework-layout.tex}
-  \end{tikzpicture}
-}
-
+  \includegraphics[width=0.7\linewidth]{opt-framework-layout}
   \caption{Schematic view of messages passed within the network between the
@@
 
-In most cases forward solver implementations are simple wrappers to run
+In most cases, forward solver implementations are simple wrappers to run
   an existing ``external'' simulation code using a set of design variables as
-  input. In case of the OPAL integration, basically the \texttt{main} function is
-  playing the role of the ``forward solver''. Underlying the general nature of our approach, 
+  input. In the case of the OPAL integration, the \texttt{main} function is
+  playing the role of the ``forward solver''. To underline the general nature of our framework's software design, 
   in a similar project, the described methods are used for cavity shape optimisation based on \cite{ARBENZ2008381}. 
@@
 \noindent
-  An expression parser using Boost Spirit~\cite{boost} was implemented.
+an expression parser using Boost Spirit~\cite{boost} was implemented.
 In addition to the parser, we need an evaluator able to evaluate an expression,
@@
   simple mechanism to define and call custom functions in expressions was introduced.
-Using simple functors, e.g. as the one shown in Listing 4 to compute an
+Using simple functors, to compute an
   average over a set of data points, enriches expressions with custom
@@
 
-\begin{code}[Simple Average Functor]
-struct avg {
-
-    double operator()(
-      client::function::arguments_t args) const {
-
-        double limit = boost::get<double>(args[0]);
-        std::string filename =
-          boost::get<std::string>(args[1]);
-
-        double sum = 0.0;
-        for(int i = 0; i < limit; i++)
-            sum += getDataFromFile(filename, i);
-
-        return sum / limit;
-    }
-};
-\end{code}
-
 All custom functions are registered with expression objects.
@@
 The framework contains a wrapper implementing the API mentioned in
-  Listing 3 for using \textsc{OPAL} \cite{opal} as the forward solver.
+  Listing 1 for using \textsc{OPAL}~\cite{opal} as the forward solver.
 \textsc{OPAL} provides different trackers for cyclotrons and linear
-  accelerators with satisfactory parallel performance \cite{akir:09}.
-
-With access to the \textsc{OPAL} forward solver the framework is able to
+  accelerators with satisfactory parallel performance. 
+With access to the \textsc{OPAL} forward solver, the framework is able to
   tackle a multitude of optimization problems arising in the domain of
@@
 
-% AA: this is too much for Phys Rev. AB  
-% By abiding to the API from Listing 3 it becomes trivial to add new forward
-% solvers to the framework (see Appendix A).
-
-If the objectives and constraints are simple arithmetical expressions, the
-  \texttt{FunctionEvaluator} simulator can be used.
-Using functors and the default expression primitives already powerful
-  multi-objective optimization problems can be specified, i.e.\ the benchmark
-  problem presented in \cite{hbwh:05}:
+If the objectives and constraints are simple arithmetical expressions, 
+the \texttt{FunctionEvaluator} simulator can be used.
+Using functors and the default expression primitives, 
+multi-objective optimization problems can be specified, 
+i.e.\ the benchmark problem presented in \cite{hbwh:05}:
 %
 
-%\begin{strip}
 	\begin{widetext}
@@
 	\end{widetext}
-%\end{strip}
 
-%
-Using the default expression primitives this can be stated in an input file
-  as:
-%
-%\vspace{0.2cm}
+\section{Example Optimization File}
 
-\begin{flushleft}
-\begin{Verbatim}[fontsize=\scriptsize]
-d1: DVAR, VARIABLE="x1", LOWERBOUND="-1.0", UPPERBOUND="1.0";
-d2: DVAR, VARIABLE="x2", LOWERBOUND="-1.0", UPPERBOUND="1.0";
-d3: DVAR, VARIABLE="x3", LOWERBOUND="-1.0", UPPERBOUND="1.0";
+This examples serves to show how a user can 
+set up a multiobjective optimization run 
+within an OPAL input file.
 
-obj1: OBJECTIVE,
-EXPR="1- exp(-1 * (sq(x1 - 1/sqrt(3)) 
-+ sq(x2 - 1/sqrt(3)) + sq(x3 - 1/sqrt(3))))";
-obj2: OBJECTIVE,
-EXPR="1- exp(-1 * (sq(x1 + 1/sqrt(3)) 
-+ sq(x2 + 1/sqrt(3)) + sq(x3 + 1/sqrt(3))))";
+The code that follows was used to perfrom ex-1 in Section~\ref{sec:experiments}.
 
-objs:    OBJECTIVES = (obj1, obj2);
-dvars:   DVARS = (d1, d2, d3);
-constrs: CONSTRAINTS = ();
-opt: OPTIMIZE, OBJECTIVES=objs, DVARS=dvars, CONSTRAINTS=constrs;
-\end{Verbatim}
-\end{flushleft}
-%\vspace{0.2cm}
-
-\input{theor-experiment}
-
-\section{CONCLUSIONS} \label{sec:conclusions}
-
-A general-purpose framework for solving multi-objective
-  optimization problems was presented.
-Its modular design simplifies the application to simulation-based optimization
-  problems for a wide range of problems and allows to exchange the
-  optimization algorithm.
-%In a recent work, we successfully implemented and integrated another
-  %optimization algorithm, originally presented in~\cite{pesc:11}, into our
- % framework.
-The flexibility of being able to adapt both ends of the optimization
-  process, the forward solver and the optimization algorithm simultaneously
-  not only leads to broad applicability but it facilitates the ability to
-  tailor the optimization strategy to the optimization problem as well.
-
-%This first study shows that the framework is ready to tackle problems arising
-%  in the domain of beam dynamics.
-%
-%Interestingly, the computation of a good approximation of the Pareto front is
-%  already feasible on a small cluster using only a modest number of MPI
-%  processes.
-%  
-%For 1000 generations consisting of 2048 feasible and 8354 infeasible function
-%  evaluations (simulations) the optimizer needed $845$ minutes on the
-%  \textsc{Felsim} cluster on $16$ processes.
-%
-%When we double the number of processes to $32$ (\textsc{Felsim} allows a
-%  maximum of $64$ processes per job) the runtime improves to $302$ minutes (2048
-%  accepted and 5426 infeasible individuals).
-%Notice that the runtime can vary due to the random nature of the process.
-%Nevertheless we see a reasonable speeduo when using more cores to solve the
-%  optimization problem. %and the parallel performance will be further evaluated
-%  in a forthcoming publication.
-%The number of individuals is the only limiting factor.
-The framework was integrated into OPAL, and used 
-to study a beam dynamics problem at the AWA.
-A scan of time step and hyper parameters was done to determine computational settings.
-Then a full scale physics optimization was performed.
-Optimization of the 3D beam size and energy spread was accomplished.
-The TBA beam line presented is currently being installed at the AWA.
-Once installation is complete, 
-the results shown here will guide future experiments at the AWA.
-%This problem also took advantage of the frameworks massively parallel capabilities by
-%running on 2624 processes on Bebop at LCRC.
-
-In contrast to approaches that are tightly coupled to the optimization
-  algorithm, the range of possible applications is much wider.
-Even in cases where the mathematical model of the forward solver is not known
-  exactly, fixed or on the real time measurements can be used to guide the
-  search for the Pareto optimal solutions.
-Finally, combining the presented multi-objective optimization framework with
-  a physicist long standing experience in the field provides a solid basis
-  for better understanding and improving the decision making process in the
-  design and operation of particle accelerators.
-
-\section{ACKNOWLEDGMENT}
-
-The authors thank the AWA team for contributing to the
-  formulation of optimization problems. 
-  We gratefully acknowledge the computing resources provided on Bebop,
-  a HPC cluster operated by the LCRC at ANL.
-  Thanks to Scott Doran for providing CAD drawings of the AWA beam lines.
-  This work was partly supported by the 
-  U.S. Department of Energy, Office of Science, under 
-  contract number DE-AC02-06CH11357 and grant number DE-SC0015479.
-
-% AA: this is too much for Phys Rev. AB
-
-% \appendix
-
-%\section{Forward Solver Implementation}
-%
-%A simple implementation, e.g.\ using a Python forward solver, is given below
-%  in Listing 6.
-%We assume the Python script executes a simulation and dumps results in the
-%  \textsc{SDDS} file format~\cite{borl:00}.
-%Utility classed are used to parse the result data and fill the appropriate
-%  structures returned to the optimizer algorithm.
-%
-%\begin{code}[Simple Simulation Wrapper]
-%#include <map>
-%#include <string>
-%#include <vector>
-%
-%#include "Util/Types.h"
-%#include "Util/CmdArguments.h"
-%#include "Simulation/Simulation.h"
-%
-%#include "boost/smart_ptr.hpp"
-%
-%class SimpleSimulation : public Simulation {
-%
-%public:
-%
-%    SimpleSimulation(Expressions::Named_t objectives,
-%                     Expressions::Named_t constraints,
-%                     Param_t params, std::string name, MPI_Comm comm,
-%                     CmdArguments_t args);
-%
-%    ~SimpleSimulation();
-%
-%    /// Calls simulation through Python wrapper and returns when simulation
-%    /// has either failed or finished.
-%    void run() {
-%        // user implements wrappers
-%        prepare_input_file();
-%        run_python_simulation();
-%    }
-%
-%    /// Parse SDDS stat file and build up requested variable dictionary.
-%    void collectResults(){
-%
-%        Expressions::Named_t::iterator it;
-%        for(it = objectives_.begin(); it != objectives_.end(); it++) {
-%
-%            Expressions::Expr_t *objective = it->second;
-%
-%            // find out which variables we need in order to evaluate the
-%            // objective
-%            variableDictionary_t variable_dictionary;
-%            std::set<std::string> req_vars = objective->getReqVars();
-%
-%            if(req_vars.size() != 0) {
-%
-%                boost::scoped_ptr<SDDSReader> sddsr(new SDDSReader(fn));
-%
-%                try {
-%                    sddsr->parseFile();
-%                } catch(OptPilotException &e) {
-%                    std::cout << "Exception while parsing SDDS file: "
-%                        << e.what() << std::endl;
-%                    break;
-%                }
-%
-%                // get all the required variable values from the stat file
-%                foreach(std::string req_var, req_vars) {
-%                    if(variable_dictionary.count(req_var) == 0) {
-%
-%                        try {
-%                            double value = 0.0;
-%                            sddsr->getValue(1 /*atTime*/, req_var, value);
-%                            variable_dictionary.insert(
-%                                std::pair<std::string, double>(req_var, value));
-%                        } catch(OptPilotException &e) {
-%                            std::cout << "Exception while getting value "
-%                                      << "from SDDS file: " << e.what()
-%                                      << std::endl;
-%                        }
-%                    }
-%                }
-%            }
-%
-%            // and evaluate the expression using the built dictionary of
-%            // variable values
-%            Expressions::Result_t result =
-%                objective->evaluate(variable_dictionary);
-%
-%            std::vector<double> values;
-%            values.push_back(boost::get<0>(result));
-%            bool is_valid = boost::get<1>(result);
-%
-%            reqVarInfo_t tmps = {EVALUATE, values, is_valid};
-%            requestedVars_.insert(
-%                std::pair<std::string, reqVarInfo_t>(it->first, tmps));
-%
-%        }
-%    }
-%
-%    /// returns container containing all requested variables with results
-%    reqVarContainer_t getResults() { return requestedVars_; }
-%
-%private:
-%
-%    /// holds solutions returned to the optimizer
-%    reqVarContainer_t requestedVars_;
-%
-%    Expressions::Named_t objectives_;
-%    Expressions::Named_t constraints_;
-%
-%    MPI_Comm comm_;
-%};
-%
-%#endif
-%\end{code}
-
-\bibliographystyle{abbrv}
 \bibliography{paper}

### 2019-03-21 paper/submission/prab.tex
finishing response 2

@@
 theory and describes the first implemented optimizer.
-In Section~\ref{sec:framework}, the implementation of the framework is discussed.
-We introduce the employed forward-solver in Section~\ref{sec:forward-solver}.
 A validation and a proof of concept application in the beam dynamics problems 
 mentioned above is discussed in Section~\ref{sec:experiments}.
+The implementation of the framework and forward-solver is 
+discussed in Supplemental Material at [URL will be inserted by publisher].
 
@@
 \end{itemize}
-%
 
@@
 
-The framework presented in \cite{lems:09} resembles our implementation the
+The framework presented in~\cite{lems:09} resembles our implementation the
   most, aside from their tight coupling with an evolutionary algorithm
@@
 User-based plug-ins can be incorporated into the framework by implementing a
-  simple set of functions.
+  simple set of functions (See Supplemental Material).
 

### 2019-03-21 paper/submission/supplemental_material.tex
finishing response 2

@@
 \end{figure}
-
 %
@@
   information.
+%
+\begin{figure}%[h!]
+	\center
+	\includegraphics[width=0.5\textwidth]{opt-framework_code}
+	\caption{Multi-objective framework: the pilot (master) solves the
+		optimization problem specified in the input file by coordinating optimizer
+		algorithms and workers running forward solves.}
+	\label{fig:framenetwork}
+\end{figure}
 
@@
 multi-objective optimization problems can be specified, 
-i.e.\ the benchmark problem presented in \cite{hbwh:05}:
-%
-
-	\begin{widetext}
-		\begin{align} \label{eqn:bench}
-		\text{min} & \left[ 1 - \exp \left( -1 \left(
-		\left(x_1 - \frac{1}{\sqrt{3}} \right)^2 +
-		\left(x_2 - \frac{1}{\sqrt{3}} \right)^2 +
-		\left(x_3 - \frac{1}{\sqrt{3}} \right)^2 \right)\right), \right. \\
-		\vspace{3em} 
-		& \left. 1 - \exp \left( -1 \left(
-		\left(x_1 + \frac{1}{\sqrt{3}} \right)^2 +
-		\left(x_2 + \frac{1}{\sqrt{3}} \right)^2 +
-		\left(x_3 + \frac{1}{\sqrt{3}} \right)^2 \right)\right) \right]^T \nonumber \\
-		\vspace{3em} \nonumber \\
-		\text{s.t.} \quad & \quad -1 \le x_i \le 1, \quad i=1,2,3 \nonumber
-		\text{.} \nonumber
-		\end{align}
-	\end{widetext}
+such as the benchmark problem presented in~\cite{hbwh:05}, 
+which was used for validation in Section IV, subsection A of the paper.
 
@@
 within an OPAL input file. 
+The code that follows was used to perform ex-1 in 
+Section IV, subsection B of the paper. 
+The template file referenced as \verb|optLinac_40nC.tmpl| contained the 
+element definitions for the AWA beam line.
 
-The code that follows was used to perfrom ex-1 in Section~\ref{sec:experiments}.
+\begin{verbatim}
+	OPTION, ECHO=FALSE;
+	OPTION, INFO=TRUE;
+
+	TITLE, STRING="ANL Optimisation";
+
+	dv0: DVAR, VARIABLE="IBF",    LOWERBOUND=200.0, UPPERBOUND=500.0;
+	dv1: DVAR, VARIABLE="IM",     LOWERBOUND=170.0, UPPERBOUND=260.0;
+	dv2: DVAR, VARIABLE="GPHASE", LOWERBOUND=-30.0, UPPERBOUND=0.0;
+	dv3: DVAR, VARIABLE="FWHM",   LOWERBOUND=1.5,   UPPERBOUND=10.0;
+
+	// Quad values
+	dv4: DVAR, VARIABLE="KQ1", LOWERBOUND=-8.0, UPPERBOUND=8.0;
+	dv5: DVAR, VARIABLE="KQ2", LOWERBOUND=-8.0, UPPERBOUND=8.0;
+	dv6: DVAR, VARIABLE="KQ3", LOWERBOUND=-8.0, UPPERBOUND=8.0;
+	dv7: DVAR, VARIABLE="KQ4", LOWERBOUND=-8.0, UPPERBOUND=8.0;
+
+	rmss1:  OBJECTIVE,EXPR="fabs(statVariableAt('rms_s',16.5))";
+	emitx1: OBJECTIVE,EXPR="fabs(statVariableAt('emit_x',16.5))";
+	rmss2:  OBJECTIVE,EXPR="fabs(statVariableAt('rms_s',18.5))";
+	emitx2: OBJECTIVE,EXPR="fabs(statVariableAt('emit_x',18.5))";
+	c1: CONSTRAINT, EXPR="fabs(statVariableAt('rms_x',16.5))<1.0e-1";
+	c2: CONSTRAINT, EXPR="fabs(statVariableAt('rms_y',16.5))<1.0e-1";
+
+	OPTIMIZE, INPUT="tmpl/optLinac_40nC.tmpl",
+	OUTPUT="optLinac_40nC",
+	OUTDIR="results",
+	OBJECTIVES = {rmss1, emitx1, rmss2, emitx2},
+	DVARS = {dv0, dv1, dv2, dv3, dv4, dv5, dv6, dv7},
+	CONSTRAINTS = {c1, c2},
+	INITIALPOPULATION=80,
+	MAXGENERATIONS=100,
+	NUM_MASTERS=1,
+	NUM_COWORKERS=8,
+	SIMTMPDIR="tmp",
+	TEMPLATEDIR="tmpl",
+	FIELDMAPDIR="fieldmaps",
+	NUM_IND_GEN=80,
+	GENE_MUTATION_PROBABILITY=0.1,
+	MUTATION_PROBABILITY=0.1,
+	RECOMBINATION_PROBABILITY=0.9;
+	QUIT;
+\end{verbatim}
 

### 2019-03-21 paper/submission/theor-experiment.tex
finishing response 2

@@
 \subsection{Optimizer Validation}
-
+To ensure that the optimizer works correctly, the benchmark problem presented in~\cite{hbwh:05}, 
+  \begin{widetext}
+  	\begin{align} \label{eqn:bench}
+  	\text{min} & \left[ 1 - \exp \left( -1 \left(
+  	\left(x_1 - \frac{1}{\sqrt{3}} \right)^2 +
+  	\left(x_2 - \frac{1}{\sqrt{3}} \right)^2 +
+  	\left(x_3 - \frac{1}{\sqrt{3}} \right)^2 \right)\right), \right. \\
+  	\vspace{3em} 
+  	& \left. 1 - \exp \left( -1 \left(
+  	\left(x_1 + \frac{1}{\sqrt{3}} \right)^2 +
+  	\left(x_2 + \frac{1}{\sqrt{3}} \right)^2 +
+  	\left(x_3 + \frac{1}{\sqrt{3}} \right)^2 \right)\right) \right]^T \nonumber \\
+  	\vspace{3em} \nonumber \\
+  	\text{s.t.} \quad & \quad -1 \le x_i \le 1, \quad i=1,2,3 \nonumber
+  	\text{.} \nonumber
+  	\end{align}
+  \end{widetext}
+was solved with the framework.  
+To that end, we use a metric for comparing the quality of a Pareto front.
+Given a point in the Pareto set, we compute the $m$ dimensional volume (for
+  $m$ objectives) of the dominated space, relative to a chosen origin.
+This is visualized for $2$ objectives in Fig.~\ref{fig:hypervolume}.
+For further information and details of the implementation see~\cite{whbb:12}.
+Figure~\ref{fig:pisa_bench}, and the corresponding hypervolume values in
+Table~\ref{tbl:bench_rms_error}, show expected convergence.
+The reference Pareto front is well approximated.
+It took a total of 1100 function evaluations to perform this computation.
+The hypervolume of the reference solution ($0.6575$) for our benchmark was
+ computed by sampling the solution provided in~\cite{hbwh:05}.
+ Table~\ref{tbl:bench_rms_error} shows satisfactory
+ convergence to the sampled reference Pareto front after 1000 (plus the
+ additional 100 evaluations for the initial population) function evaluations.
  \begin{figure}
@@
  \end{figure}
-
-To ensure that the optimizer works correctly, the benchmark
-  problem (\ref{eqn:bench}) was solved.
-To that end, we use a metric for comparing the quality of a Pareto front.
-Given a point in the Pareto set, we compute the $m$ dimensional volume (for
-  $m$ objectives) of the dominated space, relative to a chosen origin.
-This is visualized for $2$ objectives in Fig.~\ref{fig:hypervolume}.
-For further information and details of the implementation see~\cite{whbb:12}.
-Figure~\ref{fig:pisa_bench} and the corresponding hypervolume values in
-  Table~\ref{tbl:bench_rms_error} show expected convergence.
-The reference Pareto front is clearly very well approximated.
-It took a total of 1100 function evaluations to perform this computation.
-The hypervolume of the reference solution ($0.6575$) for our benchmark was
- computed by sampling the solution provided in~\cite{hbwh:05}.
 \begin{figure}
@@
 \end{table}
-Table~\ref{tbl:bench_rms_error} shows satisfactory
-  convergence to the sampled reference Pareto front after 1000 (plus the
-  additional 100 evaluations for the initial population) function evaluations.
 
@@
 followed by four quadrupoles and a stripline kicker. 
-The charge of interest, 40 nC, is needed for two beam acceleration (TBA) 
+The charge of interest, \SI{40}{nC}, is needed for two beam acceleration (TBA) 
 experiments performed at the AWA~\cite{gai_power_jing_2012,JING201872}, 
@@
 The max number of individuals per generation was~80.}
+\vspace{1em}
 \label{extable}
@@
 can be found in Supplemental Material at [URL will be inserted by publisher].
-All other optimization runs in the paper use this input file format.
+All other optimization runs in the paper follow this template.
 
@@
 		\label{tab:designopt}  
+		\vspace{1em} 
 		\begin{tabular}{l|c|c}

### 2019-03-25 paper/submission/prab.tex
small typo fix

@@
 considerably to meet different needs.  The facility operates at both low
-and high charge (up to 100 nC), and at high charge strong nonlinearities
+and high charge (up to \SI{100}{nC}), and at high charge strong nonlinearities
 require a full 3D space charge approach in simulations.  

### 2019-03-25 paper/submission/theor-experiment.tex
small typo fix

@@
 Minimizing the beam size at this location is essential to 
-to preventing loss of particles by scraping; 
+preventing loss of particles by scraping; 
 which ensures better transmission through the wakefield structures downstream.

### 2019-03-25 paper/submission/prab.tex
Linda's last edits

@@
 	optimization problem specified in the input file by coordinating optimizer
-	algorithms and workers running forward solves.}
+	algorithms and workers running a forward solver.}
 \label{fig:framenetwork}

### 2019-03-25 paper/submission/theor-experiment.tex
Linda's last edits

@@
 TBA section of the beam line were optimized, shown in Fig.~\ref{awa-tba}.
-The simulation model includes from the gun to the septum.
+The simulation model includes all elements from the gun to the septum.
 The optimization location is chosen as the  
@@
 The gene mutation probability was equal to the mutation probability (not shown) in all four experiments. 
-The max number of individuals per generation was~80.}
+The maximum number of individuals per generation was~80.}
 \vspace{1em}
@@
 	both x and y beam sizes are shown. The black line represents the relevant beam line aperture, while
-	the green line indicates the location of the optimization.}
+	the vertical green line indicates the location of the optimization.}
 	\label{fig:stat}

### 2019-03-25 paper/submission/prab.tex
adding bbl to main tex files

@@
 
-\bibliography{paper}
+%\bibliography{paper}
+
+%merlin.mbs apsrev4-1.bst 2010-07-25 4.21a (PWD, AO, DPC) hacked
+%Control: key (0)
+%Control: author (8) initials jnrlst
+%Control: editor formatted (1) identically to author
+%Control: production of article title (-1) disabled
+%Control: page (0) single
+%Control: year (1) truncated
+%Control: production of eprint (0) enabled
+\providecommand{\SortNoop}[1]{}
+\begin{thebibliography}{34}%
+	\makeatletter
+	\providecommand \@ifxundefined [1]{%
+		\@ifx{#1\undefined}
+	}%
+	\providecommand \@ifnum [1]{%
+		\ifnum #1\expandafter \@firstoftwo
+		\else \expandafter \@secondoftwo
+		\fi
+	}%
+	\providecommand \@ifx [1]{%
+		\ifx #1\expandafter \@firstoftwo
+		\else \expandafter \@secondoftwo
+		\fi
+	}%
+	\providecommand \natexlab [1]{#1}%
+	\providecommand \enquote  [1]{``#1''}%
+	\providecommand \bibnamefont  [1]{#1}%
+	\providecommand \bibfnamefont [1]{#1}%
+	\providecommand \citenamefont [1]{#1}%
+	\providecommand \href@noop [0]{\@secondoftwo}%
+	\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
+	\providecommand \@href[1]{\@@startlink{#1}\@@href}%
+	\providecommand \@@href[1]{\endgroup#1\@@endlink}%
+	\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
+		`\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
+	\providecommand \@@startlink[1]{}%
+	\providecommand \@@endlink[0]{}%
+	\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
+	\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
+	\providecommand \urlprefix  [0]{URL }%
+	\providecommand \Eprint [0]{\href }%
+	\providecommand \doibase [0]{http://dx.doi.org/}%
+	\providecommand \selectlanguage [0]{\@gobble}%
+	\providecommand \bibinfo  [0]{\@secondoftwo}%
+	\providecommand \bibfield  [0]{\@secondoftwo}%
+	\providecommand \translation [1]{[#1]}%
+	\providecommand \BibitemOpen [0]{}%
+	\providecommand \bibitemStop [0]{}%
+	\providecommand \bibitemNoStop [0]{.\EOS\space}%
+	\providecommand \EOS [0]{\spacefactor3000\relax}%
+	\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
+	\let\auto@bib@innerbib\@empty
+	%</preamble>
+	\bibitem [{\citenamefont {Huang}(2018)}]{xiaobiao}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {X.}~\bibnamefont
+			{Huang}},\ }\href {\doibase 10.1103/PhysRevAccelBeams.21.104601} {\bibfield
+		{journal} {\bibinfo  {journal} {Phys. Rev. Accel. Beams}\ }\textbf {\bibinfo
+			{volume} {21}},\ \bibinfo {pages} {104601} (\bibinfo {year}
+		{2018})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Bazarov}\ and\ \citenamefont
+		{Sinclair}(2005)}]{bazarov05}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {I.~V.}\ \bibnamefont
+			{Bazarov}}\ and\ \bibinfo {author} {\bibfnamefont {C.~K.}\ \bibnamefont
+			{Sinclair}},\ }\href {\doibase 10.1103/PhysRevSTAB.8.034202} {\bibfield
+		{journal} {\bibinfo  {journal} {Phys. Rev. ST Accel. Beams}\ }\textbf
+		{\bibinfo {volume} {8}},\ \bibinfo {pages} {034202} (\bibinfo {year}
+		{2005})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Yang}\ \emph {et~al.}(2009)\citenamefont {Yang},
+		\citenamefont {Robin}, \citenamefont {Sannibale}, \citenamefont {Steier},\
+		and\ \citenamefont {Wan}}]{yrss:09}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+			{Yang}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Robin}},
+		\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Sannibale}}, \bibinfo
+		{author} {\bibfnamefont {C.}~\bibnamefont {Steier}}, \ and\ \bibinfo {author}
+		{\bibfnamefont {W.}~\bibnamefont {Wan}},\ }\href {\doibase
+		10.1016/j.nima.2009.08.027} {\bibfield  {journal} {\bibinfo  {journal} {Nucl.
+				Instrum. Methods Phys. Res. A}\ }\textbf {\bibinfo {volume} {609}},\ \bibinfo
+		{pages} {50} (\bibinfo {year} {2009})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Chao}\ \emph {et~al.}(2009)\citenamefont {Chao},
+		\citenamefont {Ames}, \citenamefont {Baartman}, \citenamefont {Bylinskii},
+		\citenamefont {Dechoudhury}, \citenamefont {Goh}, \citenamefont
+		{Koscielniak}, \citenamefont {E~Laxdal}, \citenamefont {Marchetto},
+		\citenamefont {Merminga}, \citenamefont {Naik}, \citenamefont {A~Verzilov},
+		\citenamefont {Yan},\ and\ \citenamefont {Zvyagintsev}}]{chao09}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
+			{Chao}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Ames}}, \bibinfo
+		{author} {\bibfnamefont {R.}~\bibnamefont {Baartman}}, \bibinfo {author}
+		{\bibfnamefont {I.}~\bibnamefont {Bylinskii}}, \bibinfo {author}
+		{\bibfnamefont {S.}~\bibnamefont {Dechoudhury}}, \bibinfo {author}
+		{\bibfnamefont {G.}~\bibnamefont {Goh}}, \bibinfo {author} {\bibfnamefont
+			{S.}~\bibnamefont {Koscielniak}}, \bibinfo {author} {\bibfnamefont
+			{R.}~\bibnamefont {E~Laxdal}}, \bibinfo {author} {\bibfnamefont
+			{M.}~\bibnamefont {Marchetto}}, \bibinfo {author} {\bibfnamefont
+			{L.}~\bibnamefont {Merminga}}, \bibinfo {author} {\bibfnamefont
+			{V.}~\bibnamefont {Naik}}, \bibinfo {author} {\bibfnamefont {V.}~\bibnamefont
+			{A~Verzilov}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Yan}}, \
+		and\ \bibinfo {author} {\bibfnamefont {V.}~\bibnamefont {Zvyagintsev}},\ }in\
+	\href@noop {} {\emph {\bibinfo {booktitle} {Proc. of ICAP}}}\ (\bibinfo
+	{year} {2009})\ p.\ \bibinfo {pages} {THPSC012}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Gong}\ and\ \citenamefont {Chao}(2012)}]{gong12}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
+			{Gong}}\ and\ \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Chao}},\
+	}in\ \href@noop {} {\emph {\bibinfo {booktitle} {Proc. of ICAP}}}\ (\bibinfo
+	{year} {2012})\ p.\ \bibinfo {pages} {TUABI1}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Hofler}\ \emph {et~al.}(2013)\citenamefont {Hofler},
+		\citenamefont {Terzic}, \citenamefont {Kramer}, \citenamefont {Zvezdin},
+		\citenamefont {Morozov}, \citenamefont {Roblin}, \citenamefont {Lin},\ and\
+		\citenamefont {Jarvis}}]{hofler13}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+			{Hofler}}, \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Terzic}},
+		\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Kramer}}, \bibinfo
+		{author} {\bibfnamefont {A.}~\bibnamefont {Zvezdin}}, \bibinfo {author}
+		{\bibfnamefont {V.}~\bibnamefont {Morozov}}, \bibinfo {author} {\bibfnamefont
+			{Y.}~\bibnamefont {Roblin}}, \bibinfo {author} {\bibfnamefont
+			{F.}~\bibnamefont {Lin}}, \ and\ \bibinfo {author} {\bibfnamefont
+			{C.}~\bibnamefont {Jarvis}},\ }\href {\doibase 10.1103/PhysRevSTAB.16.010101}
+	{\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. ST Accel. Beams}\
+		}\textbf {\bibinfo {volume} {16}},\ \bibinfo {pages} {010101} (\bibinfo
+		{year} {2013})}\BibitemShut {NoStop}%
+	%%CITATION = PRSTA,16,010101;%%
+	\bibitem [{\citenamefont {Terzic}\ \emph {et~al.}(2014)\citenamefont {Terzic},
+		\citenamefont {Hofler}, \citenamefont {Reeves}, \citenamefont {Khan},
+		\citenamefont {Krafft}, \citenamefont {Benesch}, \citenamefont {Freyberger},\
+		and\ \citenamefont {Ranjan}}]{jefferson}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
+			{Terzic}}, \bibinfo {author} {\bibfnamefont {A.~S.}\ \bibnamefont {Hofler}},
+		\bibinfo {author} {\bibfnamefont {C.~J.}\ \bibnamefont {Reeves}}, \bibinfo
+		{author} {\bibfnamefont {S.~A.}\ \bibnamefont {Khan}}, \bibinfo {author}
+		{\bibfnamefont {G.~A.}\ \bibnamefont {Krafft}}, \bibinfo {author}
+		{\bibfnamefont {J.}~\bibnamefont {Benesch}}, \bibinfo {author} {\bibfnamefont
+			{A.}~\bibnamefont {Freyberger}}, \ and\ \bibinfo {author} {\bibfnamefont
+			{D.}~\bibnamefont {Ranjan}},\ }\href {\doibase 10.1103/PhysRevSTAB.17.101003}
+	{\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. ST Accel. Beams}\
+		}\textbf {\bibinfo {volume} {17}},\ \bibinfo {pages} {101003} (\bibinfo
+		{year} {2014})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Gong}\ and\ \citenamefont {Chao}(2015)}]{gong15}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
+			{Gong}}\ and\ \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Chao}},\
+	}in\ \href@noop {} {\emph {\bibinfo {booktitle} {Proc. of ICAP}}}\ (\bibinfo
+	{year} {2015})\ p.\ \bibinfo {pages} {THCWC4}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Gong}(2015)}]{gongthesis15}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
+			{Gong}},\ }\emph {\bibinfo {title} {A Novel Optimization Platform and Its
+			Applications to the TRIUMF Energy Recovery Linac}},\ \href@noop {} {Ph.D.
+		thesis},\ \bibinfo  {school} {The University of Columbia} (\bibinfo {year}
+	{2015})\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Gulliford}\ \emph {et~al.}(2016)\citenamefont
+		{Gulliford}, \citenamefont {Bartnik},\ and\ \citenamefont {Bazarov}}]{gull1}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
+			{Gulliford}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Bartnik}},
+		\ and\ \bibinfo {author} {\bibfnamefont {I.}~\bibnamefont {Bazarov}},\ }\href
+	{\doibase 10.1103/PhysRevAccelBeams.19.093402} {\bibfield  {journal}
+		{\bibinfo  {journal} {Phys. Rev. Accel. Beams}\ }\textbf {\bibinfo {volume}
+			{19}},\ \bibinfo {pages} {093402} (\bibinfo {year} {2016})}\BibitemShut
+	{NoStop}%
+	\bibitem [{\citenamefont {Gulliford}\ \emph {et~al.}(2017)\citenamefont
+		{Gulliford}, \citenamefont {Bartnik}, \citenamefont {Bazarov},\ and\
+		\citenamefont {Maxson}}]{gull2}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
+			{Gulliford}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Bartnik}},
+		\bibinfo {author} {\bibfnamefont {I.}~\bibnamefont {Bazarov}}, \ and\
+		\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Maxson}},\ }\href
+	{\doibase 10.1103/PhysRevAccelBeams.20.033401} {\bibfield  {journal}
+		{\bibinfo  {journal} {Phys. Rev. Accel. Beams}\ }\textbf {\bibinfo {volume}
+			{20}},\ \bibinfo {pages} {033401} (\bibinfo {year} {2017})}\BibitemShut
+	{NoStop}%
+	\bibitem [{\citenamefont {Kranjčević}\ \emph {et~al.}(2019)\citenamefont
+		{Kranjčević}, \citenamefont {Adelmann}, \citenamefont {Arbenz},
+		\citenamefont {Citterio},\ and\ \citenamefont {Stingelin}}]{marija}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+			{Kranjčević}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+			{Adelmann}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Arbenz}},
+		\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Citterio}}, \ and\
+		\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Stingelin}},\ }\href
+	{\doibase https://doi.org/10.1016/j.nima.2018.12.066} {\bibfield  {journal}
+		{\bibinfo  {journal} {Nucl. Instrum. Methods Phys. Res. A}\ }\textbf
+		{\bibinfo {volume} {920}},\ \bibinfo {pages} {106 } (\bibinfo {year}
+		{2019})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Physics}(2018)}]{gpt}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+			{Physics}},\ }\href@noop {} {\enquote {\bibinfo {title} {{General Particle
+					Tracer (GPT)}},}\ } (\bibinfo {year} {1996-2018}),\ \Eprint
+	{http://arxiv.org/abs/\url{http://www.pulsar.nl/gpt}}
+	{\url{http://www.pulsar.nl/gpt}} \BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Borland}(2018)}]{elegant}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+			{Borland}},\ }\href@noop {} {\emph {\bibinfo {title} {Elegant: A flexible
+				SDDS-compliant code for accelerator simulation}}},\ \bibinfo {type} {Tech.
+		Rep.}\ \bibinfo {number} {LS-287}\ (\bibinfo  {institution} {Argonne National
+		Laboratory},\ \bibinfo {year} {2000-2018})\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Adelmann}\ \emph {et~al.}(2018)\citenamefont
+		{Adelmann}, \citenamefont {Baumgarten}, \citenamefont {Frey}, \citenamefont
+		{Gsell}, \citenamefont {Rizzoglio}, \citenamefont {Snuverink}, \citenamefont
+		{Metzger-Kraus}, \citenamefont {Ineichen}, \citenamefont {Russell},
+		\citenamefont {Wang}, \citenamefont {Sheehy}, \citenamefont {Rogers},\ and\
+		\citenamefont {Winklehner}}]{opal}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+			{Adelmann}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
+			{Baumgarten}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Frey}},
+		\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Gsell}}, \bibinfo
+		{author} {\bibfnamefont {V.}~\bibnamefont {Rizzoglio}}, \bibinfo {author}
+		{\bibfnamefont {J.}~\bibnamefont {Snuverink}}, \bibinfo {author}
+		{\bibfnamefont {C.}~\bibnamefont {Metzger-Kraus}}, \bibinfo {author}
+		{\bibfnamefont {Y.}~\bibnamefont {Ineichen}}, \bibinfo {author}
+		{\bibfnamefont {S.}~\bibnamefont {Russell}}, \bibinfo {author} {\bibfnamefont
+			{C.}~\bibnamefont {Wang}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+			{Sheehy}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Rogers}}, \
+		and\ \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Winklehner}},\
+	}\href@noop {} {\emph {\bibinfo {title} {The {OPAL} (Object Oriented Parallel
+				Accelerator Library) Framework}}},\ \bibinfo {type} {Tech. Rep.}\ \bibinfo
+	{number} {PSI-PR-08-02}\ (\bibinfo  {institution} {Paul Scherrer Institut},\
+	\bibinfo {year} {2008-2018})\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Deb}\ \emph {et~al.}(2002)\citenamefont {Deb},
+		\citenamefont {Pratap}, \citenamefont {Agarwal},\ and\ \citenamefont
+		{Meyarivan}}]{dpam:02}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
+			{Deb}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Pratap}},
+		\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Agarwal}}, \ and\
+		\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont {Meyarivan}},\ }\href
+	{\doibase 10.1109/4235.996017} {\bibfield  {journal} {\bibinfo  {journal}
+			{IEEE Trans. Evol. Comp.}\ }\textbf {\bibinfo {volume} {6}},\ \bibinfo
+		{pages} {182} (\bibinfo {year} {2002})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Bleuler}\ \emph {et~al.}(2003)\citenamefont
+		{Bleuler}, \citenamefont {Laumanns}, \citenamefont {Thiele},\ and\
+		\citenamefont {Zitzler}}]{pisa}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+			{Bleuler}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Laumanns}},
+		\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Thiele}}, \ and\ \bibinfo
+		{author} {\bibfnamefont {E.}~\bibnamefont {Zitzler}},\ }in\ \href@noop {}
+	{\emph {\bibinfo {booktitle} {{E}volutionary {M}ulti-{C}riterion
+				{O}ptimization}}},\ \bibinfo {editor} {edited by\ \bibinfo {editor}
+		{\bibfnamefont {C.~M.}\ \bibnamefont {Fonseca}}, \bibinfo {editor}
+		{\bibfnamefont {P.~J.}\ \bibnamefont {Fleming}}, \bibinfo {editor}
+		{\bibfnamefont {E.}~\bibnamefont {Zitzler}}, \bibinfo {editor} {\bibfnamefont
+			{L.}~\bibnamefont {Thiele}}, \ and\ \bibinfo {editor} {\bibfnamefont
+			{K.}~\bibnamefont {Deb}}}\ (\bibinfo  {publisher} {Springer},\ \bibinfo
+	{address} {Berlin, Heidelberg},\ \bibinfo {year} {2003})\ pp.\ \bibinfo
+	{pages} {494--508}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Deb}(2009)}]{deb:09}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
+			{Deb}},\ }\href@noop {} {\emph {\bibinfo {title} {{M}ulti-{O}bjective
+				{O}ptimization {U}sing {E}volutionary {A}lgorithms}}}\ (\bibinfo  {publisher}
+	{Wiley},\ \bibinfo {year} {2009})\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Kirkpatrick}\ \emph {et~al.}(1983)\citenamefont
+		{Kirkpatrick}, \citenamefont {Gelatt},\ and\ \citenamefont
+		{Vecchi}}]{kigv:83}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+			{Kirkpatrick}}, \bibinfo {author} {\bibfnamefont {C.~D.}\ \bibnamefont
+			{Gelatt}}, \ and\ \bibinfo {author} {\bibfnamefont {M.~P.}\ \bibnamefont
+			{Vecchi}},\ }\href {\doibase 10.1126/science.220.4598.671} {\bibfield
+		{journal} {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo {volume}
+			{220}},\ \bibinfo {pages} {671} (\bibinfo {year} {1983})}\BibitemShut
+	{NoStop}%
+	\bibitem [{\citenamefont {Kennedy}\ and\ \citenamefont
+		{Eberhart}(1995)}]{keeb:95}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+			{Kennedy}}\ and\ \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
+			{Eberhart}},\ }in\ \href {\doibase 10.1109/ICNN.1995.488968} {\emph {\bibinfo
+			{booktitle} {Proc. of ICNN}}},\ Vol.~\bibinfo {volume} {4}\ (\bibinfo {year}
+	{1995})\ pp.\ \bibinfo {pages} {1942--1948}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Dorigo}\ \emph {et~al.}(1996)\citenamefont {Dorigo},
+		\citenamefont {Maniezzo},\ and\ \citenamefont {Colorni}}]{domc:96}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+			{Dorigo}}, \bibinfo {author} {\bibfnamefont {V.}~\bibnamefont {Maniezzo}}, \
+		and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Colorni}},\
+	}\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {IEEE Trans. Syst.
+				Man. Cy. B}\ }\textbf {\bibinfo {volume} {26}},\ \bibinfo {pages} {29}
+		(\bibinfo {year} {1996})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {De~Castro}\ and\ \citenamefont
+		{Timmis}(2002)}]{cati:02}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+			{De~Castro}}\ and\ \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+			{Timmis}},\ }\href@noop {} {\emph {\bibinfo {title} {Artificial immune
+				systems: a new computational intelligence approach}}}\ (\bibinfo  {publisher}
+	{Springer},\ \bibinfo {year} {2002})\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Karaboga}(2005)}]{kara:05}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
+			{Karaboga}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+			{Techn. Rep. TR06, Erciyes Univ. Press, Erciyes}\ } (\bibinfo {year}
+		{2005})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Shah-Hosseini}(2009)}]{hoss:09}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
+			{Shah-Hosseini}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+			{Int. J. Bio-Inspir. Com.}\ }\textbf {\bibinfo {volume} {1}},\ \bibinfo
+		{pages} {71} (\bibinfo {year} {2009})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Durillo}\ \emph {et~al.}(2006)\citenamefont
+		{Durillo}, \citenamefont {Nebro}, \citenamefont {Luna}, \citenamefont
+		{Dorronsoro},\ and\ \citenamefont {Alba}}]{dnld:06}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+			{Durillo}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Nebro}},
+		\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Luna}}, \bibinfo {author}
+		{\bibfnamefont {B.}~\bibnamefont {Dorronsoro}}, \ and\ \bibinfo {author}
+		{\bibfnamefont {E.}~\bibnamefont {Alba}},\ }\href@noop {} {\emph {\bibinfo
+			{title} {jMetal: a java framework for developing multi-objective optimization
+				metaheuristics}}},\ \bibinfo {type} {Tech. Rep.}\ \bibinfo {number}
+	{ITI-2006-10}\ (\bibinfo  {institution} {University of M{\'a}laga, ETSI
+		Inform{\'a}tica, Campus de Teatinos},\ \bibinfo {year} {2006})\BibitemShut
+	{NoStop}%
+	\bibitem [{\citenamefont {Liefooghe}\ \emph {et~al.}(2007)\citenamefont
+		{Liefooghe}, \citenamefont {Basseur}, \citenamefont {Jourdan},\ and\
+		\citenamefont {Talbi}}]{lbjt:07}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+			{Liefooghe}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Basseur}},
+		\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Jourdan}}, \ and\
+		\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Talbi}},\ }in\ \href@noop
+	{} {\emph {\bibinfo {booktitle} {Evolutionary Multi-Criterion
+				Optimization}}}\ (\bibinfo {organization} {Springer},\ \bibinfo {year}
+	{2007})\ pp.\ \bibinfo {pages} {386--400}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Filipi\v{c}}\ and\ \citenamefont
+		{Depolli}(2009)}]{fide:09}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
+			{Filipi\v{c}}}\ and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+			{Depolli}},\ }in\ \href {\doibase 10.1007/978-1-84882-409-6\_7} {\emph
+		{\bibinfo {booktitle} {Parallel Computing}}},\ \bibinfo {editor} {edited by\
+		\bibinfo {editor} {\bibfnamefont {R.}~\bibnamefont {Trobec}}, \bibinfo
+		{editor} {\bibfnamefont {M.}~\bibnamefont {Vajter\v{s}ic}}, \ and\ \bibinfo
+		{editor} {\bibfnamefont {P.}~\bibnamefont {Zinterhof}}}\ (\bibinfo
+	{publisher} {Springer},\ \bibinfo {year} {2009})\ pp.\ \bibinfo {pages}
+	{217--240}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Le\'{o}n}\ \emph {et~al.}(2009)\citenamefont
+		{Le\'{o}n}, \citenamefont {Miranda},\ and\ \citenamefont {Segura}}]{lems:09}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
+			{Le\'{o}n}}, \bibinfo {author} {\bibfnamefont {G.}~\bibnamefont {Miranda}}, \
+		and\ \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Segura}},\ }\href
+	{\doibase 10.1142/S0218213009000275} {\bibfield  {journal} {\bibinfo
+			{journal} {Int. J. Artif. Intell. Tools}\ }\textbf {\bibinfo {volume} {18}},\
+		\bibinfo {pages} {569} (\bibinfo {year} {2009})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Huband}\ \emph {et~al.}(2005)\citenamefont {Huband},
+		\citenamefont {Barone}, \citenamefont {While},\ and\ \citenamefont
+		{Hingston}}]{hbwh:05}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+			{Huband}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Barone}},
+		\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {While}}, \ and\ \bibinfo
+		{author} {\bibfnamefont {P.}~\bibnamefont {Hingston}},\ }in\ \href {\doibase
+		10.1007/978-3-540-31880-4_20} {\emph {\bibinfo {booktitle} {Proc. of Intl.
+				Conf. Evol. Multi-Criterion Optimization}}}\ (\bibinfo  {publisher}
+	{Springer-Verlag},\ \bibinfo {address} {Berlin, Heidelberg},\ \bibinfo {year}
+	{2005})\ pp.\ \bibinfo {pages} {280--295}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {While}\ \emph {et~al.}(2012)\citenamefont {While},
+		\citenamefont {Bradstreet},\ and\ \citenamefont {Barone}}]{whbb:12}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+			{While}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Bradstreet}}, \
+		and\ \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Barone}},\
+	}\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {IEEE Trans. Evol.
+				Comput.}\ }\textbf {\bibinfo {volume} {16}},\ \bibinfo {pages} {86} (\bibinfo
+		{year} {2012})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Gai}\ \emph {et~al.}(2012)\citenamefont {Gai},
+		\citenamefont {Power},\ and\ \citenamefont {Jing}}]{gai_power_jing_2012}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.}~\bibnamefont
+			{Gai}}, \bibinfo {author} {\bibfnamefont {J.~G.}\ \bibnamefont {Power}}, \
+		and\ \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Jing}},\ }\href
+	{\doibase 10.1017/S0022377812000037} {\bibfield  {journal} {\bibinfo
+			{journal} {Journal of Plasma Physics}\ }\textbf {\bibinfo {volume} {78}},\
+		\bibinfo {pages} {339–345} (\bibinfo {year} {2012})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Jing}\ \emph {et~al.}(2018)\citenamefont {Jing} \emph
+		{et~al.}}]{JING201872}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
+			{Jing}} \emph {et~al.},\ }\href {\doibase
+		https://doi.org/10.1016/j.nima.2018.05.007} {\bibfield  {journal} {\bibinfo
+			{journal} {Nucl. Instrum. Methods Phys. Res. A}\ }\textbf {\bibinfo {volume}
+			{898}},\ \bibinfo {pages} {72 } (\bibinfo {year} {2018})}\BibitemShut
+	{NoStop}%
+	\bibitem [{\citenamefont {Gao}\ \emph {et~al.}(2008)\citenamefont {Gao},
+		\citenamefont {Conde}, \citenamefont {Gai}, \citenamefont {Jing},
+		\citenamefont {Konecny}, \citenamefont {Liu}, \citenamefont {Power},
+		\citenamefont {Wong},\ and\ \citenamefont {Yusof}}]{PETSeq}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
+			{Gao}}, \bibinfo {author} {\bibfnamefont {M.~E.}\ \bibnamefont {Conde}},
+		\bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Gai}}, \bibinfo {author}
+		{\bibfnamefont {C.}~\bibnamefont {Jing}}, \bibinfo {author} {\bibfnamefont
+			{R.}~\bibnamefont {Konecny}}, \bibinfo {author} {\bibfnamefont
+			{W.}~\bibnamefont {Liu}}, \bibinfo {author} {\bibfnamefont {J.~G.}\
+			\bibnamefont {Power}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+			{Wong}}, \ and\ \bibinfo {author} {\bibfnamefont {Z.}~\bibnamefont {Yusof}},\
+	}\href {\doibase 10.1103/PhysRevSTAB.11.041301} {\bibfield  {journal}
+		{\bibinfo  {journal} {Phys. Rev. ST Accel. Beams}\ }\textbf {\bibinfo
+			{volume} {11}},\ \bibinfo {pages} {041301} (\bibinfo {year}
+		{2008})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Neveu}(2018)}]{neveuthesis}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
+			{Neveu}},\ }\emph {\bibinfo {title} {Beam Line Design for Fully Staged Two
+			Beam Acceleration at the Argonne Wakefield Accelerator Facility}},\
+	\href@noop {} {Ph.D. thesis},\ \bibinfo  {school} {Illinois Institute of
+		Technology} (\bibinfo {year} {2018})\BibitemShut {NoStop}%
+\end{thebibliography}%
 

### 2019-03-25 paper/submission/supplemental_material.tex
adding bbl to main tex files

@@
 
-\bibliography{paper}
+%\bibliography{paper}
+%merlin.mbs apsrev4-1.bst 2010-07-25 4.21a (PWD, AO, DPC) hacked
+%Control: key (0)
+%Control: author (8) initials jnrlst
+%Control: editor formatted (1) identically to author
+%Control: production of article title (-1) disabled
+%Control: page (0) single
+%Control: year (1) truncated
+%Control: production of eprint (0) enabled
+\providecommand{\SortNoop}[1]{}
+\begin{thebibliography}{9}%
+	\makeatletter
+	\providecommand \@ifxundefined [1]{%
+		\@ifx{#1\undefined}
+	}%
+	\providecommand \@ifnum [1]{%
+		\ifnum #1\expandafter \@firstoftwo
+		\else \expandafter \@secondoftwo
+		\fi
+	}%
+	\providecommand \@ifx [1]{%
+		\ifx #1\expandafter \@firstoftwo
+		\else \expandafter \@secondoftwo
+		\fi
+	}%
+	\providecommand \natexlab [1]{#1}%
+	\providecommand \enquote  [1]{``#1''}%
+	\providecommand \bibnamefont  [1]{#1}%
+	\providecommand \bibfnamefont [1]{#1}%
+	\providecommand \citenamefont [1]{#1}%
+	\providecommand \href@noop [0]{\@secondoftwo}%
+	\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
+	\providecommand \@href[1]{\@@startlink{#1}\@@href}%
+	\providecommand \@@href[1]{\endgroup#1\@@endlink}%
+	\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
+		`\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
+	\providecommand \@@startlink[1]{}%
+	\providecommand \@@endlink[0]{}%
+	\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
+	\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
+	\providecommand \urlprefix  [0]{URL }%
+	\providecommand \Eprint [0]{\href }%
+	\providecommand \doibase [0]{http://dx.doi.org/}%
+	\providecommand \selectlanguage [0]{\@gobble}%
+	\providecommand \bibinfo  [0]{\@secondoftwo}%
+	\providecommand \bibfield  [0]{\@secondoftwo}%
+	\providecommand \translation [1]{[#1]}%
+	\providecommand \BibitemOpen [0]{}%
+	\providecommand \bibitemStop [0]{}%
+	\providecommand \bibitemNoStop [0]{.\EOS\space}%
+	\providecommand \EOS [0]{\spacefactor3000\relax}%
+	\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
+	\let\auto@bib@innerbib\@empty
+	%</preamble>
+	\bibitem [{\citenamefont {Arbenz}\ and\ \citenamefont
+		{Chinellato}(2008)}]{ARBENZ2008381}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+			{Arbenz}}\ and\ \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont
+			{Chinellato}},\ }\href {\doibase 10.1016/j.apnum.2007.01.019} {\bibfield
+		{journal} {\bibinfo  {journal} {Appl. Numer. Math.}\ }\textbf {\bibinfo
+			{volume} {58}},\ \bibinfo {pages} {381} (\bibinfo {year} {2008})}\BibitemShut
+	{NoStop}%
+	\bibitem [{boo(2015)}]{boost}%
+	\BibitemOpen
+	\href@noop {} {\enquote {\bibinfo {title} {{The Boost Spirit Home Page}},}\ }
+	(\bibinfo {year} {2015}),\ \bibinfo {note}
+	{\url{http://boost-spirit.com/}}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {{ E. Friedman and I. Maman }}(2003)}]{boost2}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibnamefont {{ E. Friedman and I.
+					Maman }}},\ }\href@noop {} {\enquote {\bibinfo {title} {{Chapter 45.
+					Boost.Variant}},}\ } (\bibinfo {year} {2003}),\ \bibinfo {note}
+	{\url{www.boost.org/doc/html/variant.html}}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Gregor}(2004)}]{boost3}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
+			{Gregor}},\ }\href@noop {} {\enquote {\bibinfo {title} {{Chapter 15.
+					Boost.Function}},}\ } (\bibinfo {year} {2004}),\ \bibinfo {note}
+	{\url{www.boost.org/libs/function/}}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Balaji}\ \emph {et~al.}(2009)\citenamefont {Balaji},
+		\citenamefont {Chan}, \citenamefont {Thakur}, \citenamefont {Gropp},\ and\
+		\citenamefont {Lusk}}]{bctg:09}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+			{Balaji}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Chan}},
+		\bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Thakur}}, \bibinfo
+		{author} {\bibfnamefont {W.}~\bibnamefont {Gropp}}, \ and\ \bibinfo {author}
+		{\bibfnamefont {E.~L.}\ \bibnamefont {Lusk}},\ }\href {\doibase
+		http://dx.doi.org/10.1007/s00450-009-0095-3} {\bibfield  {journal} {\bibinfo
+			{journal} {Computer Science - Research and Development}\ }\textbf {\bibinfo
+			{volume} {24}},\ \bibinfo {pages} {11} (\bibinfo {year} {2009})}\BibitemShut
+	{NoStop}%
+	\bibitem [{\citenamefont {Boyd}\ \emph {et~al.}(2006)\citenamefont {Boyd},
+		\citenamefont {Ghosh}, \citenamefont {Prabhakar},\ and\ \citenamefont
+		{Shah}}]{bgps:06}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+			{Boyd}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Ghosh}},
+		\bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Prabhakar}}, \ and\
+		\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Shah}},\ }\href@noop {}
+	{\bibfield  {journal} {\bibinfo  {journal} {IEEE Trans. Inform. Theory}\
+		}\textbf {\bibinfo {volume} {52}},\ \bibinfo {pages} {2508} (\bibinfo {year}
+		{2006})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Aysal}\ \emph {et~al.}(2009)\citenamefont {Aysal},
+		\citenamefont {Yildiz}, \citenamefont {Sarwate},\ and\ \citenamefont
+		{Scaglione}}]{ayss:09}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+			{Aysal}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Yildiz}},
+		\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Sarwate}}, \ and\
+		\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Scaglione}},\ }\href@noop
+	{} {\bibfield  {journal} {\bibinfo  {journal} {IEEE Trans. Signal Process.}\
+		}\textbf {\bibinfo {volume} {57}},\ \bibinfo {pages} {2748} (\bibinfo {year}
+		{2009})}\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Adelmann}\ \emph {et~al.}(2018)\citenamefont
+		{Adelmann}, \citenamefont {Baumgarten}, \citenamefont {Frey}, \citenamefont
+		{Gsell}, \citenamefont {Rizzoglio}, \citenamefont {Snuverink}, \citenamefont
+		{Metzger-Kraus}, \citenamefont {Ineichen}, \citenamefont {Russell},
+		\citenamefont {Wang}, \citenamefont {Sheehy}, \citenamefont {Rogers},\ and\
+		\citenamefont {Winklehner}}]{opal}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+			{Adelmann}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont
+			{Baumgarten}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Frey}},
+		\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Gsell}}, \bibinfo
+		{author} {\bibfnamefont {V.}~\bibnamefont {Rizzoglio}}, \bibinfo {author}
+		{\bibfnamefont {J.}~\bibnamefont {Snuverink}}, \bibinfo {author}
+		{\bibfnamefont {C.}~\bibnamefont {Metzger-Kraus}}, \bibinfo {author}
+		{\bibfnamefont {Y.}~\bibnamefont {Ineichen}}, \bibinfo {author}
+		{\bibfnamefont {S.}~\bibnamefont {Russell}}, \bibinfo {author} {\bibfnamefont
+			{C.}~\bibnamefont {Wang}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+			{Sheehy}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Rogers}}, \
+		and\ \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Winklehner}},\
+	}\href@noop {} {\emph {\bibinfo {title} {The {OPAL} (Object Oriented Parallel
+				Accelerator Library) Framework}}},\ \bibinfo {type} {Tech. Rep.}\ \bibinfo
+	{number} {PSI-PR-08-02}\ (\bibinfo  {institution} {Paul Scherrer Institut},\
+	\bibinfo {year} {2008-2018})\BibitemShut {NoStop}%
+	\bibitem [{\citenamefont {Huband}\ \emph {et~al.}(2005)\citenamefont {Huband},
+		\citenamefont {Barone}, \citenamefont {While},\ and\ \citenamefont
+		{Hingston}}]{hbwh:05}%
+	\BibitemOpen
+	\bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+			{Huband}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Barone}},
+		\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {While}}, \ and\ \bibinfo
+		{author} {\bibfnamefont {P.}~\bibnamefont {Hingston}},\ }in\ \href {\doibase
+		10.1007/978-3-540-31880-4_20} {\emph {\bibinfo {booktitle} {Proc. of Intl.
+				Conf. Evol. Multi-Criterion Optimization}}}\ (\bibinfo  {publisher}
+	{Springer-Verlag},\ \bibinfo {address} {Berlin, Heidelberg},\ \bibinfo {year}
+	{2005})\ pp.\ \bibinfo {pages} {280--295}\BibitemShut {NoStop}%
+\end{thebibliography}%
 
